### 2019-07-10 OpenSource-3D-CSEM.tex
Initial

% \documentclass[manuscript]{geophysics}
\documentclass[paper,twocolumn,twoside]{geophysics}
% \documentclass[paper]{geophysics}
% \documentclass[paper, revised]{geophysics}
% \documentclass[manuscript,revised]{geophysics}

% Additional packages to geophysics.cls
\usepackage[USenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{upquote}
\usepackage[strings]{underscore}
\usepackage{natbib}
\PassOptionsToPackage{hyphens}{url}
\usepackage[pdftex, final, breaklinks=True]{hyperref}
\hypersetup{allcolors=blue, allbordercolors={0 0 .5}, colorlinks=true}

% Figures
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\renewcommand{\figdir}{./figures}

% Own commands
\newcommand{\mr}[1]{\mathrm{#1}}

\begin{document}

\title{Status of the open-source landscape for 3D CSEM modeling}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{GEO-2018-0069.R2}

\address{
\footnotemark[1]TU Delft,
Building 23,
Stevinweg 1 / PO-box 5048,
2628 CN Delft,
E-mail: \href{mailto:D.Werthmuller@tudelft.nl}{D.Werthmuller@tudelft.nl};
}

\author{%
Dieter Werthmüller\footnotemark[1],
Lindsey Heagy,
Raphael Rochlitz, and
Octavio Castillo-Reyes
}

\footer{}
\lefthead{Werthmüller et al.}
\righthead{Digital filter designing tool}

\maketitle

\begin{abstract} % 1-2 sentence(s) each
%
% (1) PRINCIPAL OBJECTIVES AND SCOPE OF THE WORK
%
% (2) METHODOLOGY
%
% (3) RESULTS
%
% (4) CONCLUSIONS
%
To-Do/-Discuss:
\begin{itemize}
  \item Title?
  \item Order of authors? These authors or others?
  \item Other codes to include? Currently considered:\\
    SimPEG, custEM, PETGEM, and emg3d.
  \item Are these references OK?
    \begin{itemize}
      \item \cite{CAG.15.Cockett} (SimPEG)
      \item \cite{GEO.18.Rochlitz} (custEM)
      \item \cite{CAG.18.CastilloReyes} (PETGEM)
      \item \cite{JOSS.19.Werthmuller} (emg3d).
    \end{itemize}
  \item Exact structure of the paper?
  \item Exact models to calculate/show/compare?
\end{itemize}
\end{abstract}

\section{Introduction}

\dots

\section{Codes}

Each code should outline:
\begin{itemize}
  \item Equation system it solves;
  \item the used discretization possibilities;
  \item domains (frequency, time);
  \item details (anisotropy; el. perm. and mag. perm.);
  \item other things (inversion; other methods);
  \item speed and memory estimation;
  \item plans for next features.
\end{itemize}

\subsection{emg3d}

\subsection{SimPEG}

\subsection{custEM}

\subsection{PETGEM}

\section{Numerical Results}

\subsection{Layered model}

A simple layered model, comparing with \texttt{empymod}
\citep{GEO.17.Werthmuller}.

\subsection{3D model}

A complicated, big, 3D model with bathymetry (topography).

\section{Conclusions}

The landscape in 3D CSEM modelling greatly changed in the last five years or
so. While before there were only closed-source codes owned by companies or
consortia (e.g., CEMI) there was recently a wave of openly released codes.
\dots

\section{Acknowledgment}
\dots

% REFERENCES
\bibliographystyle{references}
\bibliography{references}

% Include bbl instead above command before submission.
% \begin{thebibliography}{}
% \itemsep0pt
% \bibitem ...
% \end{thebibliography}

\end{document}

### 2019-07-11 OpenSource-3D-CSEM.tex
Update reference PETGEM
Start emg3d-specific part

@@
       \item \cite{GEO.18.Rochlitz} (custEM)
-      \item \cite{CAG.18.CastilloReyes} (PETGEM)
+      \item \cite{GJI.19.CastilloReyes} (PETGEM)
       \item \cite{JOSS.19.Werthmuller} (emg3d).
@@
 \begin{itemize}
+  \item General presentation/introduction;
   \item Equation system it solves;
@@
 \subsection{emg3d}
+
+\emph{General presentation/introduction}\\
+
+\emph{Equation system it solves}\\
+
+\emph{the used discretization possibilities}\\
+The code requires regular, but not necessary equidistant, grids.
+
+\emph{domains (frequency, time)}\\
+
+\emph{details (anisotropy; el. perm. and mag. perm.)}\\
+It currently includes tri-axial electric anisotropy and isotropic relative
+magnetic permeability; the relative electric permittivity is fixed at 1.
+
+\emph{other things (inversion; other methods)}\\
+
+\emph{speed and memory estimation}\\
+The advantage of multigrid methods is that they have optimal scaling for both
+runtime and memory usage. If the number of cells is doubled it will take twice
+as long and twice as much memory to calculate. Expand on that.
+
+\emph{plans for next features}\\
+According to the current roadmap the next step in the development of emg3d will
+see routines for fast time-domain calculations with a frequency-domain code by
+minimizing the required frequencies for the Fourier transform. Also planned are
+the extension to general anisotropy, inversion routines, and some improved
+routines for the inclusion of topography. Some of these might be sought to
+achieve by a compatibility layer to SimPEG.
 
@@
 \section{Acknowledgment}
+
+The development of emg3d was funded through the European Commission: MarTERA -
+Maritime and Marine Technologies for a New ERA (728053).
+
 \dots

### 2020-04-01 model-marlim/loadmarlim.py
Adjustments emg3d format changes (#20)

@@ -197,19 +197,18 @@ def create_survey(store_data=False, noise=False):
     # Initiate data with zeros
     dataset = {}
     for i, data in enumerate([data_il, data_bs]):
-        lineid = ['data_il', 'data_bs'][i]+'_'
-        for re_im in ['re', 'im']:
-            dataset[lineid+re_im] = xr.DataArray(
-                data=np.zeros((noff, data.freqs.size, 6), dtype=float),
-                dims=['src_x', 'freqs', 'components'],
-                coords={
-                    'src_x': xco,
-                    'freqs': data.freqs,
-                    'components': data_il.emf.emf_fieldtype.split()},
-            )
-            dataset[lineid+re_im].attrs['src_y'] = [src_il, src_bs][i][1]
-            dataset[lineid+re_im].attrs['src_z'] = [src_il, src_bs][i][2]
-            dataset[lineid+re_im].attrs['lineid'] = data.attrs['lineid']
+        lineid = ['data_il', 'data_bs'][i]
+        dataset[lineid] = xr.DataArray(
+            data=np.zeros((noff*2, data.freqs.size, 6), dtype=float),
+            dims=['src_x', 'freqs', 'components'],
+            coords={
+                'src_x': np.vstack([xco, xco]).ravel('F'),
+                'freqs': data.freqs,
+                'components': data_il.emf.emf_fieldtype.split()},
+        )
+        dataset[lineid].attrs['src_y'] = [src_il, src_bs][i][1]
+        dataset[lineid].attrs['src_z'] = [src_il, src_bs][i][2]
+        dataset[lineid].attrs['lineid'] = data.attrs['lineid']
 
     # Create a Dataset from the DataArray
     ds = xr.Dataset(dataset)
@@ -256,11 +255,11 @@ def create_survey(store_data=False, noise=False):
         tmp_bs = tmp_bs[off_bs, :, :][int_bs, :, :]
 
         # Store data
-        ds.data_il_re.data = tmp_il.real
-        ds.data_il_im.data = tmp_il.imag
+        ds.data_il.data[::2, :, :] = tmp_il.real
+        ds.data_il.data[1::2, :, :] = tmp_il.imag
 
-        ds.data_bs_re.data = tmp_bs.real
-        ds.data_bs_im.data = tmp_bs.imag
+        ds.data_bs.data[::2, :, :] = tmp_bs.real
+        ds.data_bs.data[1::2, :, :] = tmp_bs.imag
 
         # Delete our meta-data
         del ds.attrs['runtime']

### 2020-04-01 model-block/custEM/export_netcdf.py
Quasi final updates form custEM side, if everything is sorted correctly, I would call this final.
Final test with latest conda package still needs to be done before submission ...

@@ -1,0 +1,74 @@
+# -*- coding: utf-8 -*-
+"""
+@author: Rochlitz.R
+"""
+
+# ########################################################################### #
+# # # # #               layered earth and blocky model                # # # # #
+# ########################################################################### #
+# # # # #                    visualization script                     # # # # #
+# ########################################################################### #
+
+# Note, plots will be saved in the *plots* directory
+
+from custEM.post import PlotFD
+import custEM as ce
+import xarray as xr
+from datetime import datetime
+import numpy as np
+
+# import base dataset and specify custEM observation lines
+
+ds = xr.load_dataset('../block_model_and_survey.nc', engine='h5netcdf')
+lines = ['l1m_line_x', 'l2m_line_x', 'l3m_line_x']
+
+# export everything to netcdf
+for p in ['1', '2']:
+    for model in ['layered', 'block']:
+
+        # load interpolated modeling results on observation line
+        mod = 'p' + str(p)
+        if model == 'layered':
+            mesh = 'layered_earth_p' + p
+        else:
+            mesh = 'block_model_p' + p
+
+        P = PlotFD(mod=mod, mesh=mesh, approach='E_t', r_dir='./results')
+        for i, line in enumerate(lines):            
+            P.import_line_data(line, key='t' + str(i+1), EH='E')
+
+        # save the three lines
+        ds.line_1.data = np.vstack(
+                [P.line_data['t1_E_t'][:, 0].real, 
+                 P.line_data['t1_E_t'][:, 0].imag]).ravel('F') 
+        ds.line_2.data = np.vstack(
+                [P.line_data['t2_E_t'][:, 0].real, 
+                 P.line_data['t2_E_t'][:, 0].imag]).ravel('F') 
+        ds.line_3.data = np.vstack(
+                [P.line_data['t3_E_t'][:, 0].real, 
+                 P.line_data['t3_E_t'][:, 0].imag]).ravel('F') 
+
+        # Add info
+        ds.attrs['runtime'] = P.solution_time
+        ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
+        ds.attrs['max_ram'] = P.max_mem
+        ds.attrs['n_cells'] = P.cells
+        ds.attrs['n_nodes'] = P.nodes
+        ds.attrs['n_dof'] = P.dof
+        ds.attrs['extent'] = ("x = -100000 - 100000; " 
[…]

### 2020-04-01 model-block/custEM/mesh_block.py

@@ -4,7 +4,7 @@
 """
 
 # ########################################################################### #
-# # # # #                         blocky model                        # # # # #
+# # # # #                          block model                        # # # # #
 # ########################################################################### #
 # # # # #                    mesh generation script                   # # # # #
 # ########################################################################### #
@@ -72,15 +72,16 @@ for i in range(len(x1)):
 # build halfspace mesh and extend 2D surface mesh to 3D world
 M.build_layered_earth_mesh(4, [-600., -850., -3150.],
                            insert_struct=rx)
-# add second and third block
+# add second block
 for ix in range(len(x2)):
     M.add_brick(start=[x2[ix][0], y2[0], z2[0]],
                 stop=[x2[ix][1], y2[1], z2[1]],
                 cell_size=block_cell_size,
                 marker=6)
-
-for ix in range(len(x2)):
-    for iz in range(len(z2)):
+    
+# add third block
+for ix in range(len(x3)):
+    for iz in range(len(z3)):
         M.add_brick(start=[x3[ix][0], y3[0], z3[iz][0]],
                     stop=[x3[ix][1], y3[1], z3[iz][1]],
                     cell_size=block_cell_size,
@@ -139,15 +140,16 @@ for i in range(len(x1)):
 M.build_layered_earth_mesh(4, [-600., -850., -3150.],
                            insert_struct=rx)
 
-# add second and third block
+# add second block
 for ix in range(len(x2)):
     M.add_brick(start=[x2[ix][0], y2[0], z2[0]],
                 stop=[x2[ix][1], y2[1], z2[1]],
                 cell_size=block_cell_size,
                 marker=6)
 
-for ix in range(len(x2)):
-    for iz in range(len(z2)):
+# add third block
+for ix in range(len(x3)):
+    for iz in range(len(z3)):
         M.add_brick(start=[x3[ix][0], y3[0], z3[iz][0]],
                     stop=[x3[ix][1], y3[1], z3[iz][1]],
                     cell_size=block_cell_size,
@@ -164,133 +166,3 @@ M.there_is_always_a_bigger_world(10., 10., 10.)
 
 # call TetGen
 M.call_tetgen(tet_param='-pq1.6aA', export_vtk=True)
-
-
[…]

### 2020-04-01 model-marlim/custEM/modify_marlim_input_data.py

@@ -1,0 +1,210 @@
+# -*- coding: utf-8 -*-
+"""
+This script can be used to modify the input data provided by
+Correa and Menezes (2018):
+    "Marlim R3D: A realistic model for controlled-source electromagnetic
+    simulations — Phase 2: The controlled-source electromagnetic data set"
+
+The required input data can be downloaded from:
+
+    https://zenodo.org/record/400233
+    
+For the custEM simulations, you need the following files placed in the 
+directory 'model-marlim/DATA'  # (or ../DATA):
+
+    Sea_Bottom-mr3d.xyz
+    Miocene-mr3d.xyz
+    Oligocene-mr3d.xyz
+    Blue_mark-mr3d.xyz
+    Top_of_Salt-mr3d.xyz
+    Base_of_salt-mr3d.xyz
+    
+    Horizontal_resistivity.sgy
+    Vertical_Resistivity.sgy
+    EW_nonoise.zip  # extract zip file!
+
+For any questions or issues, contact
+
+    raphael.rochlitz@leibniz-liag.de
+
+"""
+
+# install missing packages via pip or conda !
+
+import segyio
+import discretize
+import numpy as np
+import xarray as xr
+
+import os
+
+if os.path.isfile('../marlim_survey.nc'):
+    pass
+else:
+    import sys
+    sys.path.append(os.path.dirname(os.path.dirname(os.path.abspath(__file__))))
+    import loadmarlim
+    os.chdir('../')
+    loadmarlim.create_survey()
+    os.chdir('./custEM')
+
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # 
+# # # # #              First part - Rx & Tx coordinates               # # # # # 
+# # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # # 
+
+# %% load original survey information
+
+data = xr.load_dataset('../marlim_survey.nc', engine='h5netcdf')
+
+# defined shifting from real coordinates to local coordinates
+easting_shift = -390275.0
+northing_shift = -7518065.
+
+rx = np.array([data.rec_x, data.rec_y, data.rec_z])
+rx[0] += easting_shift
+rx[1] += northing_shift
+
+tx_il = np.zeros((len(data.src_x[::2]), 3))
+tx_bs = np.zeros((len(data.src_x[::2]), 3))
+
[…]

### 2020-04-01 model-marlim/custEM/run_marlim.py

@@ -1,202 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-@author:  Rochlitz.R
-"""
-
-# ########################################################################### #
-# # # # #                          example 3                          # # # # #
-# ########################################################################### #
-# # # # #                      computation script                     # # # # #
-# ########################################################################### #
-
-
-import segyio
-#import discretize    # for the meshing
-#import matplotlib.pyplot as plt
-from scipy.interpolate import RegularGridInterpolator as rgi
-from custEM.misc import write_h5
-from custEM.misc import read_h5
-from custEM.meshgen import meshgen_utils as mu
-
-from custEM.core import MOD
-from custEM.misc import mpi_print as mpp
-import numpy as np
-import dolfin as df
-
-#res_h = segyio.tools.cube('./data/Horizontal_resistivity.sgy')[:, :, :]
-#res_v = segyio.tools.cube('./data/Vertical_Resistivity.sgy')[:, :, :]
-
-y = np.loadtxt('./data/resvec_x.txt') - 388993.
-x = np.loadtxt('./data/resvec_y.txt') - 7518065.
-z = np.loadtxt('./data/resvec_z.txt')
-
-res_h = np.transpose(np.load('./data/res_h.npy')[::-1, :, ::-1], (1, 0, 2))
-res_v = np.transpose(np.load('./data/res_v.npy')[::-1, :, ::-1], (1, 0, 2))
-
-#mpp(len(x))
-#mpp(len(y))
-#mpp(len(z))
-
-#nx, ny, nz = res_h.shape
-#dx, dy, dz = 75, 25, 5
-#
-##x0 = 1e100
-##y0 = 1e100
-##with segyio.open('./data/Horizontal_resistivity.sgy') as f:
-##    for i in range(nx*ny):
-##        if f.header[i][segyio.TraceField.CDP_X] < x0:
-##            x0 = f.header[i][segyio.TraceField.CDP_X]
-##        if f.header[i][segyio.TraceField.CDP_Y] < y0:
-##            y0 = f.header[i][segyio.TraceField.CDP_Y]
-##x0, y0 = x0/10, y0/10
-#
-#x0, y0 = np.loadtxt('./data/x0.txt')
-#
[…]

### 2020-04-02 model-block/custEM/export_netcdf.py
tmp commit

@@ -47,11 +47,13 @@ for p in ['1', '2']:
         ds.line_3.data = np.vstack(
                 [P.line_data['t3_E_t'][:, 0].real, 
                  P.line_data['t3_E_t'][:, 0].imag]).ravel('F') 
-
+    
+        mem_in_gib = 1e6 * P.max_mem / 1024**2
+    
         # Add info
-        ds.attrs['runtime'] = P.solution_time
+        ds.attrs['runtime'] = str(int(P.solution_time)) + ' s'
         ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
-        ds.attrs['max_ram'] = P.max_mem
+        ds.attrs['max_ram'] = '{:5.1f}'.format(mem_in_gib) + ' GiB'
         ds.attrs['n_cells'] = P.cells
         ds.attrs['n_nodes'] = P.nodes
         ds.attrs['n_dof'] = P.dof

### 2020-04-02 model-marlim/custEM/export_netcdf.py

@@ -42,14 +42,14 @@ for i, freq in enumerate(frequencies):
 
     # Save inline and broadside data for each frequency
     ds.data_il.data[::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'][0, :].real  # Inline RE
+            'il' + str(i) + '_E_t'].real  # Inline RE
     ds.data_il.data[1::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'][0, :].imag  # Inline IM
+            'il' + str(i) + '_E_t'].imag  # Inline IM
 
     ds.data_bs.data[::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'][0, :].real  # Inline RE
+            'bs' + str(i) + '_E_t'].real  # Inline RE
     ds.data_bs.data[1::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'][0, :].imag  # Inline IM
+            'bs' + str(i) + '_E_t'].imag  # Inline IM
 
 # Add info
 ds.attrs['runtime'] = solution_time

### 2020-04-02 model-marlim/custEM/run_marlim_reciprocal.py

@@ -176,7 +176,7 @@ for fi, freq in enumerate(frequencies):       # all approaches
 
     # conduct the real FE stuff
     M.FE.build_var_form(check_sigma_conformity=False)
-    M.solve_main_problem(convert_to_H=False)
+    M.solve_main_problem()  # convert_to_H=False
 
     # import existing FE results, if exported before
     # M = MOD(mod, mesh, 'E_t', p=p, overwrite=False,

### 2020-04-02 model-marlim/custEM/export_netcdf.py
next try, custEM marlim results with H and hopefully correct sorting

@@ -15,7 +15,6 @@ from custEM.post import PlotFD
 import custEM as ce
 import xarray as xr
 from datetime import datetime
-import numpy as np
 
 # import base dataset and specify custEM observation lines
 ds = xr.load_dataset('../marlim_survey.nc', engine='h5netcdf')
@@ -37,8 +36,8 @@ for i, freq in enumerate(frequencies):
     P = PlotFD(mod=mod, mesh=mesh, approach='E_t', r_dir='./results')
     solution_time += P.solution_time 
     
-    P.import_line_data(line_il, key='il' + str(i), EH='E')
-    P.import_line_data(line_bs, key='bs' + str(i), EH='E')
+    P.import_line_data(line_il, key='il' + str(i))
+    P.import_line_data(line_bs, key='bs' + str(i))
 
     # Save inline and broadside data for each frequency
     ds.data_il.data[::2, i, :3] = P.line_data[
@@ -51,10 +50,20 @@ for i, freq in enumerate(frequencies):
     ds.data_bs.data[1::2, i, :3] = P.line_data[
             'bs' + str(i) + '_E_t'].imag  # Inline IM
 
+    ds.data_il.data[::2, i, 3:] = P.line_data[
+            'il' + str(i) + '_H_t'].real  # Inline RE
+    ds.data_il.data[1::2, i, 3:] = P.line_data[
+            'il' + str(i) + '_H_t'].imag  # Inline IM
+
+    ds.data_bs.data[::2, i, 3:] = P.line_data[
+            'bs' + str(i) + '_H_t'].real  # Inline RE
+    ds.data_bs.data[1::2, i, 3:] = P.line_data[
+            'bs' + str(i) + '_H_t'].imag  # Inline IM
+
 # Add info
-ds.attrs['runtime'] = solution_time
+ds.attrs['runtime'] = str(int(solution_time)) + ' s'
 ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
-ds.attrs['max_ram'] = P.max_mem
+ds.attrs['max_ram'] = '{:5.1f}'.format(1e6 * P.max_mem / 1024**2) + ' GiB'
 ds.attrs['n_cells'] = P.cells
 ds.attrs['n_nodes'] = P.nodes
 ds.attrs['n_dof'] = P.dof

### 2020-04-02 model-marlim/custEM/run_marlim_reciprocal.py

@@ -26,6 +26,7 @@ For any questions or issues, contact
 from scipy.interpolate import RegularGridInterpolator as rgi
 from custEM.core import MOD
 from custEM.misc import mpi_print as mpp
+from custEM.misc import release_memory
 import numpy as np
 import dolfin as df
 
@@ -189,5 +190,9 @@ for fi, freq in enumerate(frequencies):       # all approaches
         M.IB.create_path_mesh(broadside, 'broadside', suffix='line_x')
     M.IB.interpolate('E_t', 'inline_path_line_x')
     M.IB.interpolate('E_t', 'broadside_path_line_x')
+    M.IB.interpolate('H_t', 'inline_path_line_x')
+    M.IB.interpolate('H_t', 'broadside_path_line_x')
     M.IB.synchronize()
     del M
+    
+    release_memory()

### 2020-04-02 model-marlim/custEM/export_netcdf.py
custEM add h-fields, sorting (#22)
Co-authored-by: Moouuzi <moouuzi@web.de>

@@ -15,7 +15,6 @@ from custEM.post import PlotFD
 import custEM as ce
 import xarray as xr
 from datetime import datetime
-import numpy as np
 
 # import base dataset and specify custEM observation lines
 ds = xr.load_dataset('../marlim_survey.nc', engine='h5netcdf')
@@ -37,24 +36,34 @@ for i, freq in enumerate(frequencies):
     P = PlotFD(mod=mod, mesh=mesh, approach='E_t', r_dir='./results')
     solution_time += P.solution_time 
     
-    P.import_line_data(line_il, key='il' + str(i), EH='E')
-    P.import_line_data(line_bs, key='bs' + str(i), EH='E')
+    P.import_line_data(line_il, key='il' + str(i))
+    P.import_line_data(line_bs, key='bs' + str(i))
 
     # Save inline and broadside data for each frequency
     ds.data_il.data[::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'][0, :].real  # Inline RE
+            'il' + str(i) + '_E_t'].real  # Inline RE
     ds.data_il.data[1::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'][0, :].imag  # Inline IM
+            'il' + str(i) + '_E_t'].imag  # Inline IM
 
     ds.data_bs.data[::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'][0, :].real  # Inline RE
+            'bs' + str(i) + '_E_t'].real  # Inline RE
     ds.data_bs.data[1::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'][0, :].imag  # Inline IM
+            'bs' + str(i) + '_E_t'].imag  # Inline IM
+
+    ds.data_il.data[::2, i, 3:] = P.line_data[
+            'il' + str(i) + '_H_t'].real  # Inline RE
+    ds.data_il.data[1::2, i, 3:] = P.line_data[
+            'il' + str(i) + '_H_t'].imag  # Inline IM
+
+    ds.data_bs.data[::2, i, 3:] = P.line_data[
+            'bs' + str(i) + '_H_t'].real  # Inline RE
+    ds.data_bs.data[1::2, i, 3:] = P.line_data[
+            'bs' + str(i) + '_H_t'].imag  # Inline IM
 
 # Add info
[…]

### 2020-04-02 model-marlim/custEM/run_marlim_reciprocal.py

@@ -26,6 +26,7 @@ For any questions or issues, contact
 from scipy.interpolate import RegularGridInterpolator as rgi
 from custEM.core import MOD
 from custEM.misc import mpi_print as mpp
+from custEM.misc import release_memory
 import numpy as np
 import dolfin as df
 
@@ -176,7 +177,7 @@ for fi, freq in enumerate(frequencies):       # all approaches
 
     # conduct the real FE stuff
     M.FE.build_var_form(check_sigma_conformity=False)
-    M.solve_main_problem(convert_to_H=False)
+    M.solve_main_problem()  # convert_to_H=False
 
     # import existing FE results, if exported before
     # M = MOD(mod, mesh, 'E_t', p=p, overwrite=False,
@@ -189,5 +190,9 @@ for fi, freq in enumerate(frequencies):       # all approaches
         M.IB.create_path_mesh(broadside, 'broadside', suffix='line_x')
     M.IB.interpolate('E_t', 'inline_path_line_x')
     M.IB.interpolate('E_t', 'broadside_path_line_x')
+    M.IB.interpolate('H_t', 'inline_path_line_x')
+    M.IB.interpolate('H_t', 'broadside_path_line_x')
     M.IB.synchronize()
     del M
+    
+    release_memory()

### 2020-04-02 model-block/custEM/export_netcdf.py
updated normalization of fields

@@ -53,7 +53,7 @@ for p in ['1', '2']:
         # Add info
         ds.attrs['runtime'] = str(int(P.solution_time)) + ' s'
         ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
-        ds.attrs['max_ram'] = '{:5.1f}'.format(mem_in_gib) + ' GiB'
+        ds.attrs['max_ram'] = f"{mem_in_gib :5.1f} GiB"
         ds.attrs['n_cells'] = P.cells
         ds.attrs['n_nodes'] = P.nodes
         ds.attrs['n_dof'] = P.dof

### 2020-04-02 model-marlim/custEM/export_netcdf.py

@@ -40,30 +40,34 @@ for i, freq in enumerate(frequencies):
     P.import_line_data(line_bs, key='bs' + str(i))
 
     # Save inline and broadside data for each frequency
+    # Divide all data by factor 10 for normalizing the transmitter moment,
+    # because the Tx was included with length 10 m in the mesh
     ds.data_il.data[::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'].real  # Inline RE
+            'il' + str(i) + '_E_t'].real / 10. # Inline RE
     ds.data_il.data[1::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'].imag  # Inline IM
+            'il' + str(i) + '_E_t'].imag / 10. # Inline IM
 
     ds.data_bs.data[::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'].real  # Inline RE
+            'bs' + str(i) + '_E_t'].real / 10. # Inline RE
     ds.data_bs.data[1::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'].imag  # Inline IM
+            'bs' + str(i) + '_E_t'].imag / 10. # Inline IM
 
     ds.data_il.data[::2, i, 3:] = P.line_data[
-            'il' + str(i) + '_H_t'].real  # Inline RE
+            'il' + str(i) + '_H_t'].real / 10. # Inline RE
     ds.data_il.data[1::2, i, 3:] = P.line_data[
-            'il' + str(i) + '_H_t'].imag  # Inline IM
+            'il' + str(i) + '_H_t'].imag / 10. # Inline IM
 
     ds.data_bs.data[::2, i, 3:] = P.line_data[
-            'bs' + str(i) + '_H_t'].real  # Inline RE
+            'bs' + str(i) + '_H_t'].real / 10. # Inline RE
     ds.data_bs.data[1::2, i, 3:] = P.line_data[
-            'bs' + str(i) + '_H_t'].imag  # Inline IM
+            'bs' + str(i) + '_H_t'].imag / 10. # Inline IM
+
+mem_in_gib = 1e6 * P.max_mem / 1024**2
 
 # Add info
 ds.attrs['runtime'] = str(int(solution_time)) + ' s'
 ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
[…]

### 2020-04-02 model-marlim/custEM/run_marlim_reciprocal.py

@@ -27,6 +27,7 @@ from scipy.interpolate import RegularGridInterpolator as rgi
 from custEM.core import MOD
 from custEM.misc import mpi_print as mpp
 from custEM.misc import release_memory
+from custEM.misc import max_mem
 import numpy as np
 import dolfin as df
 
@@ -120,8 +121,9 @@ p = 2
 
 
 # %% run p2 computations for all frequencies
-for fi, freq in enumerate(frequencies):       # all approaches
+for fi, freq in enumerate(frequencies[5:]):       # all approaches
 
+    fi = 5
     # Initialize MODel
     mod = 'f_' + str(freq)
     M = MOD(mod, mesh, 'E_t', p=p, overwrite=True,
@@ -193,6 +195,3 @@ for fi, freq in enumerate(frequencies):       # all approaches
     M.IB.interpolate('H_t', 'inline_path_line_x')
     M.IB.interpolate('H_t', 'broadside_path_line_x')
     M.IB.synchronize()
-    del M
-    
-    release_memory()

### 2020-04-03 manuscript/Manuscript.tex
Move back to LaTeX

\documentclass[
    paper,
%     manuscript,
%     twocolumn,
%     twoside,
%     revised,
  ]{geophysics}

% Remove once done
\usepackage[textsize=footnotesize, textwidth=2.8cm]{todonotes}

% Additional packages to geophysics.cls
\usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

\usepackage{amssymb, amsmath, amsfonts}
\usepackage{upquote}
\usepackage[strings]{underscore}
\usepackage{siunitx}                % SI conform commands (eg \num)
\usepackage{tabularx}
\usepackage{colortbl}
\usepackage{booktabs}
\usepackage{xspace}

\usepackage[pdftex, final]{hyperref}
% \usepackage[pdftex, hidelinks]{hyperref}
\hypersetup{allcolors=blue, allbordercolors={0 0 .5}, colorlinks=true}

% Figures
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\renewcommand{\figdir}{./figures}
\ifthenelse{\boolean{@twoc}}{%
  \newcommand{\cwidth}{250pt}}{%
  \newcommand{\cwidth}{240pt}}

\ifthenelse{\boolean{@twoc}}{%
  \newcommand{\acwidth}{250pt}%
  \newcommand{\tcwidth}{250pt}}{%
  \newcommand{\acwidth}{240pt}%
  \newcommand{\tcwidth}{312pt}}

% Own commands
\newcommand{\mr}[1]{\mathrm{#1}}
\newcommand{\emg}[2]{\texttt{emg#1#2}\xspace}
\newcommand{\empymod}{\texttt{empymod}\xspace}
\newcommand{\simpeg}{\texttt{SimPEG}\xspace}
\newcommand{\custem}{\texttt{custEM}\xspace}
\newcommand{\petgem}{\texttt{PETGEM}\xspace}

% Remove once done
\newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
\newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
\newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
\newcommand{\dul}[1]{\underline{\underline{#1}}}
\newcommand{\ul}[1]{\underline{#1}}
\newcommand{\rmk}[1]{{\color{red}{#1}}}

\begin{document}

\title{Open-source landscape for 3D CSEM modelling}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\ms{}  % ARTICLE-ID

\address{
\footnotemark[1]TU Delft,
Building 23,
Stevinweg 1 / PO-box 5048,
2628 CN Delft;\\
\footnotemark[2]TODO\\
E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
\textbf{Keywords}: CSEM, Open-Source, 3D modelling, FD, FE.
}

\author{%
Dieter Werthmüller\footnotemark[1], %            orcid: 0000-0002-8575-2484
Raphael Rochlitz\footnotemark[2], %              orcid: 0000-0002-5132-916X
Octavio Castillo-Reyes\footnotemark[2], and %    orcid: 0000-0003-4271-5015
Lindsey Heagy\footnotemark[2] %                  orcid: 0000-0002-1551-5926
}

\footer{}
\lefthead{Werthmüller et al.}
\righthead{Open-source 3D CSEM modelling}

\maketitle

%%fakesection ===    ABSTRACT    ===
\begin{abstract}
%
Write 1-2 sentence(s) each:
%
\begin{enumerate}
  \item Principal OBJECTIVES AND SCOPE OF THE WORK
  \item Methodology
  \item Results
  \item Conclusions
\end{enumerate}
%
\end{abstract}

\itodo{
We will have to decide on a Journal. Current suggestions:\\
- GMD: Geoscientific Model Development\\
- SIG: Surveys in Geophysics\\
- SE: Solid Earth\\
- GJI: Geophysical Journal International\\
- GP: Geophysical Prospecting\\
- GEO: Geophysics\\
- CAG: Computers and Geosciences\\
I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
are the favoured currently. I personally would be very interested in GMD. What
do you think? Also interesting would be the GJI, because the MT comparison was
published there, so it would be in the same place.
}

\section{Introduction}

Publications regarding 3D modelling in electromagnetic methods started to
appear as early as the 70's and 80's. These early publications where all
integral equation (IE) methods, having an anomaly embedded within a layered
medium, for loop-loop type transient EM measurements \citep{GJI.74.Raiche,
GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT)
measurements \citep{GEO.84.Wannamaker}.

In the 90's computer became sufficiently powerful that 3D modelling gained
traction, which resulted amongst other in the publication of the book
\emph{Three-Dimensional Electromagnetics}, \cite{B.SEG.99.Oristaglio} by the
SEG. Often cited publications from that time are \cite{RSC.94.Mackie} (3D MT
calculation), \cite{RS.94.Druskin} (frequency- and time-domain modelling using
a Yee grid and a global Krylov subspace approximation), and
\cite{RS.96.Alumbaugh, GJI.97.Newman} (low-to-high frequency calculation on
massively parallel computers).

The continuous improvement of computing power and the CSEM boom in the early
2000's in the hydrocarbon industry led to a wealth of publications. The amount
of available numerical solutions can be overwhelming and is part of the reason
why there are hundreds of publications about the topic. There are the different
methods to solve Maxwell's equation, such as the IE method
\citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the DE
method, for instance FD \citep{IEEE.66.Yee, RSC.94.Mackie, RS.94.Druskin,
GEO.09.Streich, CAG.13.Sommer}, FE \citep{GJI.11.Schwarzbach, GEO.12.daSilva,
GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, FV \citep{EM.90.Madsen,
ECP.07.Haber, GEO.14.Jahandari}, and FI \citep{PIER.01.Clemens, GP.06.Mulder}.
And these are just the most common ones.

There are also many different types of discretisation, where the most common
ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid
\citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also
unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, OcTree meshes
\citep{ECP.07.Haber}, or hexagonal meshes \citep{CAG.14.Cai}.

The biggest variety of all exists probably in the available solvers to solve
the system of linear equations; direct solvers \citep{GEO.09.Streich,
GEO.15.Grayver, GP.14.Chung, GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect
solvers \citep{GP.06.Mulder, GJI.15.Jaysaval} or a combination of both,
so-called hybrid solvers \citep{GEO.18.Liu}; the solvers often use
preconditioners such as the multigrid method \citep{SIAM.02.Aruliah,
GP.06.Mulder, GJI.16.Jaysaval}.

A very well written overview up to the year 2005 of the different approaches to
3D EM modelling is given by \cite{SG.05.Avdeev}. In the last 15 years the
publications with regards to 3D EM  modelling grew tremendously, driven
probably by improved computer powers.

~\\ \hrule

\paragraph{Overviews: From \cite{SG.05.Avdeev}}

Over the last decade, the EM induction community had three large international
meetings entirely devoted to the theory and practice of three-dimensional (3-D)
electromagnetic (EM) modelling and inversion (see Oristaglio and Spies, 1999;
Zhdanov and Wannamaker, 2002; Macnae and Liu, 2003). In addition, two special
issues of Inverse Problems dedicated to the same subject have been recently
published (Lesselier and Habashy, 2000; Lesselier and Chew, 2004).

«\emph{I would like to conclude this review with the following general remark.
  The most important challenge that faces the EM community today is to convince
  software developers to put their 3-D EM forward and inverse solutions into
  the public domain, at least after some time. This would have a strong impact
  on the whole subject and the developers would benefit from feedback regarding
the real needs of the end-users.}»

=> Use this quotation as a hook.

~\\ \hrule

\textbf{Just a list of ideas and notes so far.}

List codes, particularly papers presented that are, potentially, available or
not, but only by contacting the author. Mention change in coding practices,
development in the open, collaboration, bug reports, better documentation and
testing, etc. Example: \cite{CAG.17.Cai} (open or not?)

Mention \cite{GJI.13.Miensopust}, which is a similar thing, but for 3D
modelling and inversion for MT.

Common features of our codes is:

\begin{itemize}
  \item Not just open source, but also developed in the open and increasingly
    building a global community - also mention other projects as, e.g., pyGIMLi
    \citep{CAG.17.Rucker} and Fatiando (e.g., \cite{JOSS.18.Uieda}).
  \item All codes we compare work in the Python eco-system (hard work
    underlying the Python API can differ though).
  \item Also modern dev, which includes CI testing, good documentation, issue
    tracking, and extensive discussion through Slack, Gitter, or similar, with
    dozens to hundreds of members (SimPEG 09-09-2019: 189 members), which
    constitutes a vibrant community and combines a huge spectrum from coders to
    first time users, and from academia to industry.
\end{itemize}

It is worth mentioning that there are many more open-source 3D electromagnetic
codes developed in other fields than geophysics. Examples include \dots (TODO:
add at least three references). While these codes could potentially be used for
the same goals as presented here we restrict our review to codes purpose-built
for geophysical applications.

An integral part of this publication are the necessary instructions and codes
to reproduce all published results. In fact, the provided codes contain more
than just the results shown here, as including everything here would have made
the article to lengthy.

~\\ \hrule

\begin{itemize}
  \item Mention all use cases (ground water, geothermal, oil and gas, civil
        engineering, hazards).
  \item Mention other fields.
  \item Mention MT comparison paper.
\end{itemize}

Many 3D codes exist since long (SEG 3D book by oristaglio, etc). However, there
are a few key differences recently:

\begin{itemize}
  \item Codes are \emph{just available} (you don't have to write someone and
    ask if you could have the code)
  \item Codes are \emph{easy installable} (e.g., ``pip install emg3d``)
  \item Codes are well documented and come with a lot of examples
  \item It is easy to get involved (GitHub/GitLab) and contribute
  \item It is easy to get help (Slack, GitHub/GitLab)
\end{itemize}

This will significantly increase the user base and the number of people who are
actually doing 3D EM modelling.

~\\ \hrule

\begin{itemize}
  \item Why need:
    \begin{itemize}
      \item analytical solutions
      \item semi-analytical solutions such as 1D codes (analytical [recursion]
        in k-f domain followed by numerical transformation).
      \item need of comparison of more complex models.
    \end{itemize}
  \item What exists:
    \begin{itemize}
      \item very quick run-down of codes, methods, discretizations.
      \item Thesis Raphael
      \item LitRev Dieter
    \end{itemize}
  \item What changed:
    \begin{itemize}
      \item Python
      \item Demand/Desire for reproducible research
      \item Open-source has changed:
        \begin{itemize}
          \item easy install
          \item documented
          \item bug/issues
          \item communities
          \item testing/benchmarks/coverage/style/quality
        \end{itemize}
    \end{itemize}
  \item What is this paper:
    \begin{itemize}
      \item 4 codes, 2 FD 2 FE
      \item 2 models, simple one after MT paper, complex Marlim one
    \end{itemize}
  \item Outline of paper
  \item Zenodo, provide all codes to reproduce the results.
\end{itemize}

~\\ \hrule

There are many codes for EM - our focus here is on the application to
controlled-source electromagnetic measurements, even though all of the codes
can handle different setups too.

in such fields as the modelling of communication systems (antennas, radar,
satellites), medical imaging, and others.

time domain and frequency domain

1D, 2D, we look at 3D.

Common methods in geophysics are the

\begin{itemize}
  \item integral equation (IE, \cite{GJI.74.Raiche, GEO.06.Zhdanov,
    CAG.16.Kruglyakov}), (scattering equation) (anomalies in layered
    background), computational effort comparably low
  \item differential equation such as finite difference (FD \cite{IEEE.66.Yee,
    GEO.93.Wang}), simple to implement
  \item and finite volume (FV \cite{EM.90.Madsen, GEO.14.Jahandari}),
  \item or and finite element (FE \cite{GEO.04.Commer GEO.09.Streich})
    (approximating the DE on edges and nodals), good for complex geometries,
  \item finite integration technique (FIT, \cite{AEU.77.Weiland},
    \cite{PIER.01.Clemens}, \cite{GP.06.Mulder})
\end{itemize}

OctTree meshes or severe stretching \citep{ECP.07.Haber}

Elmer FEM multiphysical simulation software P. Råback, P.-L. Forsström, M. Lyly
and M. Gröhn, Elmer - finite element package for the solution of partial
differential equations, poster presentation, EGEE User Forum, 2007, Manchester,
UK. http://www.csc.fi/elmer

Many commercial, e.g., COMSOL Multiphysics; EMGS, RSI, KMS; the oil and service
companies.

Consortia (CEMI; Key)

Universities, e.g. Pottsdam (Streich, Grayver)

Computational cost IE < FD < FV < FE

Direct solvers vs indirect solvers, both its advantages and disadvantages;
memory, various sources.

Grids (regular grids, unstructured grids, Octree, tetrahedra, hexahedral,
adaptive, multigrids).

Boundary condition

\section{Codes}

Intro to it; numerical approximations (FE, FD), differences in solvers,
gridding/meshing, boundary conditions, etc.

It is beyond the scope of this paper to go into every detail of the different
modellers, however, a quick blabla...

Each code should outline:

\begin{itemize}
  \item Equation system it solves;
  \item the used discretization possibilities;
  \item domains (frequency, time);
  \item details (anisotropy; el. perm. and mag. perm.);
  \item other things (inversion; other methods);
  \item speed and memory estimation;
  \item plans for next features.
  \item Inversion capabilities
  \item Time/frequency
  \item transmitter types
\end{itemize}

Basically summarize each code in three points:
\begin{itemize}
  \item Brief intro and main features
  \item Main selling point
  \item Planned features
\end{itemize}

Cite for all: NumPy, SciPy.

The codes under consideration are presented here in alphabetical order.

\subsection{custEM}

\cite{GEO.19.Rochlitz}

FEniCS \citep{CSE.15.Alnaes}

\subsection{emg3d}

The 3D CSEM modeller \emg3d \citep{JOSS.19.Werthmuller} is a multigrid
\citep{CMMP.64.Fedorenko} solver for 3D electromagnetic diffusion following
\cite{GP.06.Mulder}, with tri-axial electrical anisotropy and isotropic
magnetic permeability. The matrix-free solver can be used as main solver or as
preconditioner for one of the Krylov subspace methods implemented in SciPy
\citep{NM.20.Virtanen}, and the governing equations are discretized on a
staggered grid by the finite-integration technique \cite{AEU.77.Weiland}, which
can be viewed as a finite-volume generalization of \cite{IEEE.66.Yee}'s scheme.
The code is written completely in Python using the NumPy
\citep{CSE.11.VanDerWalt} and SciPy stacks, where the most time- and
memory-consuming parts are sped up through jitted functions using Numba
\citep{LLVM.15.Lam}.

The multigrid method is characterized by almost linear scaling both in terms
of CPU usage and RAM, and it is therefore a comparably low-memory consumption
solver (see results). However, the way multigrid is implemented also means some
additional constraints on the chosen grid. You can input any three-dimensional
grid into \emg3d, but the implemented method works with the existing nodes,
meaning there are no new nodes created as coarsening is done by combining
adjacent cells. The more times the grid dimension can be divided by two the
better it is suited. Ideally, the dimension of the coarsest grid should be a
low prime, and grid dimensions are therefore given by their multiplication with
powers of two (${2,3,5}·2^n$).

Currently \emg3d can be used to model the electric and magnetic fields due to
arbitrary finite length electric dipole sources for a single frequency at a
time. Helper functions to calculate time-domain responses are in the works
(should be ready by publishing this article). Current development is focused
on adding inversion capabilities; averaging routines to implement strong
topography; and general anisotropy.

The 3D solver \emg3d can be found in the GitHub organization of \empymod
(`empymod.github.io <https://empymod.github.io>`_). The modeller \empymod
\citep{GEO.17.Werthmuller} is a 1D code which can calculate electric or
magnetic responses due to a 3D electric or magnetic source in a layered-earth
model with vertical transverse isotropic (VTI) resistivity, VTI electric
permittivity, and VTI magnetic permeability, from very low frequencies (DC) to
very high frequencies (GPR).

In the future it should be possible to use \emg3d as a solver within the
\simpeg framework.

\subsection{PETGEM}

\cite{GJI.19.CastilloReyes}

FEniCS \citep{CSE.15.Alnaes}

\subsection{SimPEG}

\cite{CAG.15.Cockett}

PARDISO \citep{FGCS.04.Schenk}

\section{Comparison}

\subsection{Block Model}

Simple block (one to three blocks) model similar to \cite{GJI.13.Miensopust};
potentially with a bit a funkier source (say, finite length rotated bipole and
finite length receivers). In this case I would only compare inline and
crossline responses.

\begin{itemize}
  \item VTI resistivity
  \item \simpeg => use OcTree for this example? That would be awesome!
  \item Show Ex, Ey, Ez, Hx, Hy, Hz
\end{itemize}

Tables:

%
\tabl[btp]{comp1}{Caption.}{
  \centering
\begin{tabular}{lccrS[table-format=2.4]rl}
  \toprule
  %
  Code & Method & Mesh & \#Cells & {CPU} & RAM & Computer \\
  \midrule
  %
  \custem & FE  & FE & & & & \\
  \emg3d  & FIT & FD & & & & \\
  \petgem & FE  & FE & & & & \\
  \simpeg & FD  & OcTree & & & & \\
  %
  \bottomrule
\end{tabular}}%
%

%
\plot*{block-model}{width=.6\textwidth}{
   Block model, consisting of a layered background, in which three blocks are
   embedded.
}
%

%
\plot*{layered-result}{width=.6\textwidth}{
   Comparison of the layered model.
}
%

%
\plot*{block-result}{width=.6\textwidth}{
   Comparison of the block model.
}
%

\subsection{Marlim R3D}

The Marlim R3D model is a \dots \cite{BJG.17.Carvalho} (model)
\cite{GEO.19.Correa} (CSEM data)

Comparison to an code from the industry, using \emph{SBLwiz} from EMGS.

\section{Discussion}

The landscape in 3D CSEM modelling greatly changed in the last five years or
so. While before there were only closed-source codes owned by companies or
consortia (e.g., CEMI), or codes that you had to obtain from the authors, often
without much documentation, there was recently a wave of openly released codes.

\dots

We see this only as the start. Much more comparisons and examples are required.
3D CSEM modelling is a difficult task, which requires many considerations: It
starts with the selection of the right code for the problem; then the meshing
is particularly difficult, choosing cells small enough to appropriately
represent the model yet to be as coarse as possible still achieving the desired
precision; the required model extent, particularly for shallow and marine cases
where the airwave has to be considered. The tricky part is that even if the
result is not correct it may look completely valid. The only options to verify
results are (a) by comparing different discretizations, and (b) by comparing
different codes.

Here we only consider frequency-domain results from frequency-domain
computations. Similar comparison for time-domain results from time-domain
computations, and frequency-domain results from time-domain computations and
vice versa using Fourier transforms would also be good.

The readily availability of many codes means there will be many more people
able to model 3D results, and not just a few specialists in the field. Whilst
this is amazing and will push the field much further it also means that the
same mistakes might happen over and over again, and comparisons and examples
like these can help to avoid this.

\subsection{Future (?)}

Comment KK: \emph{One thing that the community could really use is more test
models for various scenarios, and having them be easily accessible.}

\subsection{MARE3DEM}

This is, I thought, the right spot where Kerry Key could write a bit about
MARE3DEM, if (and I think only if) there are clear plans and a time-scale to
open-source it. Embedded in a wider summary of available codes (some research
required).

\section{Conclusions}

The landscape in 3D CSEM modelling greatly changed in the last five years or
so. While before there were only closed-source codes owned by companies or
consortia (e.g., CEMI) there was recently a wave of openly released codes.

Results from numerical modellers for simple models, such as a halfspace below
air or a sphere in a fullspace, can be verified by comparing them to analytical
solutions. However, there is no such possibility for complicated, realistic
models. The only way to gain confidence in numerical results is by comparing
different codes to each other. We hope that our efforts help to the confidence
in the available open-source codes\dots

Also, the runtime and memory consumption comparison together with the meshing
differences should help to decide which modeller is used best for which tasks,
as there is not one method which is best for all problems.

It is important to note that there exist many more 3D electromagnetic codes
from various fields, such as civil engineering or medicine, in Python and in
many other languages (list a few references here). Here we focused on codes in
Python developed for geophysical exploration.

\dots

\section{Acknowledgment}

\itodo{Write here your fundings; and potentially also minor contributors etc.}

We would like to thank Paulo Menezes for the help and explanations with regards
to the Marlim R3D model and corresponding CSEM data, and for making their
actual calculation model available under an open-source license.

The work of D.W. was conducted within the Gitaro.JIM project funded through
MarTERA, a EU Horizon 2020 research and innovation programme (No 728053);
\href{https://www.martera.eu}{martera.eu}.

% REFERENCES

\bibliographystyle{Refs}          % Modified SEG bibliography style.
\bibliography{Refs}

\end{document}

### 2020-04-03 manuscript/conf.py

@@ -1,29 +1,0 @@
-import os
-import re
-
-# Project information
-project = '3D-CSEM-CC'
-copyright = '2019, emg3d, SimPEG, custEM, PETGEM'
-author = 'emg3d, SimPEG, custEM, PETGEM'
-description = '3D CSEM code comparison article'
-
-# General configuration
-extensions = ['sphinx.ext.mathjax', ]
-exclude_patterns = ['_build', ]         # List of exclude patterns.
-version = re.sub('^v', '', os.popen('git describe --tags').read().strip())
-today_fmt = '%d %B %Y'
-
-# Figures
-numfig = True
-numfig_format = {'figure': 'Figure %s:'}
-
-# HTML related
-html_theme = 'sphinx_rtd_theme'
-html_static_path = ['_static', ]  # Static paths.
-html_theme_options = {
-    'prev_next_buttons_location': 'both',
-}
-
-# CSS fixes
-def setup(app):
-    app.add_stylesheet("style.css")

### 2020-04-03 model-block/custEM/export_netcdf.py
custEM: factor 10 and GiB (#23)
Co-authored-by: Moouuzi <moouuzi@web.de>

@@ -48,12 +48,10 @@ for p in ['1', '2']:
                 [P.line_data['t3_E_t'][:, 0].real, 
                  P.line_data['t3_E_t'][:, 0].imag]).ravel('F') 
     
-        mem_in_gib = 1e6 * P.max_mem / 1024**2
-    
         # Add info
         ds.attrs['runtime'] = str(int(P.solution_time)) + ' s'
         ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
-        ds.attrs['max_ram'] = '{:5.1f}'.format(mem_in_gib) + ' GiB'
+        ds.attrs['max_ram'] = f"{P.max_mem :5.1f} GiB"
         ds.attrs['n_cells'] = P.cells
         ds.attrs['n_nodes'] = P.nodes
         ds.attrs['n_dof'] = P.dof

### 2020-04-03 model-marlim/custEM/export_netcdf.py

@@ -40,30 +40,32 @@ for i, freq in enumerate(frequencies):
     P.import_line_data(line_bs, key='bs' + str(i))
 
     # Save inline and broadside data for each frequency
+    # Divide all data by factor 10 for normalizing the transmitter moment,
+    # because the Tx was included with length 10 m in the mesh
     ds.data_il.data[::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'].real  # Inline RE
+            'il' + str(i) + '_E_t'].real / 10. # Inline RE
     ds.data_il.data[1::2, i, :3] = P.line_data[
-            'il' + str(i) + '_E_t'].imag  # Inline IM
+            'il' + str(i) + '_E_t'].imag / 10. # Inline IM
 
     ds.data_bs.data[::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'].real  # Inline RE
+            'bs' + str(i) + '_E_t'].real / 10. # Inline RE
     ds.data_bs.data[1::2, i, :3] = P.line_data[
-            'bs' + str(i) + '_E_t'].imag  # Inline IM
+            'bs' + str(i) + '_E_t'].imag / 10. # Inline IM
 
     ds.data_il.data[::2, i, 3:] = P.line_data[
-            'il' + str(i) + '_H_t'].real  # Inline RE
+            'il' + str(i) + '_H_t'].real / 10. # Inline RE
     ds.data_il.data[1::2, i, 3:] = P.line_data[
-            'il' + str(i) + '_H_t'].imag  # Inline IM
+            'il' + str(i) + '_H_t'].imag / 10. # Inline IM
 
     ds.data_bs.data[::2, i, 3:] = P.line_data[
-            'bs' + str(i) + '_H_t'].real  # Inline RE
+            'bs' + str(i) + '_H_t'].real / 10. # Inline RE
     ds.data_bs.data[1::2, i, 3:] = P.line_data[
-            'bs' + str(i) + '_H_t'].imag  # Inline IM
+            'bs' + str(i) + '_H_t'].imag / 10. # Inline IM
 
 # Add info
 ds.attrs['runtime'] = str(int(solution_time)) + ' s'
 ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
[…]

### 2020-04-05 manuscript/Manuscript.tex

@@
 %
-Write 1-2 sentence(s) each:
+Write at the end; one or two sentence(s) each:
 %
@@
 
-Publications regarding 3D modelling in electromagnetic methods started to
-appear as early as the 70's and 80's. These early publications where all
-integral equation (IE) methods, having an anomaly embedded within a layered
-medium, for loop-loop type transient EM measurements \citep{GJI.74.Raiche,
-GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT)
-measurements \citep{GEO.84.Wannamaker}.
+Controlled-source electromagnetic (CSEM) measurements is a frequently applied
+method in exploration geophysics for various applications, such as ground
+water, geothermal, oil and gas, mining, civil engineering, or geo-hazards.
+Modelling these electromagnetic fields is therefore of great interest in order
+to understand the measured data. Publications regarding 3D modelling in
+electromagnetic methods started to appear as early as the 1970's and 1980's.
+These early publications where all integral equation (IE) methods, having an
+anomaly embedded within a layered medium, for loop-loop type transient EM
+measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman}
+and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
 
-In the 90's computer became sufficiently powerful that 3D modelling gained
+In the 1990's computer became sufficiently powerful that 3D modelling gained
 traction, which resulted amongst other in the publication of the book
-\emph{Three-Dimensional Electromagnetics}, \cite{B.SEG.99.Oristaglio} by the
-SEG. Often cited publications from that time are \cite{RSC.94.Mackie} (3D MT
-calculation), \cite{RS.94.Druskin} (frequency- and time-domain modelling using
-a Yee grid and a global Krylov subspace approximation), and
-\cite{RS.96.Alumbaugh, GJI.97.Newman} (low-to-high frequency calculation on
-massively parallel computers).
+\emph{Three-Dimensional Electromagnetics} \citep{B.SEG.99.Oristaglio} by the
+SEG. Often cited publications from that time are \cite{RSC.94.Mackie}, 3D MT
+computation; \cite{RS.94.Druskin}, frequency- and time-domain modelling using a
+Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh,
+GJI.97.Newman}, low-to-high frequency computation on massively parallel
+computers.
 
@@
 \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
-CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the DE
-method, for instance FD \citep{IEEE.66.Yee, RSC.94.Mackie, RS.94.Druskin,
-GEO.09.Streich, CAG.13.Sommer}, FE \citep{GJI.11.Schwarzbach, GEO.12.daSilva,
-GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, FV \citep{EM.90.Madsen,
-ECP.07.Haber, GEO.14.Jahandari}, and FI \citep{PIER.01.Clemens, GP.06.Mulder}.
-And these are just the most common ones.
+CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the
+differential equation (DE) method, for instance finite differences (FD)
+\citep{IEEE.66.Yee, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
+CAG.13.Sommer}, finite elementes (FE) \citep{GJI.11.Schwarzbach,
+GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, finite volume
+(FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari}, and finite
+integration technique (FIT) \citep{PIER.01.Clemens, GP.06.Mulder}. And these
+are just the most common ones.
 
@@
 publications with regards to 3D EM  modelling grew tremendously, driven
-probably by improved computer powers.
+probably by improved computer powers. Avdeev finished his review with the
+following statement: «\emph{The most important challenge that faces the EM
+community today is to convince software developers to put their 3-D EM forward
+and inverse solutions into the public domain, at least after some time. This
+would have a strong impact on the whole subject and the developers would
+benefit from feedback regarding the real needs of the end-users.}»
+
+It is this topic that we want to address, open-source 3D CSEM codes. Some big
+exploration companies and service companies have their own codes, as well as
+certain research consortia. But how about codes that are open-source?
+Traditionally research code was often available upon request by the author.
+Codes distributed that way often come with the request to not share the code,
+or they often come without a license attached at all (which means that they are
+not open-source). Also, at times there can be a significant hurdle to install
+a code.
+
+However, the meaning of open-source evolved rapidly in the last decades. Today
+open-source generally not only means that a code is available (with a proper
+license). It includes much more today, such as that the code is hosted online,
+is under version control, has the possibility to file issues and make pull
+requests to fix bugs. Good codes also have continuous integration that includes
+extensive testing of the code base and online hosted documentation that
+includes the API. As such the term has shifted from purely open-source code
+to development in the open and increasingly building a global community. There
+are a number of projects within the realm of geophysical exploration, besides
+the ones we present here, e.g. pyGIMLi \citep{CAG.17.Rucker} and Fatiando
+\citep{JOSS.18.Uieda}.
+
+Newer \todo{wrong term, think about it}programming environments  have also
+brought much simplifications in the installation process and have most
+importantly simplified it for code developers to make their codes easily
+available and installable. All our presented codes are in the Python
+environment, and each code can be install with a single command (which includes
+downloading and installation).
 
@@
 
-\paragraph{Overviews: From \cite{SG.05.Avdeev}}
-
-Over the last decade, the EM induction community had three large international
-meetings entirely devoted to the theory and practice of three-dimensional (3-D)
-electromagnetic (EM) modelling and inversion (see Oristaglio and Spies, 1999;
-Zhdanov and Wannamaker, 2002; Macnae and Liu, 2003). In addition, two special
-issues of Inverse Problems dedicated to the same subject have been recently
-published (Lesselier and Habashy, 2000; Lesselier and Chew, 2004).
-
-«\emph{I would like to conclude this review with the following general remark.
-  The most important challenge that faces the EM community today is to convince
-  software developers to put their 3-D EM forward and inverse solutions into
-  the public domain, at least after some time. This would have a strong impact
-  on the whole subject and the developers would benefit from feedback regarding
-the real needs of the end-users.}»
-
-=> Use this quotation as a hook.
-
-~\\ \hrule
-
-\textbf{Just a list of ideas and notes so far.}
-
-List codes, particularly papers presented that are, potentially, available or
-not, but only by contacting the author. Mention change in coding practices,
-development in the open, collaboration, bug reports, better documentation and
-testing, etc. Example: \cite{CAG.17.Cai} (open or not?)
-
 Mention \cite{GJI.13.Miensopust}, which is a similar thing, but for 3D
 modelling and inversion for MT.
-
-Common features of our codes is:
-
-\begin{itemize}
-  \item Not just open source, but also developed in the open and increasingly
-    building a global community - also mention other projects as, e.g., pyGIMLi
-    \citep{CAG.17.Rucker} and Fatiando (e.g., \cite{JOSS.18.Uieda}).
-  \item All codes we compare work in the Python eco-system (hard work
-    underlying the Python API can differ though).
-  \item Also modern dev, which includes CI testing, good documentation, issue
-    tracking, and extensive discussion through Slack, Gitter, or similar, with
-    dozens to hundreds of members (SimPEG 09-09-2019: 189 members), which
-    constitutes a vibrant community and combines a huge spectrum from coders to
-    first time users, and from academia to industry.
-\end{itemize}
 
@@
 the article to lengthy.
-
-~\\ \hrule
-
-\begin{itemize}
-  \item Mention all use cases (ground water, geothermal, oil and gas, civil
-        engineering, hazards).
-  \item Mention other fields.
-  \item Mention MT comparison paper.
-\end{itemize}
-
-Many 3D codes exist since long (SEG 3D book by oristaglio, etc). However, there
-are a few key differences recently:
-
-\begin{itemize}
-  \item Codes are \emph{just available} (you don't have to write someone and
-    ask if you could have the code)
-  \item Codes are \emph{easy installable} (e.g., ``pip install emg3d``)
-  \item Codes are well documented and come with a lot of examples
-  \item It is easy to get involved (GitHub/GitLab) and contribute
-  \item It is easy to get help (Slack, GitHub/GitLab)
-\end{itemize}
 
@@
 
+1D, 2D, we look at 3D.
 time domain and frequency domain
-
-1D, 2D, we look at 3D.
 
@@
 modellers, however, a quick blabla...
+
+All the codes presented here
+\begin{itemize}
+  \item are \emph{just available} (you don't have to write someone and ask if
+    you could have the code);
+  \item are \emph{easy installable} (through \texttt{pip} or \texttt{conda});
+  \item are under \emph{version control} and online either on GitHub or on
+    GitLab, which includes possibilities of easy involvement by either creating
+    an issue, reporting a bug, or filing a pull request; and
+  \item are well documented and come with a lot of examples.
+\end{itemize}
+
+\begin{itemize}
+  \item Code (license): \emg3d (Apache-2.0), custEM (LPGL-3.0), PETGEM
+    (GPL-3.0), and \simpeg (MIT).
+  \item Hosting: GitHub (\emg3d, \petgem, \simpeg); GitLab (\custem)
+\end{itemize}
 
@@
 arbitrary finite length electric dipole sources for a single frequency at a
-time. Helper functions to calculate time-domain responses are in the works
+time. Helper functions to compute time-domain responses are in the works
 (should be ready by publishing this article). Current development is focused
@@
 (`empymod.github.io <https://empymod.github.io>`_). The modeller \empymod
-\citep{GEO.17.Werthmuller} is a 1D code which can calculate electric or
+\citep{GEO.17.Werthmuller} is a 1D code which can compute electric or
 magnetic responses due to a 3D electric or magnetic source in a layered-earth
@@
 to the Marlim R3D model and corresponding CSEM data, and for making their
-actual calculation model available under an open-source license.
+actual computation model available under an open-source license.
 

### 2020-04-06 model-block/PETGEM/export_netcdf.py
PETGEM block-model fix indexing (#25)
* fixed error with petgem results (block model)

Co-authored-by: ocastilloreyes <ocastilloreyes@gmail.com>

@@ -28,18 +28,18 @@ sol_block = h5py.File('out/block.h5', 'r')
 # ---------------------------------------------------------------
 model = 'block'
 # Save line 1
-real_line1 = sol_block.get('line1')[()].real
-imag_line1 = sol_block.get('line1')[()].imag
+real_line1 = sol_block.get('line1')[()].conjugate().real
+imag_line1 = sol_block.get('line1')[()].conjugate().imag
 ds.line_1.data = np.vstack((real_line1, imag_line1)).ravel('F')
 
 # Save line 2
-real_line2 = sol_block.get('line2')[()].real
-imag_line2 = sol_block.get('line2')[()].imag
+real_line2 = sol_block.get('line2')[()].conjugate().real
+imag_line2 = sol_block.get('line2')[()].conjugate().imag
 ds.line_2.data = np.vstack((real_line2, imag_line2)).ravel('F')
 
 # Save line 3
-real_line3 = sol_block.get('line3')[()].real
-imag_line3 = sol_block.get('line3')[()].imag
+real_line3 = sol_block.get('line3')[()].conjugate().real
+imag_line3 = sol_block.get('line3')[()].conjugate().imag
 ds.line_3.data = np.vstack((real_line3, imag_line3)).ravel('F')
 
 # Save memory (Gb)
@@ -80,18 +80,18 @@ sol_layered = h5py.File('out/layered.h5', 'r')
 # ---------------------------------------------------------------
 model = 'layered'
 # Save line 1
-real_line1 = sol_layered.get('line1')[()].real
-imag_line1 = sol_layered.get('line1')[()].imag
+real_line1 = sol_layered.get('line1')[()].conjugate().real
+imag_line1 = sol_layered.get('line1')[()].conjugate().imag
 ds.line_1.data = np.vstack((real_line1, imag_line1)).ravel('F')
 
 # Save line 2
-real_line2 = sol_layered.get('line2')[()].real
-imag_line2 = sol_layered.get('line2')[()].imag
+real_line2 = sol_layered.get('line2')[()].conjugate().real
+imag_line2 = sol_layered.get('line2')[()].conjugate().imag
 ds.line_2.data = np.vstack((real_line2, imag_line2)).ravel('F')
 
 # Save line 3
-real_line3 = sol_layered.get('line3')[()].real
-imag_line3 = sol_layered.get('line3')[()].imag
[…]

### 2020-04-08 manuscript/Manuscript.tex
Clean-up intro

@@
 
-Controlled-source electromagnetic (CSEM) measurements is a frequently applied
-method in exploration geophysics for various applications, such as ground
-water, geothermal, oil and gas, mining, civil engineering, or geo-hazards.
-Modelling these electromagnetic fields is therefore of great interest in order
-to understand the measured data. Publications regarding 3D modelling in
-electromagnetic methods started to appear as early as the 1970's and 1980's.
-These early publications where all integral equation (IE) methods, having an
-anomaly embedded within a layered medium, for loop-loop type transient EM
-measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman}
-and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+Controlled-source electromagnetic (CSEM) measurements are a frequently applied
+method in various geophysical exploration fields, such as geothermal and ground
+water, oil and gas, mining, civil engineering, or geo-hazards. Modelling these
+electromagnetic fields is therefore of great interest in order to understand
+the measured data. Publications regarding 3D modelling in electromagnetic
+methods started to appear as early as the 1970's and 1980's. These early
+publications where integral equation (IE) methods, having an anomaly embedded
+within a layered medium, mostly for loop-loop type transient EM measurements
+\citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and
+magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
 
@@
 traction, which resulted amongst other in the publication of the book
-\emph{Three-Dimensional Electromagnetics} \citep{B.SEG.99.Oristaglio} by the
-SEG. Often cited publications from that time are \cite{RSC.94.Mackie}, 3D MT
-computation; \cite{RS.94.Druskin}, frequency- and time-domain modelling using a
-Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh,
-GJI.97.Newman}, low-to-high frequency computation on massively parallel
-computers.
+\emph{Three-Dimensional Electromagnetics} by the SEG
+\citep{B.SEG.99.Oristaglio}. Often cited publications from that time are
+\cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and
+time-domain modelling using a Yee grid and a global Krylov subspace
+approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency
+computation on massively parallel computers.
 
@@
 differential equation (DE) method, for instance finite differences (FD)
-\citep{IEEE.66.Yee, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
-CAG.13.Sommer}, finite elementes (FE) \citep{GJI.11.Schwarzbach,
+\citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
+CAG.13.Sommer}, finite elementes (FE) \citep{GJI.11.Schwarzbach, GEO.04.Commer,
 GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, finite volume
@@
 publications with regards to 3D EM  modelling grew tremendously, driven
-probably by improved computer powers. Avdeev finished his review with the
+by the ever increasing computing power. Avdeev finished his review with the
 following statement: «\emph{The most important challenge that faces the EM
@@
 
-It is this topic that we want to address, open-source 3D CSEM codes. Some big
-exploration companies and service companies have their own codes, as well as
-certain research consortia. But how about codes that are open-source?
-Traditionally research code was often available upon request by the author.
-Codes distributed that way often come with the request to not share the code,
-or they often come without a license attached at all (which means that they are
-not open-source). Also, at times there can be a significant hurdle to install
-a code.
-
-However, the meaning of open-source evolved rapidly in the last decades. Today
-open-source generally not only means that a code is available (with a proper
-license). It includes much more today, such as that the code is hosted online,
-is under version control, has the possibility to file issues and make pull
-requests to fix bugs. Good codes also have continuous integration that includes
-extensive testing of the code base and online hosted documentation that
-includes the API. As such the term has shifted from purely open-source code
+It is this topic that we address, open-source 3D CSEM codes. Some major
+exploration service companies as well as certain research consortia and
+research groups have their 3D CSEM codes. But how about codes that are
+open-source? Traditionally research code was often available upon request by
+the author. Codes distributed that way often come with the request to not share
+the code, or they often come without a license attached at all (which means
+that they are not open-source). Also, at times there can be a significant
+hurdle to install a code. However, the meaning of open-source evolved rapidly
+in the last decades. Today, open-source generally not only means that a code is
+available (with a proper license). It includes much more today, such as that
+the code is hosted online, is under version control, has the possibility to
+file issues and make pull requests to fix bugs. Well maintained codes often
+have continuous integration that includes testing of the code base and online
+hosted documentation. As such the term has shifted from purely open-source code
 to development in the open and increasingly building a global community. There
 are a number of projects within the realm of geophysical exploration, besides
-the ones we present here, e.g. pyGIMLi \citep{CAG.17.Rucker} and Fatiando
-\citep{JOSS.18.Uieda}.
+the ones we present here, \todo{Others coming to your mind?}e.g. pyGIMLi
+\citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer \todo{wrong
+term, think about it}programming environments  have also brought much
+simplifications in the installation process and have most importantly
+simplified it for code developers to make their codes easily available and
+installable. All our presented codes are in the Python ecosystem, and each code
+can be installed with a single command (which includes downloading and
+installation).
 
-Newer \todo{wrong term, think about it}programming environments  have also
-brought much simplifications in the installation process and have most
-importantly simplified it for code developers to make their codes easily
-available and installable. All our presented codes are in the Python
-environment, and each code can be install with a single command (which includes
-downloading and installation).
+A second topic we want to address is verification. New codes are generally
+verified against analytical solutions. However, analytical and semi-analytical
+solutions only exist for very simple models. There is no possibility to check
+how good a computed response is, expect for comparing the result from different
+modellers. If different modellers using different discretisation and
+implementations of Maxwell's equations yield the same result it can give
+confidence in the accuracy.
 
-~\\ \hrule
+It is worth mentioning that there are many more 3D EM codes developed in other
+fields than geophysics such as communication systems (antennas, radar,
+satellites), medical imaging. There are various open-source codes in these
+fields \todo{Add at least three references} too, e.g., Elmer
+(\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication,
+just a poster). While these codes could potentially be used for the same goals
+as presented here we restrict our review to codes purpose-built for geophysical
+applications.
 
-Mention \cite{GJI.13.Miensopust}, which is a similar thing, but for 3D
-modelling and inversion for MT.
-
-It is worth mentioning that there are many more open-source 3D electromagnetic
-codes developed in other fields than geophysics. Examples include \dots (TODO:
-add at least three references). While these codes could potentially be used for
-the same goals as presented here we restrict our review to codes purpose-built
-for geophysical applications.
-
-An integral part of this publication are the necessary instructions and codes
-to reproduce all published results. In fact, the provided codes contain more
-than just the results shown here, as including everything here would have made
-the article to lengthy.
-
-This will significantly increase the user base and the number of people who are
-actually doing 3D EM modelling.
-
-~\\ \hrule
-
-\begin{itemize}
-  \item Why need:
-    \begin{itemize}
-      \item analytical solutions
-      \item semi-analytical solutions such as 1D codes (analytical [recursion]
-        in k-f domain followed by numerical transformation).
-      \item need of comparison of more complex models.
-    \end{itemize}
-  \item What exists:
-    \begin{itemize}
-      \item very quick run-down of codes, methods, discretizations.
-      \item Thesis Raphael
-      \item LitRev Dieter
-    \end{itemize}
-  \item What changed:
-    \begin{itemize}
-      \item Python
-      \item Demand/Desire for reproducible research
-      \item Open-source has changed:
-        \begin{itemize}
-          \item easy install
-          \item documented
-          \item bug/issues
-          \item communities
-          \item testing/benchmarks/coverage/style/quality
-        \end{itemize}
-    \end{itemize}
-  \item What is this paper:
-    \begin{itemize}
-      \item 4 codes, 2 FD 2 FE
-      \item 2 models, simple one after MT paper, complex Marlim one
-    \end{itemize}
-  \item Outline of paper
-  \item Zenodo, provide all codes to reproduce the results.
-\end{itemize}
-
-~\\ \hrule
-
-There are many codes for EM - our focus here is on the application to
-controlled-source electromagnetic measurements, even though all of the codes
-can handle different setups too.
-
-in such fields as the modelling of communication systems (antennas, radar,
-satellites), medical imaging, and others.
-
-1D, 2D, we look at 3D.
-time domain and frequency domain
-
-Common methods in geophysics are the
-
-\begin{itemize}
-  \item integral equation (IE, \cite{GJI.74.Raiche, GEO.06.Zhdanov,
-    CAG.16.Kruglyakov}), (scattering equation) (anomalies in layered
-    background), computational effort comparably low
-  \item differential equation such as finite difference (FD \cite{IEEE.66.Yee,
-    GEO.93.Wang}), simple to implement
-  \item and finite volume (FV \cite{EM.90.Madsen, GEO.14.Jahandari}),
-  \item or and finite element (FE \cite{GEO.04.Commer GEO.09.Streich})
-    (approximating the DE on edges and nodals), good for complex geometries,
-  \item finite integration technique (FIT, \cite{AEU.77.Weiland},
-    \cite{PIER.01.Clemens}, \cite{GP.06.Mulder})
-\end{itemize}
-
-OctTree meshes or severe stretching \citep{ECP.07.Haber}
-
-Elmer FEM multiphysical simulation software P. Råback, P.-L. Forsström, M. Lyly
-and M. Gröhn, Elmer - finite element package for the solution of partial
-differential equations, poster presentation, EGEE User Forum, 2007, Manchester,
-UK. http://www.csc.fi/elmer
-
-Many commercial, e.g., COMSOL Multiphysics; EMGS, RSI, KMS; the oil and service
-companies.
-
-Consortia (CEMI; Key)
-
-Universities, e.g. Pottsdam (Streich, Grayver)
-
-Computational cost IE < FD < FV < FE
-
-Direct solvers vs indirect solvers, both its advantages and disadvantages;
-memory, various sources.
-
-Grids (regular grids, unstructured grids, Octree, tetrahedra, hexahedral,
-adaptive, multigrids).
-
-Boundary condition
+In the following section we introduce the codes under consideration. The
+numerical result consider two cases. First a layered background with vertical
+transverse isotropy containing three blocks, followed by a realistic, complex
+model.
 
@@
 
+Mention \cite{GJI.13.Miensopust}, which is a similar thing, but for 3D
+modelling and inversion for MT.
+
 Simple block (one to three blocks) model similar to \cite{GJI.13.Miensopust};
@@
 
+Custom meshes for these lines.
+
 \section{Discussion}
@@
 so. While before there were only closed-source codes owned by companies or
-consortia (e.g., CEMI), or codes that you had to obtain from the authors, often
+consortia, or codes that you had to obtain from the authors, often
 without much documentation, there was recently a wave of openly released codes.
+
+Points to discuss and mention
+\begin{itemize}
+  \item Direct solvers vs indirect solvers, both its advantages and
+    disadvantages; memory, various sources.
+\end{itemize}
 
@@
 so. While before there were only closed-source codes owned by companies or
-consortia (e.g., CEMI) there was recently a wave of openly released codes.
+consortia there was recently a wave of openly released codes.
 
@@
 
+\section{Data}
+
+All files to reproduce the shown results and more are available at
+\todo{zenodo}\dots.
+
 % REFERENCES

### 2020-04-09 manuscript/Manuscript.tex
Cleaning up code-section

@@
 % Remove once done
-\newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
-\newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
-\newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
+\newcommand{\mycom}[2][]{
+  \todo[]{\textbf{\uppercase{[#1]}}:~#2}}
+\newcommand{\imycom}[2][]{
+  \todo[inline]{\textbf{\uppercase{[#1]}}:~#2}}
 \newcommand{\dul}[1]{\underline{\underline{#1}}}
@@
 
-\itodo{
+\imycom[DW]{
+  For comments in the margin, use:\\[.2cm]
+  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
+  and for inline comments, use:\\[.2cm]
+  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}
+}
+
+\imycom[DW]{
 We will have to decide on a Journal. Current suggestions:\\
@@
 implementations of Maxwell's equations yield the same result it can give
-confidence in the accuracy.
+confidence in the accuracy. Providing these two models and results from four
+different codes should give a benchmark with which new codes can be compared
+and validated.
 
@@
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Codes}
 
-Intro to it; numerical approximations (FE, FD), differences in solvers,
-gridding/meshing, boundary conditions, etc.
+The four codes under consideration are, in alphabetical order, \custem
+\citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
+\citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
+codes have their user-facing routines written in Python, while the underlying
+heavy computation is mostly done in other languages (which is the normal case
+in the scientific Python stack); all of them make heavy use of \texttt{NumPy}
+\citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}. All are
+“modern” open-source projects, meaning that they not only come with open-source
+license, but they are also hosted in an online-hosted version-control system
+with feedback and tracking possibilities (raising issues, filing pull
+requests), have extensive online documentation including many examples, have
+continuous integration to some degree, and also importantly are all easily
+installable, without any user-side compilations.
 
-It is beyond the scope of this paper to go into every detail of the different
-modellers, however, a quick blabla...
+In the following a quick rundown of the codes. It is, however, beyond the scope
+of this article to go into every detail of the different modellers, and we
+refer to their references and documentation.
 
-All the codes presented here
-\begin{itemize}
-  \item are \emph{just available} (you don't have to write someone and ask if
-    you could have the code);
-  \item are \emph{easy installable} (through \texttt{pip} or \texttt{conda});
-  \item are under \emph{version control} and online either on GitHub or on
-    GitLab, which includes possibilities of easy involvement by either creating
-    an issue, reporting a bug, or filing a pull request; and
-  \item are well documented and come with a lot of examples.
-\end{itemize}
+\tabl[btp]{codecomparison}{Caption.}{
+  \centering
+  \small
+\begin{tabular}{lcccc}
+  \toprule
+  %
+  Code & \custem & \emg3d & \petgem & \simpeg  \\
+  \midrule
+  %
+  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
+       & \href{https://empymod.github.io}{empymod.github.io}
+       & \href{http://petgem.bsc.es}{petgem.bsc.es}
+       & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
+  Installation & \texttt{conda}
+               & \texttt{pip}; \texttt{conda}
+               & \texttt{pip}; \texttt{conda}
+               & \texttt{pip}; \texttt{conda} \\
+  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
+  Eq. system & ? & FIT & ? & ? \\
+  Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
+  Mesh & FE & FD & FE & FD; OcTree; CylMesh \\
+  BC & ? & PEC & ? & ? \\
+  Methods & ? & Diffusion & ? & ? \\
+  Solver & FEniCS$^\dagger$ & \emg3d & FEniCS$^\dagger$ &
+           PARDISO$^\ddagger$; SciPy \\
+  %
+  \bottomrule
+\end{tabular}}%
+%
+As is visible from Table~\ref{tbl:codecomparison}, we use two finite element
+codes and two finite difference codes; the finite element codes both make use
+of the FEniCS solver \citep{CSE.15.Alnaes}, whereas \simpeg can use either
+solvers implemented in SciPy, or the PARDISO solver \citep{FGCS.04.Schenk};
+\emg3d, on the other hand, is a solver on its own.
 
-\begin{itemize}
-  \item Code (license): \emg3d (Apache-2.0), custEM (LPGL-3.0), PETGEM
-    (GPL-3.0), and \simpeg (MIT).
-  \item Hosting: GitHub (\emg3d, \petgem, \simpeg); GitLab (\custem)
-\end{itemize}
-
-Each code should outline:
-
-\begin{itemize}
-  \item Equation system it solves;
-  \item the used discretization possibilities;
-  \item domains (frequency, time);
-  \item details (anisotropy; el. perm. and mag. perm.);
-  \item other things (inversion; other methods);
-  \item speed and memory estimation;
-  \item plans for next features.
-  \item Inversion capabilities
-  \item Time/frequency
-  \item transmitter types
-\end{itemize}
-
-Basically summarize each code in three points:
-\begin{itemize}
-  \item Brief intro and main features
-  \item Main selling point
-  \item Planned features
-\end{itemize}
-
-Cite for all: NumPy, SciPy.
-
-The codes under consideration are presented here in alphabetical order.
+\imycom[DW]{
+Each code should be briefly summarized by four points:\\
+- Brief intro and main features\\
+- Main selling point\\
+- Planned features\\
+- List (same list for all)\\
+}
 
 \subsection{custEM}
-
-\cite{GEO.19.Rochlitz}
-
-FEniCS \citep{CSE.15.Alnaes}
 
@@
 
-\cite{GJI.19.CastilloReyes}
-
-FEniCS \citep{CSE.15.Alnaes}
-
 \subsection{SimPEG}
 
-\cite{CAG.15.Cockett}
-
-PARDISO \citep{FGCS.04.Schenk}
-
+\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Comparison}
@@
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Discussion}
@@
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Conclusions}
@@
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Acknowledgment}
 
-\itodo{Write here your fundings; and potentially also minor contributors etc.}
+\imycom[DW]{Write here your fundings; and potentially also minor contributors etc.}
 
@@
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Data}
@@
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 % REFERENCES
-
 \bibliographystyle{Refs}          % Modified SEG bibliography style.

### 2020-04-09 manuscript/Manuscript.tex
Incorporate changes from Slack-chat

@@
 
-\tabl[btp]{codecomparison}{Caption.}{
+\tabl[btp]{codecomparison}{All codes solve Maxwell's Equations in its
+  differential form (DE) and with the quasistatic approximation. We use two
+  finite element codes and two finite difference codes; the finite element
+  codes both make use of the FEniCS solver \citep{CSE.15.Alnaes}, whereas
+  \simpeg can use either solvers implemented in SciPy or the PARDISO solver
+  \citep{FGCS.04.Schenk}; \emg3d, on the other hand, is a solver on its own.}{
   \centering
@@
   %
-  Code & \custem & \emg3d & \petgem & \simpeg  \\
+  & \custem & \emg3d & \petgem & \simpeg  \\
   \midrule
@@
   License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
-  Eq. system & ? & FIT & ? & ? \\
   Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
-  Mesh & FE & FD & FE & FD; OcTree; CylMesh \\
+  Method & FE & FIT & FE & FV \\
+  Mesh & tetrahedral & rectilinear & tetrahedral & rectilinear; curvilinear \\
   BC & ? & PEC & ? & ? \\
-  Methods & ? & Diffusion & ? & ? \\
   Solver & FEniCS$^\dagger$ & \emg3d & FEniCS$^\dagger$ &
@@
 %
-As is visible from Table~\ref{tbl:codecomparison}, we use two finite element
-codes and two finite difference codes; the finite element codes both make use
-of the FEniCS solver \citep{CSE.15.Alnaes}, whereas \simpeg can use either
-solvers implemented in SciPy, or the PARDISO solver \citep{FGCS.04.Schenk};
-\emg3d, on the other hand, is a solver on its own.
 

### 2020-04-10 manuscript/Manuscript.tex
Code section as draft

@@
 \usepackage{xspace}
+\usepackage{flafter}
 
@@
 %
-Write at the end; one or two sentence(s) each:
+\emph{A will draft a first abstract after the manuscript has been reviewed by
+everyone once.}
 %
-\begin{enumerate}
-  \item Principal OBJECTIVES AND SCOPE OF THE WORK
-  \item Methodology
-  \item Results
-  \item Conclusions
-\end{enumerate}
+% % Principal objectives and scope of the work
+% % Methodology
+% % Results
+% % Conclusions
 %
@@
 \citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
-codes have their user-facing routines written in Python, while the underlying
-heavy computation is mostly done in other languages (which is the normal case
-in the scientific Python stack); all of them make heavy use of \texttt{NumPy}
-\citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}. All are
-“modern” open-source projects, meaning that they not only come with open-source
-license, but they are also hosted in an online-hosted version-control system
-with feedback and tracking possibilities (raising issues, filing pull
-requests), have extensive online documentation including many examples, have
-continuous integration to some degree, and also importantly are all easily
-installable, without any user-side compilations.
+codes have their user-facing routines written in Python; all of them make heavy
+use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy}
+\citep{NM.20.Virtanen}. All are “modern” open-source projects, meaning that
+they not only come with an open-source license, but they are also in an
+online-hosted version-control system with feedback and tracking possibilities
+(raising issues, filing pull requests), have extensive online documentation
+including many examples, have continuous integration to some degree, and also
+importantly are all easily installable, without any user-side compilations.
 
@@
 of this article to go into every detail of the different modellers, and we
-refer to their references and documentation.
+refer to their documentations for more details. An overview comparison of the
+different codes is given in Tabel~\ref{tbl:codecomparison}. All codes have in
+common that they solve the Maxwell's equation in its differential form (DE)
+under the quasistatic or diffusive approximation, hence neglecting displacement
+currents.
 
-\tabl[btp]{codecomparison}{All codes solve Maxwell's Equations in its
-  differential form (DE) and with the quasistatic approximation. We use two
-  finite element codes and two finite difference codes; the finite element
-  codes both make use of the FEniCS solver \citep{CSE.15.Alnaes}, whereas
-  \simpeg can use either solvers implemented in SciPy or the PARDISO solver
-  \citep{FGCS.04.Schenk}; \emg3d, on the other hand, is a solver on its own.}{
+\tabl[btp]{codecomparison}{All codes solve Maxwell's equations in its
+  differential form (DE) under the quasistatic approximation. Note that
+  \emg3d is a solver on its own, while the other codes implement third-package
+  solvers such as PETSc, MUMPS, FEniCS \citep{CSE.15.Alnaes}, or PARDISO
+  \citep{FGCS.04.Schenk}.
+  \imycom[DW]{PETSc and MUMPS probably need citations too.}}{
   \centering
-  \small
+  \footnotesize
 \begin{tabular}{lcccc}
@@
        & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
+  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
   Installation & \texttt{conda}
@@
                & \texttt{pip}; \texttt{conda} \\
-  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
   Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
@@
   Mesh & tetrahedral & rectilinear & tetrahedral & rectilinear; curvilinear \\
-  BC & ? & PEC & ? & ? \\
-  Solver & FEniCS$^\dagger$ & \emg3d & FEniCS$^\dagger$ &
-           PARDISO$^\ddagger$; SciPy \\
+  BC & Dirichlet & PEC & Neumann; Dirichlet & Dirichlet; Neumann \\
+  Solver & PETSc; MUMPS & \emg3d & FEniCS & PARDISO; MUMPS \\
   %
@@
 \imycom[DW]{
-Each code should be briefly summarized by four points:\\
-- Brief intro and main features\\
+Each code should be briefly summarized by three points:\\
+- Brief intro\\
 - Main selling point\\
 - Planned features\\
-- List (same list for all)\\
+I think in a first round \textbf{everyone should just write what they want to
+write and think is important for their code}. In a second round we should then
+homogenize it, such that all codes have more or less the same length and also
+similar topic/layout.
 }
 
+\clearpage  % TODO: Just for now while drafting, remove later!
 \subsection{custEM}
@@
 
-The 3D CSEM modeller \emg3d \citep{JOSS.19.Werthmuller} is a multigrid
-\citep{CMMP.64.Fedorenko} solver for 3D electromagnetic diffusion following
-\cite{GP.06.Mulder}, with tri-axial electrical anisotropy and isotropic
-magnetic permeability. The matrix-free solver can be used as main solver or as
-preconditioner for one of the Krylov subspace methods implemented in SciPy
-\citep{NM.20.Virtanen}, and the governing equations are discretized on a
-staggered grid by the finite-integration technique \cite{AEU.77.Weiland}, which
-can be viewed as a finite-volume generalization of \cite{IEEE.66.Yee}'s scheme.
-The code is written completely in Python using the NumPy
-\citep{CSE.11.VanDerWalt} and SciPy stacks, where the most time- and
-memory-consuming parts are sped up through jitted functions using Numba
-\citep{LLVM.15.Lam}.
+The 3D CSEM modeller \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for
+3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial
+electrical anisotropy, isotropic electric permittivity, and isotropic magnetic
+permeability. The matrix-free solver can be used as main solver or as
+preconditioner for one of the Krylov subspace methods implemented in SciPy, and
+the governing equations are discretized on a staggered grid by the
+finite-integration technique \citep{AEU.77.Weiland}. The code is written
+completely in Python using the NumPy and SciPy stacks, where the most time- and
+memory-consuming parts are sped up through jitted (just-in-time compiled)
+functions using Numba \citep{LLVM.15.Lam}. The code computes the electric field
+due to an electric source in the frequency-domain. Implemented are functions to
+obtain the magnetic field due to an electric source; to obtain the electric and
+magnetic fields due to a magnetic source; and to obtain time-domain responses.
 
-The multigrid method is characterized by almost linear scaling both in terms
-of CPU usage and RAM, and it is therefore a comparably low-memory consumption
-solver (see results). However, the way multigrid is implemented also means some
-additional constraints on the chosen grid. You can input any three-dimensional
-grid into \emg3d, but the implemented method works with the existing nodes,
-meaning there are no new nodes created as coarsening is done by combining
-adjacent cells. The more times the grid dimension can be divided by two the
-better it is suited. Ideally, the dimension of the coarsest grid should be a
-low prime, and grid dimensions are therefore given by their multiplication with
-powers of two (${2,3,5}·2^n$).
-
-Currently \emg3d can be used to model the electric and magnetic fields due to
-arbitrary finite length electric dipole sources for a single frequency at a
-time. Helper functions to compute time-domain responses are in the works
-(should be ready by publishing this article). Current development is focused
-on adding inversion capabilities; averaging routines to implement strong
-topography; and general anisotropy.
-
-The 3D solver \emg3d can be found in the GitHub organization of \empymod
-(`empymod.github.io <https://empymod.github.io>`_). The modeller \empymod
-\citep{GEO.17.Werthmuller} is a 1D code which can compute electric or
-magnetic responses due to a 3D electric or magnetic source in a layered-earth
-model with vertical transverse isotropic (VTI) resistivity, VTI electric
-permittivity, and VTI magnetic permeability, from very low frequencies (DC) to
-very high frequencies (GPR).
-
-In the future it should be possible to use \emg3d as a solver within the
-\simpeg framework.
+The multigrid method is characterized by almost linear scaling both in terms of
+runtime (CPU) and memory (RAM) usage, and it is therefore a comparably
+low-memory consumption solver. It is also minimal in terms of requirements,
+only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
+development is focused on adding inversion capabilities. A further plan is also
+to implement a hook in order to use \emg3d as a solver for \simpeg.
 
@@
 \clearpage  % TODO: Just for now while drafting, remove later!
-\section{Comparison}
+\section{Verifications}
 
@@
 \section{Discussion}
+
+=> \textbf{Important point: Verification of existing and future codes: this is
+a start!}
 

### 2020-04-10 manuscript/Manuscript.tex
Figures for Block Model

@@
 
+In this numerical section compute the responses for two different models to
+verify that these different 3D codes yield the same electromagnetic responses.
+The first model is a simple one consisting of a layered, anisotropic
+background, in which three blocks are embedded, and the second model is a very
+complex, realistic model.
+
 \subsection{Block Model}
 
-Mention \cite{GJI.13.Miensopust}, which is a similar thing, but for 3D
-modelling and inversion for MT.
+\cite{GJI.13.Miensopust} published a review of two workshops dealing with the
+verification of magnetotelluric forward and inversion codes, hence a similar
+exercise to what we do here for CSEM codes. The block model is a derivation of
+the \emph{Dublin Test Model 1}, a model from their first workshop. We took the
+same layout of the blocks but adjusted the dimensions and resistivities to a
+typical, marine CSEM problem, as shown in Figure~\ref{fig:block-model}. We
+additionally added a layered background with vertical transverse isotropy
+(VTI).
 
-Simple block (one to three blocks) model similar to \cite{GJI.13.Miensopust};
-potentially with a bit a funkier source (say, finite length rotated bipole and
-finite length receivers). In this case I would only compare inline and
-crossline responses.
-
-\begin{itemize}
-  \item VTI resistivity
-  \item \simpeg => use OcTree for this example? That would be awesome!
-  \item Show Ex, Ey, Ez, Hx, Hy, Hz
-\end{itemize}
-
-Tables:
-
-%
-\tabl[btp]{comp1}{Caption.}{
-  \centering
-\begin{tabular}{lccrS[table-format=2.4]rl}
-  \toprule
-  %
-  Code & Method & Mesh & \#Cells & {CPU} & RAM & Computer \\
-  \midrule
-  %
-  \custem & FE  & FE & & & & \\
-  \emg3d  & FIT & FD & & & & \\
-  \petgem & FE  & FE & & & & \\
-  \simpeg & FD  & OcTree & & & & \\
-  %
-  \bottomrule
-\end{tabular}}%
-%
+\imycom[DW]{Next:\\
+  - Describe models in text\\
+  - Write text for layered and block model\\
+  - Start tables for them\\
+  - Move to Marlim\\
+  - Discussion\\
+  - Conclusions\\
+  - Send to Raphael
+}
 
@@
 \plot*{block-model}{width=.6\textwidth}{
-   Block model, consisting of a layered background, in which three blocks are
-   embedded.
+  Sketch of the block model. The layered model consists of an air layer, a
+  water layer, a thin top-layer and then a thick background layer, and at the
+  bottom a resistive basement layer. All three blocks are embedded in the thick
+  background layer, which has VTI with $\lambda=\sqrt{2}$.
+}
+%
+
+% %
+% \tabl[btp]{comp1}{Caption.}{
+%   \centering
+% \begin{tabular}{lccrS[table-format=2.4]rl}
+%   \toprule
+%   %
+%   Code & Method & Mesh & \#Cells & {CPU} & RAM & Computer \\
+%   \midrule
+%   %
+%   \custem & FE  & FE & & & & \\
+%   \emg3d  & FIT & FD & & & & \\
+%   \petgem & FE  & FE & & & & \\
+%   \simpeg & FD  & OcTree & & & & \\
+%   %
+%   \bottomrule
+% \end{tabular}}%
+% %
+
+%
+\plot*{results-layered-0}{width=\textwidth}{
+   Comparison of the layered model at y=0km.
 }
@@
 %
-\plot*{layered-result}{width=.6\textwidth}{
-   Comparison of the layered model.
+\plot*{results-layered--3}{width=\textwidth}{
+   Comparison of the layered model at y=-3km.
 }
@@
 %
-\plot*{block-result}{width=.6\textwidth}{
-   Comparison of the block model.
+\plot*{results-block--3}{width=\textwidth}{
+   Comparison of the block model at y=-3km.
 }
@@
 
+%
+\plot*{results-block-0}{width=\textwidth}{
+   Comparison of the block model at y=0km.
+}
+%
+
+%
+\plot*{results-block-3}{width=\textwidth}{
+   Comparison of the block model at y=+3km.
+}
+%
+
+\clearpage  % TODO: Just for now while drafting, remove later!
 \subsection{Marlim R3D}
@@
 
-\imycom[DW]{Write here your fundings; and potentially also minor contributors etc.}
+\imycom[DW]{Write here your fundings; and potentially also minor contributors
+etc.}
 
@@
 
-All files to reproduce the shown results and more are available at
-\todo{zenodo}\dots.
+All files to rerun the different models with the four codes and reproduce the
+shown results are available at \todo{zenodo}\dots.
 

### 2020-04-12 model-marlim/loadmarlim.py
Update Zenodo for computational Marlim model

@@ -8,10 +8,11 @@ mesh.
 
 Links to download:
 
-- Fine Model: https://doi.org/10.5281/zenodo.400233
-- Computation Model: ????????????
-- With noise: https://doi.org/10.5281/zenodo.1256787
-- Without noise: https://doi.org/10.5281/zenodo.1807135
+- Detailed resistivity model: https://doi.org/10.5281/zenodo.400233
+- Computational resistivity model (upscaled and extended):
+  https://doi.org/10.5281/zenodo.3748492
+- CSEM data with noise: https://doi.org/10.5281/zenodo.1256787
+- CSEM data without noise: https://doi.org/10.5281/zenodo.1807135
 """
 import segyio
 import discretize
@@ -34,8 +35,8 @@ def extract_model(model='orig'):
     """
 
     if model == 'comp':
-        name_h = 'novo_mrl3d_H_Z_meters.segy'
-        name_v = 'novo_mrl3d_Zmeters.segy'
+        name_h = 'Mrl3d_Rh_20metersmesh.segy'
+        name_v = 'Mrl3d_Rv_20metersmesh.segy'
         dx, dy, dz = 100, 100, 20  # Cell widths
     else:
         name_h = 'Horizontal_resistivity.sgy'
@@ -59,7 +60,7 @@ def extract_model(model='orig'):
         txt += f"{s}For model='comp' you need\n"
         txt += f"{s}- novo_mrl3d_H_Z_meters.segy\n"
         txt += f"{s}- novo_mrl3d_Zmeters.segy\n"
-        txt += f"{s}from ???????????\n"
+        txt += f"{s}from https://doi.org/10.5281/zenodo.3748492\n"
         print(txt)
         return None, None
 

### 2020-04-13 manuscript/Manuscript.tex
Draft Block Model

@@
 \newcommand{\rmk}[1]{{\color{red}{#1}}}
+\newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
 
@@
 \footnotemark[2]TODO\\
+\footnotemark[3]TODO\\
+\footnotemark[4]TODO\\
 E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
@@
 Raphael Rochlitz\footnotemark[2], %              orcid: 0000-0002-5132-916X
-Octavio Castillo-Reyes\footnotemark[2], and %    orcid: 0000-0003-4271-5015
-Lindsey Heagy\footnotemark[2] %                  orcid: 0000-0002-1551-5926
+Octavio Castillo-Reyes\footnotemark[3], and %    orcid: 0000-0003-4271-5015
+Lindsey Heagy\footnotemark[4] %                  orcid: 0000-0002-1551-5926
 }
@@
 %
-\emph{A will draft a first abstract after the manuscript has been reviewed by
+\emph{I will draft a first abstract after the manuscript has been reviewed by
 everyone once.}
@@
 refer to their documentations for more details. An overview comparison of the
-different codes is given in Tabel~\ref{tbl:codecomparison}. All codes have in
+different codes is given in Table~\ref{tbl:codecomparison}. All codes have in
 common that they solve the Maxwell's equation in its differential form (DE)
 under the quasistatic or diffusive approximation, hence neglecting displacement
-currents.
+currents. The machines on which the different codes were run are listed in
+Table~\ref{tbl:machines}, together with the responsible operator.
 
@@
   \emg3d is a solver on its own, while the other codes implement third-package
-  solvers such as PETSc, MUMPS, FEniCS \citep{CSE.15.Alnaes}, or PARDISO
-  \citep{FGCS.04.Schenk}.
-  \imycom[DW]{PETSc and MUMPS probably need citations too.}}{
+  solvers such as \texttt{PETSc}, \texttt{MUMPS}, \texttt{FEniCS}
+  \citep{CSE.15.Alnaes}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
+  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}}{
   \centering
   \footnotesize
-\begin{tabular}{lcccc}
+\begin{tabularx}{\linewidth}{lXXXX}
   \toprule
@@
   Method & FE & FIT & FE & FV \\
-  Mesh & tetrahedral & rectilinear & tetrahedral & rectilinear; curvilinear \\
-  BC & Dirichlet & PEC & Neumann; Dirichlet & Dirichlet; Neumann \\
-  Solver & PETSc; MUMPS & \emg3d & FEniCS & PARDISO; MUMPS \\
+  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
+  BC & PEC & PEC & Neumann; Dirichlet & Dirichlet; Neumann \\
+  Solver & \texttt{PETSc}; \texttt{MUMPS} & \emg3d & \texttt{FEniCS} &
+           \texttt{PARDISO}; \texttt{MUMPS} \\
   %
   \bottomrule
-\end{tabular}}%
+\end{tabularx}}%
 %
@@
 
+%
+\tabl[btp]{machines}{List of computer and operating system on which the
+  different codes were run, together with the operator.}{
+  \centering
+  \footnotesize
+  \begin{tabularx}{\linewidth}{lXl}
+  \toprule
+  %
+  Code & Computer and Operating System & Operator \\
+  \midrule
+  %
+  \custem & PowerEdge R940 server; 144 Xeon Gold 6154 CPU @2.666 GHz; ~3 TB
+            DDR4 RAM; Ubuntu 18.04
+          & Raphael Rochlitz \\
+  \emg3d  & Laptop; i7-6600U CPU@2.6 GHz x4; 16 GB of memory, Ubuntu 18.04
+          & Dieter Werthmüller \\
+  \petgem & Marenostrum4. Intel Xeon Platinum from Skylake generation; 2
+            sockets Intel Xeon Platinum 8160 CPU with 24 cores each @2.10GHz
+            for a total of 48 cores per node; 386 Gb DDR4 RAM per node; SuSE
+            Linux Enterprise
+          & Octavio Castillo-Reyes \\
+  \simpeg & ???
+          & Lindsey Heagy \\
+  %
+  \bottomrule
+\end{tabularx}}%
+%
+
 \clearpage  % TODO: Just for now while drafting, remove later!
@@
 
-In this numerical section compute the responses for two different models to
+In this numerical section we compute the responses for two different models to
 verify that these different 3D codes yield the same electromagnetic responses.
@@
 (VTI).
-
-\imycom[DW]{Next:\\
-  - Describe models in text\\
-  - Write text for layered and block model\\
-  - Start tables for them\\
-  - Move to Marlim\\
-  - Discussion\\
-  - Conclusions\\
-  - Send to Raphael
-}
-
 %
@@
 
-% %
-% \tabl[btp]{comp1}{Caption.}{
-%   \centering
-% \begin{tabular}{lccrS[table-format=2.4]rl}
-%   \toprule
-%   %
-%   Code & Method & Mesh & \#Cells & {CPU} & RAM & Computer \\
-%   \midrule
-%   %
-%   \custem & FE  & FE & & & & \\
-%   \emg3d  & FIT & FD & & & & \\
-%   \petgem & FE  & FE & & & & \\
-%   \simpeg & FD  & OcTree & & & & \\
-%   %
-%   \bottomrule
-% \end{tabular}}%
-% %
+The layered model consists of an upper halfspace of air, a 600\,m deep water
+layer, followed by a 150\,m thick, isotropic layer of 1\,\ohmm, a 3.3\,km
+thick, anisotropic layer of $\rho_\text{h}=2\,\ohmm$ and
+$\rho_\text{v}=4\,\ohmm$, and finally a resistive basement consisting of a
+lower halfspace of $1000\,\ohmm$. The 200\,m long, $x$-directed source is
+located 50\,m above the seafloor from $x=-50$ to $x=50\,$m in $x$-direction, at
+$y=0\,$m. The $x$-directed receivers are placed on the seafloor every 200\,m
+from $x=-10\,$km to $x=+10\,$km in three lines for $y=-3, 0, 3\,$km.
 
+In a first step we compare the layered background to the semi-analytical
+solutions of a 1D code, for which we use \empymod \citep{GEO.17.Werthmuller}.
+Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the
+actual responses in the top rows, and the relative error in the bottom rows
+for receiver line $y=0\,$km and $y=-3\,$km, respectively (for the layered
+background the responses for the two receiver-lines of $y=\pm3$\,km are
+identical, so we only show one here).
+
+Figure~\ref{fig:results-layered-0} shows in the top-row the inline responses
+for offsets $r>0.5\,$km. As all codes compute the same we only show the
+semi-analytical result for the real and imaginary amplitudes, and then in the
+bottom row the relative error of the 3D codes. The results show that the codes
+are literally yielding the same result, the relative error is for big parts
+below 1\,\%, and for almost all parts below a few percent. Some differences are
+due to the chosen discretizations. E.g., \emg3d is less precise close to the
+200\,m long source. This could be improved by choosing smaller cell sizes, at
+the cost of computation time. At large offsets, on the other hand, \emg3d seems
+to do a very good job.
 %
-\plot*{results-layered-0}{width=\textwidth}{
-   Comparison of the layered model at y=0km.
+\plot*{results-layered-0}{width=.8\textwidth}{
+   Comparison of the layered model for the inline receivers ($y=0\,$km).
+   Top row shows the semi-analytical responses from \empymod, and bottom row
+   show the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
+}
+%
+
+The corresponding broadside responses for $y=-3\,$km is shown in
+Figure~\ref{fig:results-layered--3}, and the required CPU and RAM is shown in
+Table~\ref{tbl:comp-layered}.
+%
+\plot*{results-layered--3}{width=.8\textwidth}{
+   Comparison of the layered model for the broadside receivers ($y=-3\,$km).
+   Top row shows the semi-analytical responses from \empymod, and bottom row
+   show the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
 }
@@
 %
-\plot*{results-layered--3}{width=\textwidth}{
-   Comparison of the layered model at y=-3km.
+\tabl[btp]{comp-layered}{Comparison of used CPU and RAM and of number of cells
+  used to discretize the layered model. \imycom[DW]{I will fill this table out
+  once we all submitted the final versions of the results.}}{
+  \centering
+\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+  \toprule
+  %
+  Code & {CPU} & \#Procs & RAM     & \#Cells \\
+       & {(s)} &         & {(GiB)} &         \\
+  \midrule
+  %
+  \custem & 0.0 & 24 & 0.0 & 0 \\
+  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
+  \petgem & 0.0 & 48 & 0.0 & 0 \\
+  \simpeg & 0.0 &    & 0.0 & 0 \\
+  %
+  \bottomrule
+\end{tabular}}%
+%
+
+Three resistive blocks are added in the 3.3\,km-thick, anisotropic background
+layer, as shown in Figure~\ref{fig:block-model}. They have resistivities of
+$\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines),
+$\rho=100\,\ohmm$ (thin plate, South-East), $\rho=500\,\ohmm$ (cube,
+North-West). As there are no analytical solutions for this model we show the
+normalized difference between different codes, instead of the relative error,
+where the normalized difference of two responses $p$ and $q$ is given by
+%
+\begin{equation}
+  \mr{NRMSD~(\%)} = 200 \frac{|p - q|}{|p| + |q|}\ .
+  \label{eq:nrmsd}
+\end{equation}
+%
+\imycom[DW]{NRMSD: Comparing all codes to all would make the
+figures too cluttered, and I don't think it would add a lot insights. My idea
+is therefore to compare \emg3d/\simpeg (the two FD ones), \custem/\petgem (the
+two FE ones), and \emg3d/\custem (a cross-comparison). What do you think?}
+
+The results for the three receiver lines $y=-3,0,3\,$km are shown in
+Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and
+\ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in
+Table~\ref{tbl:comp-block}. What we can conclude from the NRMSD is that similar
+codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are
+very similar, as well as are \custem and \petgem.
+\mycom[DW]{Write in detail when all results are available}
+%
+\plot*{results-block--3}{width=.8\textwidth}{
+   Comparison of the block model for the broadside receivers at $y=-3\,$km.
+   Top row shows the responses and bottom row the NRMSDs (\%)
+   between \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
 }
@@
 %
-\plot*{results-block--3}{width=\textwidth}{
-   Comparison of the block model at y=-3km.
+\plot*{results-block-0}{width=.8\textwidth}{
+   Comparison of the block model for the inline receivers at $y=0\,$km.
+   Top row shows the responses and bottom row the NRMSDs (\%)
+   between \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
 }
@@
 %
-\plot*{results-block-0}{width=\textwidth}{
-   Comparison of the block model at y=0km.
+\plot*{results-block-3}{width=.8\textwidth}{
+   Comparison of the block model for the broadside receivers at $y=+3\,$km.
+   Top row shows the responses and bottom row the NRMSDs (\%) between
+   \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
 }
@@
 %
-\plot*{results-block-3}{width=\textwidth}{
-   Comparison of the block model at y=+3km.
-}
+\tabl[btp]{comp-block}{Comparison of used CPU and RAM and of number of cells
+  used to discretize the block model. \imycom[DW]{I will fill this table out
+  once we all submitted the final versions of the results.}}{
+  \centering
+\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+  \toprule
+  %
+  Code & {CPU} & \#Procs & RAM     & \#Cells \\
+       & {(s)} &         & {(GiB)} &         \\
+  \midrule
+  %
+  \custem & 0.0 & 24 & 0.0 & 0 \\
+  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
+  \petgem & 0.0 & 48 & 0.0 & 0 \\
+  \simpeg & 0.0 &    & 0.0 & 0 \\
+  %
+  \bottomrule
+\end{tabular}}%
 %
@@
 \subsection{Marlim R3D}
+
+\imycom[DW]{Next:\\
+  - Create figures for Marlim\\
+  - Write text for Marlim\\
+  - Discussion\\
+  - Conclusions\\
+  - Send to Raphael
+}
 
@@
 Custom meshes for these lines.
+
+%
+\tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
+  used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
+  out once we all submitted the final versions of the results.}}{
+  \centering
+\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+  \toprule
+  %
+  Code & {CPU} & \#Procs & RAM     & \#Cells \\
+       & {(s)} &         & {(GiB)} &         \\
+  \midrule
+  %
+  \custem & 0.0 & 24 & 0.0 & 0 \\
+  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
+  \petgem & 0.0 & 48 & 0.0 & 0 \\
+  \simpeg & 0.0 &    & 0.0 & 0 \\
+  %
+  \bottomrule
+\end{tabular}}%
+%
 

### 2020-04-14 model-marlim/loadmarlim.py
Start figures Marlim

@@ -96,6 +96,57 @@ def extract_model(model='orig'):
     )
 
 
+def extract_section():
+    """Extract original or computational model of Marlim R3D and store as npz.
+
+    Extracts the original fine model or the computational model from the
+    sgy-fiels and stores them as numpy-compressed npz files.
+
+    Parameters
+    ----------
+    model : str; {<'orig'>; 'comp'}
+        If model=='comp', the computational model is returned. Else the
+        original model.
+    """
+
+    # Get original mesh and resistivities.
+    try:
+        data = np.load('marlim_orig.npz')
+    except:
+        extract_model(model='orig')
+        data = np.load('marlim_orig.npz')
+
+    full_res_h = data['res_h']
+    full_res_v = data['res_v']
+    mesh = discretize.TensorMesh(
+            [data['hx'], data['hy'], data['hz']], x0=data['x0'])
+    del data
+
+    # Get chosen data and extract the y-coordinate; find corresponding index.
+    try:
+        data = xr.load_dataset('marlim_data.nc', engine='h5netcdf')
+    except:
+        create_survey(store_data=True, noise=False)
+        data = xr.load_dataset('marlim_data.nc', engine='h5netcdf')
+
+    ycoord = data.attrs['rec_y']
+    ny = np.argmin(abs(mesh.vectorCCy - ycoord))
+    del data
+
+    # Store relevant sections.
+    res_h = full_res_h[:, ny, :]
+    res_v = full_res_v[:, ny, :]
+    del full_res_h, full_res_v
+
+    # Save it.
+    np.savez_compressed(
+            f"marlim_sections.npz",
+            hx=mesh.hx, hy=np.array([10]), hz=mesh.hz,
+            x0=np.array([mesh.x0[0], ycoord-5, mesh.x0[2]]),
+            res_h=res_h, res_v=res_v
+    )
+
+
 def load_data(noise=False):
     """Load CSEM data for our selected source and receiver positions.
 

### 2020-04-15 manuscript/Manuscript.tex
Include comments Raphael

@@
   \emg3d is a solver on its own, while the other codes implement third-package
-  solvers such as \texttt{PETSc}, \texttt{MUMPS}, \texttt{FEniCS}
-  \citep{CSE.15.Alnaes}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
-  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}}{
+  solvers such as \texttt{PETSc}, \texttt{MUMPS}, or \texttt{PARDISO}
+  \citep{FGCS.04.Schenk}.
+  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
+  \imycom[DW]{PEC/PMC instead of Dirichlet/Neumann?}
+}{
   \centering
@@
   License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
-  Installation & \texttt{conda}
+  Installation & \texttt{pip}; \texttt{conda}
                & \texttt{pip}; \texttt{conda}
-               & \texttt{pip}; \texttt{conda}
+               & \texttt{conda}
                & \texttt{pip}; \texttt{conda} \\
-  Comp. Dom. & frequency & frequency & frequency & frequency \& time \\
+  Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
   Method & FE & FIT & FE & FV \\
   Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
-  BC & PEC & PEC & Neumann; Dirichlet & Dirichlet; Neumann \\
-  Solver & \texttt{PETSc}; \texttt{MUMPS} & \emg3d & \texttt{FEniCS} &
+  BC & Neumann; Dirichlet & PEC & PEC & Dirichlet; Neumann \\
+  Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
            \texttt{PARDISO}; \texttt{MUMPS} \\
@@
 \subsection{custEM}
+
+\texttt{FEniCS} \citep{CSE.15.Alnaes}
 
@@
 
+\paragraph{Comments Raphael} “\emph{Yes, cutting the layers has an influce at
+  offsets greater distance X (see example \#2 thesis) - depending on the
+  boundary mesh. I'm sure that's the reason. I could also add a version with a
+  way larger horizontal layered earth extent, but this would require way more
+  resources - unstructured meshes are just not competitive to regular grids for
+  regular geopmetries in such cases as discussed before}“
+
 %

### 2020-04-16 manuscript/Manuscript.tex
small things

@@
 GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, finite volume
-(FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari}, and finite
-integration technique (FIT) \citep{PIER.01.Clemens, GP.06.Mulder}. And these
-are just the most common ones.
+(FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari, PIER.01.Clemens,
+GP.06.Mulder}. And these are just the most common ones.
 
@@
   Comp. Dom. & frequency \& time & frequency & frequency & frequency \& time \\
-  Method & FE & FIT & FE & FV \\
+  Method & FE & FV & FE & FV \\
   Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
@@
 
+The difference becomes only significant at offsets larger than 8\,km. However,
+this is due to a practical difference in the meshing: \textbf{Rewrite, Comments
+Raphael} “\emph{Yes, cutting the layers has an influce at offsets greater
+  distance X (see example \#2 thesis) - depending on the boundary mesh. I'm
+  sure that's the reason. I could also add a version with a way larger
+  horizontal layered earth extent, but this would require way more resources -
+  unstructured meshes are just not competitive to regular grids for regular
+geopmetries in such cases as discussed before}“
+
 \clearpage  % TODO: Just for now while drafting, remove later!
@@
 Custom meshes for these lines.
-
-\paragraph{Comments Raphael} “\emph{Yes, cutting the layers has an influce at
-  offsets greater distance X (see example \#2 thesis) - depending on the
-  boundary mesh. I'm sure that's the reason. I could also add a version with a
-  way larger horizontal layered earth extent, but this would require way more
-  resources - unstructured meshes are just not competitive to regular grids for
-  regular geopmetries in such cases as discussed before}“
 

### 2020-04-27 manuscript/Manuscript.tex
Re-work up before Marlim; next Marlim

@@
 I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
-are the favoured currently. I personally would be very interested in GMD. What
-do you think? Also interesting would be the GJI, because the MT comparison was
-published there, so it would be in the same place.
+were the favourite ones when we discussed it ones. I personally would be very
+interested in GMD. What do you think? But also interesting would be the GJI,
+because the MT comparison was published there, so it would be in the same
+place.
 }
@@
 \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
-CAG.13.Sommer}, finite elementes (FE) \citep{GJI.11.Schwarzbach, GEO.04.Commer,
-GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, finite volume
-(FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari, PIER.01.Clemens,
-GP.06.Mulder}. And these are just the most common ones.
+CAG.13.Sommer}, and finite elementes (FE) \citep{GJI.11.Schwarzbach,
+GEO.04.Commer, GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang},
+finite volume (FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari,
+PIER.01.Clemens, GP.06.Mulder}. And these are just the most common ones.
 
@@
 GEO.15.Grayver, GP.14.Chung, GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect
-solvers \citep{GP.06.Mulder, GJI.15.Jaysaval} or a combination of both,
+solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both,
 so-called hybrid solvers \citep{GEO.18.Liu}; the solvers often use
@@
 A very well written overview up to the year 2005 of the different approaches to
-3D EM modelling is given by \cite{SG.05.Avdeev}. In the last 15 years the
-publications with regards to 3D EM  modelling grew tremendously, driven
-by the ever increasing computing power. Avdeev finished his review with the
-following statement: «\emph{The most important challenge that faces the EM
-community today is to convince software developers to put their 3-D EM forward
-and inverse solutions into the public domain, at least after some time. This
-would have a strong impact on the whole subject and the developers would
-benefit from feedback regarding the real needs of the end-users.}»
+3D EM modelling is given by \cite{SG.05.Avdeev}, and also by
+\cite{SG.10.Borner}. In the last 15 years the publications with regards to 3D
+EM  modelling grew tremendously, driven by the ever increasing computing power.
+Avdeev finished his review with the following statement: «\emph{The most
+important challenge that faces the EM community today is to convince software
+developers to put their 3-D EM forward and inverse solutions into the public
+domain, at least after some time. This would have a strong impact on the whole
+subject and the developers would benefit from feedback regarding the real needs
+of the end-users.}»
 
@@
 research groups have their 3D CSEM codes. But how about codes that are
-open-source? Traditionally research code was often available upon request by
+open-source? Research code was traditionally often available upon request by
 the author. Codes distributed that way often come with the request to not share
-the code, or they often come without a license attached at all (which means
-that they are not open-source). Also, at times there can be a significant
-hurdle to install a code. However, the meaning of open-source evolved rapidly
-in the last decades. Today, open-source generally not only means that a code is
-available (with a proper license). It includes much more today, such as that
-the code is hosted online, is under version control, has the possibility to
-file issues and make pull requests to fix bugs. Well maintained codes often
-have continuous integration that includes testing of the code base and online
-hosted documentation. As such the term has shifted from purely open-source code
-to development in the open and increasingly building a global community. There
-are a number of projects within the realm of geophysical exploration, besides
-the ones we present here, \todo{Others coming to your mind?}e.g. pyGIMLi
-\citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer \todo{wrong
-term, think about it}programming environments  have also brought much
-simplifications in the installation process and have most importantly
+the code, and they often come without a license attached at all (which means
+that they are not open-source). Also, at times there can be significant hurdles
+to install a code. However, the meaning of open-source evolved rapidly in the
+last decades. Today, open-source generally not only means that a code is
+available (with a proper license). The meaning includes much more these days,
+such as that the code is hosted online, is under version control, has the
+possibility to file issues and make pull requests to fix bugs. Well maintained
+codes often have continuous integration that includes testing of the code base
+and online hosted documentation which often includes code documentation,
+examples, and tutorials. As such the term has shifted from purely open-source
+code to development in the open and increasingly building a global community.
+There are a number of projects within the realm of geophysical exploration,
+besides the ones we present here, \todo{Others coming to your mind?}e.g.
+pyGIMLi \citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer
+\todo{wrong term, think about it}programming environments  have also brought
+much simplifications in the installation process and have most importantly
 simplified it for code developers to make their codes easily available and
@@
 confidence in the accuracy. Providing these two models and results from four
-different codes should give a benchmark with which new codes can be compared
-and validated.
+different codes should give a benchmark with which new codes can be compared to
+and validated with.
 
@@
 just a poster). While these codes could potentially be used for the same goals
-as presented here we restrict our review to codes purpose-built for geophysical
-applications.
+as presented here we restrict our review to codes purpose-built, and ready
+without further adjustments, for geophysical applications.
 
@@
 transverse isotropy containing three blocks, followed by a realistic, complex
-model.
+3D model.
 
@@
 use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy}
-\citep{NM.20.Virtanen}. All are “modern” open-source projects, meaning that
-they not only come with an open-source license, but they are also in an
-online-hosted version-control system with feedback and tracking possibilities
-(raising issues, filing pull requests), have extensive online documentation
-including many examples, have continuous integration to some degree, and also
-importantly are all easily installable, without any user-side compilations.
+\citep{NM.20.Virtanen}. The four of them are “modern” open-source projects,
+meaning that they not only come with an open-source license, but they are also
+in an online-hosted version-control system with feedback and tracking
+possibilities (raising issues, filing pull requests), have extensive online
+documentation including many examples, have continuous integration to some
+degree, and also importantly are all easily installable, without any user-side
+compilations.
 
@@
 different codes is given in Table~\ref{tbl:codecomparison}. All codes have in
-common that they solve the Maxwell's equation in its differential form (DE)
-under the quasistatic or diffusive approximation, hence neglecting displacement
-currents. The machines on which the different codes were run are listed in
-Table~\ref{tbl:machines}, together with the responsible operator.
+common that they solve the\mycom[DW]{are we all using the weak form?} weak
+formulation of Maxwell's equation in its differential form (DE) under the
+quasistatic or\mycom[DW]{are we all using the diff. approx?} diffusive
+approximation, hence neglecting displacement currents. The machines on which
+the different codes were run are listed in Table~\ref{tbl:machines}, together
+with the responsible operator.
 
-\tabl[btp]{codecomparison}{All codes solve Maxwell's equations in its
-  differential form (DE) under the quasistatic approximation. Note that
+\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
+  in its differential form (DE) under the quasistatic approximation. Note that
   \emg3d is a solver on its own, while the other codes implement third-package
@@
   \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
-  \imycom[DW]{PEC/PMC instead of Dirichlet/Neumann?}
 }{
@@
   Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
-  BC & Neumann; Dirichlet & PEC & PEC & Dirichlet; Neumann \\
+  BC & PMC; PEC & PEC & PEC & PEC; PMC \\
   Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
@@
 
-\imycom[DW]{
-Each code should be briefly summarized by three points:\\
-- Brief intro\\
-- Main selling point\\
-- Planned features\\
-I think in a first round \textbf{everyone should just write what they want to
-write and think is important for their code}. In a second round we should then
-homogenize it, such that all codes have more or less the same length and also
-similar topic/layout.
-}
-
-\clearpage  % TODO: Just for now while drafting, remove later!
-\subsection{custEM}
-
-\texttt{FEniCS} \citep{CSE.15.Alnaes}
-
-\subsection{emg3d}
-
-The 3D CSEM modeller \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for
-3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial
-electrical anisotropy, isotropic electric permittivity, and isotropic magnetic
-permeability. The matrix-free solver can be used as main solver or as
-preconditioner for one of the Krylov subspace methods implemented in SciPy, and
-the governing equations are discretized on a staggered grid by the
-finite-integration technique \citep{AEU.77.Weiland}. The code is written
-completely in Python using the NumPy and SciPy stacks, where the most time- and
-memory-consuming parts are sped up through jitted (just-in-time compiled)
-functions using Numba \citep{LLVM.15.Lam}. The code computes the electric field
-due to an electric source in the frequency-domain. Implemented are functions to
-obtain the magnetic field due to an electric source; to obtain the electric and
-magnetic fields due to a magnetic source; and to obtain time-domain responses.
-
-The multigrid method is characterized by almost linear scaling both in terms of
-runtime (CPU) and memory (RAM) usage, and it is therefore a comparably
-low-memory consumption solver. It is also minimal in terms of requirements,
-only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
-development is focused on adding inversion capabilities. A further plan is also
-to implement a hook in order to use \emg3d as a solver for \simpeg.
-
-\subsection{PETGEM}
-
-\subsection{SimPEG}
-
 %
-\tabl[btp]{machines}{List of computer and operating system on which the
-  different codes were run, together with the operator.}{
+\tabl[btp]{machines}{List of computer and operating system (hardware and
+software) on which the different codes were run, together with the operator.}{
   \centering
@@
 
+\imycom[DW]{
+Each code should be briefly summarized by three points:\\
+- Brief intro\\
+- Main selling point\\
+- Planned features\\
+I think in a first round \textbf{everyone should just write what they want to
+write and think is important for their code}. In a second round we should then
+homogenize it, such that all codes have more or less the same length/weight and
+also similar topic/layout.
+}
+
 \clearpage  % TODO: Just for now while drafting, remove later!
-\section{Verifications}
+\subsection{custEM}
+
+TODO (\texttt{FEniCS}; \cite{CSE.15.Alnaes})
+
+\subsection{emg3d}
+
+The 3D CSEM modeller \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for
+3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial
+electrical anisotropy, isotropic electric permittivity, and isotropic magnetic
+permeability. The matrix-free solver can be used as main solver or as
+preconditioner for one of the Krylov subspace methods implemented in SciPy, and
+the governing equations are discretized on a staggered grid by the
+finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume
+generalization of a Yee grid. The code is written completely in Python using
+the NumPy and SciPy stacks, where the most time- and memory-consuming parts are
+sped up through jitted (just-in-time compiled) functions using Numba
+\citep{LLVM.15.Lam}. The code computes the electric field due to an electric
+source in the frequency-domain. Implemented are functions to obtain the
+magnetic field due to an electric source; to obtain the electric and magnetic
+fields due to a magnetic source; and to obtain time-domain responses.
+
+The multigrid method is characterized by almost linear scaling both in terms of
+runtime (CPU) and memory (RAM) usage, and it is therefore a comparably
+low-memory consumption solver. It is also minimal in terms of requirements,
+only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
+development is focused on adding inversion capabilities. A further plan is also
+to implement a hook in order to use \emg3d as a solver within the \simpeg
+framework.
+
+\subsection{PETGEM}
+
+TODO
+
+\subsection{SimPEG}
+
+TODO
+
+\clearpage  % TODO: Just for now while drafting, remove later!
+\section{Numerical Verifications}
 
@@
   Sketch of the block model. The layered model consists of an air layer, a
-  water layer, a thin top-layer and then a thick background layer, and at the
-  bottom a resistive basement layer. All three blocks are embedded in the thick
-  background layer, which has VTI with $\lambda=\sqrt{2}$.
+  water layer, a thin top-layer followed by a thick, anisotropic background
+  layer, and at the bottom a resistive basement layer. All three blocks are
+  embedded in the thick background layer, which has VTI with
+  $\lambda=\sqrt{2}$.
 }
@@
    Top row shows the semi-analytical responses from \empymod, and bottom row
-   show the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
+   shows the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
 }
@@
   %
-  \custem & 0.0 & 24 & 0.0 & 0 \\
-  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
-  \petgem & 0.0 & 48 & 0.0 & 0 \\
-  \simpeg & 0.0 &    & 0.0 & 0 \\
+  \custem & 0.0 &  0 & 0.0 & 0 \\
+  \emg3d  & 0.0 &  0 & 0.0 & 0 \\
+  \petgem & 0.0 &  0 & 0.0 & 0 \\
+  \simpeg & 0.0 &  0 & 0.0 & 0 \\
   %
@@
 figures too cluttered, and I don't think it would add a lot insights. My idea
-is therefore to compare \emg3d/\simpeg (the two FD ones), \custem/\petgem (the
+is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the
 two FE ones), and \emg3d/\custem (a cross-comparison). What do you think?}
@@
 The difference becomes only significant at offsets larger than 8\,km. However,
-this is due to a practical difference in the meshing: \textbf{Rewrite, Comments
-Raphael} “\emph{Yes, cutting the layers has an influce at offsets greater
-  distance X (see example \#2 thesis) - depending on the boundary mesh. I'm
-  sure that's the reason. I could also add a version with a way larger
-  horizontal layered earth extent, but this would require way more resources -
-  unstructured meshes are just not competitive to regular grids for regular
-geopmetries in such cases as discussed before}“
+this is due to a practical difference in the meshing: This simple block model
+is advantageous for FV codes, as it consists of rectangular blocks and
+horizontal layers, simple geometric objects. While having a very thin, shallow
+layer is straight-forward for FV codes, it requires many cells for a FE code.
+The thin layer was therefore limited in its horizontal extent
+to\mycom[DW]{Raphael, to what x/y?} ???. This is the reason for the increased
+NRMSD at large offsets, and it has nothing to do with the accuracy of the
+computation itself.
 

### 2020-04-28 manuscript/Manuscript.tex
First Marlim figures

@@
 %
+\plot*{model-marlim}{width=\textwidth}{
+  Needs improvements.
+}
+%
+
+%
+\plot*{results-marlim}{width=\textwidth}{
+  This is one heck of a figure. Just an idea, please make suggestions how to
+  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
+  data is a copy of \emg3d data).
+}
+%
+
+%
 \tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
@@
 
+The three meaningful responses for node-based marine CSEM: Inline Ex and
+Broadside Ex and Ey.
+
 \clearpage  % TODO: Just for now while drafting, remove later!
 \section{Discussion}
+
+\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
+and Conclusion collaboratively at the same time?}
 

### 2020-05-05 manuscript/Manuscript.tex

--- 2020-04-27 manuscript/Manuscript.tex
@@
 \newcommand{\mycom}[2][]{
-  \todo[]{\textbf{\uppercase{[#1]}}:~#2}}
+  \todo[color=yellow]{\textbf{\uppercase{[#1]}}:~#2}}
 \newcommand{\imycom}[2][]{
-  \todo[inline]{\textbf{\uppercase{[#1]}}:~#2}}
+  \todo[inline, color=yellow]{\textbf{\uppercase{[#1]}}:~#2}}
+\newcommand{\itodo}[1]{\todo[inline, color=cyan]{\sffamily #1}}
 \newcommand{\dul}[1]{\underline{\underline{#1}}}
@@
 
-\imycom[DW]{
+\itodo{
   For comments in the margin, use:\\[.2cm]
@@
 
-\imycom[DW]{
+\itodo{
 We will have to decide on a Journal. Current suggestions:\\
@@
 because the MT comparison was published there, so it would be in the same
-place.
+place. I just had a very bad experience with GP, so I am not inclined on that
+at all.
 }
@@
 There are a number of projects within the realm of geophysical exploration,
-besides the ones we present here, \todo{Others coming to your mind?}e.g.
+besides the ones we present here, \mycom[DW]{Others coming to your mind?}e.g.
 pyGIMLi \citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer
-\todo{wrong term, think about it}programming environments  have also brought
-much simplifications in the installation process and have most importantly
-simplified it for code developers to make their codes easily available and
-installable. All our presented codes are in the Python ecosystem, and each code
-can be installed with a single command (which includes downloading and
-installation).
+\mycom[DW]{wrong term, think about it}programming environments  have also
+brought much simplifications in the installation process and have most
+importantly simplified it for code developers to make their codes easily
+available and installable. All our presented codes are in the Python ecosystem,
+and each code can be installed with a single command (which includes download
+and installation).
 
@@
 fields than geophysics such as communication systems (antennas, radar,
-satellites), medical imaging. There are various open-source codes in these
-fields \todo{Add at least three references} too, e.g., Elmer
-(\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication,
-just a poster). While these codes could potentially be used for the same goals
-as presented here we restrict our review to codes purpose-built, and ready
-without further adjustments, for geophysical applications.
+satellites), medical imaging, or civil engineering. There are various
+open-source codes in these fields too, e.g., Elmer \mycom[DW]{Add 2-3 proper
+references} (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a
+publication, just a poster). While these codes could potentially be used for
+the same goals as presented here we restrict our review to codes purpose-built,
+and ready without further adjustments, for geophysical applications.
 
@@
   \emg3d is a solver on its own, while the other codes implement third-package
-  solvers such as \texttt{PETSc}, \texttt{MUMPS}, or \texttt{PARDISO}
-  \citep{FGCS.04.Schenk}.
-  \imycom[DW]{\texttt{PETSc} and \texttt{MUMPS} probably need citations too.}
+  solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS}
+  \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
 }{
@@
 
-\imycom[DW]{
+\itodo{
 Each code should be briefly summarized by three points:\\
@@
 
-TODO (\texttt{FEniCS}; \cite{CSE.15.Alnaes})
+TODO
 
@@
 \citep{LLVM.15.Lam}. The code computes the electric field due to an electric
-source in the frequency-domain. Implemented are functions to obtain the
-magnetic field due to an electric source; to obtain the electric and magnetic
-fields due to a magnetic source; and to obtain time-domain responses.
+source in the frequency-domain, which is its main application (frequency-domain
+CSEM). However, there are also routines to obtain the magnetic field due to an
+electric source, to obtain the electric and magnetic fields due to a magnetic
+source, and to obtain time-domain responses.
 
@@
 only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
-development is focused on adding inversion capabilities. A further plan is also
-to implement a hook in order to use \emg3d as a solver within the \simpeg
-framework.
+development is focused on adding basic inversion capabilities, and a further
+plan is to implement a hook in order to use \emg3d as a frequency-domain CSEM
+solver within the grander \simpeg framework.
 
@@
 The thin layer was therefore limited in its horizontal extent
-to\mycom[DW]{Raphael, to what x/y?} ???. This is the reason for the increased
-NRMSD at large offsets, and it has nothing to do with the accuracy of the
-computation itself.
+to\mycom[DW]{Raphael, to what x/y exactly?} ???. This is the reason for the
+increased NRMSD at large offsets, and it has nothing to do with the accuracy of
+the computation itself.
 
@@
 
-\imycom[DW]{Next:\\
-  - Create figures for Marlim\\
-  - Write text for Marlim\\
-  - Discussion\\
-  - Conclusions\\
-  - Send to Raphael
+The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
+the north-eastern part of the Campos Basin, offshore Brazil, which was
+discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
+log data a realistic resistivity model with vertical transverse isotropy (VTI),
+Marlim R3D (MR3D), which they released under an open-source license. Using this
+model \cite{GEO.19.Correa} computed CSEM data for six frequencies from
+0.125\,Hz to 1.25\,Hz, which they also released under an open-source license.
+To compute the data they used a state-of-the-art code from the industry
+\citep{GEO.07.Maao}. It is therefore an ideal case to verify our open-source
+codes against, as it is a complex, realistic model, and the data were computed
+by an industry-proofed code. Additionally, that code is a time-domain code,
+whereas the four codes under consideration here compute the results all in the
+frequency-domain.
+
+The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling
+to almost 466 million cells, where each cell has dimensions of 25 by 75 by
+5\,m. For the computation the model is upscaled to 515 by 563 by 310 cells,
+totalling to almost 90 million cells, where each cell has dimensions of 100 by
+100 by 20\,m.
+
+The published data set consists of a regular grid of receivers of 20 in
+eastern direction by 25 in northern direction, 500 receivers in total, with
+1\,km spacing located on the irregular seafloor. 45 source-towlines were
+located on the same grid, 50\,m above the seafloor, with shots every 100\,m. In
+\cite{GEO.19.Correa} the actual responses for one receiver with the
+corresponding East-West inline and one East-West broadside acquisition line are
+shown, which is the data we chose for our comparison. The cross-section of the
+resistivity model along the chosen inline acquisition line is shown in
+Figure~\ref{fig:model-marlim}, together with the acquisition information.
+%
+\plot*{model-marlim}{width=\textwidth}{
+  This figure obviously needs to be improved massively (at least a colorbar).
+  What would you like to show from the actual data here?
+  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
+  the drawn survey line in that figure are plainly wrong. If someone is
+  familiar with GMT and happy to make a make that would be great. Also, the
+  cross-section is currently heavily vertically exaggerated.
 }
+%
 
-The Marlim R3D model is a \dots \cite{BJG.17.Carvalho} (model)
-\cite{GEO.19.Correa} (CSEM data)
+We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$)
+for both inline and broadside acquisition lines. However, we show here only
+the three frequencies and the responses with the strongest amplitudes (which
+are generally used in processing), which are $E_x$ inline and broadside and
+$E_y$ broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
+%
+\plot*{results-marlim}{width=\textwidth}{
+  This is one heck of a figure. Just an idea, please make suggestions how to
+  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
+  data is a copy of \emg3d data).
+}
+%
 
-Comparison to an code from the industry, using \emph{SBLwiz} from EMGS.
-
-Custom meshes for these lines.
+\imycom[DW]{There are some interesting features we should highlight. But again,
+we first need all results. E.g.}
+\begin{itemize}
+  \item 0.125\,Hz: on the left side, \custem and \emg3d are almost identical,
+    but very different from MR3D. So there I actually trust more our
+    calculation, or there is a difference in the model that we did not take
+    into account.
+  \item 0.125\,Hz: on the right side, \custem is very similar to MR3D, whereas
+    \emg3d is off.
+  \item 0.125\,Hz and 0.5\,Hz: on the right side, \custem seems to very similar
+    to MR3D.
+\end{itemize}
 
@@
 \section{Discussion}
+%
+% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
+%
+% In order to make your discussion section engaging, you should include the
+% following information:
+% - The major findings of your study
+% - The meaning of those findings
+% - How these findings relate to what others have done
+% - Limitations of your findings
+% - An explanation for any surprising, unexpected, or inconclusive results
+% - Suggestions for further research
+%
+% Your discussion should NOT include any of the following information:
+% - New results or data not presented previously in the paper
+% - Unwarranted speculation
+% - Tangential issues
+% - Conclusions not supported by your data
+%
 
-=> \textbf{Important point: Verification of existing and future codes: this is
-a start!}
+\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
+collaboratively at the same time?}
 
-The landscape in 3D CSEM modelling greatly changed in the last five years or
-so. While before there were only closed-source codes owned by companies or
-consortia, or codes that you had to obtain from the authors, often
-without much documentation, there was recently a wave of openly released codes.
+We compared four different, open-source 3D CSEM modellers by computing
+responses for (a) a layered, anisotropic model without and with three resistive
+blocks, and (b) a realistic 3D model. The comparison shows that the codes do
+yield the same responses. As such we could verify the accuracy of these four
+codes.
 
-Points to discuss and mention
-\begin{itemize}
-  \item Direct solvers vs indirect solvers, both its advantages and
-    disadvantages; memory, various sources.
-\end{itemize}
+This is a very important insight. The possibilities to verify the accuracy of
+3D CSEM codes are limited. One can compare them to analytical and
+semi-analytical solutions, but they only exist for very simple models. For
+complex models comparisons to other codes is the only possibility.
+It is therefore really important to have more test models, and importantly, for
+various scenarios, and that they are easily accessible. Our data should also
+make it very easy for new codes to have a readily available data set to test
+against and verify.
 
-\dots
+A similar exercise has be done for magnetotelluric (MT) 3D modelling and
+inversion by \cite{GJI.13.Miensopust}, but we are not aware of anything like
+this for CSEM data. However, we do hope that more comparisons will emerge in
+the future, particularly with the current increase in open-source codes as well
+as open-source data.
+
+The codes under consideration consisted of finite element and finite
+differences. However, it has to be noted that the chosen models are better
+suited for finite differences codes. The first model for obvious reasons, as it
+is a layered background containing blocks, all aligned in Cartesian
+coordinates. The second model, Marlim R3D, could be an ideal case for FE codes,
+as it comes with lithological horizons from seismic data. However, the
+corresponding, published resistivity model uses a Cartesian grid. An extension
+of this work could be to use a complex model tailored for a FE code, and
+compare how the FD codes cope with it.
+
+The codes under consideration use direct and indirect solvers, \dots blabla say
+something. Having calculated in each model only one source favours in the
+runtime comparison the iterative solver and therefore \emg3d. For the iterative
+solvers additional sources would come at almost no cost, whereas for \emg3d it
+would come at the same cost as the first source. This is something to keep in
+mind when choosing the appropriate modeller for a problem at hand.
+
+\imycom[DW]{I would like to capture as many as possible of the (I) differences,
+(II) difficulties, (III) advantages, and (IV) disadvantages, that we
+encountered in this exercise. This includes differences from direct to
+iterative solver and differences from FE to FD codes etc. Please just jot down
+things that come to your mind.}
+
+Finally, the comparison in our study is limited to marine CSEM cases in the
+frequency-domain. We hope that similar studies will be carried out for land
+CSEM data and for time-domain data as well.
 
@@
 
-Here we only consider frequency-domain results from frequency-domain
-computations. Similar comparison for time-domain results from time-domain
-computations, and frequency-domain results from time-domain computations and
-vice versa using Fourier transforms would also be good.
-
-The readily availability of many codes means there will be many more people
-able to model 3D results, and not just a few specialists in the field. Whilst
-this is amazing and will push the field much further it also means that the
-same mistakes might happen over and over again, and comparisons and examples
-like these can help to avoid this.
-
-\subsection{Future (?)}
-
-Comment KK: \emph{One thing that the community could really use is more test
-models for various scenarios, and having them be easily accessible.}
-
-\subsection{MARE3DEM}
-
-This is, I thought, the right spot where Kerry Key could write a bit about
-MARE3DEM, if (and I think only if) there are clear plans and a time-scale to
-open-source it. Embedded in a wider summary of available codes (some research
-required).
-
 \clearpage  % TODO: Just for now while drafting, remove later!
 \section{Conclusions}
+%
+% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
+%
+% Your conclusion should:
+% - Restate your hypothesis or research question
+% - Restate your major findings
+% - Tell the reader what contribution your study has made to the existing
+%   literature
+% - Highlight any limitations of your study
+% - State future directions for research/recommendations
+%
+% Your conclusion should NOT:
+% - Introduce new arguments
+% - Introduce new data
+% - Fail to include your research question
+% - Fail to state your major results
+%
+
+\imycom[DW]{Maybe we should create a Google-Doc for working on the Conclusions
+collaboratively at the same time?}
+
+\imycom[DW]{I obviously haven't really done this section, just af few thoughts
+that I noted over time. I think the discussion (as the abstract) has to be
+tackled once the rest is at least in a draft status and all data is ready.}
 
@@
 so. While before there were only closed-source codes owned by companies or
-consortia there was recently a wave of openly released codes.
+consortia, or codes that you had to obtain from the authors, often without much
+documentation, there was recently a wave of openly released codes.
 
-Results from numerical modellers for simple models, such as a halfspace below
-air or a sphere in a fullspace, can be verified by comparing them to analytical
-solutions. However, there is no such possibility for complicated, realistic
-models. The only way to gain confidence in numerical results is by comparing
-different codes to each other. We hope that our efforts help to the confidence
-in the available open-source codes\dots
+What is missing for these emerging codes is a comparison and verification
+suite, test models beyond the usual, analytical fullspace and halfspace models
+and the semi-analytical layered Earth models. We hope that our efforts help to
+the confidence in the available open-source codes\dots
 
@@
 as there is not one method which is best for all problems.
-
-It is important to note that there exist many more 3D electromagnetic codes
-from various fields, such as civil engineering or medicine, in Python and in
-many other languages (list a few references here). Here we focused on codes in
-Python developed for geophysical exploration.
-
-\dots
 
@@
 All files to rerun the different models with the four codes and reproduce the
-shown results are available at \todo{zenodo}\dots.
+shown results are available at \dots.
+\itodo{Put up on Zenodo, link here.}
 

### 2020-05-05 manuscript/Manuscript.tex
updates to introduction from RR, let's see if my comment and edit style is convenient

@@
 
+\mycom[RR]{GMD looks very interesting, my only concern is that it might not be in the scope of EM modelers, but we can probably reach modeleres from other communities as well.}
+
 \section{Introduction}
 
-Controlled-source electromagnetic (CSEM) measurements are a frequently applied
-method in various geophysical exploration fields, such as geothermal and ground
-water, oil and gas, mining, civil engineering, or geo-hazards. Modelling these
-electromagnetic fields is therefore of great interest in order to understand
-the measured data. Publications regarding 3D modelling in electromagnetic
-methods started to appear as early as the 1970's and 1980's. These early
-publications where integral equation (IE) methods, having an anomaly embedded
-within a layered medium, mostly for loop-loop type transient EM measurements
-\citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and
-magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal and groundwater, oil and gas, mining, civil engineering, or geo-hazards.
+Modelling these electromagnetic fields is therefore of great interest to design survey layouts, understand the measured data and inversion purposes.
+Publications regarding 3D modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
+These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
 
-In the 1990's computer became sufficiently powerful that 3D modelling gained
-traction, which resulted amongst other in the publication of the book
+In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, which resulted amongst other publications in the book
 \emph{Three-Dimensional Electromagnetics} by the SEG
-\citep{B.SEG.99.Oristaglio}. Often cited publications from that time are
-\cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and
-time-domain modelling using a Yee grid and a global Krylov subspace
-approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency
-computation on massively parallel computers.
+\citep{B.SEG.99.Oristaglio}.
+Often cited publications from that time are \cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency computation on massively parallel computers.
 
-The continuous improvement of computing power and the CSEM boom in the early
-2000's in the hydrocarbon industry led to a wealth of publications. The amount
-of available numerical solutions can be overwhelming and is part of the reason
-why there are hundreds of publications about the topic. There are the different
-methods to solve Maxwell's equation, such as the IE method
-\citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
+The continuous improvement of computing power and the CSEM boom in the early 2000's in the hydrocarbon industry led to a wealth of developed numerical solutions and according publications.
+The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
 CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the
-differential equation (DE) method, for instance finite differences (FD)
-\citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich,
-CAG.13.Sommer}, and finite elementes (FE) \citep{GJI.11.Schwarzbach,
-GEO.04.Commer, GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang},
-finite volume (FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari,
-PIER.01.Clemens, GP.06.Mulder}. And these are just the most common ones.
+differential equation (DE) method, such as finite differences (FD)
+\citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GJI.11.Schwarzbach, GEO.04.Commer, GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari, PIER.01.Clemens, GP.06.Mulder}.
+There are also many different types of discretisation, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes\citep{ECP.07.Haber}.
+Very well written overviews about the different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
 
-There are also many different types of discretisation, where the most common
-ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid
-\citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also
-unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, OcTree meshes
-\citep{ECP.07.Haber}, or hexagonal meshes \citep{CAG.14.Cai}.
+In the last 15 years, the publications with regards to 3D EM modelling grew tremendously, driven by the ever increasing computing power.
+One reason why there are so many reports about this topic results from the variety of solution techniques for the systems of linear equations.
+They can be distinguished between direct solvers \citep{GEO.09.Streich,
+GEO.15.Grayver, GP.14.Chung, GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
+The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GP.06.Mulder, GJI.16.Jaysaval}.
 
-The biggest variety of all exists probably in the available solvers to solve
-the system of linear equations; direct solvers \citep{GEO.09.Streich,
-GEO.15.Grayver, GP.14.Chung, GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect
-solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both,
-so-called hybrid solvers \citep{GEO.18.Liu}; the solvers often use
-preconditioners such as the multigrid method \citep{SIAM.02.Aruliah,
-GP.06.Mulder, GJI.16.Jaysaval}.
+Probably the main reason for the numerous amount of code developments was already outlined by \cite{SG.05.Avdeev}, who finished his review with the following statement: «\emph{The most important challenge that faces the EM community today is to convince software developers to put their 3-D EM forward and inverse solutions into the public domain, at least after some time.
+This would have a strong impact on the whole subject and the developers would benefit from feedback regarding the real needs of the end-users.}»
+Some major exploration service companies as well as certain research consortia and research groups own their 3D CSEM codes, but how about codes that are open-source?
+Academic codes were traditionally often available upon request by authors.
+Codes distributed that way were often provided with the request to not share the code, and they often come without a license attached which means that they are not open-source.
+Also, at times there can be significant hurdles to install a code.
 
-A very well written overview up to the year 2005 of the different approaches to
-3D EM modelling is given by \cite{SG.05.Avdeev}, and also by
-\cite{SG.10.Borner}. In the last 15 years the publications with regards to 3D
-EM  modelling grew tremendously, driven by the ever increasing computing power.
-Avdeev finished his review with the following statement: «\emph{The most
-important challenge that faces the EM community today is to convince software
-developers to put their 3-D EM forward and inverse solutions into the public
-domain, at least after some time. This would have a strong impact on the whole
-subject and the developers would benefit from feedback regarding the real needs
-of the end-users.}»
+The meaning of the term open-source evolved rapidly in the last two decades.
+Today, open-source generally not only means that a code is available (with a proper license), but also that the code is hosted online, is under version control, has the possibility to file issues and make pull requests to fix bugs.
+These are important requirements for reproducible research «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{broggini2017reproducible}.
+Well maintained codes often have continuous integration that includes testing of the code base and online hosted documentation, often including examples and tutorials.
+As such, the term has shifted from purely open-source codes to developments in the open with increasingly building a global community.
+Related projects within the realm of geophysical exploration are e.g., pyGIMLi \citep{CAG.17.Rucker} or Fatiando \citep{JOSS.18.Uieda}.
+\mycom[DW]{Others coming to your mind?}\mycom[RR]{no thoughts about geophysics, but there are many projects for related topics such as gmt, gis, mesh-gen}
 
-It is this topic that we address, open-source 3D CSEM codes. Some major
-exploration service companies as well as certain research consortia and
-research groups have their 3D CSEM codes. But how about codes that are
-open-source? Research code was traditionally often available upon request by
-the author. Codes distributed that way often come with the request to not share
-the code, and they often come without a license attached at all (which means
-that they are not open-source). Also, at times there can be significant hurdles
-to install a code. However, the meaning of open-source evolved rapidly in the
-last decades. Today, open-source generally not only means that a code is
-available (with a proper license). The meaning includes much more these days,
-such as that the code is hosted online, is under version control, has the
-possibility to file issues and make pull requests to fix bugs. Well maintained
-codes often have continuous integration that includes testing of the code base
-and online hosted documentation which often includes code documentation,
-examples, and tutorials. As such the term has shifted from purely open-source
-code to development in the open and increasingly building a global community.
-There are a number of projects within the realm of geophysical exploration,
-besides the ones we present here, \mycom[DW]{Others coming to your mind?}e.g.
-pyGIMLi \citep{CAG.17.Rucker} and Fatiando \citep{JOSS.18.Uieda}. Newer
-\mycom[DW]{wrong term, think about it}programming environments  have also
-brought much simplifications in the installation process and have most
-importantly simplified it for code developers to make their codes easily
-available and installable. All our presented codes are in the Python ecosystem,
-and each code can be installed with a single command (which includes download
-and installation).
+We continue addressing the topic of open-source developments by introducing and comparing four recent projects with focus on 3D CSEM modeling.
+All presented codes are in the Python ecosystem and use either the finite-difference method on structured grids or the finite-element method on unstructured tetrahedral meshes.
+As newer package-management systems such as Conda, Docker, or pip significantly help developers to make their codes easily available and installable, each one can be downloaded and installed with a single command.
 
-A second topic we want to address is verification. New codes are generally
-verified against analytical solutions. However, analytical and semi-analytical
-solutions only exist for very simple models. There is no possibility to check
-how good a computed response is, expect for comparing the result from different
-modellers. If different modellers using different discretisation and
-implementations of Maxwell's equations yield the same result it can give
-confidence in the accuracy. Providing these two models and results from four
-different codes should give a benchmark with which new codes can be compared to
-and validated with.
+Furthermore, we deal with the topic of verification.
+New codes are generally verified against analytical solutions.
+However, analytical and semi-analytical solutions only exist for very simple models.
+There is no possibility to check how good a computed response is, expect for comparing results from different modellers.
+If different discretisations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
+We simulate EM fields for a layered background model with vertical transverse isotropy, containing three blocks, and a realistic, complex marine 3D model.
+These two model designs as well as the corresponding results from four different codes provide a benchmark for new codes to be compared to and validated with.
 
-It is worth mentioning that there are many more 3D EM codes developed in other
-fields than geophysics such as communication systems (antennas, radar,
-satellites), medical imaging, or civil engineering. There are various
-open-source codes in these fields too, e.g., Elmer \mycom[DW]{Add 2-3 proper
-references} (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a
-publication, just a poster). While these codes could potentially be used for
-the same goals as presented here we restrict our review to codes purpose-built,
-and ready without further adjustments, for geophysical applications.
+It is worth mentioning that there are many more 3D EM codes developed in other fields than geophysics such as communication systems (antennas, radar, satellites), medical imaging, or civil engineering.
+There are various open-source codes in these fields too, e.g., Elmer \imycom[DW]{Add 2-3 proper references} (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication, just a poster).
+While these codes could potentially be used for the same goals as presented here we restrict our review to codes purpose-built and ready without further adjustments for geophysical applications.
 
-In the following section we introduce the codes under consideration. The
-numerical result consider two cases. First a layered background with vertical
-transverse isotropy containing three blocks, followed by a realistic, complex
-3D model.
+\imycom[RR]{I thought a lot about this but I just think the previous paragraph is not required in our introduction and haven't find a location where it fits considering different logical structures.
+I think it is also not important for this paper to tell "that there are more codes in EM than only geophysics", that's quite obvious.
+Maybe delete or shorten to 1 sentences to add Elmer and place this sentence somewhere else?
+I think, an appropriate list of all non-geophysical open-source EM codes should be very long anyway, we just don't know them or at least I'm not familiar with them.}
+
+In the following section we introduce the codes under consideration.
+Afterwards, we present the modeling result of the two model cases.
+Finally, we discuss, conclude.\mycom[RR]{structure of the paper can be written if we are completeley clear about this and the rest of the introduction.}
 
@@
   \centering
-\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{c c c c c}  %{lS[table-format=4.2]rS[table-format=4.2]rl}
   \toprule
@@
   \centering
-\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{c c c c c}  %lS[table-format=4.2]rS[table-format=4.2]rl}
   \toprule
@@
   \centering
-\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{c c c c c}  %{ls[table-format=4.2]rs[table-format=4.2]rl}
   \toprule

### 2020-05-13 manuscript/Manuscript.tex
Extensive updates to manuscript
main points:

- introduction update
- suggestion of new comprehensive analysis figure type in results part, added also python script to create them in model-block directory
- discussion content extended and rewritten
- conclusion content extended and rewritten
- overall changes: removed redundant statements and reorganized content to fit in either intro, discussion or conclusions part

- RR -

@@
 
+\imycom[RR]{We need to take care to not mix British English with AE, I'm very used to AE, but Dieter started with (at least what I can identify) mainly BE, so I tried to follow (mainly s instead of z and ou instead of o in some words).
+I hope there are not too many inconsistencies, as probably Lindsey has to fix all these mistakes in the end:-)}
+
 Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal and groundwater, oil and gas, mining, civil engineering, or geo-hazards.
@@
 In the last 15 years, the publications with regards to 3D EM modelling grew tremendously, driven by the ever increasing computing power.
-One reason why there are so many reports about this topic results from the variety of solution techniques for the systems of linear equations.
+One reason why there are so many reports about this topic results from the variety of solution techniques for the systems of linear equations (SLE).
 They can be distinguished between direct solvers \citep{GEO.09.Streich,
@@
 
-We continue addressing the topic of open-source developments by introducing and comparing four recent projects with focus on 3D CSEM modeling.
-All presented codes are in the Python ecosystem and use either the finite-difference method on structured grids or the finite-element method on unstructured tetrahedral meshes.
-As newer package-management systems such as Conda, Docker, or pip significantly help developers to make their codes easily available and installable, each one can be downloaded and installed with a single command.
+\imycom[RR]{i suggest to use also "emph" style for all other package names, not only ours}
+
+We continue addressing the topic of open-source developments with respect to 3D CSEM modeling.
+Even though it comprises still the minority of developments, the landscape in this field of research changed in the last five years.
+Before, there were only closed-source codes owned by companies or  consortia and individual projects, often without a proper documentation, that could be requested from the authors.
+We introduce and compare four recent open-source projects with focus on 3D CSEM modeling.
+All presented codes are in the Python ecosystem and use either the FD method on structured grids or the FE method on unstructured tetrahedral meshes.
 
 Furthermore, we deal with the topic of verification.
-New codes are generally verified against analytical solutions.
-However, analytical and semi-analytical solutions only exist for very simple models.
-There is no possibility to check how good a computed response is, expect for comparing results from different modellers.
+\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the verification of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
+Hence, we first conduct a similar exercise for CSEM codes.
+We want our efforts to help to ensure the reliability of simulations, not only carried out with the available open-source codes, but also for individual closed-source project.
+Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
+Beyond them, the only objective possibility to ensure the accuracy of solutions is by comparing results from different modellers.
 If different discretisations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
-We simulate EM fields for a layered background model with vertical transverse isotropy, containing three blocks, and a realistic, complex marine 3D model.
+
+We simulate EM fields for a layered background model with vertical transverse isotropy, containing three blocks, and the complex marine Marlim R3D model.
 These two model designs as well as the corresponding results from four different codes provide a benchmark for new codes to be compared to and validated with.
+In the following section, we introduce the codes under consideration.
+Afterwards, we present the considered benchmark cases in detail and present the modeling results of our four codes in terms of accuracy and computational performance.
+Beyond that, we extensively discuss important points that control the performance and suitability of our FD and FE codes, including mainly considerations about the mesh design and the choice of solvers.
+We conclude with a summary of our results and a motivation for the EM community to continue not only extending the landscape of open-source codes and also creating a landscape of open-source benchmark models.
 
-It is worth mentioning that there are many more 3D EM codes developed in other fields than geophysics such as communication systems (antennas, radar, satellites), medical imaging, or civil engineering.
-There are various open-source codes in these fields too, e.g., Elmer \imycom[DW]{Add 2-3 proper references} (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication, just a poster).
-While these codes could potentially be used for the same goals as presented here we restrict our review to codes purpose-built and ready without further adjustments for geophysical applications.
+\imycom[RR]{Regarding "It is worth mentioning that there are many more 3D EM codes developed in other fields than geophysics such as communication systems (antennas, radar, satellites), medical imaging, or civil engineering.
+	There are various open-source codes in these fields too, e.g., Elmer ([DW]: Add 2-3 proper references) (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication, just a poster).
+	While these codes could potentially be used for the same goals as presented here we restrict our review to codes purpose-built and ready without further adjustments for geophysical applications."
 
-\imycom[RR]{I thought a lot about this but I just think the previous paragraph is not required in our introduction and haven't find a location where it fits considering different logical structures.
+	I thought a lot about this but I just think the previous paragraph is not required in our introduction and haven't find a location where it fits considering different logical structures.
 I think it is also not important for this paper to tell "that there are more codes in EM than only geophysics", that's quite obvious.
@@
 
-In the following section we introduce the codes under consideration.
-Afterwards, we present the modeling result of the two model cases.
-Finally, we discuss, conclude.\mycom[RR]{structure of the paper can be written if we are completeley clear about this and the rest of the introduction.}
-
 \clearpage  % TODO: Just for now while drafting, remove later!
@@
 
-The four codes under consideration are, in alphabetical order, \custem
-\citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
-\citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
-codes have their user-facing routines written in Python; all of them make heavy
-use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy}
-\citep{NM.20.Virtanen}. The four of them are “modern” open-source projects,
-meaning that they not only come with an open-source license, but they are also
-in an online-hosted version-control system with feedback and tracking
-possibilities (raising issues, filing pull requests), have extensive online
-documentation including many examples, have continuous integration to some
-degree, and also importantly are all easily installable, without any user-side
-compilations.
+\imycom[RR]{I think we should introduce the term degrees of freedom (dof), equivalent to the size of the SLE, as general measure of our problem sizes.
+If it is somewhat x*Nedges, or related to Ncells or Nnodes, who cares?
+We just need this one number for this paper in my opinion, more details in the jupyter notebooks - fine.}
 
-In the following a quick rundown of the codes. It is, however, beyond the scope
-of this article to go into every detail of the different modellers, and we
-refer to their documentations for more details. An overview comparison of the
-different codes is given in Table~\ref{tbl:codecomparison}. All codes have in
-common that they solve the\mycom[DW]{are we all using the weak form?} weak
-formulation of Maxwell's equation in its differential form (DE) under the
-quasistatic or\mycom[DW]{are we all using the diff. approx?} diffusive
-approximation, hence neglecting displacement currents. The machines on which
-the different codes were run are listed in Table~\ref{tbl:machines}, together
-with the responsible operator.
+The four codes under consideration are, in alphabetical order, \custem \citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem \citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}.
+All four codes have their user-facing routines written in Python; all of them make heavy use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}.
+The four of them are “modern” open-source projects, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
+Newer package-management systems such as Conda, Docker, or pip significantly supported us to make our codes easily available and installable without any user-side compilations.
+Each one can be downloaded and installed with a single command.
 
-\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
-  in its differential form (DE) under the quasistatic approximation. Note that
-  \emg3d is a solver on its own, while the other codes implement third-package
-  solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS}
-  \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
+In the following a quick rundown of the codes.
+It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details.
+An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
+All codes have in common that they solve the\mycom[DW]{are we all using the weak form?} weak formulation of Maxwell's equation in its differential form (DE) under the quasistatic or\mycom[DW]{are we all using the diff.
+approx?} diffusive approximation, hence neglecting displacement currents.
+The machines on which the different codes were run are listed in Table~\ref{tbl:machines}, together with the responsible operator.
+
+\imycom[RR]{too much info (redundancy to text) for table caption}
+
+\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations in its differential form (DE) under the quasistatic approximation.
+Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
 }{
@@
   License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
-  Installation & \texttt{pip}; \texttt{conda}
+  Installation & \texttt{conda}
                & \texttt{pip}; \texttt{conda}
@@
 
-TODO
+The customisable electromagnetic modeling Python toolbox custEM was developed for simulating arbitrary complex 3D CSEM geometries with focus on semi-airborne setups, but it supports also land-based, airborne, coastal  or marine environments.
+Multiple electric or magnetic field or potential finite-element approaches were implemented as total or secondary field formulations.
+The finite-element kernel, including higher order basis functions and parallelisation, relies on the FEniCS project \citep{logg2012, langtangen2016}.
+The resulting systems of linear equations are solved with MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming choice. 
+Primary field solutions are supplied by the COMET \citep{skibbe2020coupled} package.
+
+The toolbox considers generally anisotropic petrophysical properties.
+Even though changes of the conductivity is mainly of interest for CSEM modeling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
+Recently, induced polarization parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
+The provided meshing tools based on TetGen \citep{si2015tetgen} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
+
+The custEM toolbox is under steady development and maintenance.
+Future enhancements comprise adding iterative solution techniques, provided by FEniCS, as well as further functionalities for automatically incorporating intersecting bodies such as folds or faults in meshes.
+Furthermore, current work is on using custEM for inverse modeling applications.
 
@@
 
-In this numerical section we compute the responses for two different models to
-verify that these different 3D codes yield the same electromagnetic responses.
-The first model is a simple one consisting of a layered, anisotropic
-background, in which three blocks are embedded, and the second model is a very
-complex, realistic model.
+We computed the responses for two different models to verify that all different 3D codes yield the same electromagnetic responses.
+The first simple Block model consists of a layered, anisotropic
+background with three embedded blocks.
+The second Marlim R3D model is based on a very complex, realistic marine CSEM setup.
 
-\subsection{Block Model}
+\subsection{Block model}
 
-\cite{GJI.13.Miensopust} published a review of two workshops dealing with the
-verification of magnetotelluric forward and inversion codes, hence a similar
-exercise to what we do here for CSEM codes. The block model is a derivation of
-the \emph{Dublin Test Model 1}, a model from their first workshop. We took the
-same layout of the blocks but adjusted the dimensions and resistivities to a
-typical, marine CSEM problem, as shown in Figure~\ref{fig:block-model}. We
-additionally added a layered background with vertical transverse isotropy
-(VTI).
+\imycom[RR]{I think the miensopust argument is rather suited to motivate our work in the introduction, i hope its fine that i moved this argument}
+
+The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modeling workshop described by \cite{GJI.13.Miensopust}.
+We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}.
+We additionally added a layered background with vertical transverse isotropy (VTI).
 %
@@
 
-In a first step we compare the layered background to the semi-analytical
-solutions of a 1D code, for which we use \empymod \citep{GEO.17.Werthmuller}.
-Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the
-actual responses in the top rows, and the relative error in the bottom rows
-for receiver line $y=0\,$km and $y=-3\,$km, respectively (for the layered
-background the responses for the two receiver-lines of $y=\pm3$\,km are
-identical, so we only show one here).
+The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretisation.
+Therefore, the FE codes custEM and PETGEM used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
+This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
+\imycom[RR]{Add short information about mesh design with SIMPEG and emg3d, including something like "comparatively coarse discretization in center to minimize computation times" }
 
-Figure~\ref{fig:results-layered-0} shows in the top-row the inline responses
-for offsets $r>0.5\,$km. As all codes compute the same we only show the
-semi-analytical result for the real and imaginary amplitudes, and then in the
-bottom row the relative error of the 3D codes. The results show that the codes
-are literally yielding the same result, the relative error is for big parts
-below 1\,\%, and for almost all parts below a few percent. Some differences are
-due to the chosen discretizations. E.g., \emg3d is less precise close to the
-200\,m long source. This could be improved by choosing smaller cell sizes, at
-the cost of computation time. At large offsets, on the other hand, \emg3d seems
-to do a very good job.
+In a first step, we compare the layered background to the semi-analytical solutions of a 1D code, for which we use  \empymod\citep{GEO.17.Werthmuller}.
+Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the actual responses in the top rows, and the relative error in the bottom rows for the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
+
+Figure~\ref{fig:results-layered-0} illustrates the inline responses in the top-row for offsets $r>0.5\,$km. We only show the
+semi-analytical result for the real and imaginary amplitudes.
+The bottom row displays the relative error of the 3D codes.
+The results show that all codes are yielding accurate result with errors of around 1\,\% in most parts and overall below a few percent, disregarding locations affected by sign reversals.
+The differences can be mainly attributed to the chosen discretisations.
+The FE codes show the strongest misfits at large offsets, most likely caused by the utilized boundary mesh, whereas \emg3d seems to do a very good job\mycom[RR]{maybe reformulate to something like: whereas emg3d appears to be not affected by boundary effects}.
+Close to the 200\,m long source, emg3d is less precise which is attributed to comparatively large cell sizes in this region.
 %
@@
 
-The corresponding broadside responses for $y=-3\,$km is shown in
-Figure~\ref{fig:results-layered--3}, and the required CPU and RAM is shown in
-Table~\ref{tbl:comp-layered}.
+\imycom[RR]{I suggest to show y-component for broadside and the errors of the weak component (if not too bad), otherwise only broadside is required to save a plot, because inline should be better for Ex in general.}
+The corresponding broadside responses for $y=\pm3\,$km are shown in Figure~\ref{fig:results-layered--3}.
+The CPU and RAM requirements are listed in Table~\ref{tbl:comp-layered}.
 %
@@
   %
-  Code & {CPU} & \#Procs & RAM     & \#Cells \\
+  Code & {CPU} & \#Procs & RAM     & \#dof \\
        & {(s)} &         & {(GiB)} &         \\
@@
 
-Three resistive blocks are added in the 3.3\,km-thick, anisotropic background
-layer, as shown in Figure~\ref{fig:block-model}. They have resistivities of
-$\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines),
-$\rho=100\,\ohmm$ (thin plate, South-East), $\rho=500\,\ohmm$ (cube,
-North-West). As there are no analytical solutions for this model we show the
-normalized difference between different codes, instead of the relative error,
-where the normalized difference of two responses $p$ and $q$ is given by
+In a second step, three resistive blocks were added in the 3.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}.
+They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
+As there are no analytical solutions for this model we show the normalized difference between different codes, instead of the relative error, where the normalized difference of two responses $p$ and $q$ is given by
 %
@@
 %
-\imycom[DW]{NRMSD: Comparing all codes to all would make the
-figures too cluttered, and I don't think it would add a lot insights. My idea
-is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the
-two FE ones), and \emg3d/\custem (a cross-comparison). What do you think?}
+\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too cluttered, and I don't think it would add a lot insights.
+My idea is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones), and \emg3d/\custem (a cross-comparison).
+What do you think?}
 
-The results for the three receiver lines $y=-3,0,3\,$km are shown in
-Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and
-\ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in
-Table~\ref{tbl:comp-block}. What we can conclude from the NRMSD is that similar
-codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are
-very similar, as well as are \custem and \petgem.
+\imycom[RR]{Agreed.
+Another suggestion, I solved this visualization problem with a color coded matrix plot, showing 90th percentiles or median values of all errors along the line as meaningful comprehensive number.
+Look in my thesis - example 4.
+Comparison for real and imag could be in the lower and upper triangles, or we show absolute magnitudes for layered earth in lower triangle and for block model in upper triangle.
+With help of this plot, one could easily say if differences are higher for block model and which codes fit to each other well.}
+
+\imycom[RR]{If using the mentioned matrix plots, we would need only one of the figures 4-6, and could show the other data comprehensively.
+I added a python script to generate an example of my plotting suggestion in the model-block directory and a new Figure 7 in the manuscript that illustrates what I mean.
+Of course, any upgrade suggestion for this initial idea is welcome, aside from making it looking nice with labels  and annotations.}
+
+The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in Table~\ref{tbl:comp-block}.
+We can conclude from the NRMSD that similar codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very similar, as well as are \custem and \petgem.
 \mycom[DW]{Write in detail when all results are available}
@@
 
-The difference becomes only significant at offsets larger than 8\,km. However,
-this is due to a practical difference in the meshing: This simple block model
+The difference becomes only significant at offsets larger than 8\,km. This is due to a practical difference in the meshing: This simple block model
 is advantageous for FV codes, as it consists of rectangular blocks and
@@
 increased NRMSD at large offsets, and it has nothing to do with the accuracy of
-the computation itself.
+the computation itself.\mycom[RR]{see imycom below figure 6}
+
+\imycom[RR]{60 x 60 km (30 km in each direction from center).
+I already added a paragraph about mesh generation in the beginning, I suggest to remove this description here and jsut refer to like "Similar to the layered earth model, the largest errors occur at offsets $>8$\,km due to the differences in mesh design."
+We should also mention that relative errors are related to the magnitudes, as real is so much weaker at larger offsets, it is clear that errors increase significantly.
+Alternatively, we could show absolute magnitude or phase errors such as in the Marlim model.}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=5cm]{figures/median-stats-block--3.pdf}\hfill
+	\includegraphics[width=5cm]{figures/median-stats-block-0.pdf}\hfill
+	\includegraphics[width=5cm]{figures/median-stats-block-3.pdf}
+	\caption[Median errors]{Overall misfit relations between all codes for the three receiver lines y=-3, y=0 \& y=3 f.l.t.r.
+Colors indicate the median values of the 101 calculated NRMSD arguments for each line between all codes.
+Errors for real parts are shown in the lower triangle, for imaginary parts in the upper triangle.}
+	\label{medianmisfits}	
+\end{figure}
 
@@
 
-The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
-the north-eastern part of the Campos Basin, offshore Brazil, which was
-discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
-log data a realistic resistivity model with vertical transverse isotropy (VTI),
-Marlim R3D (MR3D), which they released under an open-source license. Using this
-model \cite{GEO.19.Correa} computed CSEM data for six frequencies from
-0.125\,Hz to 1.25\,Hz, which they also released under an open-source license.
-To compute the data they used a state-of-the-art code from the industry
-\citep{GEO.07.Maao}. It is therefore an ideal case to verify our open-source
-codes against, as it is a complex, realistic model, and the data were computed
-by an industry-proofed code. Additionally, that code is a time-domain code,
-whereas the four codes under consideration here compute the results all in the
-frequency-domain.
+The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in the north-eastern part of the Campos Basin, offshore Brazil, which was discovered in 1985.
+\cite{BJG.17.Carvalho} created from seismic data and well log data a realistic resistivity model with vertical transverse isotropy (VTI), Marlim R3D (MR3D), which they released under an open-source license.
+\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to 1.25\,Hz, released under an open-source license.
+To compute the data they used a state-of-the-art code from the industry \citep{GEO.07.Maao}.
+It is therefore an ideal case to verify our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.\mycom[RR]{I would delete this sentence, not that important and a bit redundant}
+Additionally, that code is a time-domain code, whereas the four codes under consideration here compute the results all in the frequency-domain.
 
-The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling
-to almost 466 million cells, where each cell has dimensions of 25 by 75 by
-5\,m. For the computation the model is upscaled to 515 by 563 by 310 cells,
-totalling to almost 90 million cells, where each cell has dimensions of 100 by
-100 by 20\,m.
+The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
+For the computation the model is upscaled to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
 
-The published data set consists of a regular grid of receivers of 20 in
-eastern direction by 25 in northern direction, 500 receivers in total, with
-1\,km spacing located on the irregular seafloor. 45 source-towlines were
-located on the same grid, 50\,m above the seafloor, with shots every 100\,m. In
-\cite{GEO.19.Correa} the actual responses for one receiver with the
-corresponding East-West inline and one East-West broadside acquisition line are
-shown, which is the data we chose for our comparison. The cross-section of the
-resistivity model along the chosen inline acquisition line is shown in
-Figure~\ref{fig:model-marlim}, together with the acquisition information.
+The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
+45 source-towlines were located on the same grid, 50\,m above the seafloor, with shots every 100\,m. In
+\cite{GEO.19.Correa} the actual responses for one receiver with the corresponding East-West inline and one East-West broadside acquisition line are shown, which is the data we chose for our comparison.
+The cross-section of the resistivity model along the chosen inline acquisition line is shown in Figure~\ref{fig:model-marlim}, together with the acquisition information.
+
+\imycom[RR]{I used gmt the last time 7 years ago , in between I tried the gmt4py tools, but they did not work well on my machine.
+I suggest to use two plots next to each other, a similar figure as in the notebook and a simple x-y coord sketch (identical extent as the bird perspective view in the other plot) with all Tx / Rx locations, highlighting the relevant line and Rx for us.}
+
 %
@@
   the drawn survey line in that figure are plainly wrong. If someone is
-  familiar with GMT and happy to make a make that would be great. Also, the
+  familiar with GMT and happy to make that would be great. Also, the
   cross-section is currently heavily vertically exaggerated.
@@
 
-We compared four different, open-source 3D CSEM modellers by computing
-responses for (a) a layered, anisotropic model without and with three resistive
-blocks, and (b) a realistic 3D model. The comparison shows that the codes do
-yield the same responses. As such we could verify the accuracy of these four
-codes.
+\imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone adds the own thoughts when he receives the manuscript.
+Same for conclusions.
+We need to take care to not mix discussion and conclusions, some of the statements from here belong rather to the conclusions, I hope it's fine that I reorganized the content.
+Aside from that, I already added all thoughts of mine.}
 
-This is a very important insight. The possibilities to verify the accuracy of
-3D CSEM codes are limited. One can compare them to analytical and
-semi-analytical solutions, but they only exist for very simple models. For
-complex models comparisons to other codes is the only possibility.
-It is therefore really important to have more test models, and importantly, for
-various scenarios, and that they are easily accessible. Our data should also
-make it very easy for new codes to have a readily available data set to test
-against and verify.
+Even if modeling results may look completely valid, they could not be correct at all.
+Verifying the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
+Overall, we observed an excellent match between all solutions.
+The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation.
+Considering this satisfactory result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
+The following arguments are based on a comparison of only marine CSEM models, which are the focus of industry applications.
+Nevertheless, we are confident that many observations would hold in a similar manner for land-based, airborne, or mixed setups.
 
-A similar exercise has be done for magnetotelluric (MT) 3D modelling and
-inversion by \cite{GJI.13.Miensopust}, but we are not aware of anything like
-this for CSEM data. However, we do hope that more comparisons will emerge in
-the future, particularly with the current increase in open-source codes as well
-as open-source data.
+We point out that making a synthetic and a real benchmark model available to cross-validate any 3D CSEM code was the determining reason for their choice, regardless of the suitability of the considered FD and FE codes for these problems.
+The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
+Aside from the idea of analyzing an industrially relevant benchmark example, the Marlim R3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretisation. 
+At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
+Hence, the chosen examples favoured the finite-difference codes, since they used either regular grids or octree-meshes, whereas the two finite-element codes were required to tetrahedralise the model geometries.
 
-The codes under consideration consisted of finite element and finite
-differences. However, it has to be noted that the chosen models are better
-suited for finite differences codes. The first model for obvious reasons, as it
-is a layered background containing blocks, all aligned in Cartesian
-coordinates. The second model, Marlim R3D, could be an ideal case for FE codes,
-as it comes with lithological horizons from seismic data. However, the
-corresponding, published resistivity model uses a Cartesian grid. An extension
-of this work could be to use a complex model tailored for a FE code, and
-compare how the FD codes cope with it.
+In the first model, the necessity of discretising regular structures with tetrahedra, especially thin layers, led to comparatively large FE problem sizes and computational resource demands.
+FE codes with unstructured meshes were probably the poorest choice of all commonly used methods for this setup in terms of computational performance.
+However, thinking about introducing just one slight irregularity such as bathymetry, a thin dipping plate or an anticline, the performance behaviour could likely switch.
+All of these changes would barely change the problem size for the FE codes, but significantly increase it for the FD codes if the true geometry should be approximated sufficiently accurate.
 
-The codes under consideration use direct and indirect solvers, \dots blabla say
-something. Having calculated in each model only one source favours in the
-runtime comparison the iterative solver and therefore \emg3d. For the iterative
-solvers additional sources would come at almost no cost, whereas for \emg3d it
-would come at the same cost as the first source. This is something to keep in
-mind when choosing the appropriate modeller for a problem at hand.
+The real Marlim R3D model was, ironically, the ideal case for FE codes because it's structure was characterized by irregular lithological horizons obtained from seismic data.
+Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
+We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
+Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
+The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+
+The codes under consideration use direct and indirect solvers. In general, the biggest advantage of iterative solvers with appropriate preconditioners are the comparatively small memory requirements.
+Direct solvers can be considered as most robust to solve any ill-conditioned SLE, which is most important for systems of the FE method on unstructured meshes.
+As the consumed computational resources indicate, a more powerful machine than a laptop is required for most 3D CSEM problems, but no high-performance-computing architecture.
+
+The computation times can differ significantly for specific simulations, but there is no clear general advantage for one of the solver types. 
+In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d.
+Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be calculated in the same computational domain.
+As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d.
+For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the calculation for multiple sources, but this argumentation is beyond the scope of this work.
+
+We see this work as the start for future elaboration on the validation of modeling codes, not necessarily restricted to CSEM problems.
+Much more comparisons and examples are required which not only result in the finding that a sufficient accuracy was observed. 
+3D CSEM modelling is a difficult task, which requires many considerations. It starts with the selection of the right code for the problem. 
+We found that the meshing task, which is most performance determining, is particularly difficult and relevant, choosing cells small enough to appropriately represent the model yet to be as coarse as possible still achieving the desired precision.
+The required model extent has to be considered as well, thinking also about effects of the so-called airwave in marine setups or boundary meshes in general.
+This is not a new finding but rather well known fact.
+We are surprised that only the minority of publications in the field of 3D EM modeling considers a sufficiently detailed elaboration of the meshing process.
+
+A completely objective evaluation of codes is only possible by cross-validation.
+Nevertheless, we point out that using different discretizations or formulations of the numerical approach, e.g.
+by choosing field or potential approaches, second or total field formulations, different polynomial order basis functions, and others, is a suitable alternative to the cross-comparison of multiple codes for self-validating complex 3D results.
+This is a very powerful method to confirm the general functionality of codes for any modeling problem, which might not be covered by existing cross-validation benchmark examples.
+Considering for instance  this study, it would be very optimistic to estimate the accuracy of the utilized codes for a land-based mineral exploration setup with a highly-conductive, steeply-dipping conductor.
+However, each modeller could run multiple simulations with different configurations to increase the reliability of the obtained results.
 
@@
 
-Finally, the comparison in our study is limited to marine CSEM cases in the
-frequency-domain. We hope that similar studies will be carried out for land
-CSEM data and for time-domain data as well.
-
-We see this only as the start. Much more comparisons and examples are required.
-3D CSEM modelling is a difficult task, which requires many considerations: It
-starts with the selection of the right code for the problem; then the meshing
-is particularly difficult, choosing cells small enough to appropriately
-represent the model yet to be as coarse as possible still achieving the desired
-precision; the required model extent, particularly for shallow and marine cases
-where the airwave has to be considered. The tricky part is that even if the
-result is not correct it may look completely valid. The only options to verify
-results are (a) by comparing different discretizations, and (b) by comparing
-different codes.
-
 \clearpage  % TODO: Just for now while drafting, remove later!
-\section{Conclusions}
+\section{Conclusions \& Outlook}
 %
@@
 
-The landscape in 3D CSEM modelling greatly changed in the last five years or
-so. While before there were only closed-source codes owned by companies or
-consortia, or codes that you had to obtain from the authors, often without much
-documentation, there was recently a wave of openly released codes.
+\imycom[RR]{I also rearranged some of your thoughts and formulated mine. I moved some of them (the few sentences that were rather redundant motivation content) to the introdcution.}
 
-What is missing for these emerging codes is a comparison and verification
-suite, test models beyond the usual, analytical fullspace and halfspace models
-and the semi-analytical layered Earth models. We hope that our efforts help to
-the confidence in the available open-source codes\dots
+We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, including a modification with three resistive blocks, and the realistic marine Marlim R3D model.
+All comparisons exhibited an excellent reliability of the solutions.
+Our data should make it very easy for new codes to have a readily available data set to test against and verify.
+We are confident that the discussions about runtimes, memory consumptions, solver choices, and, most important, discretisations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
 
-Also, the runtime and memory consumption comparison together with the meshing
-differences should help to decide which modeller is used best for which tasks,
-as there is not one method which is best for all problems.
+As none of the considered methods is best suited for all problems,
+it is important to have more test models for various scenarios in future.
+Our study is limited to marine CSEM cases in the frequency-domain.
+Reasonable extensions include providing benchmark models for land, airborne, or mixed CSEM environments as well as time-domain data.
+Another addition to this work would be focusing on complex irregular  models, tailored for an FE or FV code based on unstructured meshes, and to compare how the FD codes can cope with it.
+
+We encourage the community to not only work on new open-source code developments but also to create a landscape of easily accessible benchmark models for increasing the number of reliable and reproducible solutions.
+Our study could provide one of the primary inputs for this task.  
+We are confident that the mentioned development will and should be taking place, taking into account the current general trend in science to open-source papers, codes or data.
 
@@
 
-We would like to thank Paulo Menezes for the help and explanations with regards
-to the Marlim R3D model and corresponding CSEM data, and for making their
-actual computation model available under an open-source license.
+We would like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
 
-The work of D.W. was conducted within the Gitaro.JIM project funded through
-MarTERA, a EU Horizon 2020 research and innovation programme (No 728053);
-\href{https://www.martera.eu}{martera.eu}.
+The work of D.W. was conducted within the Gitaro.JIM project funded through MarTERA, a EU Horizon 2020 research and innovation programme (No 728053); \href{https://www.martera.eu}{martera.eu}.
+The development of custEM as part of the DESMEX project was funded by the Germany Ministry for Education and Research (BMBF) in the framework of the research and development program Fona-r4 under grant 033R130D.
 
@@
 
-All files to rerun the different models with the four codes and reproduce the
-shown results are available at \dots.
+All files to rerun the different models with the four codes and reproduce the shown results are available at \dots.
 \itodo{Put up on Zenodo, link here.}

### 2020-05-13 model-block/BlockModel-Comparison-Medians.py

@@ -1,0 +1,303 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# # Block Model with a 1D background - Comparison
+# 
+# ### For the model, see the notebook BlockModel.ipynb
+
+# In[1]:
+
+
+import numpy as np
+import xarray as xr
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+
+# ## Load data
+
+# In[3]:
+
+
+def extract_lines(name):
+    inp = xr.load_dataset(name, engine='h5netcdf')
+    print_attributes(inp)
+    out = np.stack([
+        inp.line_1[::2]+1j*inp.line_1[1::2],
+        inp.line_2[::2]+1j*inp.line_2[1::2],
+        inp.line_3[::2]+1j*inp.line_3[1::2],
+    ]).T
+    return out
+
+
+def print_attributes(inp):
+    for key in ['runtime', 'n_procs', 'max_ram',
+                'n_cells', 'n_nodes', 'n_dof', 'extent',
+                'min_vol', 'max_vol', 'machine',
+                'version', 'date']:
+        print(f"{key:10} : {inp.attrs[key]}")
+
+
+# In[4]:
+
+
+ds = xr.load_dataset('block_model_and_survey.nc', engine='h5netcdf')
+rec_x = ds.x[::2].data
+rec_y = ds.attrs['rec_y']
+
+
+# ### Semi-analytical background result from `empymod`
+
+# In[5]:
+
+
+epm_1d = extract_lines('results/layered_empymod.nc')
+
+
+# ### `emg3d`
+
+# In[6]:
+
+
+# BACKGROUND
+egd_bg = extract_lines('results/layered_emg3d.nc')
+print(f"\n= - = - =  :  {14*'= - '}=\n")
+# 3D
+egd_tg = extract_lines('results/block_emg3d.nc')
+
+
+# ### `PETGEM`
+
+# In[7]:
+
+
+# BACKGROUND
+ptg_bg = extract_lines('results/layered_petgem.nc')
+print(f"\n= - = - =  :  {14*'= - '}=\n")
+# 3D
+ptg_tg = extract_lines('results/block_petgem.nc')
+
+
+# ### `custEM`
+
+# In[8]:
+
+
+# BACKGROUND
+#cst_bg = extract_lines('results/layered_custEM_p1.nc')
+cst_bg = extract_lines('results/layered_custEM_p2.nc')
[…]

### 2020-05-18 manuscript/Manuscript.tex
Refs: Add DOI's; adj. form. to match existing

@@
 Today, open-source generally not only means that a code is available (with a proper license), but also that the code is hosted online, is under version control, has the possibility to file issues and make pull requests to fix bugs.
-These are important requirements for reproducible research «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{broggini2017reproducible}.
+These are important requirements for reproducible research «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{GEO.17.Broggini}.
 Well maintained codes often have continuous integration that includes testing of the code base and online hosted documentation, often including examples and tutorials.
@@
 Multiple electric or magnetic field or potential finite-element approaches were implemented as total or secondary field formulations.
-The finite-element kernel, including higher order basis functions and parallelisation, relies on the FEniCS project \citep{logg2012, langtangen2016}.
+The finite-element kernel, including higher order basis functions and parallelisation, relies on the FEniCS project \citep{B.SPR.12.Logg, B.SPR.16.Langtangen}.
 The resulting systems of linear equations are solved with MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming choice. 
-Primary field solutions are supplied by the COMET \citep{skibbe2020coupled} package.
+Primary field solutions are supplied by the COMET \citep{GEO.20.Skibbe} package.
 
@@
 Recently, induced polarization parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
-The provided meshing tools based on TetGen \citep{si2015tetgen} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
+The provided meshing tools based on TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
 

### 2020-05-18 manuscript/Manuscript.tex
Median Figure
- Integrate the figure into the comparison notebook.
- Combine the three plots into one plot, only one colorbar.
- Change the median calulation to only take the abs() once.

@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=5cm]{figures/median-stats-block--3.pdf}\hfill
-	\includegraphics[width=5cm]{figures/median-stats-block-0.pdf}\hfill
-	\includegraphics[width=5cm]{figures/median-stats-block-3.pdf}
-	\caption[Median errors]{Overall misfit relations between all codes for the three receiver lines y=-3, y=0 \& y=3 f.l.t.r.
-Colors indicate the median values of the 101 calculated NRMSD arguments for each line between all codes.
-Errors for real parts are shown in the lower triangle, for imaginary parts in the upper triangle.}
-	\label{medianmisfits}	
-\end{figure}
+%
+\plot*{median-stats-block}{width=\textwidth}{
+    Overall misfit relations between all codes for the three receiver lines
+    y=-3, y=0, and y=3 (f.l.t.r.). Colors indicate the median values of the 101
+    calculated NRMSD arguments for each line between all codes. Errors for real
+    parts are shown in the lower triangle, for imaginary parts in the upper
+  triangle.
+}
+%
 

### 2020-05-18 model-block/BlockModel-Comparison-Medians.py

@@ -1,303 +1,0 @@
-#!/usr/bin/env python
-# coding: utf-8
-
-# # Block Model with a 1D background - Comparison
-# 
-# ### For the model, see the notebook BlockModel.ipynb
-
-# In[1]:
-
-
-import numpy as np
-import xarray as xr
-import matplotlib.pyplot as plt
-from matplotlib.colors import LogNorm
-
-# ## Load data
-
-# In[3]:
-
-
-def extract_lines(name):
-    inp = xr.load_dataset(name, engine='h5netcdf')
-    print_attributes(inp)
-    out = np.stack([
-        inp.line_1[::2]+1j*inp.line_1[1::2],
-        inp.line_2[::2]+1j*inp.line_2[1::2],
-        inp.line_3[::2]+1j*inp.line_3[1::2],
-    ]).T
-    return out
-
-
-def print_attributes(inp):
-    for key in ['runtime', 'n_procs', 'max_ram',
-                'n_cells', 'n_nodes', 'n_dof', 'extent',
-                'min_vol', 'max_vol', 'machine',
-                'version', 'date']:
-        print(f"{key:10} : {inp.attrs[key]}")
-
-
-# In[4]:
-
-
-ds = xr.load_dataset('block_model_and_survey.nc', engine='h5netcdf')
-rec_x = ds.x[::2].data
-rec_y = ds.attrs['rec_y']
-
-
-# ### Semi-analytical background result from `empymod`
-
-# In[5]:
-
-
-epm_1d = extract_lines('results/layered_empymod.nc')
-
-
-# ### `emg3d`
-
-# In[6]:
-
-
-# BACKGROUND
-egd_bg = extract_lines('results/layered_emg3d.nc')
-print(f"\n= - = - =  :  {14*'= - '}=\n")
-# 3D
-egd_tg = extract_lines('results/block_emg3d.nc')
-
-
-# ### `PETGEM`
-
-# In[7]:
-
-
-# BACKGROUND
-ptg_bg = extract_lines('results/layered_petgem.nc')
-print(f"\n= - = - =  :  {14*'= - '}=\n")
-# 3D
-ptg_tg = extract_lines('results/block_petgem.nc')
-
-
-# ### `custEM`
-
-# In[8]:
-
-
-# BACKGROUND
-#cst_bg = extract_lines('results/layered_custEM_p1.nc')
-cst_bg = extract_lines('results/layered_custEM_p2.nc')
[…]

### 2020-05-18 manuscript/Manuscript.tex
Assimilated changes

@@
 
-\mycom[RR]{GMD looks very interesting, my only concern is that it might not be in the scope of EM modelers, but we can probably reach modeleres from other communities as well.}
+\mycom[RR]{GMD looks very interesting, my only concern is that it might not be
+in the scope of EM modelers, but we can probably reach modeleres from other
+communities as well.}
 
@@
 
-\imycom[RR]{We need to take care to not mix British English with AE, I'm very used to AE, but Dieter started with (at least what I can identify) mainly BE, so I tried to follow (mainly s instead of z and ou instead of o in some words).
-I hope there are not too many inconsistencies, as probably Lindsey has to fix all these mistakes in the end:-)}
+\imycom[RR]{We need to take care to not mix British English with AE, I'm very
+  used to AE, but Dieter started with (at least what I can identify) mainly BE,
+  so I tried to follow (mainly s instead of z and ou instead of o in some
+  words). I hope there are not too many inconsistencies, as probably Lindsey
+  has to fix all these mistakes in the end:-)}
+\imycom[DW]{Be aware of Canadian English and Australian English :-D -- You are
+  of course right. I am usually mostly BE, having done my PhD in Scotland.
+  However, I don't think it matters at the moment, because it will depend to
+  what journal we submit. With an appropriate spellchecker that should be a
+  quick thing then.}
 
-Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal and groundwater, oil and gas, mining, civil engineering, or geo-hazards.
-Modelling these electromagnetic fields is therefore of great interest to design survey layouts, understand the measured data and inversion purposes.
-Publications regarding 3D modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
-These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+Controlled-source electromagnetic (CSEM) measurements are a frequently applied
+method in various geophysical exploration fields, such as geothermal and
+groundwater, oil and gas, mining, civil engineering, or geo-hazards. Modelling
+these electromagnetic fields is therefore of great interest to design survey
+layouts, understand the measured data and inversion purposes. Publications
+regarding 3D modelling in electromagnetic methods started to appear as early as
+the 1970's and 1980's. These early publications were integral equation (IE)
+methods, having an anomaly embedded within a layered medium, mostly for
+loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann,
+GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements
+\citep{GEO.84.Wannamaker}.
 
-In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, which resulted amongst other publications in the book
+In the 1990's, computer became sufficiently powerful that 3D modelling gained
+traction, which resulted amongst other publications in the book
 \emph{Three-Dimensional Electromagnetics} by the SEG
-\citep{B.SEG.99.Oristaglio}.
-Often cited publications from that time are \cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency computation on massively parallel computers.
+\citep{B.SEG.99.Oristaglio}. Often cited publications from that time are
+\cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and
+time-domain modelling using a Yee grid and a global Krylov subspace
+approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency
+computation on massively parallel computers.
 
-The continuous improvement of computing power and the CSEM boom in the early 2000's in the hydrocarbon industry led to a wealth of developed numerical solutions and according publications.
-The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani,
-CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the
-differential equation (DE) method, such as finite differences (FD)
-\citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GJI.11.Schwarzbach, GEO.04.Commer, GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari, PIER.01.Clemens, GP.06.Mulder}.
-There are also many different types of discretisation, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes\citep{ECP.07.Haber}.
-Very well written overviews about the different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
+The continuous improvement of computing power and the CSEM boom in the early
+2000's in the hydrocarbon industry led to a wealth of developed numerical
+solutions and according publications. The most common applied methods to solve
+Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan,
+GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and
+different variations of the differential equation (DE) method, such as finite
+differences (FD) \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin,
+GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GJI.11.Schwarzbach,
+GEO.04.Commer, GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang},
+and finite volumes (FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari,
+PIER.01.Clemens, GP.06.Mulder}. There are also many different types of
+discretisation, where the most common ones are regular grids (Cartesian,
+rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid
+\citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids
+\citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or
+OcTree meshes\citep{ECP.07.Haber}. Very well written overviews about the
+different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and
+\cite{SG.10.Borner}.
 
-In the last 15 years, the publications with regards to 3D EM modelling grew tremendously, driven by the ever increasing computing power.
-One reason why there are so many reports about this topic results from the variety of solution techniques for the systems of linear equations (SLE).
-They can be distinguished between direct solvers \citep{GEO.09.Streich,
-GEO.15.Grayver, GP.14.Chung, GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
-The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GP.06.Mulder, GJI.16.Jaysaval}.
+In the last 15 years, the publications with regards to 3D EM modelling grew
+tremendously, driven by the ever increasing computing power. One reason why
+there are so many reports about this topic results from the variety of solution
+techniques for the systems of linear equations (SLE). They can be distinguished
+between direct solvers \citep{GEO.09.Streich, GEO.15.Grayver, GP.14.Chung,
+GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder,
+GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers
+\citep{GEO.18.Liu}. The solvers often use preconditioners such as the multigrid
+method \citep{SIAM.02.Aruliah, GP.06.Mulder, GJI.16.Jaysaval}.
 
-Probably the main reason for the numerous amount of code developments was already outlined by \cite{SG.05.Avdeev}, who finished his review with the following statement: «\emph{The most important challenge that faces the EM community today is to convince software developers to put their 3-D EM forward and inverse solutions into the public domain, at least after some time.
-This would have a strong impact on the whole subject and the developers would benefit from feedback regarding the real needs of the end-users.}»
-Some major exploration service companies as well as certain research consortia and research groups own their 3D CSEM codes, but how about codes that are open-source?
-Academic codes were traditionally often available upon request by authors.
-Codes distributed that way were often provided with the request to not share the code, and they often come without a license attached which means that they are not open-source.
-Also, at times there can be significant hurdles to install a code.
+Probably the main reason for the numerous amount of code developments was
+already outlined by \cite{SG.05.Avdeev}, who finished his review with the
+following statement: «\emph{The most important challenge that faces the EM
+community today is to convince software developers to put their 3-D EM forward
+and inverse solutions into the public domain, at least after some time. This
+would have a strong impact on the whole subject and the developers would
+benefit from feedback regarding the real needs of the end-users.}» Some major
+exploration service companies as well as certain research consortia and
+research groups own their 3D CSEM codes, but how about codes that are
+open-source? Academic codes were traditionally often available upon request by
+authors. Codes distributed that way were often provided with the request to not
+share the code, and they often come without a license attached which means that
+they are not open-source. Also, at times there can be significant hurdles to
+install a code.
 
 The meaning of the term open-source evolved rapidly in the last two decades.
-Today, open-source generally not only means that a code is available (with a proper license), but also that the code is hosted online, is under version control, has the possibility to file issues and make pull requests to fix bugs.
-These are important requirements for reproducible research «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{GEO.17.Broggini}.
-Well maintained codes often have continuous integration that includes testing of the code base and online hosted documentation, often including examples and tutorials.
-As such, the term has shifted from purely open-source codes to developments in the open with increasingly building a global community.
-Related projects within the realm of geophysical exploration are e.g., pyGIMLi \citep{CAG.17.Rucker} or Fatiando \citep{JOSS.18.Uieda}.
-\mycom[DW]{Others coming to your mind?}\mycom[RR]{no thoughts about geophysics, but there are many projects for related topics such as gmt, gis, mesh-gen}
+Today, open-source generally not only means that a code is available (with a
+proper license), but also that the code is hosted online, is under version
+control, has the possibility to file issues and make pull requests to fix bugs.
+These are important requirements for reproducible research «\emph{to provide
+the means by which the reader can verify the validity of the results and make
+use of them in further research}» \citep{GEO.17.Broggini}. Well maintained
+codes often have continuous integration that includes testing of the code base
+and online hosted documentation, often including examples and tutorials. As
+such, the term has shifted from purely open-source codes to developments in the
+open with increasingly building a global community. Related projects within the
+realm of geophysical exploration are e.g., pyGIMLi \citep{CAG.17.Rucker} or
+Fatiando \citep{JOSS.18.Uieda}. \mycom[DW]{Others coming to your
+mind?}\mycom[RR]{no thoughts about geophysics, but there are many projects for
+related topics such as gmt, gis, mesh-gen}
 
-\imycom[RR]{i suggest to use also "emph" style for all other package names, not only ours}
+\imycom[RR]{i suggest to use also "emph" style for all other package names, not
+only ours}
 
-We continue addressing the topic of open-source developments with respect to 3D CSEM modeling.
-Even though it comprises still the minority of developments, the landscape in this field of research changed in the last five years.
-Before, there were only closed-source codes owned by companies or  consortia and individual projects, often without a proper documentation, that could be requested from the authors.
-We introduce and compare four recent open-source projects with focus on 3D CSEM modeling.
-All presented codes are in the Python ecosystem and use either the FD method on structured grids or the FE method on unstructured tetrahedral meshes.
+We continue addressing the topic of open-source developments with respect to 3D
+CSEM modeling. Even though it comprises still the minority of developments, the
+landscape in this field of research changed in the last five years. Before,
+there were only closed-source codes owned by companies or  consortia and
+individual projects, often without a proper documentation, that could be
+requested from the authors. We introduce and compare four recent open-source
+projects with focus on 3D CSEM modeling. All presented codes are in the Python
+ecosystem and use either the FD method on structured grids or the FE method on
+unstructured tetrahedral meshes.
 
-Furthermore, we deal with the topic of verification.
-\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the verification of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
-Hence, we first conduct a similar exercise for CSEM codes.
-We want our efforts to help to ensure the reliability of simulations, not only carried out with the available open-source codes, but also for individual closed-source project.
-Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
-Beyond them, the only objective possibility to ensure the accuracy of solutions is by comparing results from different modellers.
-If different discretisations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
+Furthermore, we deal with the topic of verification. \cite{GJI.13.Miensopust}
+presents a review of two workshops dealing with the verification of
+magnetotelluric forward and inversion codes, but we are not aware of any
+comparable study or benchmark suite for CSEM data. Hence, we first conduct a
+similar exercise for CSEM codes. We want our efforts to help to ensure the
+reliability of simulations, not only carried out with the available open-source
+codes, but also for individual closed-source project. Analytical and
+semi-analytical solutions only exist for simple halfspace or layered-Earth
+models, which served mostly to verify new codes. Beyond them, the only
+objective possibility to ensure the accuracy of solutions is by comparing
+results from different modellers. If different discretisations and
+implementations of Maxwell's equations yield the same result, it gives
+confidence in their accuracy.
 
-We simulate EM fields for a layered background model with vertical transverse isotropy, containing three blocks, and the complex marine Marlim R3D model.
-These two model designs as well as the corresponding results from four different codes provide a benchmark for new codes to be compared to and validated with.
-In the following section, we introduce the codes under consideration.
-Afterwards, we present the considered benchmark cases in detail and present the modeling results of our four codes in terms of accuracy and computational performance.
-Beyond that, we extensively discuss important points that control the performance and suitability of our FD and FE codes, including mainly considerations about the mesh design and the choice of solvers.
-We conclude with a summary of our results and a motivation for the EM community to continue not only extending the landscape of open-source codes and also creating a landscape of open-source benchmark models.
+We simulate EM fields for a layered background model with vertical transverse
+isotropy, containing three blocks, and the complex marine Marlim R3D model.
+These two model designs as well as the corresponding results from four
+different codes provide a benchmark for new codes to be compared to and
+validated with. In the following section, we introduce the codes under
+consideration. Afterwards, we present the considered benchmark cases in detail
+and present the modeling results of our four codes in terms of accuracy and
+computational performance. Beyond that, we extensively discuss important points
+that control the performance and suitability of our FD and FE codes, including
+mainly considerations about the mesh design and the choice of solvers. We
+conclude with a summary of our results and a motivation for the EM community to
+continue not only extending the landscape of open-source codes and also
+creating a landscape of open-source benchmark models.
 
-\imycom[RR]{Regarding "It is worth mentioning that there are many more 3D EM codes developed in other fields than geophysics such as communication systems (antennas, radar, satellites), medical imaging, or civil engineering.
-    There are various open-source codes in these fields too, e.g., Elmer ([DW]: Add 2-3 proper references) (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't find a publication, just a poster).
-    While these codes could potentially be used for the same goals as presented here we restrict our review to codes purpose-built and ready without further adjustments for geophysical applications."
+\imycom[RR]{Regarding "It is worth mentioning that there are many more 3D EM
+  codes developed in other fields than geophysics such as communication systems
+  (antennas, radar, satellites), medical imaging, or civil engineering. There
+  are various open-source codes in these fields too, e.g., Elmer ([DW]: Add 2-3
+  proper references) (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't
+  find a publication, just a poster). While these codes could potentially be
+  used for the same goals as presented here we restrict our review to codes
+  purpose-built and ready without further adjustments for geophysical
+  applications."
 
-    I thought a lot about this but I just think the previous paragraph is not required in our introduction and haven't find a location where it fits considering different logical structures.
-I think it is also not important for this paper to tell "that there are more codes in EM than only geophysics", that's quite obvious.
-Maybe delete or shorten to 1 sentences to add Elmer and place this sentence somewhere else?
-I think, an appropriate list of all non-geophysical open-source EM codes should be very long anyway, we just don't know them or at least I'm not familiar with them.}
+  I thought a lot about this but I just think the previous paragraph is not
+  required in our introduction and haven't find a location where it fits
+  considering different logical structures. I think it is also not important
+  for this paper to tell "that there are more codes in EM than only
+  geophysics", that's quite obvious. Maybe delete or shorten to 1 sentences to
+  add Elmer and place this sentence somewhere else? I think, an appropriate
+  list of all non-geophysical open-source EM codes should be very long anyway,
+  we just don't know them or at least I'm not familiar with them.}
 
@@
 
-\imycom[RR]{I think we should introduce the term degrees of freedom (dof), equivalent to the size of the SLE, as general measure of our problem sizes.
-If it is somewhat x*Nedges, or related to Ncells or Nnodes, who cares?
-We just need this one number for this paper in my opinion, more details in the jupyter notebooks - fine.}
+\imycom[RR]{I think we should introduce the term degrees of freedom (dof),
+  equivalent to the size of the SLE, as general measure of our problem sizes.
+  If it is somewhat x*Nedges, or related to Ncells or Nnodes, who cares? We
+  just need this one number for this paper in my opinion, more details in the
+  jupyter notebooks - fine.}
 
-The four codes under consideration are, in alphabetical order, \custem \citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem \citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}.
-All four codes have their user-facing routines written in Python; all of them make heavy use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}.
-The four of them are “modern” open-source projects, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
-All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
-Newer package-management systems such as Conda, Docker, or pip significantly supported us to make our codes easily available and installable without any user-side compilations.
-Each one can be downloaded and installed with a single command.
+The four codes under consideration are, in alphabetical order, \custem
+\citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
+\citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
+codes have their user-facing routines written in Python; all of them make heavy
+use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy}
+\citep{NM.20.Virtanen}. The four of them are “modern” open-source projects,
+meaning that they come with both, an open-source license and an online-hosted
+version-control system with tracking possibilities (raising issues, filing pull
+requests). All developments comprise an extensive online documentation with
+many examples and have continuous integration to some degree. Newer
+package-management systems such as Conda, Docker, or pip significantly
+supported us to make our codes easily available and installable without any
+user-side compilations. Each one can be downloaded and installed with a single
+command.
 
-In the following a quick rundown of the codes.
-It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details.
-An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
-All codes have in common that they solve the\mycom[DW]{are we all using the weak form?} weak formulation of Maxwell's equation in its differential form (DE) under the quasistatic or\mycom[DW]{are we all using the diff.
-approx?} diffusive approximation, hence neglecting displacement currents.
-The machines on which the different codes were run are listed in Table~\ref{tbl:machines}, together with the responsible operator.
+In the following a quick rundown of the codes. It is, however, beyond the scope
+of this article to go into every detail of the different modellers, and we
+refer to their documentations for more details. An overview comparison of the
+different codes is given in Table~\ref{tbl:codecomparison}. All codes have in
+common that they solve the\mycom[DW]{are we all using the weak form?} weak
+formulation of Maxwell's equation in its differential form (DE) under the
+quasistatic or\mycom[DW]{are we all using the diff. approx?} diffusive
+approximation, hence neglecting displacement currents. The machines on which
+the different codes were run are listed in Table~\ref{tbl:machines}, together
+with the responsible operator.
 
@@
 
-\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations in its differential form (DE) under the quasistatic approximation.
-Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
+\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
+  in its differential form (DE) under the quasistatic approximation. Note that
+  \emg3d is a solver on its own, while the other codes implement third-package
+  solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS}
+  \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
 }{
@@
 
-The customisable electromagnetic modeling Python toolbox custEM was developed for simulating arbitrary complex 3D CSEM geometries with focus on semi-airborne setups, but it supports also land-based, airborne, coastal  or marine environments.
-Multiple electric or magnetic field or potential finite-element approaches were implemented as total or secondary field formulations.
-The finite-element kernel, including higher order basis functions and parallelisation, relies on the FEniCS project \citep{B.SPR.12.Logg, B.SPR.16.Langtangen}.
-The resulting systems of linear equations are solved with MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming choice. 
-Primary field solutions are supplied by the COMET \citep{GEO.20.Skibbe} package.
+The customisable electromagnetic modeling Python toolbox custEM was developed
+for simulating arbitrary complex 3D CSEM geometries with focus on semi-airborne
+setups, but it supports also land-based, airborne, coastal  or marine
+environments. Multiple electric or magnetic field or potential finite-element
+approaches were implemented as total or secondary field formulations. The
+finite-element kernel, including higher order basis functions and
+parallelisation, relies on the FEniCS project \citep{B.SPR.12.Logg,
+B.SPR.16.Langtangen}. The resulting systems of linear equations are solved with
+MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming
+choice. Primary field solutions are supplied by the COMET \citep{GEO.20.Skibbe}
+package.
 
-The toolbox considers generally anisotropic petrophysical properties.
-Even though changes of the conductivity is mainly of interest for CSEM modeling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
-Recently, induced polarization parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
-The provided meshing tools based on TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
+The toolbox considers generally anisotropic petrophysical properties. Even
+though changes of the conductivity is mainly of interest for CSEM modeling, the
+electric permittivity and magnetic permeability can be taken into account using
+the preferred electric field approach on Nédélec elements. Recently, induced
+polarization parameters in frequency-domain and three methods for simulating
+time-domain responses were added to custEM. The provided meshing tools based on
+TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker}
+facilitate the generation of tetrahedral meshes including layered-earth
+geometries with topography or bathymetry and anomalous bodies which are allowed
+to be connected or to reach the surface.
 
-The custEM toolbox is under steady development and maintenance.
-Future enhancements comprise adding iterative solution techniques, provided by FEniCS, as well as further functionalities for automatically incorporating intersecting bodies such as folds or faults in meshes.
-Furthermore, current work is on using custEM for inverse modeling applications.
+The custEM toolbox is under steady development and maintenance. Future
+enhancements comprise adding iterative solution techniques, provided by FEniCS,
+as well as further functionalities for automatically incorporating intersecting
+bodies such as folds or faults in meshes. Furthermore, current work is on using
+custEM for inverse modeling applications.
 
@@
 
-We computed the responses for two different models to verify that all different 3D codes yield the same electromagnetic responses.
-The first simple Block model consists of a layered, anisotropic
-background with three embedded blocks.
-The second Marlim R3D model is based on a very complex, realistic marine CSEM setup.
+We computed the responses for two different models to verify that all different
+3D codes yield the same electromagnetic responses. The first simple Block model
+consists of a layered, anisotropic background with three embedded blocks. The
+second Marlim R3D model is based on a very complex, realistic marine CSEM
+setup.
 
@@
 
-\imycom[RR]{I think the miensopust argument is rather suited to motivate our work in the introduction, i hope its fine that i moved this argument}
+\imycom[RR]{I think the miensopust argument is rather suited to motivate our
+work in the introduction, i hope its fine that i moved this argument}
 
-The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modeling workshop described by \cite{GJI.13.Miensopust}.
-We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}.
-We additionally added a layered background with vertical transverse isotropy (VTI).
+The block model is a derivation of the \emph{Dublin Test Model 1} from the
+first EM modeling workshop described by \cite{GJI.13.Miensopust}. We took the
+same layout of the blocks but adjusted the dimensions and resistivities to a
+typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}. We
+additionally added a layered background with vertical transverse isotropy
+(VTI).
 %
@@
 
-The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretisation.
-Therefore, the FE codes custEM and PETGEM used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
-This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
-\imycom[RR]{Add short information about mesh design with SIMPEG and emg3d, including something like "comparatively coarse discretization in center to minimize computation times" }
+The thin isotropic layer beneath the water requires many tetrahedra for a
+good-quality discretisation. Therefore, the FE codes custEM and PETGEM used the
+same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the
+origin, surrounded by a ten times larger halfspace-like boundary mesh with
+water conductivities assigned to the subsurface. This approximation
+significantly reduced the problem size compared to considering the
+layered-earth geometry for the whole computational domain. \imycom[RR]{Add
+short information about mesh design with SIMPEG and emg3d, including something
+like "comparatively coarse discretization in center to minimize computation
+times" }
 
-In a first step, we compare the layered background to the semi-analytical solutions of a 1D code, for which we use  \empymod\citep{GEO.17.Werthmuller}.
-Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the actual responses in the top rows, and the relative error in the bottom rows for the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
+In a first step, we compare the layered background to the semi-analytical
+solutions of a 1D code, for which we use  \empymod\citep{GEO.17.Werthmuller}.
+Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the
+actual responses in the top rows, and the relative error in the bottom rows for
+the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
 
-Figure~\ref{fig:results-layered-0} illustrates the inline responses in the top-row for offsets $r>0.5\,$km. We only show the
-semi-analytical result for the real and imaginary amplitudes.
-The bottom row displays the relative error of the 3D codes.
-The results show that all codes are yielding accurate result with errors of around 1\,\% in most parts and overall below a few percent, disregarding locations affected by sign reversals.
-The differences can be mainly attributed to the chosen discretisations.
-The FE codes show the strongest misfits at large offsets, most likely caused by the utilized boundary mesh, whereas \emg3d seems to do a very good job\mycom[RR]{maybe reformulate to something like: whereas emg3d appears to be not affected by boundary effects}.
-Close to the 200\,m long source, emg3d is less precise which is attributed to comparatively large cell sizes in this region.
+Figure~\ref{fig:results-layered-0} illustrates the inline responses in the
+top-row for offsets $r>0.5\,$km. We only show the semi-analytical result for
+the real and imaginary amplitudes. The bottom row displays the relative error
+of the 3D codes. The results show that all codes are yielding accurate result
+with errors of around 1\,\% in most parts and overall below a few percent,
+disregarding locations affected by sign reversals. The differences can be
+mainly attributed to the chosen discretisations. The FE codes show the
+strongest misfits at large offsets, most likely caused by the utilized boundary
+mesh, whereas \emg3d seems to do a very good job\mycom[RR]{maybe reformulate to
+something like: whereas emg3d appears to be not affected by boundary effects}.
+Close to the 200\,m long source, emg3d is less precise which is attributed to
+comparatively large cell sizes in this region.
 %
@@
 
-\imycom[RR]{I suggest to show y-component for broadside and the errors of the weak component (if not too bad), otherwise only broadside is required to save a plot, because inline should be better for Ex in general.}
-The corresponding broadside responses for $y=\pm3\,$km are shown in Figure~\ref{fig:results-layered--3}.
-The CPU and RAM requirements are listed in Table~\ref{tbl:comp-layered}.
+\imycom[RR]{I suggest to show y-component for broadside and the errors of the
+  weak component (if not too bad), otherwise only broadside is required to save
+  a plot, because inline should be better for Ex in general.} The corresponding
+  broadside responses for $y=\pm3\,$km are shown in
+  Figure~\ref{fig:results-layered--3}. The CPU and RAM requirements are listed
+  in Table~\ref{tbl:comp-layered}.
 %
@@
 
-In a second step, three resistive blocks were added in the 3.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}.
-They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
-As there are no analytical solutions for this model we show the normalized difference between different codes, instead of the relative error, where the normalized difference of two responses $p$ and $q$ is given by
+In a second step, three resistive blocks were added in the 3.3\,km-thick,
+anisotropic background layer as shown in Figure~\ref{fig:block-model}. They
+have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey
+lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$
+(cube, North-West). As there are no analytical solutions for this model we show
+the normalized difference between different codes, instead of the relative
+error, where the normalized difference of two responses $p$ and $q$ is given by
 %
@@
 %
-\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too cluttered, and I don't think it would add a lot insights.
-My idea is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones), and \emg3d/\custem (a cross-comparison).
-What do you think?}
+\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too
+cluttered, and I don't think it would add a lot insights. My idea is therefore
+to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones),
+and \emg3d/\custem (a cross-comparison). What do you think?}
 
-\imycom[RR]{Agreed.
-Another suggestion, I solved this visualization problem with a color coded matrix plot, showing 90th percentiles or median values of all errors along the line as meaningful comprehensive number.
-Look in my thesis - example 4.
-Comparison for real and imag could be in the lower and upper triangles, or we show absolute magnitudes for layered earth in lower triangle and for block model in upper triangle.
-With help of this plot, one could easily say if differences are higher for block model and which codes fit to each other well.}
+\imycom[RR]{Agreed. Another suggestion, I solved this visualization problem
+  with a color coded matrix plot, showing 90th percentiles or median values of
+  all errors along the line as meaningful comprehensive number. Look in my
+  thesis - example 4. Comparison for real and imag could be in the lower and
+  upper triangles, or we show absolute magnitudes for layered earth in lower
+  triangle and for block model in upper triangle. With help of this plot, one
+  could easily say if differences are higher for block model and which codes
+  fit to each other well.}
 
-\imycom[RR]{If using the mentioned matrix plots, we would need only one of the figures 4-6, and could show the other data comprehensively.
-I added a python script to generate an example of my plotting suggestion in the model-block directory and a new Figure 7 in the manuscript that illustrates what I mean.
-Of course, any upgrade suggestion for this initial idea is welcome, aside from making it looking nice with labels  and annotations.}
+\imycom[RR]{If using the mentioned matrix plots, we would need only one of the
+  figures 4-6, and could show the other data comprehensively. I added a python
+  script to generate an example of my plotting suggestion in the model-block
+  directory and a new Figure 7 in the manuscript that illustrates what I mean.
+  Of course, any upgrade suggestion for this initial idea is welcome, aside
+  from making it looking nice with labels  and annotations.}
 
-The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in Table~\ref{tbl:comp-block}.
-We can conclude from the NRMSD that similar codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very similar, as well as are \custem and \petgem.
-\mycom[DW]{Write in detail when all results are available}
+The results for the three receiver lines $y=-3,0,3\,$km are shown in
+Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and
+\ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in
+Table~\ref{tbl:comp-block}. We can conclude from the NRMSD that similar codes
+have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very
+similar, as well as are \custem and \petgem. \mycom[DW]{Write in detail when
+all results are available}
 %
@@
 
-The difference becomes only significant at offsets larger than 8\,km. This is due to a practical difference in the meshing: This simple block model
-is advantageous for FV codes, as it consists of rectangular blocks and
-horizontal layers, simple geometric objects. While having a very thin, shallow
-layer is straight-forward for FV codes, it requires many cells for a FE code.
-The thin layer was therefore limited in its horizontal extent
-to\mycom[DW]{Raphael, to what x/y exactly?} ???. This is the reason for the
-increased NRMSD at large offsets, and it has nothing to do with the accuracy of
-the computation itself.\mycom[RR]{see imycom below figure 6}
+The difference becomes only significant at offsets larger than 8\,km. This is
+due to a practical difference in the meshing: This simple block model is
+advantageous for FV codes, as it consists of rectangular blocks and horizontal
+layers, simple geometric objects. While having a very thin, shallow layer is
+straight-forward for FV codes, it requires many cells for a FE code. The thin
+layer was therefore limited in its horizontal extent to\mycom[DW]{Raphael, to
+what x/y exactly?} ???. This is the reason for the increased NRMSD at large
+offsets, and it has nothing to do with the accuracy of the computation
+itself.\mycom[RR]{see imycom below figure 6}
 
-\imycom[RR]{60 x 60 km (30 km in each direction from center).
-I already added a paragraph about mesh generation in the beginning, I suggest to remove this description here and jsut refer to like "Similar to the layered earth model, the largest errors occur at offsets $>8$\,km due to the differences in mesh design."
-We should also mention that relative errors are related to the magnitudes, as real is so much weaker at larger offsets, it is clear that errors increase significantly.
-Alternatively, we could show absolute magnitude or phase errors such as in the Marlim model.}
+\imycom[RR]{60 x 60 km (30 km in each direction from center). I already added a
+  paragraph about mesh generation in the beginning, I suggest to remove this
+  description here and jsut refer to like "Similar to the layered earth model,
+  the largest errors occur at offsets $>8$\,km due to the differences in mesh
+  design." We should also mention that relative errors are related to the
+  magnitudes, as real is so much weaker at larger offsets, it is clear that
+  errors increase significantly. Alternatively, we could show absolute
+  magnitude or phase errors such as in the Marlim model.}
 
@@
 
-The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in the north-eastern part of the Campos Basin, offshore Brazil, which was discovered in 1985.
-\cite{BJG.17.Carvalho} created from seismic data and well log data a realistic resistivity model with vertical transverse isotropy (VTI), Marlim R3D (MR3D), which they released under an open-source license.
-\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to 1.25\,Hz, released under an open-source license.
-To compute the data they used a state-of-the-art code from the industry \citep{GEO.07.Maao}.
-It is therefore an ideal case to verify our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.\mycom[RR]{I would delete this sentence, not that important and a bit redundant}
-Additionally, that code is a time-domain code, whereas the four codes under consideration here compute the results all in the frequency-domain.
+The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
+the north-eastern part of the Campos Basin, offshore Brazil, which was
+discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
+log data a realistic resistivity model with vertical transverse isotropy (VTI),
+Marlim R3D (MR3D), which they released under an open-source license.
+\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to
+1.25\,Hz, released under an open-source license. To compute the data they used
+a state-of-the-art code from the industry \citep{GEO.07.Maao}. It is therefore
+an ideal case to verify our open-source codes against, as it is a complex,
+realistic model and the data were computed by an industry-proofed
+code.\mycom[RR]{I would delete this sentence, not that important and a bit
+redundant} Additionally, that code is a time-domain code, whereas the four
+codes under consideration here compute the results all in the frequency-domain.
 
-The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
-For the computation the model is upscaled to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
+The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling
+to almost 466 million cells, where each cell has dimensions of 25 by 75 by
+5\,m. For the computation the model is upscaled to 515 by 563 by 310 cells,
+totalling to almost 90 million cells, where each cell has dimensions of 100 by
+100 by 20\,m.
 
-The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
-45 source-towlines were located on the same grid, 50\,m above the seafloor, with shots every 100\,m. In
-\cite{GEO.19.Correa} the actual responses for one receiver with the corresponding East-West inline and one East-West broadside acquisition line are shown, which is the data we chose for our comparison.
-The cross-section of the resistivity model along the chosen inline acquisition line is shown in Figure~\ref{fig:model-marlim}, together with the acquisition information.
+The published data set consists of a regular grid of receivers of 20 in eastern
+direction by 25 in northern direction, 500 receivers in total, with 1\,km
+spacing located on the irregular seafloor. 45 source-towlines were located on
+the same grid, 50\,m above the seafloor, with shots every 100\,m. In
+\cite{GEO.19.Correa} the actual responses for one receiver with the
+corresponding East-West inline and one East-West broadside acquisition line are
+shown, which is the data we chose for our comparison. The cross-section of the
+resistivity model along the chosen inline acquisition line is shown in
+Figure~\ref{fig:model-marlim}, together with the acquisition information.
 
-\imycom[RR]{I used gmt the last time 7 years ago , in between I tried the gmt4py tools, but they did not work well on my machine.
-I suggest to use two plots next to each other, a similar figure as in the notebook and a simple x-y coord sketch (identical extent as the bird perspective view in the other plot) with all Tx / Rx locations, highlighting the relevant line and Rx for us.}
+\imycom[RR]{I used gmt the last time 7 years ago , in between I tried the
+  gmt4py tools, but they did not work well on my machine. I suggest to use two
+  plots next to each other, a similar figure as in the notebook and a simple
+  x-y coord sketch (identical extent as the bird perspective view in the other
+  plot) with all Tx / Rx locations, highlighting the relevant line and Rx for
+  us.}
 
@@
 We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$)
-for both inline and broadside acquisition lines. However, we show here only
-the three frequencies and the responses with the strongest amplitudes (which
-are generally used in processing), which are $E_x$ inline and broadside and
-$E_y$ broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
+for both inline and broadside acquisition lines. However, we show here only the
+three frequencies and the responses with the strongest amplitudes (which are
+generally used in processing), which are $E_x$ inline and broadside and $E_y$
+broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
 %
@@
 
-\imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone adds the own thoughts when he receives the manuscript.
-Same for conclusions.
-We need to take care to not mix discussion and conclusions, some of the statements from here belong rather to the conclusions, I hope it's fine that I reorganized the content.
-Aside from that, I already added all thoughts of mine.}
+\imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone
+  adds the own thoughts when he receives the manuscript. Same for conclusions.
+  We need to take care to not mix discussion and conclusions, some of the
+  statements from here belong rather to the conclusions, I hope it's fine that
+  I reorganized the content. Aside from that, I already added all thoughts of
+  mine.}
 
-Even if modeling results may look completely valid, they could not be correct at all.
-Verifying the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
-Overall, we observed an excellent match between all solutions.
-The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation.
-Considering this satisfactory result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
-The following arguments are based on a comparison of only marine CSEM models, which are the focus of industry applications.
-Nevertheless, we are confident that many observations would hold in a similar manner for land-based, airborne, or mixed setups.
+Even if modeling results may look completely valid, they could not be correct
+at all. Verifying the performance of 3D CSEM codes for real 3D problems is only
+possible by cross-validating multiple solutions. Overall, we observed an
+excellent match between all solutions. The relative misfits, almost always
+smaller than 10\,\%, were related to the either weak or strong amplitudes of
+real or imaginary parts and can be attributed to particularities regarding the
+discretization, boundary effects, and interpolation. Considering this
+satisfactory result in terms of accuracy and robustness, it is more interesting
+to discuss the characteristics of the four considered codes with focus on the
+demand of computational resources and the capability of handling the
+investigated CSEM geometries, including the very important underlying mesh
+design. The following arguments are based on a comparison of only marine CSEM
+models, which are the focus of industry applications. Nevertheless, we are
+confident that many observations would hold in a similar manner for land-based,
+airborne, or mixed setups.
 
-We point out that making a synthetic and a real benchmark model available to cross-validate any 3D CSEM code was the determining reason for their choice, regardless of the suitability of the considered FD and FE codes for these problems.
-The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
-Aside from the idea of analyzing an industrially relevant benchmark example, the Marlim R3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretisation. 
-At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
-Hence, the chosen examples favoured the finite-difference codes, since they used either regular grids or octree-meshes, whereas the two finite-element codes were required to tetrahedralise the model geometries.
+We point out that making a synthetic and a real benchmark model available to
+cross-validate any 3D CSEM code was the determining reason for their choice,
+regardless of the suitability of the considered FD and FE codes for these
+problems. The first model, including the block-anomalies variation, is exactly
+reproducible by using any numerical method with either regular or irregular
+computational domains. Aside from the idea of analyzing an industrially
+relevant benchmark example, the Marlim R3D model was also considered since the
+primary design from \cite{GEO.19.Correa} uses a regular discretisation. At
+least theoretically, the exact geometry might be reconstructed with
+unstructured meshes, but it is never possible to convert an irregular geometry
+to a regular grid without approximations. Hence, the chosen examples favoured
+the finite-difference codes, since they used either regular grids or
+octree-meshes, whereas the two finite-element codes were required to
+tetrahedralise the model geometries.
 
-In the first model, the necessity of discretising regular structures with tetrahedra, especially thin layers, led to comparatively large FE problem sizes and computational resource demands.
-FE codes with unstructured meshes were probably the poorest choice of all commonly used methods for this setup in terms of computational performance.
-However, thinking about introducing just one slight irregularity such as bathymetry, a thin dipping plate or an anticline, the performance behaviour could likely switch.
-All of these changes would barely change the problem size for the FE codes, but significantly increase it for the FD codes if the true geometry should be approximated sufficiently accurate.
+In the first model, the necessity of discretising regular structures with
+tetrahedra, especially thin layers, led to comparatively large FE problem sizes
+and computational resource demands. FE codes with unstructured meshes were
+probably the poorest choice of all commonly used methods for this setup in
+terms of computational performance. However, thinking about introducing just
+one slight irregularity such as bathymetry, a thin dipping plate or an
+anticline, the performance behaviour could likely switch. All of these changes
+would barely change the problem size for the FE codes, but significantly
+increase it for the FD codes if the true geometry should be approximated
+sufficiently accurate.
 
-The real Marlim R3D model was, ironically, the ideal case for FE codes because it's structure was characterized by irregular lithological horizons obtained from seismic data.
-Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
-We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
-Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
-The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+The real Marlim R3D model was, ironically, the ideal case for FE codes because
+it's structure was characterized by irregular lithological horizons obtained
+from seismic data. Since the corresponding published resistivity model was
+defined on a regular grid, we were forced to approximate the comparatively fine
+regular discretization by an unstructured one and interpolate the resistivity
+data for being able to apply the FE codes to this problem. We are completely
+aware about the ineptness of this re-approximation procedure, unless it served
+for the cross-validation purposes. Nevertheless, the chosen tetrahedral
+discretization, especially in combination with second order basis functions,
+showed clearly the intrinsic strength of the FE codes, requiring significantly
+less dof for meshing irregular geometries in general. The p2 FE solution
+required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system
+by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
 
-The codes under consideration use direct and indirect solvers. In general, the biggest advantage of iterative solvers with appropriate preconditioners are the comparatively small memory requirements.
-Direct solvers can be considered as most robust to solve any ill-conditioned SLE, which is most important for systems of the FE method on unstructured meshes.
-As the consumed computational resources indicate, a more powerful machine than a laptop is required for most 3D CSEM problems, but no high-performance-computing architecture.
+The codes under consideration use direct and indirect solvers. In general, the
+biggest advantage of iterative solvers with appropriate preconditioners are the
+comparatively small memory requirements. Direct solvers can be considered as
+most robust to solve any ill-conditioned SLE, which is most important for
+systems of the FE method on unstructured meshes. As the consumed computational
+resources indicate, a more powerful machine than a laptop is required for most
+3D CSEM problems, but no high-performance-computing architecture.
 
-The computation times can differ significantly for specific simulations, but there is no clear general advantage for one of the solver types. 
-In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d.
-Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be calculated in the same computational domain.
-As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d.
-For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the calculation for multiple sources, but this argumentation is beyond the scope of this work.
+The computation times can differ significantly for specific simulations, but
+there is no clear general advantage for one of the solver types. In our models,
+the runtime comparison favoured the iterative solver and therefore, \emg3d.
+Even though not shown here, direct solvers exhibit their strongest advantage in
+terms of computation times if responses of multiple CSEM transmitters need to
+be calculated in the same computational domain. As the system matrix
+factorisation requires 98-99\,\% of the solution time, computations for
+additional sources come at almost no cost for direct solvers, i.e., MUMPS,
+whereas it would come at the same cost as the first source for \emg3d. For the
+sake of completeness, note that there are also advanced techniques for
+iterative solvers to make use of preconditioners, factorisations, or
+intermediate solutions of the previous SLE to speed up the calculation for
+multiple sources, but this argumentation is beyond the scope of this work.
 
-We see this work as the start for future elaboration on the validation of modeling codes, not necessarily restricted to CSEM problems.
-Much more comparisons and examples are required which not only result in the finding that a sufficient accuracy was observed. 
-3D CSEM modelling is a difficult task, which requires many considerations. It starts with the selection of the right code for the problem. 
-We found that the meshing task, which is most performance determining, is particularly difficult and relevant, choosing cells small enough to appropriately represent the model yet to be as coarse as possible still achieving the desired precision.
-The required model extent has to be considered as well, thinking also about effects of the so-called airwave in marine setups or boundary meshes in general.
-This is not a new finding but rather well known fact.
-We are surprised that only the minority of publications in the field of 3D EM modeling considers a sufficiently detailed elaboration of the meshing process.
+We see this work as the start for future elaboration on the validation of
+modeling codes, not necessarily restricted to CSEM problems. Much more
+comparisons and examples are required which not only result in the finding that
+a sufficient accuracy was observed. 3D CSEM modelling is a difficult task,
+which requires many considerations. It starts with the selection of the right
+code for the problem. We found that the meshing task, which is most performance
+determining, is particularly difficult and relevant, choosing cells small
+enough to appropriately represent the model yet to be as coarse as possible
+still achieving the desired precision. The required model extent has to be
+considered as well, thinking also about effects of the so-called airwave in
+marine setups or boundary meshes in general. This is not a new finding but
+rather well known fact. We are surprised that only the minority of publications
+in the field of 3D EM modeling considers a sufficiently detailed elaboration of
+the meshing process.
 
-A completely objective evaluation of codes is only possible by cross-validation.
-Nevertheless, we point out that using different discretizations or formulations of the numerical approach, e.g.
-by choosing field or potential approaches, second or total field formulations, different polynomial order basis functions, and others, is a suitable alternative to the cross-comparison of multiple codes for self-validating complex 3D results.
-This is a very powerful method to confirm the general functionality of codes for any modeling problem, which might not be covered by existing cross-validation benchmark examples.
-Considering for instance  this study, it would be very optimistic to estimate the accuracy of the utilized codes for a land-based mineral exploration setup with a highly-conductive, steeply-dipping conductor.
-However, each modeller could run multiple simulations with different configurations to increase the reliability of the obtained results.
+A completely objective evaluation of codes is only possible by
+cross-validation. Nevertheless, we point out that using different
+discretizations or formulations of the numerical approach, e.g. by choosing
+field or potential approaches, second or total field formulations, different
+polynomial order basis functions, and others, is a suitable alternative to the
+cross-comparison of multiple codes for self-validating complex 3D results. This
+is a very powerful method to confirm the general functionality of codes for any
+modeling problem, which might not be covered by existing cross-validation
+benchmark examples. Considering for instance  this study, it would be very
+optimistic to estimate the accuracy of the utilized codes for a land-based
+mineral exploration setup with a highly-conductive, steeply-dipping conductor.
+However, each modeller could run multiple simulations with different
+configurations to increase the reliability of the obtained results.
 
@@
   encountered in this exercise. This includes differences from direct to
-    iterative solver and differences from FE to FD codes etc. Please just jot down
-    things that come to your mind.}
+  iterative solver and differences from FE to FD codes etc. Please just jot
+  down things that come to your mind.}
 
@@
 
-\imycom[RR]{I also rearranged some of your thoughts and formulated mine. I moved some of them (the few sentences that were rather redundant motivation content) to the introdcution.}
+\imycom[RR]{I also rearranged some of your thoughts and formulated mine. I
+  moved some of them (the few sentences that were rather redundant motivation
+content) to the introdcution.}
 
-We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, including a modification with three resistive blocks, and the realistic marine Marlim R3D model.
-All comparisons exhibited an excellent reliability of the solutions.
-Our data should make it very easy for new codes to have a readily available data set to test against and verify.
-We are confident that the discussions about runtimes, memory consumptions, solver choices, and, most important, discretisations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
+We compared four different open-source 3D CSEM modellers by computing responses
+for a layered, anisotropic model, including a modification with three resistive
+blocks, and the realistic marine Marlim R3D model. All comparisons exhibited an
+excellent reliability of the solutions. Our data should make it very easy for
+new codes to have a readily available data set to test against and verify. We
+are confident that the discussions about runtimes, memory consumptions, solver
+choices, and, most important, discretisations of the 3D CSEM problems help
+potential users not only to decide which modeller is best suited for specific
+tasks, but also to support their individual projects.
 
-As none of the considered methods is best suited for all problems,
-it is important to have more test models for various scenarios in future.
-Our study is limited to marine CSEM cases in the frequency-domain.
-Reasonable extensions include providing benchmark models for land, airborne, or mixed CSEM environments as well as time-domain data.
-Another addition to this work would be focusing on complex irregular  models, tailored for an FE or FV code based on unstructured meshes, and to compare how the FD codes can cope with it.
+As none of the considered methods is best suited for all problems, it is
+important to have more test models for various scenarios in future. Our study
+is limited to marine CSEM cases in the frequency-domain. Reasonable extensions
+include providing benchmark models for land, airborne, or mixed CSEM
+environments as well as time-domain data. Another addition to this work would
+be focusing on complex irregular  models, tailored for an FE or FV code based
+on unstructured meshes, and to compare how the FD codes can cope with it.
 
-We encourage the community to not only work on new open-source code developments but also to create a landscape of easily accessible benchmark models for increasing the number of reliable and reproducible solutions.
-Our study could provide one of the primary inputs for this task.  
-We are confident that the mentioned development will and should be taking place, taking into account the current general trend in science to open-source papers, codes or data.
+We encourage the community to not only work on new open-source code
+developments but also to create a landscape of easily accessible benchmark
+models for increasing the number of reliable and reproducible solutions. Our
+study could provide one of the primary inputs for this task.  We are confident
+that the mentioned development will and should be taking place, taking into
+account the current general trend in science to open-source papers, codes or
+data.
 
@@
 
-We would like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
+We would like to thank Paulo Menezes for the help and explanations with regards
+to the Marlim R3D model and corresponding CSEM data, and for making their
+actual computation model available under an open-source license.
 
-The work of D.W. was conducted within the Gitaro.JIM project funded through MarTERA, a EU Horizon 2020 research and innovation programme (No 728053); \href{https://www.martera.eu}{martera.eu}.
-The development of custEM as part of the DESMEX project was funded by the Germany Ministry for Education and Research (BMBF) in the framework of the research and development program Fona-r4 under grant 033R130D.
+The work of D.W. was conducted within the Gitaro.JIM project funded through
+MarTERA, a EU Horizon 2020 research and innovation programme (No 728053);
+\href{https://www.martera.eu}{martera.eu}. The development of custEM as part of
+the DESMEX project was funded by the Germany Ministry for Education and
+Research (BMBF) in the framework of the research and development program
+Fona-r4 under grant 033R130D.
 
@@
 
-All files to rerun the different models with the four codes and reproduce the shown results are available at \dots.
+All files to rerun the different models with the four codes and reproduce the
+shown results are available at \dots.
 \itodo{Put up on Zenodo, link here.}

### 2020-05-25 manuscript/Manuscript.tex

@@
 \usepackage[textsize=footnotesize, textwidth=2.8cm]{todonotes}
+% \usepackage[textsize=footnotesize, textwidth=2.8cm, disable]{todonotes}
 
@@
   and for inline comments, use:\\[.2cm]
-  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}
+  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}\\[.5cm]
+  If you want to compile it without comments, comment the line\\[.2cm]
+  \qquad\texttt{\textbackslash usepackage[textsize=footnotesize, textwidth=2.8cm]\{todonotes\}}\\[.2cm]
+  and uncomment the line\\[.2cm]
+  \qquad\texttt{\% \textbackslash usepackage[textsize=footnotesize, textwidth=2.8cm, disable]\{todonotes\}}
 }
@@
   words). I hope there are not too many inconsistencies, as probably Lindsey
-  has to fix all these mistakes in the end:-)}
+  has to fix all these mistakes in the end:-)
 \imycom[DW]{Be aware of Canadian English and Australian English :-D -- You are
@@
   what journal we submit. With an appropriate spellchecker that should be a
-  quick thing then.}
+  quick thing then.}}
 
@@
 these electromagnetic fields is therefore of great interest to design survey
-layouts, understand the measured data and inversion purposes. Publications
-regarding 3D modelling in electromagnetic methods started to appear as early as
-the 1970's and 1980's. These early publications were integral equation (IE)
-methods, having an anomaly embedded within a layered medium, mostly for
-loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann,
-GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements
-\citep{GEO.84.Wannamaker}.
+layouts, to understand the measured data, and for inversion purposes.
+Publications regarding 3D modelling in electromagnetic methods started to
+appear as early as the 1970's and 1980's. These early publications were
+integral equation (IE) methods, having an anomaly embedded within a layered
+medium, mostly for loop-loop type transient EM measurements
+\citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and
+magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
 
@@
 exploration service companies as well as certain research consortia and
-research groups own their 3D CSEM codes, but how about codes that are
+research groups have their own 3D CSEM codes, but how about codes that are
 open-source? Academic codes were traditionally often available upon request by
@@
 share the code, and they often come without a license attached which means that
-they are not open-source. Also, at times there can be significant hurdles to
-install a code.
+they are, legally, not open-source. Also, at times there can be significant
+hurdles to install a code.
 
@@
 open with increasingly building a global community. Related projects within the
-realm of geophysical exploration are e.g., pyGIMLi \citep{CAG.17.Rucker} or
-Fatiando \citep{JOSS.18.Uieda}. \mycom[DW]{Others coming to your
-mind?}\mycom[RR]{no thoughts about geophysics, but there are many projects for
-related topics such as gmt, gis, mesh-gen}
-
-\imycom[RR]{i suggest to use also "emph" style for all other package names, not
-only ours}
+realm of geophysical exploration are e.g., \texttt{pyGIMLi}
+\citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}.
+\imycom[DW]{Others coming to your mind?\imycom[RR]{no thoughts about geophysics,
+  but there are many projects for related topics such as gmt, gis, mesh-gen}}
 
@@
 conclude with a summary of our results and a motivation for the EM community to
-continue not only extending the landscape of open-source codes and also
-creating a landscape of open-source benchmark models.
-
-\imycom[RR]{Regarding "It is worth mentioning that there are many more 3D EM
+not only continue to extend the landscape of open-source codes but to also
+create a landscape of open-source benchmark models.
+
+\imycom[RR]{Regarding
+  \todo[inline, color=white]{
+  "It is worth mentioning that there are many more 3D EM
   codes developed in other fields than geophysics such as communication systems
   (antennas, radar, satellites), medical imaging, or civil engineering. There
-  are various open-source codes in these fields too, e.g., Elmer ([DW]: Add 2-3
-  proper references) (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't
-  find a publication, just a poster). While these codes could potentially be
-  used for the same goals as presented here we restrict our review to codes
-  purpose-built and ready without further adjustments for geophysical
-  applications."
-
+  are various open-source codes in these fields too, e.g., Elmer
+  (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't
+  find a publication, just a poster).
+  \todo[inline, color=gray]{(\textbf{[DW]}: Add 2-3 proper references)}
+  While these codes could potentially be used for the same goals as presented
+  here we restrict our review to codes purpose-built and ready without further
+  adjustments for geophysical applications."
+}
   I thought a lot about this but I just think the previous paragraph is not
@@
 
-\imycom[RR]{too much info (redundancy to text) for table caption}
-
-\tabl[btp]{codecomparison}{All codes solve the weak form of Maxwell's equations
-  in its differential form (DE) under the quasistatic approximation. Note that
-  \emg3d is a solver on its own, while the other codes implement third-package
-  solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS}
-  \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.
+\tabl[btp]{codecomparison}{Comparison of the four codes under consideration.
+  Note that \emg3d is a solver on its own, while the other codes implement
+  third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar},
+  \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO}
+  \citep{FGCS.04.Schenk}.
 }{
@@
 We computed the responses for two different models to verify that all different
-3D codes yield the same electromagnetic responses. The first simple Block model
-consists of a layered, anisotropic background with three embedded blocks. The
-second Marlim R3D model is based on a very complex, realistic marine CSEM
-setup.
-
-\subsection{Block model}
-
-\imycom[RR]{I think the miensopust argument is rather suited to motivate our
-work in the introduction, i hope its fine that i moved this argument}
+3D codes yield the same electromagnetic responses. The first simple \emph{Block
+model} consists of a layered, anisotropic background with three embedded
+blocks. The second Marlim R3D model is based on a very complex, realistic
+marine CSEM setup.
+
+\subsection{Block Model}
 
@@
 strongest misfits at large offsets, most likely caused by the utilized boundary
-mesh, whereas \emg3d seems to do a very good job\mycom[RR]{maybe reformulate to
-something like: whereas emg3d appears to be not affected by boundary effects}.
-Close to the 200\,m long source, emg3d is less precise which is attributed to
-comparatively large cell sizes in this region.
+mesh. Very low errors at large offsets are achieved by \emg3d, whereas it
+suffers at short offsets from a coarse grid.
 %
@@
 to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones),
-and \emg3d/\custem (a cross-comparison). What do you think?}
+and \emg3d/\custem (a cross-comparison). What do you think?
 
@@
   fit to each other well.}
-
 \imycom[RR]{If using the mentioned matrix plots, we would need only one of the
@@
   from making it looking nice with labels  and annotations.}
+}
 
@@
 layers, simple geometric objects. While having a very thin, shallow layer is
-straight-forward for FV codes, it requires many cells for a FE code. The thin
-layer was therefore limited in its horizontal extent to\mycom[DW]{Raphael, to
-what x/y exactly?} ???. This is the reason for the increased NRMSD at large
-offsets, and it has nothing to do with the accuracy of the computation
-itself.\mycom[RR]{see imycom below figure 6}
-
-\imycom[RR]{60 x 60 km (30 km in each direction from center). I already added a
-  paragraph about mesh generation in the beginning, I suggest to remove this
-  description here and jsut refer to like "Similar to the layered earth model,
-  the largest errors occur at offsets $>8$\,km due to the differences in mesh
-  design." We should also mention that relative errors are related to the
-  magnitudes, as real is so much weaker at larger offsets, it is clear that
-  errors increase significantly. Alternatively, we could show absolute
-  magnitude or phase errors such as in the Marlim model.}
+straight-forward for FV codes, it requires many cells for a FE code, and
+a similar approach as for the Block Model was used. This is the reason for the
+increased NRMSD at large offsets, and it has nothing to do with the accuracy of
+the computation itself.
 
@@
 \plot*{median-stats-block}{width=\textwidth}{
+  {\imycom[DW]{Suggestion from Raphael for a statistics plot.}}
     Overall misfit relations between all codes for the three receiver lines
@@
 realistic model and the data were computed by an industry-proofed
-code.\mycom[RR]{I would delete this sentence, not that important and a bit
-redundant} Additionally, that code is a time-domain code, whereas the four
-codes under consideration here compute the results all in the frequency-domain.
+code. Additionally, that code is a time-domain code, whereas the four codes
+under consideration here compute the results all in the frequency-domain.
+\imycom[RR]{I would delete this sentence, not that important and a bit
+redundant.\imycom[DW]{Did you refer to the last sentence or the one before? I
+think the last sentence contains quite important info.}}
 
@@
 
+%
+\plot*{model-marlim}{width=\textwidth}{
+  This figure obviously needs to be improved massively (at least a colorbar).
+  What would you like to show from the actual data here?
+  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
+  the drawn survey line in that figure are plainly wrong.
+  {\imycom[DW]{If someone is
+  familiar with GMT and happy to make that would be great. Also, the
+cross-section is currently heavily vertically exaggerated.
 \imycom[RR]{I used gmt the last time 7 years ago , in between I tried the
@@
   plot) with all Tx / Rx locations, highlighting the relevant line and Rx for
-  us.}
-
-%
-\plot*{model-marlim}{width=\textwidth}{
-  This figure obviously needs to be improved massively (at least a colorbar).
-  What would you like to show from the actual data here?
-  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
-  the drawn survey line in that figure are plainly wrong. If someone is
-  familiar with GMT and happy to make that would be great. Also, the
-  cross-section is currently heavily vertically exaggerated.
+  us.}}}
 }
@@
 \imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
-collaboratively at the same time?}
-
+collaboratively at the same time?
 \imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone
@@
   mine.}
+}
 

### 2020-05-31 model-marlim/PETGEM/export_netcdf.py
Added final results for block model and marlim model. Comments are also added to the manuscript

@@ -1,0 +1,60 @@
+#!/usr/bin/env python3
+# Author:  Octavio Castillo Reyes
+# Contact: octavio.castillo@bsc.es
+''' Export marlim model results using PETGEM to netcdf format
+'''
+
+# ---------------------------------------------------------------
+#                         MARLIM MODEL
+# ---------------------------------------------------------------
+import xarray as xr
+from datetime import datetime
+import numpy as np
+import h5py
+
+# ---------------------------------------------------------------
+# Import base dataset and specify PETGEM observation lines
+# ---------------------------------------------------------------
+ds = xr.load_dataset('../marlim_survey.nc', engine='h5netcdf')
+line_il = 'data_il'
+line_bs = 'data_bs'
+
+# ---------------------------------------------------------------
+# Open PETGEM results file
+# ---------------------------------------------------------------
+f = h5py.File('out/electric_fields.h5', 'r')
+
+# ---------------------------------------------------------------
+# Save inline data and broadside data for all frequencies
+# ---------------------------------------------------------------
+ds.data_il.data = f.get(line_il)[()]
+ds.data_bs.data = f.get(line_bs)[()]
+
+# ---------------------------------------------------------------
+# Add info
+# ---------------------------------------------------------------
+ds.attrs['runtime'] = str(int(f.get('runtime')[()])) + ' s'
+ds.attrs['n_procs'] = f.get('n_procs')[()]
+ds.attrs['max_ram'] = '{:5.1f}'.format(f.get('max_mem')[()]) + ' GiB'
+ds.attrs['n_cells'] = f.get('n_cells')[()]
+ds.attrs['n_nodes'] = f.get('n_nodes')[()]
+ds.attrs['n_dof'] = f.get('n_dof')[()]
+ds.attrs['extent'] = ("x = -22800 - 22800; "
+                      "y = -22800 - 22800; "
+                      "z = -22800 - 22800")
+ds.attrs['min_volume'] = f.get('min_volume')[()]
+ds.attrs['max_volume'] = f.get('max_volume')[()]
+ds.attrs['machine'] = ("Marenostrum4. Intel Xeon Platinum from Skylake generation; "
+                       "2 sockets Intel Xeon Platinum 8160 CPU with 24 cores each @2.10GHz for a total of 48 cores per node; "
+                       "386 Gb DDR4 RAM per node; SuSE Linux Enterprise")
+ds.attrs['version'] = "PETGEM v" + str(f.get('version')[()])
[…]

### 2020-05-31 model-marlim/PETGEM/run_preprocessing.py

@@ -1,0 +1,509 @@
+#!/usr/bin/env python3
+# Author:  Octavio Castillo Reyes
+# Contact: octavio.castillo@bsc.es
+''' This script can be used to preprocess data for PETGEM modeling
+
+For any questions or issues, contact
+
+    octavio.castillo@bsc.es
+'''
+
+if __name__ == '__main__':
+    # ---------------------------------------------------------------
+    # Load python modules
+    # ---------------------------------------------------------------
+    import sys
+    import petsc4py
+    import numpy as np
+    import meshio
+    from scipy.spatial import Delaunay
+
+    # ---------------------------------------------------------------
+    # PETSc init
+    # ---------------------------------------------------------------
+    petsc4py.init(sys.argv)
+    # ---------------------------------------------------------------
+    # Load python modules
+    # ---------------------------------------------------------------
+    from petsc4py import PETSc
+    # ---------------------------------------------------------------
+    # Load petgem modules (BSC)
+    # ---------------------------------------------------------------
+    from petgem.common import Print, InputParameters, Timers
+    from petgem.parallel import MPIEnvironment, createSequentialDenseMatrixWithArray
+    from petgem.parallel import writeParallelDenseMatrix, createSequentialVectorWithArray
+    from petgem.parallel import writePetscVector
+    from petgem.mesh import readGmshNodes, readGmshConnectivity, computeEdges, computeFaces
+    from petgem.mesh import computeBoundaryFaces, computeBoundaryEdges, computeBoundaries
+    from petgem.vectors import invConnectivity
+    from petgem.hvfem import computeConnectivityDOFS
+
+    # ---------------------------------------------------------------
+    # Load system setup (both parameters and dataset configuration)
+    # ---------------------------------------------------------------
+    # Obtain the MPI environment
+    parEnv = MPIEnvironment()
+
+    # Import parameters file
+    inputSetup = InputParameters(sys.argv[1], parEnv)
+
+    # Initialize timers
+    Timers(inputSetup.output.directory)
+
+    # ---------------------------------------------------------------
+    # Print header
+    # ---------------------------------------------------------------
[…]

### 2020-06-01 manuscript/Manuscript.tex

@@
 communities as well.}
+\mycom[OCR]{I also find GMD very interesting, in fact it was my first option to publish the first petgem version (2 years ago).
+The answer was: "manuscript outside of journal's scope".
+In this sense I agree with Raphael.
+My vote is for SIG}
 
@@
   quick thing then.}}
+
+\imycom[OCR]{In general, I believe that the content is adequate and the ideas are clear and in accordance with the objective that we have initially set.
+However, I want to highlight the task of being careful when justifying the absence of the SimPEG results for the marlim model (I have read it in slack, although it may not be definitive).
+I believe that this may or may not be a weak point depending on how we explain it.
+I know that perhaps it is not serious, I only make this comment so that the speech justifies the facts.
+}
 
@@
 
+\mycom[OCR]{I have rearranged some references according to the year of publication (here and in the rest of the paper)}
 The continuous improvement of computing power and the CSEM boom in the early
@@
 differences (FD) \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin,
-GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GJI.11.Schwarzbach,
-GEO.04.Commer, GEO.12.daSilva, GJI.13.Puzyrev, GJI.13.Grayver, SEG.16.Zhang},
-and finite volumes (FV) \citep{EM.90.Madsen, ECP.07.Haber, GEO.14.Jahandari,
-PIER.01.Clemens, GP.06.Mulder}. There are also many different types of
-discretisation, where the most common ones are regular grids (Cartesian,
+GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer,
+GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang},
+and finite volumes (FV) \citep{EM.90.Madsen, PIER.01.Clemens, GP.06.Mulder, ECP.07.Haber, GEO.14.Jahandari}. There are also many different types of
+discretisation, where the most common ones are regular grids (cartesian,
 rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid
@@
 techniques for the systems of linear equations (SLE). They can be distinguished
-between direct solvers \citep{GEO.09.Streich, GEO.15.Grayver, GP.14.Chung,
-GEO.14.Jaysaval, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder,
-GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers
+between direct solvers \citep{GEO.09.Streich, GP.14.Chung,
+GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers
 \citep{GEO.18.Liu}. The solvers often use preconditioners such as the multigrid
@@
 benefit from feedback regarding the real needs of the end-users.}» Some major
-exploration service companies as well as certain research consortia and
-research groups have their own 3D CSEM codes, but how about codes that are
+exploration service companies, as well as certain research consortia and
+research groups, have their own 3D CSEM codes, but how about codes that are
 open-source? Academic codes were traditionally often available upon request by
@@
 \imycom[DW]{Others coming to your mind?\imycom[RR]{no thoughts about geophysics,
-  but there are many projects for related topics such as gmt, gis, mesh-gen}}
+  but there are many projects for related topics such as gmt, gis, mesh-gen}
+  \imycom[OCR]{No idea from my side}}
 
@@
 there were only closed-source codes owned by companies or  consortia and
-individual projects, often without a proper documentation, that could be
+individual projects, often without proper documentation, that could be
 requested from the authors. We introduce and compare four recent open-source
@@
 reliability of simulations, not only carried out with the available open-source
-codes, but also for individual closed-source project. Analytical and
+codes, but also for individual closed-source projects. Analytical and
 semi-analytical solutions only exist for simple halfspace or layered-Earth
@@
 \citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
-\citep{GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
+\citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
 codes have their user-facing routines written in Python; all of them make heavy
@@
 formulation of Maxwell's equation in its differential form (DE) under the
-quasistatic or\mycom[DW]{are we all using the diff. approx?} diffusive
+quasistatic or\mycom[DW]{are we all using the diff. approx?}\mycom[OCR]{petgem consider the weak work of maxwell equations in their diffusive form (quasi-static approximation)} diffusive
 approximation, hence neglecting displacement currents. The machines on which
@@
                & \texttt{pip}; \texttt{conda}
-               & \texttt{conda}
+               & \texttt{pip}; \texttt{conda}
                & \texttt{pip}; \texttt{conda} \\
@@
 
-TODO
+\petgem is a parallel code for frequency-domain 3D CSEM data from marine and land surveys.
+The high-order edge FE method (HEFEM) is used for the discretization of the governing equations in its diffusive form.
+This technique provides a suitable mechanism to obtain stable numerical solutions as well as a good trade-off between number of dof\mycom[OCR]{I assume we have previously mentioned the term dofs} and computational effort.
+The current implementation supports up to six-order tetrahedral vector basis functions.
+Moreover, because the HEFEM belongs to the FE family, the unstructured meshes can be used efficiently on complex geometries (e.g., models with topography and bathymetry).
+
+\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyze the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type, among others).
+Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$ mesh refinement) based on physical parameters and on polynomial order to satisfy quality criteria chosen by the user.
+Nonetheless, only Horizontal electric dipole (HED) has been implemented.
+
+For the parallel forward modelling computations, a highly scalable MPI domain decomposition allows reducing run-times and the solution of large-scale modelling cases.
+This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-performance Computing architectures).
+
+Based on the current state of the \petgem project, there are many possibilities
+to improve or to add additional features. For instance, in the short-term, more
+modeling routines and support for multi-source set-ups will be implemented. For the long-term, the obvious next step is to move to 3D CSEM data inversion.
 
@@
 The thin isotropic layer beneath the water requires many tetrahedra for a
-good-quality discretisation. Therefore, the FE codes custEM and PETGEM used the
+good-quality discretisation. Therefore, the FE codes \custem and \petgem used the
 same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the
@@
   from making it looking nice with labels  and annotations.}
+\imycom[OCR]{I really liked this way of presenting the comparison, in addition to saving space, we gained in understanding. Looks really nice!}
+
 }
@@
   used to discretize the block model. \imycom[DW]{I will fill this table out
-  once we all submitted the final versions of the results.}}{
+  once we all submitted the final versions of the results.\imycom[OCR]{I can help you to fill this table and with its analysis}}}{
   \centering
@@
 redundant.\imycom[DW]{Did you refer to the last sentence or the one before? I
-think the last sentence contains quite important info.}}
-
-The detailed reservoir model consists of 1022 by 371 by 1229 cells, totalling
+think the last sentence contains quite important info. .\imycom[OCR]{If possible, I would like to uphold this sentence. I agree with dieter, it contains relevant information.}}}
+
+The detailed reservoir model consists of 1022 by 371 by 1229 cells\mycom[OCR]{I prefer this notation $1022 \times 371 \times 1229$. Nothing special, just format}, totalling
 to almost 466 million cells, where each cell has dimensions of 25 by 75 by
@@
 three frequencies and the responses with the strongest amplitudes (which are
-generally used in processing), which are $E_x$ inline and broadside and $E_y$
+generally used in processing), which are $E_x$ inline and broadside, and $E_y$
 broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
@@
   used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
-  out once we all submitted the final versions of the results.}}{
+  out once we all submitted the final versions of the results.\imycom[OCR]{I can help you to fill this table and with its analysis}}}{
   \centering
@@
 to a regular grid without approximations. Hence, the chosen examples favoured
-the finite-difference codes, since they used either regular grids or
-octree-meshes, whereas the two finite-element codes were required to
+the FD codes, since they used either regular grids or
+octree-meshes, whereas the two FE codes were required to
 tetrahedralise the model geometries.
@@
   iterative solver and differences from FE to FD codes etc. Please just jot
-  down things that come to your mind.}
+  down things that come to your mind.
+  \imycom[OCR]{ I think an important point is the user experience (modeler). I know this is an intangible element but perhaps we could add a line about it. It is my opinion}}
 
@@
 MarTERA, a EU Horizon 2020 research and innovation programme (No 728053);
-\href{https://www.martera.eu}{martera.eu}. The development of custEM as part of
+\href{https://www.martera.eu}{martera.eu}. The development of \custem as part of
 the DESMEX project was funded by the Germany Ministry for Education and
@@
 Fona-r4 under grant 033R130D.
+The work of O.C-R.
+has received funding from the \textit{European Union\textquotesingle s Horizon 2020 programme} under the \textit{Marie Sklodowska-Curie} grant agreement N$^\circ$ 777778.
+Further, the development of \petgem has received funding from the \textit{European Union\textquotesingle s Horizon 2020 programme}, grant agreement N$^\circ$ 828947, and from the Mexican Department of Energy, CONACYT-SENER Hidrocarburos grant agreement N$^\circ$ B-S-69926.
+Furthermore, O.C-R.
+has been 65\% cofinanced by the European Regional Development Fund (ERDF) through the Interreg V-A Spain-France-Andorra program (POCTEFA2014-2020).
+POCTEFA aims to reinforce the economic and social integration of the French-Spanish-Andorran border.
+Its support is focused on developing economic, social and environmental cross-border activities through joint strategies favouring sustainable territorial development.\mycom[OCR]{My apologies for these long acks, but they are the projects in which I am participating and the BSC makes a lot of emphasis on complying verbatim with the thansk sentences (too rigorous in my opinion)}
 

### 2020-06-19 manuscript/Manuscript.tex

@@
 - CAG: Computers and Geosciences\\
+\imycom[DW]{
 I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
@@
 place. I just had a very bad experience with GP, so I am not inclined on that
-at all.
-}
-
-\mycom[RR]{GMD looks very interesting, my only concern is that it might not be
+at all.}
+\imycom[RR]{GMD looks very interesting, my only concern is that it might not be
 in the scope of EM modelers, but we can probably reach modeleres from other
 communities as well.}
-\mycom[OCR]{I also find GMD very interesting, in fact it was my first option to publish the first petgem version (2 years ago).
-The answer was: "manuscript outside of journal's scope".
-In this sense I agree with Raphael.
-My vote is for SIG}
+\imycom[OCR]{I also find GMD very interesting, in fact it was my first option to
+publish the first petgem version (2 years ago). The answer was: "manuscript
+outside of journal's scope". In this sense I agree with Raphael. My vote is for
+SIG}
+}
 
@@
 
-\imycom[OCR]{In general, I believe that the content is adequate and the ideas are clear and in accordance with the objective that we have initially set.
-However, I want to highlight the task of being careful when justifying the absence of the SimPEG results for the marlim model (I have read it in slack, although it may not be definitive).
-I believe that this may or may not be a weak point depending on how we explain it.
-I know that perhaps it is not serious, I only make this comment so that the speech justifies the facts.
-}
+\imycom[OCR]{In general, I believe that the content is adequate and the ideas
+are clear and in accordance with the objective that we have initially set.
+However, I want to highlight the task of being careful when justifying the
+absence of the SimPEG results for the Marlim model (I have read it in Slack,
+although it may not be definitive). I believe that this may or may not be a
+weak point depending on how we explain it. I know that perhaps it is not
+serious, I only make this comment so that the speech justifies the facts. }
 
@@
 
-\mycom[OCR]{I have rearranged some references according to the year of publication (here and in the rest of the paper)}
 The continuous improvement of computing power and the CSEM boom in the early
@@
 GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer,
-GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang},
-and finite volumes (FV) \citep{EM.90.Madsen, PIER.01.Clemens, GP.06.Mulder, ECP.07.Haber, GEO.14.Jahandari}. There are also many different types of
-discretisation, where the most common ones are regular grids (cartesian,
-rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid
-\citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids
+GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev,
+SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, PIER.01.Clemens,
+GP.06.Mulder, ECP.07.Haber, GEO.14.Jahandari}. There are also many different
+types of discretisation, where the most common ones are regular grids
+(cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a
+Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids
 \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or
@@
 techniques for the systems of linear equations (SLE). They can be distinguished
-between direct solvers \citep{GEO.09.Streich, GP.14.Chung,
-GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers
+between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval,
+GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder,
+GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers
 \citep{GEO.18.Liu}. The solvers often use preconditioners such as the multigrid
@@
 \citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}.
-\imycom[DW]{Others coming to your mind?\imycom[RR]{no thoughts about geophysics,
-  but there are many projects for related topics such as gmt, gis, mesh-gen}
-  \imycom[OCR]{No idea from my side}}
+\imycom[DW]{Others coming to your mind? An interesting looking one is
+  \href{https://github.com/fancompute/ceviche}{github.com/fancompute/ceviche},
+  but they are at very high frequencies on nm-distances.
+\imycom[RR]{no thoughts about geophysics, but there are many projects for
+  related topics such as gmt, gis, mesh-gen}
+\imycom[OCR]{No idea from my side}
+}
 
@@
 \citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
-\citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett}. All four
-codes have their user-facing routines written in Python; all of them make heavy
-use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy}
-\citep{NM.20.Virtanen}. The four of them are “modern” open-source projects,
-meaning that they come with both, an open-source license and an online-hosted
-version-control system with tracking possibilities (raising issues, filing pull
-requests). All developments comprise an extensive online documentation with
-many examples and have continuous integration to some degree. Newer
-package-management systems such as Conda, Docker, or pip significantly
-supported us to make our codes easily available and installable without any
-user-side compilations. Each one can be downloaded and installed with a single
-command.
+\citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg
+\citep{CAG.15.Cockett}. All four codes have their user-facing routines written
+in Python; all of them make heavy use of \texttt{NumPy}
+\citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}. The four
+of them are “modern” open-source projects, meaning that they come with both, an
+open-source license and an online-hosted version-control system with tracking
+possibilities (raising issues, filing pull requests). All developments comprise
+an extensive online documentation with many examples and have continuous
+integration to some degree. Newer package-management systems such as Conda,
+Docker, or pip significantly supported us to make our codes easily available
+and installable without any user-side compilations. Each one can be downloaded
+and installed with a single command.
 
@@
 formulation of Maxwell's equation in its differential form (DE) under the
-quasistatic or\mycom[DW]{are we all using the diff. approx?}\mycom[OCR]{petgem consider the weak work of maxwell equations in their diffusive form (quasi-static approximation)} diffusive
-approximation, hence neglecting displacement currents. The machines on which
-the different codes were run are listed in Table~\ref{tbl:machines}, together
-with the responsible operator.
+quasistatic or\mycom[DW]{are we all using the diff. approx?}\mycom[OCR]{petgem
+consider the weak work of maxwell equations in their diffusive form
+(quasi-static approximation)} diffusive approximation, hence neglecting
+displacement currents. The machines on which the different codes were run are
+listed in Table~\ref{tbl:machines}, together with the responsible operator.
 
@@
                & \texttt{pip}; \texttt{conda}
-               & \texttt{pip}; \texttt{conda}
+               & \texttt{pip}
                & \texttt{pip}; \texttt{conda} \\
@@
   %
-  \custem & PowerEdge R940 server; 144 Xeon Gold 6154 CPU @2.666 GHz; ~3 TB
-            DDR4 RAM; Ubuntu 18.04
+  \custem & \textbf{PowerEdge R940 server}; 144 Xeon Gold 6154 CPU @2.666 GHz;
+            ~3 TB DDR4 RAM; Ubuntu 18.04
           & Raphael Rochlitz \\
-  \emg3d  & Laptop; i7-6600U CPU@2.6 GHz x4; 16 GB of memory, Ubuntu 18.04
-          & Dieter Werthmüller \\
-  \petgem & Marenostrum4. Intel Xeon Platinum from Skylake generation; 2
-            sockets Intel Xeon Platinum 8160 CPU with 24 cores each @2.10GHz
-            for a total of 48 cores per node; 386 Gb DDR4 RAM per node; SuSE
-            Linux Enterprise
+  \emg3d  & \textbf{Laptop}; i7-6600U CPU@2.6 GHz x4; 16 GB of memory,
+            Ubuntu 18.04 & Dieter Werthmüller \\
+  \petgem & \textbf{Marenostrum4 (supercomputer)}. Intel Xeon Platinum from
+            Skylake generation; 2 sockets Intel Xeon Platinum 8160 CPU with 24
+            cores each @2.10GHz for a total of 48 cores per node; 386 Gb DDR4
+            RAM per node; SuSE Linux Enterprise
           & Octavio Castillo-Reyes \\
@@
 
-\petgem is a parallel code for frequency-domain 3D CSEM data from marine and land surveys.
-The high-order edge FE method (HEFEM) is used for the discretization of the governing equations in its diffusive form.
-This technique provides a suitable mechanism to obtain stable numerical solutions as well as a good trade-off between number of dof\mycom[OCR]{I assume we have previously mentioned the term dofs} and computational effort.
-The current implementation supports up to six-order tetrahedral vector basis functions.
-Moreover, because the HEFEM belongs to the FE family, the unstructured meshes can be used efficiently on complex geometries (e.g., models with topography and bathymetry).
-
-\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyze the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type, among others).
-Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$ mesh refinement) based on physical parameters and on polynomial order to satisfy quality criteria chosen by the user.
-Nonetheless, only Horizontal electric dipole (HED) has been implemented.
-
-For the parallel forward modelling computations, a highly scalable MPI domain decomposition allows reducing run-times and the solution of large-scale modelling cases.
-This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-performance Computing architectures).
+\petgem is a parallel code for frequency-domain 3D CSEM data from marine and
+land surveys. The high-order edge FE method (HEFEM) is used for the
+discretization of the governing equations in its diffusive form. This technique
+provides a suitable mechanism to obtain stable numerical solutions as well as a
+good trade-off between number of dof\mycom[OCR]{I assume we have previously
+mentioned the term dofs} and computational effort. The current implementation
+supports up to six-order tetrahedral vector basis functions. Moreover, because
+the HEFEM belongs to the FE family, the unstructured meshes can be used
+efficiently on complex geometries (e.g., models with topography and
+bathymetry).
+
+\petgem permits to locate the source and receivers anywhere in the
+computational domain\mycom[DW]{I think this applies to all four codes} (e.g.,
+sediments, seafloor, sea, ground), allowing to analyze the physical environment
+of the electric responses and how parameters impact them (e.g., frequency,
+conductivity, dependence on mesh setup, basis order, solver type, among
+others). Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$
+mesh refinement) based on physical parameters and on polynomial order to
+satisfy quality criteria chosen by the user. Nonetheless, only Horizontal
+Electric Dipole (HED) has been implemented.
+
+For the parallel forward modelling computations, a highly scalable MPI domain
+decomposition allows reducing run-times and the solution of large-scale
+modelling cases. This strategy is capable of exploiting the parallelism offered
+by both modest multi-core computers and cutting-edge clusters (e.g.,
+High-performance Computing architectures).
 
@@
 to improve or to add additional features. For instance, in the short-term, more
-modeling routines and support for multi-source set-ups will be implemented. For the long-term, the obvious next step is to move to 3D CSEM data inversion.
+modeling routines and support for multi-source set-ups will be implemented. For
+the long-term, the obvious next step is to move to 3D CSEM data inversion.
 
@@
 The thin isotropic layer beneath the water requires many tetrahedra for a
-good-quality discretisation. Therefore, the FE codes \custem and \petgem used the
-same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the
-origin, surrounded by a ten times larger halfspace-like boundary mesh with
+good-quality discretisation. Therefore, the FE codes \custem and \petgem used
+the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from
+the origin, surrounded by a ten times larger halfspace-like boundary mesh with
 water conductivities assigned to the subsurface. This approximation
@@
 an ideal case to verify our open-source codes against, as it is a complex,
-realistic model and the data were computed by an industry-proofed
-code. Additionally, that code is a time-domain code, whereas the four codes
-under consideration here compute the results all in the frequency-domain.
+realistic model and the data were computed by an industry-proofed code.
+Additionally, that code is a time-domain code, whereas the four codes under
+consideration here compute the results all in the frequency-domain.
 \imycom[RR]{I would delete this sentence, not that important and a bit
-redundant.\imycom[DW]{Did you refer to the last sentence or the one before? I
-think the last sentence contains quite important info. .\imycom[OCR]{If possible, I would like to uphold this sentence. I agree with dieter, it contains relevant information.}}}
-
-The detailed reservoir model consists of 1022 by 371 by 1229 cells\mycom[OCR]{I prefer this notation $1022 \times 371 \times 1229$. Nothing special, just format}, totalling
-to almost 466 million cells, where each cell has dimensions of 25 by 75 by
-5\,m. For the computation the model is upscaled to 515 by 563 by 310 cells,
-totalling to almost 90 million cells, where each cell has dimensions of 100 by
-100 by 20\,m.
+  redundant.
+\imycom[DW]{Did you refer to the last sentence or the one before? I think the
+  last sentence contains quite important info.}
+\imycom[OCR]{If possible, I would like to uphold this sentence. I agree with
+  Dieter, it contains relevant information.}
+}
+
+The detailed reservoir model consists of $1022 \times 371 \times 1229$ cells,
+totalling to almost 466 million cells, where each cell has dimensions of 25 by
+75 by 5\,m. For the computation the model is upscaled to 515 by 563 by 310
+cells, totalling to almost 90 million cells, where each cell has dimensions of
+100 by 100 by 20\,m.
 
@@
 \tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
-  used to discretize the Marlim R3D model. \imycom[DW]{I will fill this table
-  out once we all submitted the final versions of the results.\imycom[OCR]{I can help you to fill this table and with its analysis}}}{
+  used to discretize the Marlim R3D model.
+  \imycom[DW]{I will fill this table out once we all submitted the final
+    versions of the results.\imycom[OCR]{I can help you to fill this table and
+    with its analysis}}}{
   \centering
@@
   down things that come to your mind.
-  \imycom[OCR]{ I think an important point is the user experience (modeler). I know this is an intangible element but perhaps we could add a line about it. It is my opinion}}
+\imycom[OCR]{I think an important point is the user experience (modeler). I
+  know this is an intangible element but perhaps we could add a line about it.
+  It is my opinion}
+}
 
@@
 Research (BMBF) in the framework of the research and development program
-Fona-r4 under grant 033R130D.
-The work of O.C-R.
-has received funding from the \textit{European Union\textquotesingle s Horizon 2020 programme} under the \textit{Marie Sklodowska-Curie} grant agreement N$^\circ$ 777778.
-Further, the development of \petgem has received funding from the \textit{European Union\textquotesingle s Horizon 2020 programme}, grant agreement N$^\circ$ 828947, and from the Mexican Department of Energy, CONACYT-SENER Hidrocarburos grant agreement N$^\circ$ B-S-69926.
-Furthermore, O.C-R.
-has been 65\% cofinanced by the European Regional Development Fund (ERDF) through the Interreg V-A Spain-France-Andorra program (POCTEFA2014-2020).
-POCTEFA aims to reinforce the economic and social integration of the French-Spanish-Andorran border.
-Its support is focused on developing economic, social and environmental cross-border activities through joint strategies favouring sustainable territorial development.\mycom[OCR]{My apologies for these long acks, but they are the projects in which I am participating and the BSC makes a lot of emphasis on complying verbatim with the thansk sentences (too rigorous in my opinion)}
+Fona-r4 under grant 033R130D. The work of O.C-R. has received funding from the
+\emph{European Union's Horizon 2020 programme} under the \emph{Marie
+Sklodowska-Curie} grant agreement N$^\circ$ 777778. Further, the development of
+\petgem has received funding from the \emph{European Union's Horizon 2020
+programme}, grant agreement N$^\circ$ 828947, and from the Mexican Department
+of Energy, CONACYT-SENER Hidrocarburos grant agreement N$^\circ$ B-S-69926.
+Furthermore, O.C-R. has been 65\% cofinanced by the European Regional
+Development Fund (ERDF) through the Interreg V-A Spain-France-Andorra program
+(POCTEFA2014-2020). POCTEFA aims to reinforce the economic and social
+integration of the French-Spanish-Andorran border. Its support is focused on
+developing economic, social and environmental cross-border activities through
+joint strategies favouring sustainable territorial development.
+\imycom[OCR]{My
+  apologies for these long acks, but they are the projects in which I am
+  participating and the BSC makes a lot of emphasis on complying verbatim with
+  the thansk sentences (too rigorous in my opinion)}
 

### 2020-06-27 manuscript/Manuscript.tex
Lindsey edits to the Intro

@@
 % Additional packages to geophysics.cls
-\usepackage[UKenglish]{babel}
+% \usepackage[UKenglish]{babel}
 \usepackage[utf8]{inputenc}
@@
 \footnotemark[3]TODO\\
-\footnotemark[4]TODO\\
+\footnotemark[4]University of California Berkeley, Department of Statistics\\
 E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
@@
 }
+\imycom[LH]{SIG does look like a good option. Given the spirit of the paper, it
+would be nice to publish it open-access. Does anyone have a sense of how much that
+costs with SIG? I could likely get partial funding towards this. Solid Earth
+might be a nice option in that case because it is open-access by default. }
 
@@
   quick thing then.}}
+\imycom[LH]{It's true! Canadian English ends up being an interesting hybrid(!)}
 
@@
 Controlled-source electromagnetic (CSEM) measurements are a frequently applied
-method in various geophysical exploration fields, such as geothermal and
+method in various geophysical exploration fields, such as geothermal,
 groundwater, oil and gas, mining, civil engineering, or geo-hazards. Modelling
@@
 \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and
-magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}. \cite{Ward1988}
+assemble many of these solutions in ``Electromagnetic Theory for Geophysical
+Applications,'' which is widely viewed as an authoritative publication on
+electromagnetic geophysics.
 
@@
 computation on massively parallel computers.
+
+\imycom[LH]{I added a couple citations here - I think the Haber 2001 is important to include in the FV list (if we want to remove the 2007 one to reduce duplicating authors, I think that is okay as we cite it later)}
 
@@
 GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev,
-SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, PIER.01.Clemens,
+SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, Haber2001,PIER.01.Clemens,
 GP.06.Mulder, ECP.07.Haber, GEO.14.Jahandari}. There are also many different
@@
 \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or
-OcTree meshes\citep{ECP.07.Haber}. Very well written overviews about the
+OcTree meshes \citep{ECP.07.Haber}. Very well written overviews about the
 different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and
@@
 
+\imycom[LH]{Here, I think that there
+is a point to make about duplication of efforts vs. new methodologies. Often
+the development of a new methodology requires that a new implementation be
+built from scratch. As a field though, we have matured to a point where we
+know what the methods / approaches are, and much of the next stage of
+advancements will be more incremental. (We argued this in Oldenburg et al,
+2019 - so to self-cite ;) (doi: https://doi.org/10.1080/08123985.2019.1580118,
+arxiv: https://arxiv.org/pdf/1902.08245.pdf). See what you think of the
+following framing for the next paragraph - we can discuss:
+
+Many of the advancements made in the EM modelling community over the past
+decades have required that authors develop new implementation from scratch.
+These codes often provided the research group or company with a competitive
+advantage for a time, and thus the source codes were often kept internal. In
+some cases, executables have been made available for academic purposes upon
+request or to sponsoring consortium members. As the field continues to mature,
+advancements become more incremental, and particularly in an applied field,
+many advancements are driven by new use-cases and applications that were not
+considered by the original authors. In his review on EM modelling and
+inversion \cite{SG.05.Avdeev} concludes with the
+following statement: «\emph{The most important challenge that faces the EM
+community today is to convince software developers to put their 3-D EM forward
+and inverse solutions into the public domain, at least after some time. This
+would have a strong impact on the whole subject and the developers would
+benefit from feedback regarding the real needs of the end-users.}» Further,
+\cite{Oldenburg2019} argue that an open-source paradigm has the potential to
+accelerate multidisciplinary research by encouraging the development of
+modular, interoperable tools that are supported by a community of researchers.
+}
+
 Probably the main reason for the numerous amount of code developments was
-already outlined by \cite{SG.05.Avdeev}, who finished his review with the
+outlined by \cite{SG.05.Avdeev}, who finished his review with the
 following statement: «\emph{The most important challenge that faces the EM
@@
 open-source? Academic codes were traditionally often available upon request by
-authors. Codes distributed that way were often provided with the request to not
+authors. Codes distributed that way are often provided with the request that users not
 share the code, and they often come without a license attached which means that
@@
 hurdles to install a code.
+
+\imycom[LH]{Here, I think it is worth discussing the distinction between
+open-source: source code available + openly licensed (with an Open Source
+Initiative (OSI, https://opensource.org) approved license), open-development:
+code is versioned, development and issue tracking happens publicly (e.g. on
+GitHub or similar), and open communities: actively soliciting contributions
+and pull requests which change the code. and then the push towards open
+development / open communities motivates best practices including continuous
+integration, documentation, etc. See what you think of my suggested adaptation
+below. There might be a few citations we can add for an open model of development / open community project. I will do some digging. Again, happy to discuss.
+
+In many domains of science, it is becoming more common for researchers to
+release source-code with an open license that allows use and modification (
+e.g. see the Open Source Initiative approved licenses:
+\href{https://opensource.org/licenses}{https://opensource.org/licenses}). This
+is an important step for improving reproducibility of research: «\emph{to
+provide the means by which the reader can verify the validity of the results
+and make use of them in further research}» \citep{GEO.17.Broggini}. Going a
+step beyond releasing open-source software, many groups adopt an open model of
+development where code is hosted and versioned in an online repository,
+all changes are public, and users can engage by submitting and track issues.
+Community oriented projects further engagement by encouraging pull-requests,
+which are suggested changes to the code. Successful, well-maintained projects
+often have unit-testing and continuous integration that runs those tests with
+any changes to the code. Additionally, documentation that includes examples
+and tutorials is an important component for on-boarding new users and
+contributors. As a result, in many areas of the geosciences, we are seeing a
+shift away from a one-way distribution of code towards building global
+communities around open projects. Related projects within the
+realm of geophysical exploration are e.g., \texttt{pyGIMLi}
+\citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}
+}
 
@@
 \imycom[OCR]{No idea from my side}
-}
-
-We continue addressing the topic of open-source developments with respect to 3D
+\imycom[LH]{Could we cite: https://github.com/softwareunderground/awesome-open-geoscience ?. Maybe we could ask them to put it on zenodo so it has a doi?? Also Madagascar in seismic?}
+}
+
+In this paper, we discuss the topic of open-source developments with respect to 3D
 CSEM modeling. Even though it comprises still the minority of developments, the
-landscape in this field of research changed in the last five years. Before,
+landscape in this field of research changed in the last five years. Previously,
 there were only closed-source codes owned by companies or  consortia and
@@
 projects with focus on 3D CSEM modeling. All presented codes are in the Python
-ecosystem and use either the FD method on structured grids or the FE method on
+ecosystem and use either the FV method on structured grids or the FE method on
 unstructured tetrahedral meshes.
@@
 semi-analytical solutions only exist for simple halfspace or layered-Earth
-models, which served mostly to verify new codes. Beyond them, the only
+models, which served mostly to verify new codes. Beyond these simple models, the only
 objective possibility to ensure the accuracy of solutions is by comparing
@@
 We simulate EM fields for a layered background model with vertical transverse
-isotropy, containing three blocks, and the complex marine Marlim R3D model.
+isotropy, containing three blocks, as well as for the complex marine Marlim R3D model.
 These two model designs as well as the corresponding results from four
@@
 computational performance. Beyond that, we extensively discuss important points
-that control the performance and suitability of our FD and FE codes, including
+that control the performance and suitability of our FV and FE codes, including
 mainly considerations about the mesh design and the choice of solvers. We

### 2020-06-28 manuscript/Manuscript.tex
first pass at the SimPEG section

@@
 
+\imycom[LH]{Just a thought, but right now we don't state Maxwell's equations anywhere!
+That seems like something we should do :) That also provides an easy space for talking about Fourier Transform conventions and such too.
+
+% Following the conventions of Ward and Hohmann \cite{Ward1988}, the quasi-static Maxwell's equations are
+
+% \begin{equation}
+% \begin{split}
+%     \nabla \times \vec{E} &= -i \omega\vec{B}  \\
+%     \nabla \times \vec{H} &= \vec{J}
+% \end{split}
+% \label{eq:maxwell_freq_quasi}
+% \end{equation}
+}
+
 \clearpage  % TODO: Just for now while drafting, remove later!
@@
 \citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg
-\citep{CAG.15.Cockett}. All four codes have their user-facing routines written
+\citep{CAG.15.Cockett, Heagy2017}. All four codes have their user-facing routines written
 in Python; all of them make heavy use of \texttt{NumPy}
@@
 
-In the following a quick rundown of the codes. It is, however, beyond the scope
+In the following, we provide a quick overview of the codes. It is, however, beyond the scope
 of this article to go into every detail of the different modellers, and we
@@
 different codes is given in Table~\ref{tbl:codecomparison}. All codes have in
-common that they solve the\mycom[DW]{are we all using the weak form?} weak
+common that they solve the\mycom[DW]{are we all using the weak form?}\mycom[LH]{SimPEG uses weak form} weak
 formulation of Maxwell's equation in its differential form (DE) under the
@@
 consider the weak work of maxwell equations in their diffusive form
-(quasi-static approximation)} diffusive approximation, hence neglecting
+(quasi-static approximation)}\mycom[LH]{SimPEG uses quasistatic approx.} diffusive approximation, hence neglecting
 displacement currents. The machines on which the different codes were run are
-listed in Table~\ref{tbl:machines}, together with the responsible operator.
+listed in Table~\ref{tbl:machines}\mycom[LH]{SimPEG also interfaces to the scipy solvers (but in practice those are use much less than Pardiso / mumps)}, together with the responsible operator.
 
@@
 
-TODO
-
-\clearpage  % TODO: Just for now while drafting, remove later!
+\simpeg is a modular toolbox for simulations and gradient based inversions in
+geophysics. Current functionality includes modelling and inversion
+capabilities for gravity, magnetics, direct current resistivity, induced
+polarization, electromagnetics (time, frequency, as well as natural sources,
+e.g. magnetotellurics), and fluid flow (Richards equation). It is a community
+driven project that aims to support researchers by providing a flexible,
+extensible framework and to facilitate integration of data sets from a variety
+of geophysical methods, including joint inversions \citep{Astic2020}, by
+providing a common interface to each method.
+
+Meshes and finite volume differential operators are implemented in the
+\texttt{discretize} package. It currently includes tensor, OcTree,
+cylindrical, and logically rectangular meshes. Each mesh type inherits from a
+common structure and uses the same naming conventions for methods and
+properties. This allows us to decouple the implementation of a discretized
+partial differential equation from the details of the mesh geometry and
+therefore we can write a single implementation of discretized partial
+differential equation (or set of partial differential equations) in \simpeg
+that will support all mesh types implemented in \texttt{discretize}.
+
+The electromagnetics implementations use a staggered grid finite volume
+approach where physical properties are discretized at cell centers, fields on
+cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
+discretizing Maxwell's equations, we recommend \cite{Haber2014}). There are
+two different discretization strategies implemented for Maxwell's equations: (
+a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
+cell edges and the magnetic flux density ($\vec{h}$) on cell faces, and (b)
+the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
+edges and the current density ($\vec{j}$) on cell faces. In both cases the
+physical properties: electrical conductivity / resistivity and magnetic
+permeability are discretized at cell centers. Having multiple implementations
+allows for testing that compares results from each approach, as well as the
+representation of both electrical and magnetic sources on cylindrically
+symmetric meshes. \simpeg supports variable magnetic permeability and
+full-tensor anisotropy for the physical properties.
+
+% Support for domain decomposition approaches (see for example \cite{Fournier2020})
+
+\simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}.
+For problems with many sources (and reciprocity is not a natural solution, e.g.
+in 3D airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{Fournier2020}.
+
+\clearpage  % TODO: Just for now while drafting, remove late{}r!{}
 \section{Numerical Verifications}

### 2020-06-28 manuscript/Manuscript.tex
fix Haber book reference

@@
 cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
-discretizing Maxwell's equations, we recommend \cite{Haber2014}). There are
+discretizing Maxwell's equations, we recommend \cite{Haber2014b}). There are
 two different discretization strategies implemented for Maxwell's equations: (

### 2020-07-06 manuscript/Manuscript.tex

@@
 a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
-cell edges and the magnetic flux density ($\vec{h}$) on cell faces, and (b)
+cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (b)
 the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
@@
 }
+
+\imycom[LH]{From the discussion in slack - also a TODO on adding points on if there were any changes (or new motivation for development) based on this exercise --> goal: highlight benefits of open source collaborations.
+
+Within SimPEG: This work has motivated feature development including: (a)
+interpolation and averaging strategies from mapping physical properties on a
+fine mesh to a coarser mesh for computation and (b) new examples to include in
+the documentation for designing OcTree meshes. Furthermore, as a part of
+a broader development objective of interoperating with other
+forward-simulation engines, connecting \emg3d and \simpeg provided a
+motivating use-case for the latest refactor and release of \simpeg 0.14.0
+\citep{simpeg0.14.0}. }
 

### 2020-07-06 manuscript/Manuscript.tex
Incorporating LH's changes; start to rework.

@@
 
-% Remove once done
-\usepackage[textsize=footnotesize, textwidth=2.8cm]{todonotes}
-% \usepackage[textsize=footnotesize, textwidth=2.8cm, disable]{todonotes}
-
-% Additional packages to geophysics.cls
-% \usepackage[UKenglish]{babel}
+% TODO's
+\usepackage[color=cyan, textsize=footnotesize, textwidth=2.8cm]{todonotes}
+
+% Additional packages
+\usepackage[UKenglish]{babel}
 \usepackage[utf8]{inputenc}
@@
 \usepackage[T1]{fontenc}
-
 \usepackage{amssymb, amsmath, amsfonts}
-\usepackage{upquote}
-\usepackage[strings]{underscore}
-\usepackage{siunitx}                % SI conform commands (eg \num)
+\usepackage{siunitx}
 \usepackage{tabularx}
-\usepackage{colortbl}
 \usepackage{booktabs}
@@
 \usepackage{flafter}
-
-\usepackage[pdftex, final]{hyperref}
-% \usepackage[pdftex, hidelinks]{hyperref}
-\hypersetup{allcolors=blue, allbordercolors={0 0 .5}, colorlinks=true}
+\usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}
 
 % Figures
-\DeclareGraphicsExtensions{.pdf,.png,.jpg}
 \renewcommand{\figdir}{./figures}
-\ifthenelse{\boolean{@twoc}}{%
-  \newcommand{\cwidth}{250pt}}{%
-  \newcommand{\cwidth}{240pt}}
-
-\ifthenelse{\boolean{@twoc}}{%
-  \newcommand{\acwidth}{250pt}%
-  \newcommand{\tcwidth}{250pt}}{%
-  \newcommand{\acwidth}{240pt}%
-  \newcommand{\tcwidth}{312pt}}
 
@@
 \newcommand{\simpeg}{\texttt{SimPEG}\xspace}
+\newcommand{\discretize}{\texttt{discretize}\xspace}
 \newcommand{\custem}{\texttt{custEM}\xspace}
 \newcommand{\petgem}{\texttt{PETGEM}\xspace}
-
-% Remove once done
-\newcommand{\mycom}[2][]{
-  \todo[color=yellow]{\textbf{\uppercase{[#1]}}:~#2}}
-\newcommand{\imycom}[2][]{
-  \todo[inline, color=yellow]{\textbf{\uppercase{[#1]}}:~#2}}
-\newcommand{\itodo}[1]{\todo[inline, color=cyan]{\sffamily #1}}
-\newcommand{\dul}[1]{\underline{\underline{#1}}}
-\newcommand{\ul}[1]{\underline{#1}}
-\newcommand{\rmk}[1]{{\color{red}{#1}}}
 \newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
 
+% TODO's
+% For comments in the margin, use:   \mycom[YOURINITIALS]{comment}
+% and for inline comments, use:      \imycom[YOURINITIALS]{comment}
+\newcommand{\mycom}[2][]{\todo{\textbf{\uppercase{[#1]}}:~#2}}
+\newcommand{\imycom}[2][]{\todo[inline]{\textbf{\uppercase{[#1]}}:~#2}}
+\newcommand{\itodo}[1]{\todo[inline]{\sffamily #1}}
+
 \begin{document}
@@
 \address{
-\footnotemark[1]TU Delft,
+\footnotemark[1]%
+TU Delft,
 Building 23,
 Stevinweg 1 / PO-box 5048,
-2628 CN Delft;\\
-\footnotemark[2]TODO\\
-\footnotemark[3]TODO\\
-\footnotemark[4]University of California Berkeley, Department of Statistics\\
+2628 CN Delft (NL);\\
+\footnotemark[2]%
+Leibniz Institut für Angewandte Geophysik,
+Stilleweg 2,
+30655 Hannover (DE);\\
+\footnotemark[3]%
+Barcelona Supercomputing Center (BSC),
+Nexus II Building c/Jordi Girona, 29,
+08034 Barcelona (ES);\\
+\footnotemark[4]%
+University of California Berkeley,
+Department of Statistics (USA).\\
 E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
-\textbf{Keywords}: CSEM, Open-Source, 3D modelling, FD, FE.
+\textbf{Keywords}: CSEM, Open-Source, 3D modelling, FV, FE.
 }
@@
 %
-\emph{I will draft a first abstract after the manuscript has been reviewed by
-everyone once.}
-%
-% % Principal objectives and scope of the work
-% % Methodology
-% % Results
-% % Conclusions
+Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) used to be only possible for large companies or research consortia.
+However, this changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
+%
+Four different open-source 3D CSEM codes are considered in this work, where in all cases at least the user-facing functionality is written in Python.
+Two codes, \simpeg and \emg3d, use finite volumes, the other two codes, \custem and \petgem, use finite elements.
+Three different mesh-types are used, simple tensor meshes, unstructured tetrahedral meshes, and octree meshes.
+Two models are used to compare the codes, a layered background containing three resistive blocks, and Marlim R3D, a complex, real-world, open-source resistivity data.
+%
+The comparison shows that all four codes are able to compute the model to sufficient precision.
+The biggest difference between the codes are actually the used mesh types.
+The required runtime and memory varies greatly between the codes.
+However, these requirements depend mainly on the underlying solver, and not on the actual CSEM codes.
+%
+The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further.
+We hope that these results may be useful for the entire CSEM community, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
+For a start, all the scripts to reproduce our shown results are available.
 %
@@
 
-\itodo{
-  For comments in the margin, use:\\[.2cm]
-  \qquad\texttt{\textbackslash mycom[YOURINITIALS]\{comment\}}\\[.2cm]
-  and for inline comments, use:\\[.2cm]
-  \qquad\texttt{\textbackslash imycom[YOURINITIALS]\{comment\}}\\[.5cm]
-  If you want to compile it without comments, comment the line\\[.2cm]
-  \qquad\texttt{\textbackslash usepackage[textsize=footnotesize, textwidth=2.8cm]\{todonotes\}}\\[.2cm]
-  and uncomment the line\\[.2cm]
-  \qquad\texttt{\% \textbackslash usepackage[textsize=footnotesize, textwidth=2.8cm, disable]\{todonotes\}}
-}
-
-\itodo{
-We will have to decide on a Journal. Current suggestions:\\
-- GMD: Geoscientific Model Development\\
-- SIG: Surveys in Geophysics\\
-- SE: Solid Earth\\
-- GJI: Geophysical Journal International\\
-- GP: Geophysical Prospecting\\
-- GEO: Geophysics\\
-- CAG: Computers and Geosciences\\
-\imycom[DW]{
-I think \emph{Geoscientific Model Development} and \emph{Surveys in Geophysics}
-were the favourite ones when we discussed it ones. I personally would be very
-interested in GMD. What do you think? But also interesting would be the GJI,
-because the MT comparison was published there, so it would be in the same
-place. I just had a very bad experience with GP, so I am not inclined on that
-at all.}
-\imycom[RR]{GMD looks very interesting, my only concern is that it might not be
-in the scope of EM modelers, but we can probably reach modeleres from other
-communities as well.}
-\imycom[OCR]{I also find GMD very interesting, in fact it was my first option to
-publish the first petgem version (2 years ago). The answer was: "manuscript
-outside of journal's scope". In this sense I agree with Raphael. My vote is for
-SIG}
-}
-\imycom[LH]{SIG does look like a good option. Given the spirit of the paper, it
-would be nice to publish it open-access. Does anyone have a sense of how much that
-costs with SIG? I could likely get partial funding towards this. Solid Earth
-might be a nice option in that case because it is open-access by default. }
-
 \section{Introduction}
 
-\imycom[RR]{We need to take care to not mix British English with AE, I'm very
-  used to AE, but Dieter started with (at least what I can identify) mainly BE,
-  so I tried to follow (mainly s instead of z and ou instead of o in some
-  words). I hope there are not too many inconsistencies, as probably Lindsey
-  has to fix all these mistakes in the end:-)
-\imycom[DW]{Be aware of Canadian English and Australian English :-D -- You are
-  of course right. I am usually mostly BE, having done my PhD in Scotland.
-  However, I don't think it matters at the moment, because it will depend to
-  what journal we submit. With an appropriate spellchecker that should be a
-  quick thing then.}}
-\imycom[LH]{It's true! Canadian English ends up being an interesting hybrid(!)}
-
-\imycom[OCR]{In general, I believe that the content is adequate and the ideas
-are clear and in accordance with the objective that we have initially set.
-However, I want to highlight the task of being careful when justifying the
-absence of the SimPEG results for the Marlim model (I have read it in Slack,
-although it may not be definitive). I believe that this may or may not be a
-weak point depending on how we explain it. I know that perhaps it is not
-serious, I only make this comment so that the speech justifies the facts. }
-
-Controlled-source electromagnetic (CSEM) measurements are a frequently applied
-method in various geophysical exploration fields, such as geothermal,
-groundwater, oil and gas, mining, civil engineering, or geo-hazards. Modelling
-these electromagnetic fields is therefore of great interest to design survey
-layouts, to understand the measured data, and for inversion purposes.
-Publications regarding 3D modelling in electromagnetic methods started to
-appear as early as the 1970's and 1980's. These early publications were
-integral equation (IE) methods, having an anomaly embedded within a layered
-medium, mostly for loop-loop type transient EM measurements
-\citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and
-magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}. \cite{Ward1988}
-assemble many of these solutions in ``Electromagnetic Theory for Geophysical
-Applications,'' which is widely viewed as an authoritative publication on
-electromagnetic geophysics.
-
-In the 1990's, computer became sufficiently powerful that 3D modelling gained
-traction, which resulted amongst other publications in the book
-\emph{Three-Dimensional Electromagnetics} by the SEG
-\citep{B.SEG.99.Oristaglio}. Often cited publications from that time are
-\cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and
-time-domain modelling using a Yee grid and a global Krylov subspace
-approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency
-computation on massively parallel computers.
-
-\imycom[LH]{I added a couple citations here - I think the Haber 2001 is important to include in the FV list (if we want to remove the 2007 one to reduce duplicating authors, I think that is okay as we cite it later)}
-
-The continuous improvement of computing power and the CSEM boom in the early
-2000's in the hydrocarbon industry led to a wealth of developed numerical
-solutions and according publications. The most common applied methods to solve
-Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan,
-GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and
-different variations of the differential equation (DE) method, such as finite
-differences (FD) \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin,
-GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer,
-GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev,
-SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, Haber2001,PIER.01.Clemens,
-GP.06.Mulder, ECP.07.Haber, GEO.14.Jahandari}. There are also many different
-types of discretisation, where the most common ones are regular grids
-(cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a
-Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids
-\citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or
-OcTree meshes \citep{ECP.07.Haber}. Very well written overviews about the
-different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and
-\cite{SG.10.Borner}.
-
-In the last 15 years, the publications with regards to 3D EM modelling grew
-tremendously, driven by the ever increasing computing power. One reason why
-there are so many reports about this topic results from the variety of solution
-techniques for the systems of linear equations (SLE). They can be distinguished
-between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval,
-GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder,
-GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers
-\citep{GEO.18.Liu}. The solvers often use preconditioners such as the multigrid
-method \citep{SIAM.02.Aruliah, GP.06.Mulder, GJI.16.Jaysaval}.
-
-\imycom[LH]{Here, I think that there
-is a point to make about duplication of efforts vs. new methodologies. Often
-the development of a new methodology requires that a new implementation be
-built from scratch. As a field though, we have matured to a point where we
-know what the methods / approaches are, and much of the next stage of
-advancements will be more incremental. (We argued this in Oldenburg et al,
-2019 - so to self-cite ;) (doi: https://doi.org/10.1080/08123985.2019.1580118,
-arxiv: https://arxiv.org/pdf/1902.08245.pdf). See what you think of the
-following framing for the next paragraph - we can discuss:
-
-Many of the advancements made in the EM modelling community over the past
-decades have required that authors develop new implementation from scratch.
-These codes often provided the research group or company with a competitive
-advantage for a time, and thus the source codes were often kept internal. In
-some cases, executables have been made available for academic purposes upon
-request or to sponsoring consortium members. As the field continues to mature,
-advancements become more incremental, and particularly in an applied field,
-many advancements are driven by new use-cases and applications that were not
-considered by the original authors. In his review on EM modelling and
-inversion \cite{SG.05.Avdeev} concludes with the
-following statement: «\emph{The most important challenge that faces the EM
-community today is to convince software developers to put their 3-D EM forward
-and inverse solutions into the public domain, at least after some time. This
-would have a strong impact on the whole subject and the developers would
-benefit from feedback regarding the real needs of the end-users.}» Further,
-\cite{Oldenburg2019} argue that an open-source paradigm has the potential to
-accelerate multidisciplinary research by encouraging the development of
-modular, interoperable tools that are supported by a community of researchers.
-}
-
-Probably the main reason for the numerous amount of code developments was
-outlined by \cite{SG.05.Avdeev}, who finished his review with the
-following statement: «\emph{The most important challenge that faces the EM
-community today is to convince software developers to put their 3-D EM forward
-and inverse solutions into the public domain, at least after some time. This
-would have a strong impact on the whole subject and the developers would
-benefit from feedback regarding the real needs of the end-users.}» Some major
-exploration service companies, as well as certain research consortia and
-research groups, have their own 3D CSEM codes, but how about codes that are
-open-source? Academic codes were traditionally often available upon request by
-authors. Codes distributed that way are often provided with the request that users not
-share the code, and they often come without a license attached which means that
-they are, legally, not open-source. Also, at times there can be significant
-hurdles to install a code.
-
-\imycom[LH]{Here, I think it is worth discussing the distinction between
-open-source: source code available + openly licensed (with an Open Source
-Initiative (OSI, https://opensource.org) approved license), open-development:
-code is versioned, development and issue tracking happens publicly (e.g. on
-GitHub or similar), and open communities: actively soliciting contributions
-and pull requests which change the code. and then the push towards open
-development / open communities motivates best practices including continuous
-integration, documentation, etc. See what you think of my suggested adaptation
-below. There might be a few citations we can add for an open model of development / open community project. I will do some digging. Again, happy to discuss.
-
-In many domains of science, it is becoming more common for researchers to
-release source-code with an open license that allows use and modification (
-e.g. see the Open Source Initiative approved licenses:
-\href{https://opensource.org/licenses}{https://opensource.org/licenses}). This
-is an important step for improving reproducibility of research: «\emph{to
-provide the means by which the reader can verify the validity of the results
-and make use of them in further research}» \citep{GEO.17.Broggini}. Going a
-step beyond releasing open-source software, many groups adopt an open model of
-development where code is hosted and versioned in an online repository,
-all changes are public, and users can engage by submitting and track issues.
-Community oriented projects further engagement by encouraging pull-requests,
-which are suggested changes to the code. Successful, well-maintained projects
-often have unit-testing and continuous integration that runs those tests with
-any changes to the code. Additionally, documentation that includes examples
-and tutorials is an important component for on-boarding new users and
-contributors. As a result, in many areas of the geosciences, we are seeing a
-shift away from a one-way distribution of code towards building global
-communities around open projects. Related projects within the
-realm of geophysical exploration are e.g., \texttt{pyGIMLi}
-\citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}
-}
-
-The meaning of the term open-source evolved rapidly in the last two decades.
-Today, open-source generally not only means that a code is available (with a
-proper license), but also that the code is hosted online, is under version
-control, has the possibility to file issues and make pull requests to fix bugs.
-These are important requirements for reproducible research «\emph{to provide
-the means by which the reader can verify the validity of the results and make
-use of them in further research}» \citep{GEO.17.Broggini}. Well maintained
-codes often have continuous integration that includes testing of the code base
-and online hosted documentation, often including examples and tutorials. As
-such, the term has shifted from purely open-source codes to developments in the
-open with increasingly building a global community. Related projects within the
-realm of geophysical exploration are e.g., \texttt{pyGIMLi}
-\citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}.
-\imycom[DW]{Others coming to your mind? An interesting looking one is
-  \href{https://github.com/fancompute/ceviche}{github.com/fancompute/ceviche},
-  but they are at very high frequencies on nm-distances.
-\imycom[RR]{no thoughts about geophysics, but there are many projects for
-  related topics such as gmt, gis, mesh-gen}
-\imycom[OCR]{No idea from my side}
-\imycom[LH]{Could we cite: https://github.com/softwareunderground/awesome-open-geoscience ?. Maybe we could ask them to put it on zenodo so it has a doi?? Also Madagascar in seismic?}
-}
-
-In this paper, we discuss the topic of open-source developments with respect to 3D
-CSEM modeling. Even though it comprises still the minority of developments, the
-landscape in this field of research changed in the last five years. Previously,
-there were only closed-source codes owned by companies or  consortia and
-individual projects, often without proper documentation, that could be
-requested from the authors. We introduce and compare four recent open-source
-projects with focus on 3D CSEM modeling. All presented codes are in the Python
-ecosystem and use either the FV method on structured grids or the FE method on
-unstructured tetrahedral meshes.
-
-Furthermore, we deal with the topic of verification. \cite{GJI.13.Miensopust}
-presents a review of two workshops dealing with the verification of
-magnetotelluric forward and inversion codes, but we are not aware of any
-comparable study or benchmark suite for CSEM data. Hence, we first conduct a
-similar exercise for CSEM codes. We want our efforts to help to ensure the
-reliability of simulations, not only carried out with the available open-source
-codes, but also for individual closed-source projects. Analytical and
-semi-analytical solutions only exist for simple halfspace or layered-Earth
-models, which served mostly to verify new codes. Beyond these simple models, the only
-objective possibility to ensure the accuracy of solutions is by comparing
-results from different modellers. If different discretisations and
-implementations of Maxwell's equations yield the same result, it gives
-confidence in their accuracy.
-
-We simulate EM fields for a layered background model with vertical transverse
-isotropy, containing three blocks, as well as for the complex marine Marlim R3D model.
-These two model designs as well as the corresponding results from four
-different codes provide a benchmark for new codes to be compared to and
-validated with. In the following section, we introduce the codes under
-consideration. Afterwards, we present the considered benchmark cases in detail
-and present the modeling results of our four codes in terms of accuracy and
-computational performance. Beyond that, we extensively discuss important points
-that control the performance and suitability of our FV and FE codes, including
-mainly considerations about the mesh design and the choice of solvers. We
-conclude with a summary of our results and a motivation for the EM community to
-not only continue to extend the landscape of open-source codes but to also
-create a landscape of open-source benchmark models.
-
-\imycom[RR]{Regarding
-  \todo[inline, color=white]{
-  "It is worth mentioning that there are many more 3D EM
-  codes developed in other fields than geophysics such as communication systems
-  (antennas, radar, satellites), medical imaging, or civil engineering. There
-  are various open-source codes in these fields too, e.g., Elmer
-  (\href{http://www.csc.fi/elmer}{csc.fi/elmer}, couldn't
-  find a publication, just a poster).
-  \todo[inline, color=gray]{(\textbf{[DW]}: Add 2-3 proper references)}
-  While these codes could potentially be used for the same goals as presented
-  here we restrict our review to codes purpose-built and ready without further
-  adjustments for geophysical applications."
-}
-  I thought a lot about this but I just think the previous paragraph is not
-  required in our introduction and haven't find a location where it fits
-  considering different logical structures. I think it is also not important
-  for this paper to tell "that there are more codes in EM than only
-  geophysics", that's quite obvious. Maybe delete or shorten to 1 sentences to
-  add Elmer and place this sentence somewhere else? I think, an appropriate
-  list of all non-geophysical open-source EM codes should be very long anyway,
-  we just don't know them or at least I'm not familiar with them.}
-
-\imycom[LH]{Just a thought, but right now we don't state Maxwell's equations anywhere!
-That seems like something we should do :) That also provides an easy space for talking about Fourier Transform conventions and such too.
-
+Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geo-hazards.
+Modelling these electromagnetic fields is therefore of great interest to design survey layouts, to understand the measured data, and for inversion purposes.
+Publications regarding 3D modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
+These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+\cite{B.SEG.88.Ward} assemble many of these solutions in \emph{Electromagnetic Theory for Geophysical Applications}, which is widely viewed as an authoritative publication on electromagnetic geophysics.
+
+In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, which resulted amongst other publications in the book \emph{Three-Dimensional Electromagnetics} by the SEG \citep{B.SEG.99.Oristaglio}.
+Often cited publications from that time are \cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency computation on massively parallel computers.
+
+The continuous improvement of computing power and the CSEM boom in the early 2000's in the hydrocarbon industry led to a wealth of developed numerical solutions and according publications.
+The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
+There are also many different types of discretisation, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes \citep{ECP.07.Haber}.
+Very well written overviews about the different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
+
+In the last 15 years, the publications with regards to 3D EM modelling grew tremendously, driven by the ever increasing computing power.
+One reason why there are so many reports about this topic results from the variety of solution techniques for the systems of linear equations (SLE).
+They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
+The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GP.06.Mulder, GJI.16.Jaysaval}.
+
+Many of the advancements made in the EM modelling community over the past decades have required that authors develop new implementation from scratch.
+These codes often provided the research group or company with a competitive advantage for a time, and thus the source codes were often kept internal.
+In some cases, executables have been made available for academic purposes upon request or to sponsoring consortium members.
+As the field continues to mature, advancements become more incremental, and particularly in an applied field, many advancements are driven by new use-cases and applications that were not considered by the original authors.
+In his review on EM modelling and inversion \cite{SG.05.Avdeev} concludes with the following statement: «\emph{The most important challenge that faces the EM community today is to convince software developers to put their 3-D EM forward and inverse solutions into the public domain, at least after some time.
+This would have a strong impact on the whole subject and the developers would benefit from feedback regarding the real needs of the end-users.}» Further, \cite{EXG.19.Oldenburg} argue that an open-source paradigm has the potential to accelerate multidisciplinary research by encouraging the development of modular, interoperable tools that are supported by a community of researchers.
+
+In many domains of science, it is becoming more common for researchers to release source-code with an open license that allows use and modification (e.g., see the Open Source Initiative approved licenses: \href{https://opensource.org/licenses}{opensource.org/licenses}).
+This is an important step for improving reproducibility of research, «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{GEO.17.Broggini}.
+Going a step beyond releasing open-source software, many groups adopt an open model of development where code is hosted and versioned in an online repository, all changes are public, and users can engage by submitting and track issues.
+Community oriented projects further engage by encouraging pull-requests, which are suggested changes to the code.
+Successful, well-maintained projects often have unit-testing and continuous integration that runs those tests with any changes to the code.
+Additionally, documentation that includes examples and tutorials is an important component for on-boarding new users and contributors.
+As a result, in many areas of the geosciences, we are seeing a shift away from a one-way distribution of code towards building global communities around open projects.
+Related projects within the realm of geophysical exploration are, e.g., \texttt{pyGIMLi} \citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}
+% Others coming to mind?
+% DW: - https://github.com/fancompute/ceviche
+% RR: - no thoughts about geophysics, but there are many projects for
+%       related topics such as gmt, gis, mesh-gen
+% LH  - https://github.com/softwareunderground/awesome-open-geoscience ?
+%     - Madagascar in seismic?
+
+In this paper, we discuss the topic of open-source developments with respect to 3D CSEM modelling.
+Even though it comprises still the minority of developments, the landscape in this field of research changed in the last five years.
+Previously, there were only closed-source codes owned by companies or consortia and individual projects, often without proper documentation, that could be requested from the authors.
+We introduce and compare four recent open-source projects with focus on 3D CSEM modelling.
+All presented codes are in the Python ecosystem and use either the FV method on structured grids or the FE method on unstructured tetrahedral meshes.
+
+Furthermore, we deal with the topic of verification.
+\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the verification of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
+Hence, we first conduct a similar exercise for CSEM codes.
+We want our efforts to help to ensure the reliability of simulations, not only carried out with the available open-source codes, but also for individual closed-source projects.
+Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
+Beyond these simple models, the only objective possibility to ensure the accuracy of solutions is by comparing results from different modellers.
+If different discretisations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
+
+We simulate EM fields for a layered background model with vertical transverse isotropy, containing three blocks, as well as for the complex marine Marlim R3D model.
+These two model designs as well as the corresponding results from four different codes provide a benchmark for new codes to be compared to and validated with.
+In the following section, we introduce the codes under consideration.
+Afterwards, we present the considered benchmark cases in detail and present the modelling results of our four codes in terms of accuracy and computational performance.
+Beyond that, we extensively discuss important points that control the performance and suitability of our FV and FE codes, including mainly considerations about the mesh design and the choice of solvers.
+We conclude with a summary of our results and a motivation for the EM community to not only continue to extend the landscape of open-source codes but to also create a landscape of open-source benchmark models.
+
+\itodo{Introduce Maxwell's Equations or not? Miensopust et al., 2013, don't.}
 % Following the conventions of Ward and Hohmann \cite{Ward1988}, the quasi-static Maxwell's equations are
@@
 % \end{equation}
-}
-
-\clearpage  % TODO: Just for now while drafting, remove later!
+
 \section{Codes}
@@
 \citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg
-\citep{CAG.15.Cockett, Heagy2017}. All four codes have their user-facing routines written
+\citep{CAG.15.Cockett, CAG.17.Heagy}. All four codes have their user-facing
+routines written
 in Python; all of them make heavy use of \texttt{NumPy}
@@
 
-In the following, we provide a quick overview of the codes. It is, however, beyond the scope
-of this article to go into every detail of the different modellers, and we
-refer to their documentations for more details. An overview comparison of the
-different codes is given in Table~\ref{tbl:codecomparison}. All codes have in
-common that they solve the\mycom[DW]{are we all using the weak form?}\mycom[LH]{SimPEG uses weak form} weak
-formulation of Maxwell's equation in its differential form (DE) under the
-quasistatic or\mycom[DW]{are we all using the diff. approx?}\mycom[OCR]{petgem
-consider the weak work of maxwell equations in their diffusive form
-(quasi-static approximation)}\mycom[LH]{SimPEG uses quasistatic approx.} diffusive approximation, hence neglecting
-displacement currents. The machines on which the different codes were run are
-listed in Table~\ref{tbl:machines}\mycom[LH]{SimPEG also interfaces to the scipy solvers (but in practice those are use much less than Pardiso / mumps)}, together with the responsible operator.
+In the following, we provide a quick overview of the codes. It is, however,
+beyond the scope of this article to go into every detail of the different
+modellers, and we refer to their documentations for more details. An overview
+comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
+All codes have in common that they solve the weak formulation of Maxwell's
+equation in its differential form (DE) under the quasistatic or diffusive
+approximation, hence neglecting displacement currents. The machines on which
+the different codes were run are listed in Table~\ref{tbl:machines} together
+with the responsible operator.
+% LH: SimPEG also interfaces to the scipy solvers; but in practice those are
+%     use much less than Pardiso / mumps
+% => I leave them out for now, as you did not use them for this paper either,
+%    right? Maybe to mention in the SimPEG-section.
 
@@
 
-\itodo{
-Each code should be briefly summarized by three points:\\
-- Brief intro\\
-- Main selling point\\
-- Planned features\\
-I think in a first round \textbf{everyone should just write what they want to
-write and think is important for their code}. In a second round we should then
-homogenize it, such that all codes have more or less the same length/weight and
-also similar topic/layout.
-}
-
-\clearpage  % TODO: Just for now while drafting, remove later!
 \subsection{custEM}
 
-The customisable electromagnetic modeling Python toolbox custEM was developed
+The customisable electromagnetic modelling Python toolbox custEM was developed
 for simulating arbitrary complex 3D CSEM geometries with focus on semi-airborne
@@
 The toolbox considers generally anisotropic petrophysical properties. Even
-though changes of the conductivity is mainly of interest for CSEM modeling, the
+though changes of the conductivity is mainly of interest for CSEM modelling, the
 electric permittivity and magnetic permeability can be taken into account using
@@
 bodies such as folds or faults in meshes. Furthermore, current work is on using
-custEM for inverse modeling applications.
+custEM for inverse modelling applications.
 
@@
 to improve or to add additional features. For instance, in the short-term, more
-modeling routines and support for multi-source set-ups will be implemented. For
+modelling routines and support for multi-source set-ups will be implemented. For
 the long-term, the obvious next step is to move to 3D CSEM data inversion.
@@
 extensible framework and to facilitate integration of data sets from a variety
-of geophysical methods, including joint inversions \citep{Astic2020}, by
+of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by
 providing a common interface to each method.
@@
 Meshes and finite volume differential operators are implemented in the
-\texttt{discretize} package. It currently includes tensor, OcTree,
-cylindrical, and logically rectangular meshes. Each mesh type inherits from a
-common structure and uses the same naming conventions for methods and
-properties. This allows us to decouple the implementation of a discretized
-partial differential equation from the details of the mesh geometry and
-therefore we can write a single implementation of discretized partial
-differential equation (or set of partial differential equations) in \simpeg
-that will support all mesh types implemented in \texttt{discretize}.
+\discretize package. It currently includes tensor, OcTree, cylindrical, and
+logically rectangular meshes. Each mesh type inherits from a common structure
+and uses the same naming conventions for methods and properties. This allows us
+to decouple the implementation of a discretized partial differential equation
+from the details of the mesh geometry and therefore we can write a single
+implementation of discretized partial differential equation (or set of partial
+differential equations) in \simpeg that will support all mesh types implemented
+in \discretize.
 
@@
 cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
-discretizing Maxwell's equations, we recommend \cite{Haber2014b}). There are
+discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}). There are
 two different discretization strategies implemented for Maxwell's equations: (
@@
 
-% Support for domain decomposition approaches (see for example \cite{Fournier2020})
-
-\simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}.
-For problems with many sources (and reciprocity is not a natural solution, e.g.
-in 3D airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{Fournier2020}.
-
-\clearpage  % TODO: Just for now while drafting, remove late{}r!{}
+% Support for domain decomposition approaches (see for example
+% \cite{GEO.20.Fournier})
+
+\simpeg interfaces to various solvers including \texttt{PARDISO}
+\citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as
+those implemented in the \texttt{scipy.sparse.linalg} module
+\citep{NM.20.Virtanen}. For problems with many sources (and reciprocity is not
+a natural solution, e.g. in 3D airborne EM), \simpeg contains machinery for
+domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
+
 \section{Numerical Verifications}
@@
 The block model is a derivation of the \emph{Dublin Test Model 1} from the
-first EM modeling workshop described by \cite{GJI.13.Miensopust}. We took the
+first EM modelling workshop described by \cite{GJI.13.Miensopust}. We took the
 same layout of the blocks but adjusted the dimensions and resistivities to a
@@
 \tabl[btp]{comp-layered}{Comparison of used CPU and RAM and of number of cells
-  used to discretize the layered model. \imycom[DW]{I will fill this table out
-  once we all submitted the final versions of the results.}}{
+  used to discretize the layered model.}{
   \centering
-\begin{tabular}{c c c c c}  %{lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
   \toprule
@@
 have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very
-similar, as well as are \custem and \petgem. \mycom[DW]{Write in detail when
-all results are available}
+similar, as well as are \custem and \petgem.
+\imycom[DW]{Write in detail when all results are available}
 %
@@
 \tabl[btp]{comp-block}{Comparison of used CPU and RAM and of number of cells
-  used to discretize the block model. \imycom[DW]{I will fill this table out
-  once we all submitted the final versions of the results.\imycom[OCR]{I can help you to fill this table and with its analysis}}}{
+  used to discretize the block model.}{
   \centering
-\begin{tabular}{c c c c c}  %lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
   \toprule
@@
 
-\clearpage  % TODO: Just for now while drafting, remove later!
 \subsection{Marlim R3D}
@@
 consideration here compute the results all in the frequency-domain.
-\imycom[RR]{I would delete this sentence, not that important and a bit
-  redundant.
-\imycom[DW]{Did you refer to the last sentence or the one before? I think the
-  last sentence contains quite important info.}
-\imycom[OCR]{If possible, I would like to uphold this sentence. I agree with
-  Dieter, it contains relevant information.}
-}
 
@@
   the drawn survey line in that figure are plainly wrong.
-  {\imycom[DW]{If someone is
-  familiar with GMT and happy to make that would be great. Also, the
-cross-section is currently heavily vertically exaggerated.
-\imycom[RR]{I used gmt the last time 7 years ago , in between I tried the
-  gmt4py tools, but they did not work well on my machine. I suggest to use two
-  plots next to each other, a similar figure as in the notebook and a simple
-  x-y coord sketch (identical extent as the bird perspective view in the other
-  plot) with all Tx / Rx locations, highlighting the relevant line and Rx for
-  us.}}}
 }
@@
 \tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
-  used to discretize the Marlim R3D model.
-  \imycom[DW]{I will fill this table out once we all submitted the final
-    versions of the results.\imycom[OCR]{I can help you to fill this table and
-    with its analysis}}}{
+  used to discretize the Marlim R3D model.}{
   \centering
-\begin{tabular}{c c c c c}  %{ls[table-format=4.2]rs[table-format=4.2]rl}
+\begin{tabular}{ls[table-format=4.2]rs[table-format=4.2]rl}
   \toprule
@@
 
-\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Discussion}
@@
 
-\imycom[DW]{Maybe we should create a Google-Doc for working on the Discussion
-collaboratively at the same time?
-\imycom[RR]{if you prefer ok, but I don't think this is necessary, if everyone
-  adds the own thoughts when he receives the manuscript. Same for conclusions.
-  We need to take care to not mix discussion and conclusions, some of the
-  statements from here belong rather to the conclusions, I hope it's fine that
-  I reorganized the content. Aside from that, I already added all thoughts of
-  mine.}
-}
-
-Even if modeling results may look completely valid, they could not be correct
+Even if modelling results may look completely valid, they could not be correct
 at all. Verifying the performance of 3D CSEM codes for real 3D problems is only
@@
 We see this work as the start for future elaboration on the validation of
-modeling codes, not necessarily restricted to CSEM problems. Much more
+modelling codes, not necessarily restricted to CSEM problems. Much more
 comparisons and examples are required which not only result in the finding that
@@
 rather well known fact. We are surprised that only the minority of publications
-in the field of 3D EM modeling considers a sufficiently detailed elaboration of
+in the field of 3D EM modelling considers a sufficiently detailed elaboration of
 the meshing process.
@@
 is a very powerful method to confirm the general functionality of codes for any
-modeling problem, which might not be covered by existing cross-validation
+modelling problem, which might not be covered by existing cross-validation
 benchmark examples. Considering for instance  this study, it would be very
@@
 
-\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Conclusions \& Outlook}
@@
 %
-
-\imycom[DW]{Maybe we should create a Google-Doc for working on the Conclusions
-collaboratively at the same time?}
-
-\imycom[DW]{I obviously haven't really done this section, just af few thoughts
-  that I noted over time. I think the discussion (as the abstract) has to be
-tackled once the rest is at least in a draft status and all data is ready.}
-
-\imycom[RR]{I also rearranged some of your thoughts and formulated mine. I
-  moved some of them (the few sentences that were rather redundant motivation
-content) to the introdcution.}
 
@@
 
-\clearpage  % TODO: Just for now while drafting, remove later!
 \section{Acknowledgment}
 
-\imycom[DW]{Write here your fundings; and potentially also minor contributors
-etc.}
-
-We would like to thank Paulo Menezes for the help and explanations with regards
-to the Marlim R3D model and corresponding CSEM data, and for making their
-actual computation model available under an open-source license.
-
-The work of D.W. was conducted within the Gitaro.JIM project funded through
-MarTERA, a EU Horizon 2020 research and innovation programme (No 728053);
-\href{https://www.martera.eu}{martera.eu}. The development of \custem as part of
-the DESMEX project was funded by the Germany Ministry for Education and
-Research (BMBF) in the framework of the research and development program
-Fona-r4 under grant 033R130D. The work of O.C-R. has received funding from the
-\emph{European Union's Horizon 2020 programme} under the \emph{Marie
-Sklodowska-Curie} grant agreement N$^\circ$ 777778. Further, the development of
-\petgem has received funding from the \emph{European Union's Horizon 2020
-programme}, grant agreement N$^\circ$ 828947, and from the Mexican Department
-of Energy, CONACYT-SENER Hidrocarburos grant agreement N$^\circ$ B-S-69926.
-Furthermore, O.C-R. has been 65\% cofinanced by the European Regional
-Development Fund (ERDF) through the Interreg V-A Spain-France-Andorra program
-(POCTEFA2014-2020). POCTEFA aims to reinforce the economic and social
-integration of the French-Spanish-Andorran border. Its support is focused on
-developing economic, social and environmental cross-border activities through
-joint strategies favouring sustainable territorial development.
-\imycom[OCR]{My
-  apologies for these long acks, but they are the projects in which I am
-  participating and the BSC makes a lot of emphasis on complying verbatim with
-  the thansk sentences (too rigorous in my opinion)}
-
-\clearpage  % TODO: Just for now while drafting, remove later!
+We would like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
+
+The work of D.W.
+was conducted within the Gitaro.JIM project funded through MarTERA, a \emph{European Union's Horizon 2020} research and innovation programme, grant agreement N$^\circ$~728053; \href{https://www.martera.eu}{martera.eu}.
+
+The development of \custem as part of the DESMEX project was funded by the Germany Ministry for Education and Research (BMBF) in the framework of the research and development program Fona-r4 under grant 033R130D.
+
+The work of O.C-R.
+has received funding from the \emph{European Union's Horizon 2020 programme} under the \emph{Marie Sklodowska-Curie} grant agreement N$^\circ$ 777778.
+Further, the development of \petgem has received funding from the \emph{European Union's Horizon 2020 programme}, grant agreement N$^\circ$~828947, and from the Mexican Department of Energy, CONACYT-SENER Hidrocarburos grant agreement N$^\circ$ B-S-69926.
+Furthermore, O.C-R.
+has been 65\% cofinanced by the European Regional Development Fund (ERDF) through the Interreg V-A Spain-France-Andorra program (POCTEFA2014-2020).
+POCTEFA aims to reinforce the economic and social integration of the French-Spanish-Andorran border.
+Its support is focused on developing economic, social and environmental cross-border activities through joint strategies favouring sustainable territorial development.
+
 \section{Data}
 
-All files to rerun the different models with the four codes and reproduce the
-shown results are available at \dots.
+All files to rerun the different models with the four codes and reproduce the shown results are available at \dots.
 \itodo{Put up on Zenodo, link here.}
 
-\clearpage  % TODO: Just for now while drafting, remove later!
 % REFERENCES

### 2020-07-07 manuscript/Manuscript.tex
2nd round DW working on it

@@
 % \end{equation}
+%
+% If we include Maxwell's equations, we might cite here Haber, 2014, for its
+% discretization.
 
@@
 
-\imycom[RR]{I think we should introduce the term degrees of freedom (dof),
-  equivalent to the size of the SLE, as general measure of our problem sizes.
-  If it is somewhat x*Nedges, or related to Ncells or Nnodes, who cares? We
-  just need this one number for this paper in my opinion, more details in the
-  jupyter notebooks - fine.}
+The four codes under consideration are, in alphabetical order, \custem \citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem \citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett, CAG.17.Heagy}.
+All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}.
+The four of them are “modern” open-source projects, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
+Newer package-management systems such as Conda, Docker, or pip significantly supported us to make our codes easily available and installable on any of the major operating system without any user-side compilations.
+Each one can be downloaded and installed with a single command.
 
-The four codes under consideration are, in alphabetical order, \custem
-\citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem
-\citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg
-\citep{CAG.15.Cockett, CAG.17.Heagy}. All four codes have their user-facing
-routines written
-in Python; all of them make heavy use of \texttt{NumPy}
-\citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}. The four
-of them are “modern” open-source projects, meaning that they come with both, an
-open-source license and an online-hosted version-control system with tracking
-possibilities (raising issues, filing pull requests). All developments comprise
-an extensive online documentation with many examples and have continuous
-integration to some degree. Newer package-management systems such as Conda,
-Docker, or pip significantly supported us to make our codes easily available
-and installable without any user-side compilations. Each one can be downloaded
-and installed with a single command.
-
-In the following, we provide a quick overview of the codes. It is, however,
-beyond the scope of this article to go into every detail of the different
-modellers, and we refer to their documentations for more details. An overview
-comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
-All codes have in common that they solve the weak formulation of Maxwell's
-equation in its differential form (DE) under the quasistatic or diffusive
-approximation, hence neglecting displacement currents. The machines on which
-the different codes were run are listed in Table~\ref{tbl:machines} together
-with the responsible operator.
+In the following, we provide a quick overview of the codes.
+It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details.
+An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
+All codes have in common that they solve the weak formulation of Maxwell's equation in its differential form (DE) under the quasistatic or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
+The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
 % LH: SimPEG also interfaces to the scipy solvers; but in practice those are
@@
             Skylake generation; 2 sockets Intel Xeon Platinum 8160 CPU with 24
-            cores each @2.10GHz for a total of 48 cores per node; 386 Gb DDR4
+            cores each @2.10GHz for a total of 48 cores per node; 386 GB DDR4
             RAM per node; SuSE Linux Enterprise
           & Octavio Castillo-Reyes \\
-  \simpeg & ???
+          \simpeg & \itodo{Todo Lindsey}
           & Lindsey Heagy \\
@@
 
+\imycom[DW]{Raphael: I think here would be the right place? I guess for
+  tensor meshes as mine it is simply number of cells (times the anisotropy
+  type; for VTI x2). But you know better what it means for \custem/\petgem.
+  \imycom[RR]{I think we should introduce the term degrees of freedom (dof),
+    equivalent to the size of the SLE, as general measure of our problem sizes.
+    If it is somewhat x*Nedges, or related to Ncells or Nnodes, who cares? We
+    just need this one number for this paper in my opinion, more details in the
+    jupyter notebooks - fine.
+  }
+}
+
 \subsection{custEM}
 
-The customisable electromagnetic modelling Python toolbox custEM was developed
-for simulating arbitrary complex 3D CSEM geometries with focus on semi-airborne
-setups, but it supports also land-based, airborne, coastal  or marine
-environments. Multiple electric or magnetic field or potential finite-element
-approaches were implemented as total or secondary field formulations. The
-finite-element kernel, including higher order basis functions and
-parallelisation, relies on the FEniCS project \citep{B.SPR.12.Logg,
-B.SPR.16.Langtangen}. The resulting systems of linear equations are solved with
-MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming
-choice. Primary field solutions are supplied by the COMET \citep{GEO.20.Skibbe}
-package.
+The customisable electromagnetic modelling Python toolbox custEM was developed for simulating arbitrary complex 3D CSEM geometries with a focus on semi-airborne setups, but it supports also land-based, airborne, coastal, or marine environments.
+Multiple electric or magnetic field or potential finite-element approaches were implemented as total or secondary field formulations.
+The finite-element kernel, including higher order basis functions and parallelisation, relies on the FEniCS project \citep{B.SPR.12.Logg, B.SPR.16.Langtangen}.
+The resulting systems of linear equations are solved with MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming choice.
+Primary field solutions are supplied by the COMET \citep{GEO.20.Skibbe} package.
 
-The toolbox considers generally anisotropic petrophysical properties. Even
-though changes of the conductivity is mainly of interest for CSEM modelling, the
-electric permittivity and magnetic permeability can be taken into account using
-the preferred electric field approach on Nédélec elements. Recently, induced
-polarization parameters in frequency-domain and three methods for simulating
-time-domain responses were added to custEM. The provided meshing tools based on
-TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker}
-facilitate the generation of tetrahedral meshes including layered-earth
-geometries with topography or bathymetry and anomalous bodies which are allowed
-to be connected or to reach the surface.
+The toolbox considers generally anisotropic petrophysical properties.
+Even though changes of the conductivity is mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
+Recently, induced polarization parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
+The provided meshing tools based on TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
 
-The custEM toolbox is under steady development and maintenance. Future
-enhancements comprise adding iterative solution techniques, provided by FEniCS,
-as well as further functionalities for automatically incorporating intersecting
-bodies such as folds or faults in meshes. Furthermore, current work is on using
-custEM for inverse modelling applications.
+The custEM toolbox is under steady development and maintenance.
+Future enhancements comprise adding iterative solution techniques, provided by FEniCS, as well as further functionalities for automatically incorporating intersecting bodies such as folds or faults in meshes.
+Furthermore, current work is on using custEM for inverse modelling applications.
 
@@
 
-The 3D CSEM modeller \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for
-3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial
-electrical anisotropy, isotropic electric permittivity, and isotropic magnetic
-permeability. The matrix-free solver can be used as main solver or as
-preconditioner for one of the Krylov subspace methods implemented in SciPy, and
-the governing equations are discretized on a staggered grid by the
-finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume
-generalization of a Yee grid. The code is written completely in Python using
-the NumPy and SciPy stacks, where the most time- and memory-consuming parts are
-sped up through jitted (just-in-time compiled) functions using Numba
-\citep{LLVM.15.Lam}. The code computes the electric field due to an electric
-source in the frequency-domain, which is its main application (frequency-domain
-CSEM). However, there are also routines to obtain the magnetic field due to an
-electric source, to obtain the electric and magnetic fields due to a magnetic
-source, and to obtain time-domain responses.
+The 3D CSEM code \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for 3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial electrical anisotropy, isotropic electric permittivity, and isotropic magnetic permeability.
+The matrix-free solver can be used as main solver or as preconditioner for one of the Krylov subspace methods implemented in SciPy, and the governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalization of a Yee grid.
+The code is written completely in Python using the NumPy and SciPy stacks, where the most time- and memory-consuming parts are sped up through jitted (just-in-time compiled) functions using Numba \citep{LLVM.15.Lam}.
+The multigrid method is characterized by almost linear scaling both in terms of runtime (CPU) and memory (RAM) usage, and it is therefore a comparably low-memory consumption solver.
 
-The multigrid method is characterized by almost linear scaling both in terms of
-runtime (CPU) and memory (RAM) usage, and it is therefore a comparably
-low-memory consumption solver. It is also minimal in terms of requirements,
-only NumPy, SciPy, and Numba are required, with Python 3.7+. The current
-development is focused on adding basic inversion capabilities, and a further
-plan is to implement a hook in order to use \emg3d as a frequency-domain CSEM
-solver within the grander \simpeg framework.
+The code comes with functionalities to be used directly as a CSEM modeller too, in addition to serve as a solver.
+As such, it computes the electric field due to an electric source in the frequency-domain, which is its main application (frequency-domain CSEM).
+However, there are also routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses.
+
+Current development is focused on adding basic inversion capabilities, and a further plan is to implement a hook in order to use \emg3d as a frequency-domain CSEM solver within the grander \simpeg framework.
 
@@
 
-\petgem is a parallel code for frequency-domain 3D CSEM data from marine and
-land surveys. The high-order edge FE method (HEFEM) is used for the
-discretization of the governing equations in its diffusive form. This technique
-provides a suitable mechanism to obtain stable numerical solutions as well as a
-good trade-off between number of dof\mycom[OCR]{I assume we have previously
-mentioned the term dofs} and computational effort. The current implementation
-supports up to six-order tetrahedral vector basis functions. Moreover, because
-the HEFEM belongs to the FE family, the unstructured meshes can be used
-efficiently on complex geometries (e.g., models with topography and
-bathymetry).
+\petgem is a parallel code for frequency-domain 3D CSEM data for marine and land surveys.
+The high-order edge FE method (HEFEM) is used for the discretization of the governing equations in its diffusive form.
+This technique provides a suitable mechanism to obtain stable numerical solutions as well as a good trade-off between number of dof and computational effort.
+The current implementation supports up to sixth-order tetrahedral vector basis functions.
+Moreover, because the HEFEM belongs to the FE family, the unstructured meshes can be used efficiently on complex geometries, e.g., models with topography and bathymetry.
 
-\petgem permits to locate the source and receivers anywhere in the
-computational domain\mycom[DW]{I think this applies to all four codes} (e.g.,
-sediments, seafloor, sea, ground), allowing to analyze the physical environment
-of the electric responses and how parameters impact them (e.g., frequency,
-conductivity, dependence on mesh setup, basis order, solver type, among
-others). Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$
-mesh refinement) based on physical parameters and on polynomial order to
-satisfy quality criteria chosen by the user. Nonetheless, only Horizontal
-Electric Dipole (HED) has been implemented.
+\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyze the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type, among others).
+Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$ mesh refinement) based on physical parameters and on polynomial order to satisfy quality criteria chosen by the user.
+Nonetheless, only Horizontal Electric Dipole (HED) has been implemented.
 
-For the parallel forward modelling computations, a highly scalable MPI domain
-decomposition allows reducing run-times and the solution of large-scale
-modelling cases. This strategy is capable of exploiting the parallelism offered
-by both modest multi-core computers and cutting-edge clusters (e.g.,
-High-performance Computing architectures).
+For the parallel forward modelling computations, a highly scalable MPI domain decomposition allows reducing run-times and the solution of large-scale modelling cases.
+This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing architectures).
 
-Based on the current state of the \petgem project, there are many possibilities
-to improve or to add additional features. For instance, in the short-term, more
-modelling routines and support for multi-source set-ups will be implemented. For
-the long-term, the obvious next step is to move to 3D CSEM data inversion.
+Based on the current state of the \petgem project, there are many possibilities to improve or to add additional features.
+For instance, in the short-term, more modelling routines and support for multi-source set-ups will be implemented.
+For the long-term, the obvious next step is to move to 3D CSEM data inversion.
 
@@
 
-\simpeg is a modular toolbox for simulations and gradient based inversions in
-geophysics. Current functionality includes modelling and inversion
-capabilities for gravity, magnetics, direct current resistivity, induced
-polarization, electromagnetics (time, frequency, as well as natural sources,
-e.g. magnetotellurics), and fluid flow (Richards equation). It is a community
-driven project that aims to support researchers by providing a flexible,
-extensible framework and to facilitate integration of data sets from a variety
-of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by
-providing a common interface to each method.
+\simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
+Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarization, electromagnetics (time, frequency, as well as natural sources such as magnetotellurics), and fluid flow (Richards equation).
+It is a community driven project that aims to support researchers by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.
+\imycom[DW]{Lindsey: «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}
 
-Meshes and finite volume differential operators are implemented in the
-\discretize package. It currently includes tensor, OcTree, cylindrical, and
-logically rectangular meshes. Each mesh type inherits from a common structure
-and uses the same naming conventions for methods and properties. This allows us
-to decouple the implementation of a discretized partial differential equation
-from the details of the mesh geometry and therefore we can write a single
-implementation of discretized partial differential equation (or set of partial
-differential equations) in \simpeg that will support all mesh types implemented
-in \discretize.
+Meshes and finite volume differential operators are implemented in the \discretize package, which currently includes tensor, OcTree, cylindrical, and logically rectangular meshes.
+Each mesh type inherits from a common structure and uses the same naming conventions for methods and properties.
+This allows us to decouple the implementation of a discretized partial differential equation from the details of the mesh geometry and therefore we can write a single implementation of discretized partial differential equation (or set of partial differential equations) in \simpeg that will support all mesh types implemented in \discretize.
 
-The electromagnetics implementations use a staggered grid finite volume
-approach where physical properties are discretized at cell centers, fields on
-cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
-discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}). There are
-two different discretization strategies implemented for Maxwell's equations: (
-a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
-cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (b)
-the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
-edges and the current density ($\vec{j}$) on cell faces. In both cases the
-physical properties: electrical conductivity / resistivity and magnetic
-permeability are discretized at cell centers. Having multiple implementations
-allows for testing that compares results from each approach, as well as the
-representation of both electrical and magnetic sources on cylindrically
-symmetric meshes. \simpeg supports variable magnetic permeability and
-full-tensor anisotropy for the physical properties.
+The electromagnetics implementations use a staggered grid finite volume approach where physical properties are discretized at cell centers, fields on cell edges and fluxes on cell faces \citep{IEEE.66.Yee}.
+%(for an overview of discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}).
+There are two different discretization strategies implemented for Maxwell's equations: (a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (b) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces.
+In both cases the physical properties: electrical conductivity / resistivity and magnetic permeability are discretized at cell centers.
+Having multiple implementations allows for testing that compares results from each approach, as well as the representation of both electrical and magnetic sources on cylindrically symmetric meshes.
+\simpeg supports variable magnetic permeability and full-tensor anisotropy for the physical properties.
 
-% Support for domain decomposition approaches (see for example
-% \cite{GEO.20.Fournier})
-
-\simpeg interfaces to various solvers including \texttt{PARDISO}
-\citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as
-those implemented in the \texttt{scipy.sparse.linalg} module
-\citep{NM.20.Virtanen}. For problems with many sources (and reciprocity is not
-a natural solution, e.g. in 3D airborne EM), \simpeg contains machinery for
-domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
+\simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}.
+For problems with many sources (and reciprocity is not a natural solution, e.g.
+in 3D airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
 
@@
 
-We computed the responses for two different models to verify that all different
-3D codes yield the same electromagnetic responses. The first simple \emph{Block
-model} consists of a layered, anisotropic background with three embedded
-blocks. The second Marlim R3D model is based on a very complex, realistic
-marine CSEM setup.
+We computed the responses for two different models to verify that all different 3D codes yield the same electromagnetic responses.
+The first simple \emph{Block model} consists of a layered, anisotropic background with three embedded blocks.
+The second model, \emph{Marlim R3D}, is based on a very complex, realistic marine CSEM setup.
 
@@
 
-The block model is a derivation of the \emph{Dublin Test Model 1} from the
-first EM modelling workshop described by \cite{GJI.13.Miensopust}. We took the
-same layout of the blocks but adjusted the dimensions and resistivities to a
-typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}. We
-additionally added a layered background with vertical transverse isotropy
-(VTI).
+The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
+We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}.
+We additionally added a layered background with vertical transverse isotropy (VTI).
 %
 \plot*{block-model}{width=.6\textwidth}{
-  Sketch of the block model. The layered model consists of an air layer, a
-  water layer, a thin top-layer followed by a thick, anisotropic background
-  layer, and at the bottom a resistive basement layer. All three blocks are
-  embedded in the thick background layer, which has VTI with
-  $\lambda=\sqrt{2}$.
+  Sketch of the block model.
+The layered model consists of an air layer, a water layer, a thin top-layer followed by a thick, anisotropic background layer, and at the bottom a resistive basement layer.
+All three blocks are embedded in the thick background layer, which has VTI with $\lambda=\sqrt{2}$.
 }
@@
 
-The layered model consists of an upper halfspace of air, a 600\,m deep water
-layer, followed by a 150\,m thick, isotropic layer of 1\,\ohmm, a 3.3\,km
-thick, anisotropic layer of $\rho_\text{h}=2\,\ohmm$ and
-$\rho_\text{v}=4\,\ohmm$, and finally a resistive basement consisting of a
-lower halfspace of $1000\,\ohmm$. The 200\,m long, $x$-directed source is
-located 50\,m above the seafloor from $x=-50$ to $x=50\,$m in $x$-direction, at
-$y=0\,$m. The $x$-directed receivers are placed on the seafloor every 200\,m
-from $x=-10\,$km to $x=+10\,$km in three lines for $y=-3, 0, 3\,$km.
+The layered model consists of an upper halfspace of air, a 600\,m deep water layer, followed by a 150\,m thick, isotropic layer of 1\,\ohmm, a 3.3\,km thick, anisotropic layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive basement consisting of a lower halfspace of $1000\,\ohmm$.
+The 200\,m long, $x$-directed source is located 50\,m above the seafloor from $x=-50$ to $x=50\,$m in $x$-direction, at $y=0\,$m.
+The $x$-directed receivers are placed on the seafloor every 200\,m from $x=-10\,$km to $x=+10\,$km in three lines for $y=-3, 0, 3\,$km.
 
-The thin isotropic layer beneath the water requires many tetrahedra for a
-good-quality discretisation. Therefore, the FE codes \custem and \petgem used
-the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from
-the origin, surrounded by a ten times larger halfspace-like boundary mesh with
-water conductivities assigned to the subsurface. This approximation
-significantly reduced the problem size compared to considering the
-layered-earth geometry for the whole computational domain. \imycom[RR]{Add
-short information about mesh design with SIMPEG and emg3d, including something
-like "comparatively coarse discretization in center to minimize computation
-times" }
+The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretisation.
+Therefore, the FE codes \custem and \petgem used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
+This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
+\imycom[RR]{Add short information about mesh design with SIMPEG and emg3d, including something like "comparatively coarse discretization in center to minimize computation times" }
 
-In a first step, we compare the layered background to the semi-analytical
-solutions of a 1D code, for which we use  \empymod\citep{GEO.17.Werthmuller}.
-Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the
-actual responses in the top rows, and the relative error in the bottom rows for
-the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
+In a first step, we compare the layered background to the semi-analytical solutions of a 1D code, for which we use  \empymod\citep{GEO.17.Werthmuller}.
+Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the actual responses in the top rows, and the relative error in the bottom rows for the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
 
-Figure~\ref{fig:results-layered-0} illustrates the inline responses in the
-top-row for offsets $r>0.5\,$km. We only show the semi-analytical result for
-the real and imaginary amplitudes. The bottom row displays the relative error
-of the 3D codes. The results show that all codes are yielding accurate result
-with errors of around 1\,\% in most parts and overall below a few percent,
-disregarding locations affected by sign reversals. The differences can be
-mainly attributed to the chosen discretisations. The FE codes show the
-strongest misfits at large offsets, most likely caused by the utilized boundary
-mesh. Very low errors at large offsets are achieved by \emg3d, whereas it
-suffers at short offsets from a coarse grid.
+Figure~\ref{fig:results-layered-0} illustrates the inline responses in the top-row for offsets $r>0.5\,$km.
+We only show the semi-analytical result for the real and imaginary amplitudes.
+The bottom row displays the relative error of the 3D codes.
+The results show that all codes are yielding accurate result with errors of around 1\,\% in most parts and overall below a few percent, disregarding locations affected by sign reversals.
+The differences can be mainly attributed to the chosen discretisations.
+The FE codes show the strongest misfits at large offsets, most likely caused by the utilized boundary mesh.
+Very low errors at large offsets are achieved by \emg3d, whereas it suffers at short offsets from a coarse grid.
 %
@@
 
-In a second step, three resistive blocks were added in the 3.3\,km-thick,
-anisotropic background layer as shown in Figure~\ref{fig:block-model}. They
-have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey
-lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$
-(cube, North-West). As there are no analytical solutions for this model we show
-the normalized difference between different codes, instead of the relative
-error, where the normalized difference of two responses $p$ and $q$ is given by
+In a second step, three resistive blocks were added in the 3.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}.
+They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
+As there are no analytical solutions for this model we show the normalized difference between different codes, instead of the relative error, where the normalized difference of two responses $p$ and $q$ is given by
 %
@@
 %
-\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too
-cluttered, and I don't think it would add a lot insights. My idea is therefore
-to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones),
-and \emg3d/\custem (a cross-comparison). What do you think?
+\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too cluttered, and I don't think it would add a lot insights.
+My idea is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones), and \emg3d/\custem (a cross-comparison).
+What do you think?
 
@@
 
-The results for the three receiver lines $y=-3,0,3\,$km are shown in
-Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and
-\ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in
-Table~\ref{tbl:comp-block}. We can conclude from the NRMSD that similar codes
-have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very
-similar, as well as are \custem and \petgem.
+The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in Table~\ref{tbl:comp-block}.
+We can conclude from the NRMSD that similar codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very similar, as well as are \custem and \petgem.
 \imycom[DW]{Write in detail when all results are available}
@@
 
-The difference becomes only significant at offsets larger than 8\,km. This is
-due to a practical difference in the meshing: This simple block model is
-advantageous for FV codes, as it consists of rectangular blocks and horizontal
-layers, simple geometric objects. While having a very thin, shallow layer is
-straight-forward for FV codes, it requires many cells for a FE code, and
-a similar approach as for the Block Model was used. This is the reason for the
-increased NRMSD at large offsets, and it has nothing to do with the accuracy of
-the computation itself.
+The difference becomes only significant at offsets larger than 8\,km.
+This is due to a practical difference in the meshing: This simple block model is advantageous for FV codes, as it consists of rectangular blocks and horizontal layers, simple geometric objects.
+While having a very thin, shallow layer is straight-forward for FV codes, it requires many cells for a FE code, and a similar approach as for the Block Model was used.
+This is the reason for the increased NRMSD at large offsets, and it has nothing to do with the accuracy of the computation itself.
 
@@
 
-The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in
-the north-eastern part of the Campos Basin, offshore Brazil, which was
-discovered in 1985. \cite{BJG.17.Carvalho} created from seismic data and well
-log data a realistic resistivity model with vertical transverse isotropy (VTI),
-Marlim R3D (MR3D), which they released under an open-source license.
-\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to
-1.25\,Hz, released under an open-source license. To compute the data they used
-a state-of-the-art code from the industry \citep{GEO.07.Maao}. It is therefore
-an ideal case to verify our open-source codes against, as it is a complex,
-realistic model and the data were computed by an industry-proofed code.
-Additionally, that code is a time-domain code, whereas the four codes under
-consideration here compute the results all in the frequency-domain.
+The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in the north-eastern part of the Campos Basin, offshore Brazil, which was discovered in 1985.
+\cite{BJG.17.Carvalho} created from seismic data and well log data a realistic resistivity model with vertical transverse isotropy (VTI), Marlim R3D (MR3D), which they released under an open-source license.
+\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to 1.25\,Hz, released under an open-source license.
+To compute the data they used a state-of-the-art code from the industry \citep{GEO.07.Maao}.
+It is therefore an ideal case to verify our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
+Additionally, that code is a time-domain code, whereas the four codes under consideration here compute the results all in the frequency-domain.
 
-The detailed reservoir model consists of $1022 \times 371 \times 1229$ cells,
-totalling to almost 466 million cells, where each cell has dimensions of 25 by
-75 by 5\,m. For the computation the model is upscaled to 515 by 563 by 310
-cells, totalling to almost 90 million cells, where each cell has dimensions of
-100 by 100 by 20\,m.
+The detailed reservoir model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
+For the computation the model is upscaled to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
 
-The published data set consists of a regular grid of receivers of 20 in eastern
-direction by 25 in northern direction, 500 receivers in total, with 1\,km
-spacing located on the irregular seafloor. 45 source-towlines were located on
-the same grid, 50\,m above the seafloor, with shots every 100\,m. In
-\cite{GEO.19.Correa} the actual responses for one receiver with the
-corresponding East-West inline and one East-West broadside acquisition line are
-shown, which is the data we chose for our comparison. The cross-section of the
-resistivity model along the chosen inline acquisition line is shown in
-Figure~\ref{fig:model-marlim}, together with the acquisition information.
+The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
+45 source-towlines were located on the same grid, 50\,m above the seafloor, with shots every 100\,m.
+In \cite{GEO.19.Correa} the actual responses for one receiver with the corresponding East-West inline and one East-West broadside acquisition line are shown, which is the data we chose for our comparison.
+The cross-section of the resistivity model along the chosen inline acquisition line is shown in Figure~\ref{fig:model-marlim}, together with the acquisition information.
 
@@
 
-We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$)
-for both inline and broadside acquisition lines. However, we show here only the
-three frequencies and the responses with the strongest amplitudes (which are
-generally used in processing), which are $E_x$ inline and broadside, and $E_y$
-broadside. The comparison is shown in Figure~\ref{fig:results-marlim}.
+We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$) for both inline and broadside acquisition lines.
+However, we show here only the three frequencies and the responses with the strongest amplitudes (which are generally used in processing), which are $E_x$ inline and broadside, and $E_y$ broadside.
+The comparison is shown in Figure~\ref{fig:results-marlim}.
 %
@@
 
-Even if modelling results may look completely valid, they could not be correct
-at all. Verifying the performance of 3D CSEM codes for real 3D problems is only
-possible by cross-validating multiple solutions. Overall, we observed an
-excellent match between all solutions. The relative misfits, almost always
-smaller than 10\,\%, were related to the either weak or strong amplitudes of
-real or imaginary parts and can be attributed to particularities regarding the
-discretization, boundary effects, and interpolation. Considering this
-satisfactory result in terms of accuracy and robustness, it is more interesting
-to discuss the characteristics of the four considered codes with focus on the
-demand of computational resources and the capability of handling the
-investigated CSEM geometries, including the very important underlying mesh
-design. The following arguments are based on a comparison of only marine CSEM
-models, which are the focus of industry applications. Nevertheless, we are
-confident that many observations would hold in a similar manner for land-based,
-airborne, or mixed setups.
+Even if modelling results may look completely valid, they could not be correct at all.
+Verifying the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
+Overall, we observed an excellent match between all solutions.
+The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation.
+Considering this satisfactory result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
+The following arguments are based on a comparison of only marine CSEM models, which are the focus of industry applications.
+Nevertheless, we are confident that many observations would hold in a similar manner for land-based, airborne, or mixed setups.
 
-We point out that making a synthetic and a real benchmark model available to
-cross-validate any 3D CSEM code was the determining reason for their choice,
-regardless of the suitability of the considered FD and FE codes for these
-problems. The first model, including the block-anomalies variation, is exactly
-reproducible by using any numerical method with either regular or irregular
-computational domains. Aside from the idea of analyzing an industrially
-relevant benchmark example, the Marlim R3D model was also considered since the
-primary design from \cite{GEO.19.Correa} uses a regular discretisation. At
-least theoretically, the exact geometry might be reconstructed with
-unstructured meshes, but it is never possible to convert an irregular geometry
-to a regular grid without approximations. Hence, the chosen examples favoured
-the FD codes, since they used either regular grids or
-octree-meshes, whereas the two FE codes were required to
-tetrahedralise the model geometries.
+We point out that making a synthetic and a real benchmark model available to cross-validate any 3D CSEM code was the determining reason for their choice, regardless of the suitability of the considered FD and FE codes for these problems.
+The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
+Aside from the idea of analyzing an industrially relevant benchmark example, the Marlim R3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretisation.
+At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
+Hence, the chosen examples favoured the FD codes, since they used either regular grids or octree-meshes, whereas the two FE codes were required to tetrahedralise the model geometries.
 
-In the first model, the necessity of discretising regular structures with
-tetrahedra, especially thin layers, led to comparatively large FE problem sizes
-and computational resource demands. FE codes with unstructured meshes were
-probably the poorest choice of all commonly used methods for this setup in
-terms of computational performance. However, thinking about introducing just
-one slight irregularity such as bathymetry, a thin dipping plate or an
-anticline, the performance behaviour could likely switch. All of these changes
-would barely change the problem size for the FE codes, but significantly
-increase it for the FD codes if the true geometry should be approximated
-sufficiently accurate.
+In the first model, the necessity of discretising regular structures with tetrahedra, especially thin layers, led to comparatively large FE problem sizes and computational resource demands.
+FE codes with unstructured meshes were probably the poorest choice of all commonly used methods for this setup in terms of computational performance.
+However, thinking about introducing just one slight irregularity such as bathymetry, a thin dipping plate or an anticline, the performance behaviour could likely switch.
+All of these changes would barely change the problem size for the FE codes, but significantly increase it for the FD codes if the true geometry should be approximated sufficiently accurate.
 
-The real Marlim R3D model was, ironically, the ideal case for FE codes because
-it's structure was characterized by irregular lithological horizons obtained
-from seismic data. Since the corresponding published resistivity model was
-defined on a regular grid, we were forced to approximate the comparatively fine
-regular discretization by an unstructured one and interpolate the resistivity
-data for being able to apply the FE codes to this problem. We are completely
-aware about the ineptness of this re-approximation procedure, unless it served
-for the cross-validation purposes. Nevertheless, the chosen tetrahedral
-discretization, especially in combination with second order basis functions,
-showed clearly the intrinsic strength of the FE codes, requiring significantly
-less dof for meshing irregular geometries in general. The p2 FE solution
-required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system
-by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+The real Marlim R3D model was, ironically, the ideal case for FE codes because it's structure was characterized by irregular lithological horizons obtained from seismic data.
+Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
+We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
+Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
+The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
 
-The codes under consideration use direct and indirect solvers. In general, the
-biggest advantage of iterative solvers with appropriate preconditioners are the
-comparatively small memory requirements. Direct solvers can be considered as
-most robust to solve any ill-conditioned SLE, which is most important for
-systems of the FE method on unstructured meshes. As the consumed computational
-resources indicate, a more powerful machine than a laptop is required for most
-3D CSEM problems, but no high-performance-computing architecture.
+The codes under consideration use direct and indirect solvers.
+In general, the biggest advantage of iterative solvers with appropriate preconditioners are the comparatively small memory requirements.
+Direct solvers can be considered as most robust to solve any ill-conditioned SLE, which is most important for systems of the FE method on unstructured meshes.
+As the consumed computational resources indicate, a more powerful machine than a laptop is required for most 3D CSEM problems, but no high-performance-computing architecture.
 
-The computation times can differ significantly for specific simulations, but
-there is no clear general advantage for one of the solver types. In our models,
-the runtime comparison favoured the iterative solver and therefore, \emg3d.
-Even though not shown here, direct solvers exhibit their strongest advantage in
-terms of computation times if responses of multiple CSEM transmitters need to
-be calculated in the same computational domain. As the system matrix
-factorisation requires 98-99\,\% of the solution time, computations for
-additional sources come at almost no cost for direct solvers, i.e., MUMPS,
-whereas it would come at the same cost as the first source for \emg3d. For the
-sake of completeness, note that there are also advanced techniques for
-iterative solvers to make use of preconditioners, factorisations, or
-intermediate solutions of the previous SLE to speed up the calculation for
-multiple sources, but this argumentation is beyond the scope of this work.
+The computation times can differ significantly for specific simulations, but there is no clear general advantage for one of the solver types.
+In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d.
+Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be calculated in the same computational domain.
+As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d.
+For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the calculation for multiple sources, but this argumentation is beyond the scope of this work.
 
-We see this work as the start for future elaboration on the validation of
-modelling codes, not necessarily restricted to CSEM problems. Much more
-comparisons and examples are required which not only result in the finding that
-a sufficient accuracy was observed. 3D CSEM modelling is a difficult task,
-which requires many considerations. It starts with the selection of the right
-code for the problem. We found that the meshing task, which is most performance
-determining, is particularly difficult and relevant, choosing cells small
-enough to appropriately represent the model yet to be as coarse as possible
-still achieving the desired precision. The required model extent has to be
-considered as well, thinking also about effects of the so-called airwave in
-marine setups or boundary meshes in general. This is not a new finding but
-rather well known fact. We are surprised that only the minority of publications
-in the field of 3D EM modelling considers a sufficiently detailed elaboration of
-the meshing process.
+We see this work as the start for future elaboration on the validation of modelling codes, not necessarily restricted to CSEM problems.
+Much more comparisons and examples are required which not only result in the finding that a sufficient accuracy was observed.
+3D CSEM modelling is a difficult task, which requires many considerations.
+It starts with the selection of the right code for the problem.
+We found that the meshing task, which is most performance determining, is particularly difficult and relevant, choosing cells small enough to appropriately represent the model yet to be as coarse as possible still achieving the desired precision.
+The required model extent has to be considered as well, thinking also about effects of the so-called airwave in marine setups or boundary meshes in general.
+This is not a new finding but rather well known fact.
+We are surprised that only the minority of publications in the field of 3D EM modelling considers a sufficiently detailed elaboration of the meshing process.
 
-A completely objective evaluation of codes is only possible by
-cross-validation. Nevertheless, we point out that using different
-discretizations or formulations of the numerical approach, e.g. by choosing
-field or potential approaches, second or total field formulations, different
-polynomial order basis functions, and others, is a suitable alternative to the
-cross-comparison of multiple codes for self-validating complex 3D results. This
-is a very powerful method to confirm the general functionality of codes for any
-modelling problem, which might not be covered by existing cross-validation
-benchmark examples. Considering for instance  this study, it would be very
-optimistic to estimate the accuracy of the utilized codes for a land-based
-mineral exploration setup with a highly-conductive, steeply-dipping conductor.
-However, each modeller could run multiple simulations with different
-configurations to increase the reliability of the obtained results.
+A completely objective evaluation of codes is only possible by cross-validation.
+Nevertheless, we point out that using different discretizations or formulations of the numerical approach, e.g.
+by choosing field or potential approaches, second or total field formulations, different polynomial order basis functions, and others, is a suitable alternative to the cross-comparison of multiple codes for self-validating complex 3D results.
+This is a very powerful method to confirm the general functionality of codes for any modelling problem, which might not be covered by existing cross-validation benchmark examples.
+Considering for instance  this study, it would be very optimistic to estimate the accuracy of the utilized codes for a land-based mineral exploration setup with a highly-conductive, steeply-dipping conductor.
+However, each modeller could run multiple simulations with different configurations to increase the reliability of the obtained results.
 
@@
 
-Within SimPEG: This work has motivated feature development including: (a)
-interpolation and averaging strategies from mapping physical properties on a
-fine mesh to a coarser mesh for computation and (b) new examples to include in
-the documentation for designing OcTree meshes. Furthermore, as a part of
-a broader development objective of interoperating with other
-forward-simulation engines, connecting \emg3d and \simpeg provided a
-motivating use-case for the latest refactor and release of \simpeg 0.14.0
-\citep{simpeg0.14.0}. }
+Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing OcTree meshes.
+Furthermore, as a part of a broader development objective of interoperating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0 \citep{simpeg0.14.0}.
+}
 
@@
 
-We compared four different open-source 3D CSEM modellers by computing responses
-for a layered, anisotropic model, including a modification with three resistive
-blocks, and the realistic marine Marlim R3D model. All comparisons exhibited an
-excellent reliability of the solutions. Our data should make it very easy for
-new codes to have a readily available data set to test against and verify. We
-are confident that the discussions about runtimes, memory consumptions, solver
-choices, and, most important, discretisations of the 3D CSEM problems help
-potential users not only to decide which modeller is best suited for specific
-tasks, but also to support their individual projects.
+We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, including a modification with three resistive blocks, and the realistic marine Marlim R3D model.
+All comparisons exhibited an excellent reliability of the solutions.
+Our data should make it very easy for new codes to have a readily available data set to test against and verify.
+We are confident that the discussions about runtimes, memory consumptions, solver choices, and, most important, discretisations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
 
-As none of the considered methods is best suited for all problems, it is
-important to have more test models for various scenarios in future. Our study
-is limited to marine CSEM cases in the frequency-domain. Reasonable extensions
-include providing benchmark models for land, airborne, or mixed CSEM
-environments as well as time-domain data. Another addition to this work would
-be focusing on complex irregular  models, tailored for an FE or FV code based
-on unstructured meshes, and to compare how the FD codes can cope with it.
+As none of the considered methods is best suited for all problems, it is important to have more test models for various scenarios in future.
+Our study is limited to marine CSEM cases in the frequency-domain.
+Reasonable extensions include providing benchmark models for land, airborne, or mixed CSEM environments as well as time-domain data.
+Another addition to this work would be focusing on complex irregular  models, tailored for an FE or FV code based on unstructured meshes, and to compare how the FD codes can cope with it.
 
-We encourage the community to not only work on new open-source code
-developments but also to create a landscape of easily accessible benchmark
-models for increasing the number of reliable and reproducible solutions. Our
-study could provide one of the primary inputs for this task. We are confident
-that the mentioned development will and should be taking place, taking into
-account the current general trend in science to open-source papers, codes or
-data.
+We encourage the community to not only work on new open-source code developments but also to create a landscape of easily accessible benchmark models for increasing the number of reliable and reproducible solutions.
+Our study could provide one of the primary inputs for this task.
+We are confident that the mentioned development will and should be taking place, taking into account the current general trend in science to open-source papers, codes or data.
 

### 2020-07-07 manuscript/Manuscript.tex
Fix all errors reported in Overleaf

@@
 Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing OcTree meshes.
-Furthermore, as a part of a broader development objective of interoperating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0 \citep{simpeg0.14.0}.
+Furthermore, as a part of a broader development objective of interoperating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
+% \citep{simpeg0.14.0}.
 }

### 2020-09-02 manuscript/Manuscript.tex

@@
 \simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}.
-For problems with many sources (and reciprocity is not a natural solution, e.g.
-in 3D airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
+For problems with many sources (e.g.
+airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
 

### 2020-09-04 manuscript/Manuscript.tex
Updates from Overleaf

@@
 \footnotemark[2]%
-Leibniz Institut für Angewandte Geophysik,
+Leibniz Institut for Applied Geophysics,
 Stilleweg 2,
@@
 %
-Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) used to be only possible for large companies or research consortia.
+Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
 However, this changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.

### 2020-09-08 manuscript/Manuscript.tex
Working on manuscript, EOD 08 Sep

@@
 
-%%fakesection ===    ABSTRACT    ===
 \begin{abstract}
@@
 %
-Four different open-source 3D CSEM codes are considered in this work, where in all cases at least the user-facing functionality is written in Python.
-Two codes, \simpeg and \emg3d, use finite volumes, the other two codes, \custem and \petgem, use finite elements.
-Three different mesh-types are used, simple tensor meshes, unstructured tetrahedral meshes, and octree meshes.
+We have a closer look at four different open-source 3D CSEM codes, where in all cases at least the user-facing functionality is written in Python.
+Two of the codes use finite volumes and the other two use finite elements.
+For the modelling we consider three different mesh-types, simple tensor meshes, unstructured tetrahedral meshes, and octree meshes.
 Two models are used to compare the codes, a layered background containing three resistive blocks, and Marlim R3D, a complex, real-world, open-source resistivity data.
 %
-The comparison shows that all four codes are able to compute the model to sufficient precision.
-The biggest difference between the codes are actually the used mesh types.
+The comparison shows that all four codes are able to compute the different models to sufficient precision.
+The biggest difference between the codes are actually the used discretization.
 The required runtime and memory varies greatly between the codes.
@@
 \end{abstract}
+
+\itodo{We probably should be careful to not mention the actual code names too often. I also removed them from the abstract.}
+
+\itodo{Notes on orthography: I settled on discretize with a "z".
+My dictionary says that discretize ("z") is AE and discretise ("s") is BE, but that "z" is also used in BE in mathematical contexts.
+Is that fine or any other opinions?}
 
@@
 In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, which resulted amongst other publications in the book \emph{Three-Dimensional Electromagnetics} by the SEG \citep{B.SEG.99.Oristaglio}.
-Often cited publications from that time are \cite{RSC.94.Mackie}, 3D MT computation; \cite{RS.94.Druskin}, frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman}, low-to-high frequency computation on massively parallel computers.
+Often cited publications from that time are \cite{RSC.94.Mackie} for 3D MT computation; \cite{RS.94.Druskin} for frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman} for low-to-high frequency computation on massively parallel computers.
 
@@
 The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
-There are also many different types of discretisation, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes \citep{ECP.07.Haber}.
+There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes \citep{ECP.07.Haber}.
 Very well written overviews about the different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
@@
 In the last 15 years, the publications with regards to 3D EM modelling grew tremendously, driven by the ever increasing computing power.
-One reason why there are so many reports about this topic results from the variety of solution techniques for the systems of linear equations (SLE).
+One reason why there are so many publications about this topic results from the variety of solution techniques for the systems of linear equations (SLE).
 They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
@@
 
-Many of the advancements made in the EM modelling community over the past decades have required that authors develop new implementation from scratch.
+Many of the advancements made in the EM modelling community over the past decades have required that authors develop new implementations from scratch.
 These codes often provided the research group or company with a competitive advantage for a time, and thus the source codes were often kept internal.
@@
 This is an important step for improving reproducibility of research, «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{GEO.17.Broggini}.
-Going a step beyond releasing open-source software, many groups adopt an open model of development where code is hosted and versioned in an online repository, all changes are public, and users can engage by submitting and track issues.
+Going a step beyond releasing open-source software, many groups adopt an \emph{open model} of development where code is hosted and versioned in an online repository, all changes are public, and users can engage by submitting and track issues.
 Community oriented projects further engage by encouraging pull-requests, which are suggested changes to the code.
@@
 As a result, in many areas of the geosciences, we are seeing a shift away from a one-way distribution of code towards building global communities around open projects.
-Related projects within the realm of geophysical exploration are, e.g., \texttt{pyGIMLi} \citep{CAG.17.Rucker} or \texttt{Fatiando} \citep{JOSS.18.Uieda}
-% Others coming to mind?
-% DW: - https://github.com/fancompute/ceviche
-% RR: - no thoughts about geophysics, but there are many projects for
-%       related topics such as gmt, gis, mesh-gen
-% LH  - https://github.com/softwareunderground/awesome-open-geoscience ?
-%     - Madagascar in seismic?
+Notable other open-source Python projects within the same realm are \texttt{pyGIMLi} \citep{CAG.17.Rucker}, \texttt{Fatiando} \citep{JOSS.18.Uieda}, \texttt{GemPy} \citep{GMD.19.DeLaVarga}, and \texttt{PyVista} \citep{JOSS.19.Sullivan}.
 
@@
 Even though it comprises still the minority of developments, the landscape in this field of research changed in the last five years.
-Previously, there were only closed-source codes owned by companies or consortia and individual projects, often without proper documentation, that could be requested from the authors.
-We introduce and compare four recent open-source projects with focus on 3D CSEM modelling.
+Previously, there were only closed-source codes owned by companies or consortia and individual projects, that were only available directly from the authors upon request.
+These codes often came without proper documentation, and also often without a proper License, which essentially means that they are not open source.
+We introduce and compare four recent open-source projects with a focus on 3D CSEM modelling.
 All presented codes are in the Python ecosystem and use either the FV method on structured grids or the FE method on unstructured tetrahedral meshes.
@@
 Furthermore, we deal with the topic of verification.
+Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
+Beyond these simple models, the only objective possibility to ensure the accuracy of solutions is by comparing results from different modellers.
+If different discretizations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
 \cite{GJI.13.Miensopust} presents a review of two workshops dealing with the verification of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
@@
 We want our efforts to help to ensure the reliability of simulations, not only carried out with the available open-source codes, but also for individual closed-source projects.
-Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
-Beyond these simple models, the only objective possibility to ensure the accuracy of solutions is by comparing results from different modellers.
-If different discretisations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
 
@@
 Afterwards, we present the considered benchmark cases in detail and present the modelling results of our four codes in terms of accuracy and computational performance.
-Beyond that, we extensively discuss important points that control the performance and suitability of our FV and FE codes, including mainly considerations about the mesh design and the choice of solvers.
+Beyond that, we extensively discuss important points that control the performance and suitability of our FV and FE codes, including considerations about the mesh design and the choice of solvers.
 We conclude with a summary of our results and a motivation for the EM community to not only continue to extend the landscape of open-source codes but to also create a landscape of open-source benchmark models.
 
-\itodo{Introduce Maxwell's Equations or not? Miensopust et al., 2013, don't.}
+\itodo{Introduce Maxwell's Equations or not?
+Miensopust et al., 2013, do not touch on any equation.
+We agreed that we wait and see how large the paper becomes, and see at the end if it should be added or not.}
 % Following the conventions of Ward and Hohmann \cite{Ward1988}, the quasi-static Maxwell's equations are
@@
 All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}.
-The four of them are “modern” open-source projects, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+The four of them are \mycom[DW]{change to open dev} “modern” open-source projects, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
 All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
@@
 An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
-All codes have in common that they solve the weak formulation of Maxwell's equation in its differential form (DE) under the quasistatic or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
+All codes have in common that they solve the weak formulation of Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
 The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
@@
 \tabl[btp]{codecomparison}{Comparison of the four codes under consideration.
-  Note that \emg3d is a solver on its own, while the other codes implement
-  third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar},
-  \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO}
-  \citep{FGCS.04.Schenk}.
-}{
+Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}{
   \centering
@@
   %
-  \custem & \textbf{PowerEdge R940 server}; 144 Xeon Gold 6154 CPU @2.666 GHz;
+  \custem & \textbf{PowerEdge R940 (server)}; 144 Xeon Gold 6154 CPU @2.666 GHz;
             ~3 TB DDR4 RAM; Ubuntu 18.04
           & Raphael Rochlitz \\
-  \emg3d  & \textbf{Laptop}; i7-6600U CPU@2.6 GHz x4; 16 GB of memory,
+  \emg3d  & \textbf{Dell Latitude (laptop)}; i7-6600U CPU@2.6 GHz x4; 15.5 GiB of memory,
             Ubuntu 18.04 & Dieter Werthmüller \\
@@
           & Octavio Castillo-Reyes \\
-          \simpeg & \itodo{Todo Lindsey}
+  \simpeg & \textbf{GKE n2-custom (Google cloud)}. Intel Cascade Lake; 8 vCPUs, 355 GB memory; Ubuntu 16.04
           & Lindsey Heagy \\
@@
 %
+\mycom[DW]{Introduce dof, PEC, PMC}
 
@@
 The resulting systems of linear equations are solved with MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming choice.
-Primary field solutions are supplied by the COMET \citep{GEO.20.Skibbe} package.
+Primary field solutions are supplied by the \texttt{COMET} package \citep{GEO.20.Skibbe}.
 
@@
 Even though changes of the conductivity is mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
-Recently, induced polarization parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
-The provided meshing tools based on TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
+Recently, induced polarisation parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
+The provided meshing tools are based on TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
 
@@
 
-The 3D CSEM code \emg3d is a multigrid \citep{CMMP.64.Fedorenko} solver for 3D electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial electrical anisotropy, isotropic electric permittivity, and isotropic magnetic permeability.
-The matrix-free solver can be used as main solver or as preconditioner for one of the Krylov subspace methods implemented in SciPy, and the governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalization of a Yee grid.
+The 3D CSEM code \emg3d is a multigrid solver \citep{CMMP.64.Fedorenko} for electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial electrical anisotropy, isotropic electric permittivity, and isotropic magnetic permeability.
+The matrix-free solver can be used as main solver or as preconditioner for one of the Krylov subspace methods implemented in SciPy, and the governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalisation of a Yee grid.
 The code is written completely in Python using the NumPy and SciPy stacks, where the most time- and memory-consuming parts are sped up through jitted (just-in-time compiled) functions using Numba \citep{LLVM.15.Lam}.
-The multigrid method is characterized by almost linear scaling both in terms of runtime (CPU) and memory (RAM) usage, and it is therefore a comparably low-memory consumption solver.
+The strength of \emg3d is the matrix-free multigrid implementation, which is characterised by almost linear scaling both in terms of runtime (CPU) and memory (RAM) usage, and it is therefore a comparably low-memory consumption solver.
 
@@
 
-Current development is focused on adding basic inversion capabilities, and a further plan is to implement a hook in order to use \emg3d as a frequency-domain CSEM solver within the grander \simpeg framework.
+Current development is focused on adding basic inversion capabilities, and a further plan is to implement a wrapper in order to use \emg3d as a frequency-domain CSEM solver within the grander \simpeg framework.
 
@@
 
-\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyze the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type, among others).
+\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyse the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type, among others).
 Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$ mesh refinement) based on physical parameters and on polynomial order to satisfy quality criteria chosen by the user.
@@
 
-For the parallel forward modelling computations, a highly scalable MPI domain decomposition allows reducing run-times and the solution of large-scale modelling cases.
+For the parallel forward modelling computations, a highly scalable MPI domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
 This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing architectures).
@@
 \simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
-Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarization, electromagnetics (time, frequency, as well as natural sources such as magnetotellurics), and fluid flow (Richards equation).
+Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, electromagnetics (time and frequency, controlled and natural sources such as magnetotellurics), and fluid flow (Richards equation).
 It is a community driven project that aims to support researchers by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.
-\imycom[DW]{Lindsey: «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}
+\mycom[DW]{Lindsey: «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}
 
@@
 
-The electromagnetics implementations use a staggered grid finite volume approach where physical properties are discretized at cell centers, fields on cell edges and fluxes on cell faces \citep{IEEE.66.Yee}.
+The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces \citep{IEEE.66.Yee}.
 %(for an overview of discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}).
-There are two different discretization strategies implemented for Maxwell's equations: (a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (b) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces.
-In both cases the physical properties: electrical conductivity / resistivity and magnetic permeability are discretized at cell centers.
+There are two different discretization strategies implemented for Maxwell's equations: (I) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (II) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces.
+The physical properties electrical conductivity / resistivity and magnetic permeability are discretized in both cases at cell centres.
 Having multiple implementations allows for testing that compares results from each approach, as well as the representation of both electrical and magnetic sources on cylindrically symmetric meshes.
@@
 airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
+\mycom[DW]{only cite ones MUMPS etc, check and adjust}
 
-\section{Numerical Verifications}
+\section{Numerical Verification}
 
@@
 
-The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretisation.
+The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretization.
 Therefore, the FE codes \custem and \petgem used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
 This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
-\imycom[RR]{Add short information about mesh design with SIMPEG and emg3d, including something like "comparatively coarse discretization in center to minimize computation times" }
+\imycom[RR]{Add short information about mesh design with \simpeg and \emg3d, including something like "comparatively coarse discretization in centre to minimise computation times" }
 
+\imycom[DW]{rewrite next paragraph}
 In a first step, we compare the layered background to the semi-analytical solutions of a 1D code, for which we use \empymod\citep{GEO.17.Werthmuller}.
@@
 The results show that all codes are yielding accurate result with errors of around 1\,\% in most parts and overall below a few percent, disregarding locations affected by sign reversals.
-The differences can be mainly attributed to the chosen discretisations.
-The FE codes show the strongest misfits at large offsets, most likely caused by the utilized boundary mesh.
+The differences can be mainly attributed to the chosen discretizations.
+The FE codes show the strongest misfits at large offsets, most likely caused by the utilised boundary mesh.
 Very low errors at large offsets are achieved by \emg3d, whereas it suffers at short offsets from a coarse grid.
@@
 
+\imycom[DW]{\simpeg/\emg3d I put now ncells in ndof, which is wrong. Think about this}
+
+\itodo{EVERYONE: Please check all three tables.
+The numbers should only include time/ram for the actual solving of Maxwell's equations (not mesh generation or similar things); they should be the total (CPU) and the max (RAM), respectively, for/of all frequencies (if applicable).: (1) Is the CPU correct, and does it include the total runtime for all frequencies?
+(2) Is the number of processors correct?
+(3) Is RAM correct, and corresponds to maximum used RAM?
+(4) dof correct?}
+
 %
@@
   \centering
-\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{lS[table-format=6.0]rS[table-format=4.1]S[table-format=8.0]}
   \toprule
   %
-  Code & {CPU} & \#Procs & RAM     & \#dof \\
+  Code & {CPU} & \#Procs & {RAM}   & {\#dof} \\
        & {(s)} &         & {(GiB)} &         \\
@@
   %
-  \custem & 0.0 &  0 & 0.0 & 0 \\
-  \emg3d  & 0.0 &  0 & 0.0 & 0 \\
-  \petgem & 0.0 &  0 & 0.0 & 0 \\
-  \simpeg & 0.0 &  0 & 0.0 & 0 \\
+  \custem &   118 & 24 &  97.8 & 3061616 \\
+  \emg3d  &   116 &  1 &   0.4 & 4813216 \\
+  \petgem &    90 & 24 &  34.2 & 2455868 \\
+  \simpeg & 10089 &  1 & 280.3 & 4813216 \\
   %
@@
 They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
-As there are no analytical solutions for this model we show the normalized difference between different codes, instead of the relative error, where the normalized difference of two responses $p$ and $q$ is given by
+As there are no (semi-)analytical solutions for this model we use the normalised root-mean square difference (NRMSD) between different codes, where the NRMSD of two responses $p$ and $q$ is given by
 %
@@
 
-\imycom[RR]{Agreed. Another suggestion, I solved this visualization problem
+\imycom[RR]{Agreed. Another suggestion, I solved this visualisation problem
   with a color coded matrix plot, showing 90th percentiles or median values of
@@
 
-The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding CPU and RAM in Table~\ref{tbl:comp-block}.
+The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding required CPU and RAM are listed in Table~\ref{tbl:comp-block}.
 We can conclude from the NRMSD that similar codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very similar, as well as are \custem and \petgem.
@@
   \centering
-\begin{tabular}{lS[table-format=4.2]rS[table-format=4.2]rl}
+\begin{tabular}{lS[table-format=6.0]rS[table-format=4.1]S[table-format=8.0]}
 \toprule
   %
-  Code & {CPU} & \#Procs & RAM     & \#dof \\
+  Code & {CPU} & \#Procs & {RAM}   & {\#dof} \\
        & {(s)} &         & {(GiB)} &         \\
@@
   %
-  \custem & 0.0 & 24 & 0.0 & 0 \\
-  \emg3d  & 0.0 &  1 & 0.0 & 0 \\
-  \petgem & 0.0 & 48 & 0.0 & 0 \\
-  \simpeg & 0.0 &    & 0.0 & 0 \\
+  \custem &   158 & 24 & 115.9 & 3308484 \\
+  \emg3d  &   115 &  1 &   0.4 & 4813216 \\
+  \petgem &    72 & 24 &  35.8 & 2455868 \\
+  \simpeg &  9993 &  1 & 280.6 & 4813216 \\
   %
@@
 
+\itodo{ADD cross section plots!}
+
 \section{Discussion}
@@
 The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
-Aside from the idea of analyzing an industrially relevant benchmark example, the Marlim R3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretisation.
+Aside from the idea of analysing an industrially relevant benchmark example, the Marlim R3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretization.
 At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
@@
 
-In the first model, the necessity of discretising regular structures with tetrahedra, especially thin layers, led to comparatively large FE problem sizes and computational resource demands.
+In the first model, the necessity of discretizing regular structures with tetrahedra, especially thin layers, led to comparatively large FE problem sizes and computational resource demands.
 FE codes with unstructured meshes were probably the poorest choice of all commonly used methods for this setup in terms of computational performance.
@@
 
-The real Marlim R3D model was, ironically, the ideal case for FE codes because it's structure was characterized by irregular lithological horizons obtained from seismic data.
+The real Marlim R3D model was, ironically, the ideal case for FE codes because it's structure was characterised by irregular lithological horizons obtained from seismic data.
 Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
@@
 This is a very powerful method to confirm the general functionality of codes for any modelling problem, which might not be covered by existing cross-validation benchmark examples.
-Considering for instance  this study, it would be very optimistic to estimate the accuracy of the utilized codes for a land-based mineral exploration setup with a highly-conductive, steeply-dipping conductor.
+Considering for instance  this study, it would be very optimistic to estimate the accuracy of the utilised codes for a land-based mineral exploration setup with a highly-conductive, steeply-dipping conductor.
 However, each modeller could run multiple simulations with different configurations to increase the reliability of the obtained results.
@@
   down things that come to your mind.
-\imycom[OCR]{I think an important point is the user experience (modeler). I
+\imycom[OCR]{I think an important point is the user experience (modeller). I
   know this is an intangible element but perhaps we could add a line about it.
@@
 Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing OcTree meshes.
-Furthermore, as a part of a broader development objective of interoperating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
+Furthermore, as a part of a broader development objective of inter-operating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
 % \citep{simpeg0.14.0}.
 }
+
+\section{TODOs}
+
+\begin{itemize}
+    \item Add cross-section
+    \item Cite 3D EM Schlumberger-Doll book Ward \& Hohmann; probably also Zhdanov
+    \item Focus on the different open source tools that can deliver industry-standard results.
+That there is choice.
+That these people work together (!).
+That the collaboration improved all codes.
+That you can do things with tetrahedrals or tensor meshes or octree meshes, some are better for one task, the other is better for another task.
+Because, as you mentioned Lindsey, in the end for SimPEG, custEM, and PETGEM speed and memory in the end falls a lot on the solver used (Fenics, petsc, pardiso), and not actually on the code.
+Swapping the solver might yield very different metrics.
+    \item Focus on Result Comparison, as this is the only way to verify 3D modellers.
+\end{itemize}
+
+Add what improvements were initiated by article (“But also, a plus-point of such collaboration is if it brings the realm as such further.
+So we should note down if this collaboration resulted in new features implemented in some codes, new releases etc.
+What did it push forward?
+It would be a motivation for further cross-project/community collaborations.
+Something for the discussion or conclusion part.”):
+
+\begin{itemize}
+    \item Lindsey: For SimPEG - this will result in new utilities for volume averaging, and likely more documentation on tips for designing tree meshes.
+This could be a pretty compelling piece to bring in to the discussion
+    \item Raphael:
+    \begin{itemize}
+        \item cell-wise resistivity interpolation added
+        \item multi-layer subsurface topography first time applied
+        \item reciprocity modeling (even though that has not too much to do with implementation)
+        \item mesh design (resolution, refinement, etc.)
+    \end{itemize}
+\end{itemize}
+
+Add somewhere Trivia: All codes could be used for a multitude of applications (oil, mining, geothermal, groundwater, environmental, even non-geophysical). The main work, however:
+\begin{itemize}
+    \item custEM: mining;
+    \item SimPEG: mining, environmental;
+    \item PETGEM: used to be oil, now medical and geothermal;
+    \item emg3d: developed for project dealing with oil, methane, and deep sea mining.
+\end{itemize}
+
+Many things to discuss and take into account
+\begin{itemize}
+    \item Examples are in favour of FD codes, (rectangle blocks, complex model provided as FD model)
+    \item Examples are in favour of iterative solver, as only one source was computed.
+Iterative solvers (\emg3d) will require the same amount of time for each new source, whereas direct solvers have additional source locations almost for free
+    \item Not possible to exactly reproduce published results unless the codes is also open-source, as one cannot know what internally is actually done (show example!)
+    \item In the end the codes (\custem, \emg3d, \petgem, \simpeg) define mainly, how easy the interaction is.
+How easy is it to set-up the mesh, to create sources and receivers, etc etc.
+The \emph{actual} computation time, however,
+    is mostly NOT defined by these codes, but by the underlying solver. (The exception to that is \emg3d, which is its own solver.)
+    \item In the end it comes down to the most important, crucial, difficult, AND TIME CONSUMING point: mesh generation.
+It took all of us MUCH more time to generate appropriate meshes, then to actually compute the responses.
+\end{itemize}
 
@@
 Our data should make it very easy for new codes to have a readily available data set to test against and verify.
-We are confident that the discussions about runtimes, memory consumptions, solver choices, and, most important, discretisations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
+We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
 
@@
 
-\section{Acknowledgment}
+\section{Acknowledgement}
 

### 2020-09-09 manuscript/Manuscript.tex
Updates from Overleaf

@@
 
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+
 \begin{document}
 
+% META INFO
 \title{Open-source landscape for 3D CSEM modelling}
 
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+% ARTICLE-ID
+\ms{}
 
-\ms{}  % ARTICLE-ID
-
+% ADDRESSES
 \address{
-\footnotemark[1]%
-TU Delft,
-Building 23,
-Stevinweg 1 / PO-box 5048,
-2628 CN Delft (NL);\\
-\footnotemark[2]%
-Leibniz Institut for Applied Geophysics,
-Stilleweg 2,
-30655 Hannover (DE);\\
-\footnotemark[3]%
-Barcelona Supercomputing Center (BSC),
-Nexus II Building c/Jordi Girona, 29,
-08034 Barcelona (ES);\\
-\footnotemark[4]%
-University of California Berkeley,
-Department of Statistics (USA).\\
+  \footnotemark[1]TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL);\\
+  \footnotemark[2]Leibniz Institut for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE);\\
+  \footnotemark[3]Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES);\\
+  \footnotemark[4]University of California Berkeley, Department of Statistics (USA).\\
   E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
@@
 }
-
+% AUTHORS
 \author{%
@@
 
+% HEADER / FOOTER
 \footer{}
@@
 \begin{abstract}
-%
+% The (points) are from Mahrer (1993), Geophysics, Some Considerations When Abstracting; DOI: 10.1190/1.58010001.1
+% (1) principal objectives and scope of the work
 Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
-However, this changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
-%
-We have a closer look at four different open-source 3D CSEM codes, where in all cases at least the user-facing functionality is written in Python.
+However, this has changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
+We have a closer look at four different ones, where in all cases at least the user-facing functionality is written in Python.
+% (2) methodology
+For the numerical comparison we choose three models, a layered background, ones on its own and ones containing three resistive blocks, and Marlim R3D, a complex, anisotropic, real-world and open-source resistivity model.
+The analysis includes three different mesh-types, simple tensor meshes, octree meshes, and unstructured tetrahedral meshes.
 Two of the codes use finite volumes and the other two use finite elements.
-For the modelling we consider three different mesh-types, simple tensor meshes, unstructured tetrahedral meshes, and octree meshes.
-Two models are used to compare the codes, a layered background containing three resistive blocks, and Marlim R3D, a complex, real-world, open-source resistivity data.
-%
+% (3) results
 The comparison shows that all four codes are able to compute the different models to sufficient precision.
-The biggest difference between the codes are actually the used discretization.
+The biggest difference between codes is actually the discretization and the ease of creating a suitable mesh, particularly as that part often takes much more time than the actual computation.
 The required runtime and memory varies greatly between the codes.
-However, these requirements depend mainly on the underlying solver, and not on the actual CSEM codes.
-%
+However, these depend mainly on the underlying solver, and not on the actual CSEM codes.
+% (4) conclusions
 The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further.
-We hope that these results may be useful for the entire CSEM community, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
-For a start, all the scripts to reproduce our shown results are available.
-%
+We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
+All our scripts to reproduce the shown results are open-source.
 \end{abstract}
 
-\itodo{We probably should be careful to not mention the actual code names too often. I also removed them from the abstract.}
-
-\itodo{Notes on orthography: I settled on discretize with a "z".
-My dictionary says that discretize ("z") is AE and discretise ("s") is BE, but that "z" is also used in BE in mathematical contexts.
-Is that fine or any other opinions?}
+\newpage
+\itodo{\hfill$\Downarrow$\hfill$\Downarrow$\hfill List of things ToDo, Notes, etc\hfill$\Downarrow$\hfill$\Downarrow$\hfill~}
+\begin{itemize}
+    \item Notes on orthography: I settled on discretize with a «z».
+My dictionary says that discreti{\color{red}\bfseries z}e is AE and discreti{\color{red}\bfseries s}e is BE, but that «z» is also used in BE in mathematical contexts.
+Is that fine or any other opinions?
+    \item We probably should be careful to not mention the actual code names too often. E.g., I removed them from the abstract.
+    \item I tried to avoid double reference.
+E.g., SciPy, MUMPS, pyGIMLi: I referenced them the first time they are mentioned, and not afterwards.
+Current exceptions: Miensopust et al., 2013, is cited twice.
+\end{itemize}
+\itodo{\hfill$\Uparrow$\hfill$\Uparrow$\hfill List of things ToDo, Notes, etc\hfill$\Uparrow$\hfill$\Uparrow$\hfill~}
+\newpage
 
@@
 Modelling these electromagnetic fields is therefore of great interest to design survey layouts, to understand the measured data, and for inversion purposes.
-Publications regarding 3D modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
+Publications regarding three-dimensional (3D) modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
 These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
@@
 
-In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, which resulted amongst other publications in the book \emph{Three-Dimensional Electromagnetics} by the SEG \citep{B.SEG.99.Oristaglio}.
+In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
+This symposium resulted eventually in the book \emph{Three-Dimensional Electromagnetics} by the SEG \citep{B.SEG.99.Oristaglio}, and another book by \cite{B.02.Wannamaker} with the exactly same title came out only three years later.
 Often cited publications from that time are \cite{RSC.94.Mackie} for 3D MT computation; \cite{RS.94.Druskin} for frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman} for low-to-high frequency computation on massively parallel computers.
@@
 The continuous improvement of computing power and the CSEM boom in the early 2000's in the hydrocarbon industry led to a wealth of developed numerical solutions and according publications.
-The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{IEEE.66.Yee, GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
+The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
 There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes \citep{ECP.07.Haber}.
+
 Very well written overviews about the different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
-
-In the last 15 years, the publications with regards to 3D EM modelling grew tremendously, driven by the ever increasing computing power.
-One reason why there are so many publications about this topic results from the variety of solution techniques for the systems of linear equations (SLE).
-They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
-The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GP.06.Mulder, GJI.16.Jaysaval}.
+But there was also a tremendous publications output with regards to 3D EM modelling in the last 10-15 years, at least partly driven by the ever increasing computing power.
+One reason why there are so many publications about this topic results from the variety of techniques to solve the systems of linear equations (SLE).
+They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
+The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GJI.16.Jaysaval}.
 
@@
 As the field continues to mature, advancements become more incremental, and particularly in an applied field, many advancements are driven by new use-cases and applications that were not considered by the original authors.
-In his review on EM modelling and inversion \cite{SG.05.Avdeev} concludes with the following statement: «\emph{The most important challenge that faces the EM community today is to convince software developers to put their 3-D EM forward and inverse solutions into the public domain, at least after some time.
+In the aforementioned review on EM modelling and inversion Dmitry Avdeev concludes with the following statement: «\emph{The most important challenge that faces the EM community today is to convince software developers to put their 3-D EM forward and inverse solutions into the public domain, at least after some time.
 This would have a strong impact on the whole subject and the developers would benefit from feedback regarding the real needs of the end-users.}» Further, \cite{EXG.19.Oldenburg} argue that an open-source paradigm has the potential to accelerate multidisciplinary research by encouraging the development of modular, interoperable tools that are supported by a community of researchers.
 
-In many domains of science, it is becoming more common for researchers to release source-code with an open license that allows use and modification (e.g., see the Open Source Initiative approved licenses: \href{https://opensource.org/licenses}{opensource.org/licenses}).
+It is becoming more common for researchers in many domains of science to release source-code with an open license that allows use and modification (e.g., see the Open Source Initiative approved licenses: \href{https://opensource.org/licenses}{opensource.org/licenses}).
 This is an important step for improving reproducibility of research, «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{GEO.17.Broggini}.
-Going a step beyond releasing open-source software, many groups adopt an \emph{open model} of development where code is hosted and versioned in an online repository, all changes are public, and users can engage by submitting and track issues.
+Going a step beyond releasing open-source software, many groups adopt an \emph{open model of development} where code is hosted and versioned in an online repository, all changes are public, and users can engage by submitting and track issues.
 Community oriented projects further engage by encouraging pull-requests, which are suggested changes to the code.
@@
 Additionally, documentation that includes examples and tutorials is an important component for on-boarding new users and contributors.
-As a result, in many areas of the geosciences, we are seeing a shift away from a one-way distribution of code towards building global communities around open projects.
-Notable other open-source Python projects within the same realm are \texttt{pyGIMLi} \citep{CAG.17.Rucker}, \texttt{Fatiando} \citep{JOSS.18.Uieda}, \texttt{GemPy} \citep{GMD.19.DeLaVarga}, and \texttt{PyVista} \citep{JOSS.19.Sullivan}.
+As a result, in many areas of the geosciences, we are seeing a shift away from a one-way distribution of (open-source) code towards building global communities around open projects.
+Other notable Python projects with an open model of development within the same realm as the codes under considerations are \texttt{pyGIMLi} \citep{CAG.17.Rucker}, \texttt{Fatiando} \citep{JOSS.18.Uieda}, \texttt{GemPy} \citep{GMD.19.DeLaVarga}, and \texttt{PyVista} \citep{JOSS.19.Sullivan}.
 
-In this paper, we discuss the topic of open-source developments with respect to 3D CSEM modelling.
-Even though it comprises still the minority of developments, the landscape in this field of research changed in the last five years.
-Previously, there were only closed-source codes owned by companies or consortia and individual projects, that were only available directly from the authors upon request.
-These codes often came without proper documentation, and also often without a proper License, which essentially means that they are not open source.
+We discuss the topic of open-source developments with respect to 3D CSEM modelling.
+Even though it comprises still the minority of developments, the open-source landscape in this field of research changed in the last five years quite dramatically.
+Previously, there existed only closed-source codes owned by companies and consortia, or individual projects that were only available directly from the authors upon request.
+These codes often came without proper documentation.
+But more importantly, they also often came without a proper license, which essentially means that they are not open source (no license means legally speaking that, in most countries of the world, all rights are reserved by the author; see, for instance, the \emph{Berne Convention}).
 We introduce and compare four recent open-source projects with a focus on 3D CSEM modelling.
@@
 \cite{GJI.13.Miensopust} presents a review of two workshops dealing with the verification of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
-Hence, we first conduct a similar exercise for CSEM codes.
-We want our efforts to help to ensure the reliability of simulations, not only carried out with the available open-source codes, but also for individual closed-source projects.
+This is, to the best of our knowledge, the first comparison exercise for CSEM codes.
+We hope our efforts help to ensure the reliability of simulations for any new or existing, open-source or closed-source 3D CSEM project.
 
-We simulate EM fields for a layered background model with vertical transverse isotropy, containing three blocks, as well as for the complex marine Marlim R3D model.
-These two model designs as well as the corresponding results from four different codes provide a benchmark for new codes to be compared to and validated with.
-In the following section, we introduce the codes under consideration.
-Afterwards, we present the considered benchmark cases in detail and present the modelling results of our four codes in terms of accuracy and computational performance.
+We simulate EM fields for a layered background model with vertical transverse isotropy, with and without three resistive blocks, as well as for the complex marine Marlim R3D model.
+These three models as well as the corresponding results from four different codes provide a benchmark for new (and existing) codes to be compared to and validated with.
+First we introduce the codes under consideration, and present afterwards the considered benchmark cases in detail together with the modelling results of our four codes in terms of accuracy and computational performance.
 Beyond that, we extensively discuss important points that control the performance and suitability of our FV and FE codes, including considerations about the mesh design and the choice of solvers.
-We conclude with a summary of our results and a motivation for the EM community to not only continue to extend the landscape of open-source codes but to also create a landscape of open-source benchmark models.
+We conclude with a discussion and conclusions, and a motivation for the EM community at large to not only continue to extend the landscape of open-source codes but to also create a landscape of open-source benchmark models.
 
-\itodo{Introduce Maxwell's Equations or not?
-Miensopust et al., 2013, do not touch on any equation.
-We agreed that we wait and see how large the paper becomes, and see at the end if it should be added or not.}
-% Following the conventions of Ward and Hohmann \cite{Ward1988}, the quasi-static Maxwell's equations are
-
-% \begin{equation}
-% \begin{split}
-%     \nabla \times \vec{E} &= -i \omega\vec{B}  \\
-%     \nabla \times \vec{H} &= \vec{J}
-% \end{split}
-% \label{eq:maxwell_freq_quasi}
-% \end{equation}
-%
-% If we include Maxwell's equations, we might cite here Haber, 2014, for its
-% discretization.
+\itodo{Ones were ready check if we should introduce Maxwell's equations or not. Miensopust et al., 2013, for instance, do not touch on any equation.}
 
@@
 All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}.
-The four of them are \mycom[DW]{change to open dev} “modern” open-source projects, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+The four of them are not just open-source but follow the open model of development, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
 All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
-Newer package-management systems such as Conda, Docker, or pip significantly supported us to make our codes easily available and installable on any of the major operating system without any user-side compilations.
-Each one can be downloaded and installed with a single command.
+Newer package-management systems such as \texttt{conda}, \texttt{docker}, or \texttt{pip} significantly supported us to make our codes easily available and installable on any of the major operating system without any user-side compilations.
+Each one can be downloaded and installed with a \mycom[DW]{I guess this statement is currently a bit of a stretch for \petgem, correct Octavio?}single command.
 
@@
 An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
-All codes have in common that they solve the weak formulation of Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
+All codes have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
 The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
-% LH: SimPEG also interfaces to the scipy solvers; but in practice those are
-%     use much less than Pardiso / mumps
-% => I leave them out for now, as you did not use them for this paper either,
-%    right? Maybe to mention in the SimPEG-section.
+\imycom[DW]{I took out «the weak formulation of», as it actually doesn't apply to \emg3d. Please make sure that everything stated above («have in common that...») actually applies to your code.}
 
+A few clarifying words on abbreviations: For the boundary conditions (BC) in the comparison table we use the abbreviations PEC and PMC, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
+Another abbreviation used in the tables is dof for degree of freedom, which is equivalent to the size of the SLE we are solving.
+Finally, we abbreviate runtime with CPU and memory with RAM.
+CPU refers throughout to the wall- or real-world time used from start to end of a computation, whether or not there are several processes running in parallel or not (hence it is not actual computation time, which would be significantly higher for parallel computations).
+RAM, on the other hand, refers to the maximum used memory at any point of the computation.
+
+% Lindsey, I leave the SciPy solvers out.
+You mention that in practice they are not often used.
+emg3d can also use those solvers, and then multigrid is used as preconditioner.
+However, we cite SciPy, and as you say, SimPEG mostly uses PARDISO or MUMPS.
+To keep it simply I think we can leave SciPy out on the solver side.
+I mention it in the emg3d-section, if you want you can mention it in the SimPEG section too.
 \tabl[btp]{codecomparison}{Comparison of the four codes under consideration.
@@
 %
-\tabl[btp]{machines}{List of computer and operating system (hardware and
-software) on which the different codes were run, together with the operator.}{
+\tabl[btp]{machines}{List of hardware, software, and operator with which the different codes were run.\itodo{Could everyone check if their RAM is GB or GiB?}}{
   \centering
@@
   %
-  \custem & \textbf{PowerEdge R940 (server)}; 144 Xeon Gold 6154 CPU @2.666 GHz;
-            ~3 TB DDR4 RAM; Ubuntu 18.04
-          & Raphael Rochlitz \\
-  \emg3d  & \textbf{Dell Latitude (laptop)}; i7-6600U CPU@2.6 GHz x4; 15.5 GiB of memory,
-            Ubuntu 18.04 & Dieter Werthmüller \\
-  \petgem & \textbf{Marenostrum4 (supercomputer)}. Intel Xeon Platinum from
-            Skylake generation; 2 sockets Intel Xeon Platinum 8160 CPU with 24
-            cores each @2.10GHz for a total of 48 cores per node; 386 GB DDR4
-            RAM per node; SuSE Linux Enterprise
-          & Octavio Castillo-Reyes \\
-  \simpeg & \textbf{GKE n2-custom (Google cloud)}. Intel Cascade Lake; 8 vCPUs, 355 GB memory; Ubuntu 16.04
-          & Lindsey Heagy \\
+  \custem & \textbf{PowerEdge R940 (server)}                  & Raphael Rochlitz \\
+          & - 144 Xeon Gold 6154 CPU @2.666 GHz               & \\
+          & - $\approx3$ TB DDR4 RAM                          & \\
+          & - Ubuntu 18.04                                    & \\[.5em]
+  \emg3d  & \textbf{Dell Latitude (laptop)}                   & Dieter Werthmüller \\
+          & - i7-6600U CPU@2.6 GHz x4                         & \\
+          & - 15.5 GiB RAM                                    & \\
+          & - Ubuntu 18.04                                    & \\[.5em]
+  \petgem & \textbf{Marenostrum4 (supercomputer)}             & Octavio Castillo-Reyes \\
+          & - Intel Xeon Platinum from Skylake generation; 2 sockets Intel Xeon Platinum 8160 CPU with 24 cores each @2.10GHz for a total of 48 cores per node & \\
+          & - 386 GB DDR4 RAM per node                        & \\
+          & - SuSE Linux Enterprise                           & \\[.5em]
+  \simpeg & \textbf{GKE n2-custom (Google cloud)}             & Lindsey Heagy \\
+          & - Intel Cascade Lake, 8 vCPUs                     & \\
+          & - 355 GB RAM                                      & \\
+          & - Ubuntu 16.04                                    & \\
   %
@@
 %
-\mycom[DW]{Introduce dof, PEC, PMC}
-
-\imycom[DW]{Raphael: I think here would be the right place? I guess for
-  tensor meshes as mine it is simply number of cells (times the anisotropy
-  type; for VTI x2). But you know better what it means for \custem/\petgem.
-  \imycom[RR]{I think we should introduce the term degrees of freedom (dof),
-    equivalent to the size of the SLE, as general measure of our problem sizes.
-    If it is somewhat x*Nedges, or related to Ncells or Nnodes, who cares? We
-    just need this one number for this paper in my opinion, more details in the
-    jupyter notebooks - fine.
-  }
-}
 
@@
 
-The customisable electromagnetic modelling Python toolbox custEM was developed for simulating arbitrary complex 3D CSEM geometries with a focus on semi-airborne setups, but it supports also land-based, airborne, coastal, or marine environments.
+The customisable electromagnetic modelling Python toolbox \custem was developed for simulating arbitrary complex 3D CSEM geometries with a focus on semi-airborne setups, but it supports also land-based, airborne, coastal, and marine environments.
 Multiple electric or magnetic field or potential finite-element approaches were implemented as total or secondary field formulations.
-The finite-element kernel, including higher order basis functions and parallelisation, relies on the FEniCS project \citep{B.SPR.12.Logg, B.SPR.16.Langtangen}.
-The resulting systems of linear equations are solved with MUMPS \citep{SIAM.01.Amestoy}, which is a very robust but memory consuming choice.
+The finite-element kernel, including higher order basis functions and parallelisation, relies on the \texttt{FEniCS} project \citep{B.SPR.12.Logg, B.SPR.16.Langtangen}.
+The resulting SLEs are solved with \texttt{MUMPS}, which is a very robust but memory consuming choice.
 Primary field solutions are supplied by the \texttt{COMET} package \citep{GEO.20.Skibbe}.
@@
 Even though changes of the conductivity is mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
-Recently, induced polarisation parameters in frequency-domain and three methods for simulating time-domain responses were added to custEM.
-The provided meshing tools are based on TetGen \citep{TOM.15.Si} and functionalities of pyGIMLi \citep{CAG.17.Rucker} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
+Recently, induced polarisation parameters in frequency-domain and three methods for simulating time-domain responses were added to \custem.
+The provided meshing tools are based on \texttt{TetGen} \citep{TOM.15.Si} and functionalities of \texttt{pyGIMLi} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
 
-The custEM toolbox is under steady development and maintenance.
-Future enhancements comprise adding iterative solution techniques, provided by FEniCS, as well as further functionalities for automatically incorporating intersecting bodies such as folds or faults in meshes.
-Furthermore, current work is on using custEM for inverse modelling applications.
+The \custem toolbox is under steady development and maintenance.
+Future enhancements comprise adding iterative solution techniques, provided by \texttt{FEniCS}, as well as further functionalities for automatically incorporating intersecting bodies such as folds or faults in meshes.
+Furthermore, current work is on using \custem for inverse modelling applications.
 
@@
 The 3D CSEM code \emg3d is a multigrid solver \citep{CMMP.64.Fedorenko} for electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial electrical anisotropy, isotropic electric permittivity, and isotropic magnetic permeability.
-The matrix-free solver can be used as main solver or as preconditioner for one of the Krylov subspace methods implemented in SciPy, and the governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalisation of a Yee grid.
+The matrix-free solver can be used as main solver, or alternatively as preconditioner for one of the Krylov subspace methods implemented in SciPy.
+The governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalisation of a Yee grid.
 The code is written completely in Python using the NumPy and SciPy stacks, where the most time- and memory-consuming parts are sped up through jitted (just-in-time compiled) functions using Numba \citep{LLVM.15.Lam}.
-The strength of \emg3d is the matrix-free multigrid implementation, which is characterised by almost linear scaling both in terms of runtime (CPU) and memory (RAM) usage, and it is therefore a comparably low-memory consumption solver.
+The strength of \emg3d is the matrix-free multigrid implementation, which is characterised by almost linear scaling both in terms of runtime and memory usage, and it is therefore a solver that uses comparably very little memory.
 
-The code comes with functionalities to be used directly as a CSEM modeller too, in addition to serve as a solver.
-As such, it computes the electric field due to an electric source in the frequency-domain, which is its main application (frequency-domain CSEM).
-However, there are also routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses.
+As such the code is, contrary to the other three, primarily a solver, which solves the Maxwell's equation for a single frequency and a single, electric source.
+However, recent developments added functionalities such that \emg3d can be used directly as a more general EM modeller too.
+It features now routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and also to obtain time-domain responses.
+The most recent development added the possibility to compute the responses for entire surveys, and also to compute the misfit and the gradient of the misfit function, and \emg3d is as such ready to be used in inversion schemes.
 
-Current development is focused on adding basic inversion capabilities, and a further plan is to implement a wrapper in order to use \emg3d as a frequency-domain CSEM solver within the grander \simpeg framework.
+For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem. Interoperability between \simpeg and \emg3d is therefore straightforward.
 
@@
 
-For the parallel forward modelling computations, a highly scalable MPI domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
+For the parallel forward modelling computations, a highly scalable MPI (message passing interface) domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
 This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing architectures).
@@
 Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, electromagnetics (time and frequency, controlled and natural sources such as magnetotellurics), and fluid flow (Richards equation).
-It is a community driven project that aims to support researchers by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.
-\mycom[DW]{Lindsey: «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}
+It is a community driven project that aims to support researchers and \mycom[DW]{I added «and practitioners», as I think «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}practitioners by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.
 
@@
 
-The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces \citep{IEEE.66.Yee}.
+The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces.
 %(for an overview of discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}).
@@
 
-\simpeg interfaces to various solvers including \texttt{PARDISO} \citep{FGCS.04.Schenk}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, as well as those implemented in the \texttt{scipy.sparse.linalg} module \citep{NM.20.Virtanen}.
+\simpeg interfaces to various solvers including \texttt{PARDISO} and \texttt{MUMPS}, and also to some implemented in SciPy.
 For problems with many sources (e.g.
 airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
-\mycom[DW]{only cite ones MUMPS etc, check and adjust}
 
@@
 45 source-towlines were located on the same grid, 50\,m above the seafloor, with shots every 100\,m.
-In \cite{GEO.19.Correa} the actual responses for one receiver with the corresponding East-West inline and one East-West broadside acquisition line are shown, which is the data we chose for our comparison.
+In the original paper the actual responses for one receiver with the corresponding East-West inline and one East-West broadside acquisition line are shown, which is the data we chose for our comparison.
 The cross-section of the resistivity model along the chosen inline acquisition line is shown in Figure~\ref{fig:model-marlim}, together with the acquisition information.
@@
   What would you like to show from the actual data here?
-  A nice figure would  be Figure 2 in \cite{GEO.19.Correa}; however, note that
+  A nice figure would  be Figure 2 in the original paper; however, note that
   the drawn survey line in that figure are plainly wrong.
@@
     \item Add cross-section
-    \item Cite 3D EM Schlumberger-Doll book Ward \& Hohmann; probably also Zhdanov
     \item Focus on the different open source tools that can deliver industry-standard results.

### 2020-09-10 manuscript/Manuscript.tex

@@
 \begin{itemize}
+    \item {\color{red}\bfseries This version is quite different from the previous you revised.
+However, from now on we do not expect too many changes.
+To make it easier for everyone to see the new changes please make sure that from now on "Track Changes" is always in Overleaf.}
     \item Notes on orthography: I settled on discretize with a «z».
@@
 Current exceptions: Miensopust et al., 2013, is cited twice.
+    \item  {\color{red}\bfseries Everyone: Please ensure the info in the tables is correct:}
+      \begin{enumerate}
+          \item machine info;
+          \item runtime;
+          \item memory;
+          \item nproc;
+          \item dof.
+      \end{enumerate}
+    I got all the info out of the ".nc" files, so make sure you wrote the correct info into the nc-files. Further notes:
+      \begin{description}
+        \item[runtime] Should only include the wall time (or elapsed real time, \url{https://en.wikipedia.org/wiki/Elapsed_real_time}) of solving the SLE, for ALL frequencies (in \emg3d some frequencies are slower than others, but in any case, we report the sum of all of them); any pre-/postprocessing such as mesh generation or model interpolation can be ignored.
+        \item[memory] It should be the maximum memory increase when solving the SLE (again, ignoring any pre-/postprocessing).
+Again, of all frequencies.
+In \emg3d some frequencies require more RAM than others (more iterations), but we only report the "worst", the heaviest consumer.
+        \item[nproc] Not sure we reached agreement on Slack, but I took no everything in here (threads and (virtual) processes); please note here if you think it should be different.
+        \item[dof] Similarly, not sure we reached agreement on Slack. I put it here now for complex value, hence halving the dof of custEM. Again, please write here if we should change it.
+    \end{description}
+    We could discuss if we should report CPU time instead (hence summing all parallel processes); but I think for the user of interest is the real-world time, how long do I have to wait.
+(Either way, the reader can make a quick estimation in one or the other direction; important is that we are consistent throughout the paper.)
 \end{itemize}
@@
 
-A few clarifying words on abbreviations: For the boundary conditions (BC) in the comparison table we use the abbreviations PEC and PMC, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
+A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations PEC and PMC, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
 Another abbreviation used in the tables is dof for degree of freedom, which is equivalent to the size of the SLE we are solving.
-Finally, we abbreviate runtime with CPU and memory with RAM.
-CPU refers throughout to the wall- or real-world time used from start to end of a computation, whether or not there are several processes running in parallel or not (hence it is not actual computation time, which would be significantly higher for parallel computations).
-RAM, on the other hand, refers to the maximum used memory at any point of the computation.
+Finally, we use \emph{runtime} as the wall time or elapsed real time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
+Note that the actual computation or CPU time is therefore much higher than the reported runtime for the codes that run in parallel.
+Memory refers to the maximum memory increase at any point of solving the SLE.
 
@@
   Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
-  BC & PMC; PEC & PEC & PEC & PEC; PMC \\
+  BC & PEC; PMC & PEC & PEC & PEC; PMC \\
   Solver & \texttt{MUMPS} & \emg3d & \texttt{PETSc}; \texttt{MUMPS} &
@@
 
+\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
 We computed the responses for two different models to verify that all different 3D codes yield the same electromagnetic responses.
@@
   broadside responses for $y=\pm3\,$km are shown in
-  Figure~\ref{fig:results-layered--3}. The CPU and RAM requirements are listed
+  Figure~\ref{fig:results-layered--3}. The runtime and memory requirements are listed
   in Table~\ref{tbl:comp-layered}.
@@
 
-\imycom[DW]{\simpeg/\emg3d I put now ncells in ndof, which is wrong. Think about this}
-
-\itodo{EVERYONE: Please check all three tables.
-The numbers should only include time/ram for the actual solving of Maxwell's equations (not mesh generation or similar things); they should be the total (CPU) and the max (RAM), respectively, for/of all frequencies (if applicable).: (1) Is the CPU correct, and does it include the total runtime for all frequencies?
-(2) Is the number of processors correct?
-(3) Is RAM correct, and corresponds to maximum used RAM?
-(4) dof correct?}
-
 %
-\tabl[btp]{comp-layered}{Comparison of used CPU and RAM and of number of cells
-  used to discretize the layered model.}{
+\tabl[btp]{comp-layered}{Comparison of runtime, memory, and number of cells used to discretize the layered model.}{
   \centering
@@
   %
-  Code & {CPU} & \#Procs & {RAM}   & {\#dof} \\
-       & {(s)} &         & {(GiB)} &         \\
+       & {Runtime (s)} & \#Procs & {Memory (GiB)}   & {\#dof} \\
   \midrule
   %
-  \custem &   118 & 24 &  97.8 & 3061616 \\
+  \custem &   118 & 24 &  97.8 & 1530808 \\ % dof: 3061616 / 2 (Real+Imag -> Complex)
   \emg3d  &   116 &  1 &   0.4 & 4813216 \\
   \petgem &    90 & 24 &  34.2 & 2455868 \\
-  \simpeg & 10089 &  1 & 280.3 & 4813216 \\
+  \simpeg & 10089 &  4 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
   %
@@
 
-The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding required CPU and RAM are listed in Table~\ref{tbl:comp-block}.
+The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
 We can conclude from the NRMSD that similar codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very similar, as well as are \custem and \petgem.
@@
 %
-\tabl[btp]{comp-block}{Comparison of used CPU and RAM and of number of cells
+\tabl[btp]{comp-block}{Comparison of used runtime, memory, and number of cells
   used to discretize the block model.}{
@@
   %
-  Code & {CPU} & \#Procs & {RAM}   & {\#dof} \\
-       & {(s)} &         & {(GiB)} &         \\
+       & {Runtime (s)} & \#Procs & {Memory (GiB)}   & {\#dof} \\
   \midrule
   %
-  \custem &   158 & 24 & 115.9 & 3308484 \\
+  \custem &   158 & 24 & 115.9 & 1654242 \\ % dof: 3308484 / 2  (Real+Imag -> Complex)
   \emg3d  &   115 &  1 &   0.4 & 4813216 \\
   \petgem &    72 & 24 &  35.8 & 2455868 \\
-  \simpeg &  9993 &  1 & 280.6 & 4813216 \\
+  \simpeg &  9993 &  4 & 280.6 & 4813216 \\ % nprocs: 1*4 threads
   %
@@
 %
-\tabl[btp]{comp-marlim}{Comparison of used CPU and RAM and of number of cells
+\tabl[btp]{comp-marlim}{Comparison of used runtime, memory, and number of cells
   used to discretize the Marlim R3D model.}{
   \centering
-\begin{tabular}{ls[table-format=4.2]rs[table-format=4.2]rl}
+\begin{tabular}{lS[table-format=6.0]rS[table-format=4.1]S[table-format=8.0]}
   \toprule
   %
-  Code & {CPU} & \#Procs & RAM     & \#dof \\
-       & {(s)} &         & {(GiB)} &         \\
+       & {Runtime (s)} & \#Procs & {Memory (GiB)}   & {\#dof} \\
   \midrule
   %
-  \custem & 0.0 &  0 & 0.0 & 0 \\
-  \emg3d  & 0.0 &  0 & 0.0 & 0 \\
-  \petgem & 0.0 &  0 & 0.0 & 0 \\
-  \simpeg & 0.0 &  0 & 0.0 & 0 \\
+  \custem & 4984 & 64 & 558.5 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
+  \emg3d  & 1478 &  1 &   0.5 & 5998992 \\
+  \petgem & 3527 & 96 & 437.8 & 4539474 \\
+  \simpeg &  422 &  4 &  12.8 &  720146 \\ % nprocs: 1*4 threads
   %
@@
 It took all of us MUCH more time to generate appropriate meshes, then to actually compute the responses.
+    \item very different application area.
+E.g.
+\emg3d is for f-domain, CSEM; not too low frequencies, as it becomes slow (null-space).
+\simpeg, on the other hand, has from 1D, 2D, 3D, DC, IP, Magnetic, TEM, inversion, you-name-it things; so from very specialist to very broad.
 \end{itemize}

### 2020-09-11 manuscript/Manuscript.tex
Updates from Overleaf
Move local up to 2nd version

@@
 The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
-There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or OcTree meshes \citep{ECP.07.Haber}.
+There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or octree meshes \citep{ECP.07.Haber}.
 
@@
 
-Meshes and finite volume differential operators are implemented in the \discretize package, which currently includes tensor, OcTree, cylindrical, and logically rectangular meshes.
+Meshes and finite volume differential operators are implemented in the \discretize package, which currently includes tensor, octree, cylindrical, and logically rectangular meshes.
 Each mesh type inherits from a common structure and uses the same naming conventions for methods and properties.
@@
 
+We computed the responses for three different models to verify that the four 3D CSEM codes yield the same electromagnetic responses and to compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, tensor, octree) in different scenarios.
+The first model is an anisotropic layered model, which can be compared to semi-analytical solutions.
+The layered model serves also as background model for the second verification, where we add three resistive blocks into the subsurface.
+The third test is based on a realistic, anisotropic marine model.
+
+\subsection{Layered Model}
+
 \itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
-We computed the responses for two different models to verify that all different 3D codes yield the same electromagnetic responses.
-The first simple \emph{Block model} consists of a layered, anisotropic background with three embedded blocks.
-The second model, \emph{Marlim R3D}, is based on a very complex, realistic marine CSEM setup.
-
-\subsection{Block Model}
-
-The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
-We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}.
-We additionally added a layered background with vertical transverse isotropy (VTI).
-%
-\plot*{block-model}{width=.6\textwidth}{
-  Sketch of the block model.
-The layered model consists of an air layer, a water layer, a thin top-layer followed by a thick, anisotropic background layer, and at the bottom a resistive basement layer.
-All three blocks are embedded in the thick background layer, which has VTI with $\lambda=\sqrt{2}$.
-}
-%
 
@@
 \end{tabular}}%
+%
+
+\subsection{Block Model}
+
+The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
+We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}.
+We additionally added a layered background with vertical transverse isotropy (VTI).
+%
+\plot*{block-model}{width=.6\textwidth}{
+  Sketch of the block model.
+The layered model consists of an air layer, a water layer, a thin top-layer followed by a thick, anisotropic background layer, and at the bottom a resistive basement layer.
+All three blocks are embedded in the thick background layer, which has VTI with $\lambda=\sqrt{2}$.
+}
 %
@@
     but very different from MR3D. So there I actually trust more our
-    calculation, or there is a difference in the model that we did not take
+    computation, or there is a difference in the model that we did not take
     into account.
@@
     to MR3D.
+  \item FD needs comparably a lot of cells
 \end{itemize}
@@
   \custem & 4984 & 64 & 558.5 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
-  \emg3d  & 1478 &  1 &   0.5 & 5998992 \\
+  \emg3d  & 1200 &  1 &   0.5 & 5998992 \\
   \petgem & 3527 & 96 & 437.8 & 4539474 \\
@@
 In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d.
-Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be calculated in the same computational domain.
+Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain.
 As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d.
-For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the calculation for multiple sources, but this argumentation is beyond the scope of this work.
+For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
 
@@
 
-Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing OcTree meshes.
+Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing octree meshes.
 Furthermore, as a part of a broader development objective of inter-operating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.

### 2020-09-11 manuscript/Manuscript.tex
Figures Layered/Block Model

@@
 \newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
+
+\newcommand{\rmk}[1]{{\color{red}\bfseries #1}}
 
@@
 The layered model serves also as background model for the second verification, where we add three resistive blocks into the subsurface.
-The third test is based on a realistic, anisotropic marine model.
+The final comparison is based on a realistic, anisotropic marine model.
+This is an open-source model, for which also published data from a commercial code exist.
 
@@
 
+The layered (1D) model consists of an upper halfspace of air ($\rho_\text{air}=\num{e8}\,\ohmm$), a 600\,m deep water layer ($\rho_\text{sea}=\num{0.3}\,\ohmm$), followed by a 250\,m thick, isotropic layer of 1\,\ohmm, a 2.3\,km thick, anisotropic layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive, isotropic basement consisting of a lower halfspace of $1000\,\ohmm$.
+The survey consists of a 200\,m long and 800\,A strong source at a single position with frequency $f=1\,$Hz, and three receiver lines of 101 receivers each.
+The centre the $x$-directed source is at $x=y=0\,$m, 50\,m above the seafloor.
+The $x$-directed receivers are placed on the seafloor every 200\,m from $x=-10\,$km to $x=+10\,$km in three lines for $y=-3; 0; +3\,$km.
+(Note that for the layered model we only show results for the receiver lines $y=-3; 0\,$km, as the results for $y=\pm3\,$km are the same in the 1D case.)
+
+A layered model fails to show the strength of 3D modellers, and in reality one would not choose a 3D code to compute responses for a layered model.
+However, it is one of the few examples that can be compared to semi-analytical results, and is therefore still a valuable test.
+All semi-analytical responses are computed using the code \empymod\citep{GEO.17.Werthmuller}.
+
 \itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
+\rmk{$\Downarrow$ Re-arrange and re-write all this $\Downarrow$}
 
-The layered model consists of an upper halfspace of air, a 600\,m deep water layer, followed by a 150\,m thick, isotropic layer of 1\,\ohmm, a 3.3\,km thick, anisotropic layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive basement consisting of a lower halfspace of $1000\,\ohmm$.
-The 200\,m long, $x$-directed source is located 50\,m above the seafloor from $x=-50$ to $x=50\,$m in $x$-direction, at $y=0\,$m.
-The $x$-directed receivers are placed on the seafloor every 200\,m from $x=-10\,$km to $x=+10\,$km in three lines for $y=-3, 0, 3\,$km.
-
-The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretization.
-Therefore, the FE codes \custem and \petgem used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
-This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
-\imycom[RR]{Add short information about mesh design with \simpeg and \emg3d, including something like "comparatively coarse discretization in centre to minimise computation times" }
-
-\imycom[DW]{rewrite next paragraph}
-In a first step, we compare the layered background to the semi-analytical solutions of a 1D code, for which we use \empymod\citep{GEO.17.Werthmuller}.
 Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the actual responses in the top rows, and the relative error in the bottom rows for the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
@@
 %
-\plot*{results-layered-0}{width=.8\textwidth}{
+\plot*{results-layered}{width=\textwidth}{
    Comparison of the layered model for the inline receivers ($y=0\,$km).
@@
 %
+
+The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretization.
+Therefore, the FE codes \custem and \petgem used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
+This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
+\imycom[RR]{Add short information about mesh design with \simpeg and \emg3d, including something like "comparatively coarse discretization in centre to minimise computation times" }
 
@@
   in Table~\ref{tbl:comp-layered}.
-%
-\plot*{results-layered--3}{width=.8\textwidth}{
-   Comparison of the layered model for the broadside receivers ($y=-3\,$km).
-   Top row shows the semi-analytical responses from \empymod, and bottom row
-   show the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
-}
-%
+
+\rmk{$\Uparrow$ Re-arrange and re-write all this $\Uparrow$}
 
@@
 
-In a second step, three resistive blocks were added in the 3.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}.
+In a second step, three resistive blocks were added in the 2.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}.
 They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
@@
 %
-\plot*{results-block--3}{width=.8\textwidth}{
+\plot*{results-block}{width=\textwidth}{
    Comparison of the block model for the broadside receivers at $y=-3\,$km.
@@
    between \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
-}
-%
-
-%
-\plot*{results-block-0}{width=.8\textwidth}{
-   Comparison of the block model for the inline receivers at $y=0\,$km.
-   Top row shows the responses and bottom row the NRMSDs (\%)
-   between \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
-}
-%
-
-%
-\plot*{results-block-3}{width=.8\textwidth}{
-   Comparison of the block model for the broadside receivers at $y=+3\,$km.
-   Top row shows the responses and bottom row the NRMSDs (\%) between
-   \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
 }

### 2020-09-15 manuscript/Manuscript.tex
MarlimR3d responses figures

@@
 The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
-We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:block-model}.
+We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}.
 We additionally added a layered background with vertical transverse isotropy (VTI).
 %
-\plot*{block-model}{width=.6\textwidth}{
+\plot*{model-block}{width=.6\textwidth}{
   Sketch of the block model.
@@
 
-In a second step, three resistive blocks were added in the 2.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:block-model}.
+In a second step, three resistive blocks were added in the 2.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:model-block}.
 They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
@@
 
-%
-\plot*{median-stats-block}{width=\textwidth}{
-  {\imycom[DW]{Suggestion from Raphael for a statistics plot.}}
-    Overall misfit relations between all codes for the three receiver lines
-    y=-3, y=0, and y=3 (f.l.t.r.). Colors indicate the median values of the 101
-    calculated NRMSD arguments for each line between all codes. Errors for real
-    parts are shown in the lower triangle, for imaginary parts in the upper
-  triangle.
-}
-%
-
 \subsection{Marlim R3D}
@@
 The comparison is shown in Figure~\ref{fig:results-marlim}.
+
 %
-\plot*{results-marlim}{width=\textwidth}{
+\plot*{results-marlim-responses}{width=\textwidth}{
+}
+%
+
+%
+\plot*{results-marlim_2published}{width=\textwidth}{
   This is one heck of a figure. Just an idea, please make suggestions how to
@@
   data is a copy of \emg3d data).
+}
+%
+
+%
+\plot*{results-marlim_2ours}{width=\textwidth}{
+}
+%
+
+%
+\plot*{results-marlim_entire}{width=\textwidth}{
+}
+%
+%
+\plot*{results-marlim_survey}{width=\textwidth}{
 }

### 2020-09-16 model-marlim/loadmarlim.py
Draft figures of everything

@@ -97,16 +97,10 @@ def extract_model(model='orig'):
 
 
 def extract_section():
-    """Extract original or computational model of Marlim R3D and store as npz.
+    """Extract x-z-slice at receiver location of the original mesh.
 
-    Extracts the original fine model or the computational model from the
-    sgy-fiels and stores them as numpy-compressed npz files.
-
-    Parameters
-    ----------
-    model : str; {<'orig'>; 'comp'}
-        If model=='comp', the computational model is returned. Else the
-        original model.
+    Extracts a x-z-slice of the original fine resistivity model and stores it
+    as numpy-compressed npz file.
     """
 
     # Get original mesh and resistivities.

### 2020-09-16 manuscript/Manuscript.tex
Draft figures of everything
Reworked Layered/Block; Marlim missing

@@
 However, from now on we do not expect too many changes.
-To make it easier for everyone to see the new changes please make sure that from now on "Track Changes" is always in Overleaf.}
+To make it easier for everyone to see the new changes please make sure that from now on "Track Changes" is always on in Overleaf.}
     \item Notes on orthography: I settled on discretize with a «z».
@@
 Current exceptions: Miensopust et al., 2013, is cited twice.
+    \item {\color{red}\bfseries Please let me know} if you think the order of authors should be different. The last thing we want in this collaboration is that someone feels unhappy about that.
     \item  {\color{red}\bfseries Everyone: Please ensure the info in the tables is correct:}
@@
       \begin{description}
-        \item[runtime] Should only include the wall time (or elapsed real time, \url{https://en.wikipedia.org/wiki/Elapsed_real_time}) of solving the SLE, for ALL frequencies (in \emg3d some frequencies are slower than others, but in any case, we report the sum of all of them); any pre-/postprocessing such as mesh generation or model interpolation can be ignored.
+        \item[runtime] Should only include the wall time (or elapsed real time, \href{https://en.wikipedia.org/wiki/Elapsed_real_time}{wikipedia.org/\-wiki/\-Elapsed\-\_real\-\_time}) of solving the SLE, for ALL frequencies (in \emg3d some frequencies are slower than others, but in any case, we report the sum of all of them); any pre-/postprocessing such as mesh generation or model interpolation can be ignored.
         \item[memory] It should be the maximum memory increase when solving the SLE (again, ignoring any pre-/postprocessing).
@@
     \end{description}
-    We could discuss if we should report CPU time instead (hence summing all parallel processes); but I think for the user of interest is the real-world time, how long do I have to wait.
+    We could discuss if we should report CPU time instead (hence summing all parallel processes); but I think for the user of interest is the real-world time, how long do I have to wait, so I think it is good as we do it now.
 (Either way, the reader can make a quick estimation in one or the other direction; important is that we are consistent throughout the paper.)
@@
 The final comparison is based on a realistic, anisotropic marine model.
-This is an open-source model, for which also published data from a commercial code exist.
+This is an open-source resistivity model which comes with computed CSEM responses.
 
@@
 
-The layered (1D) model consists of an upper halfspace of air ($\rho_\text{air}=\num{e8}\,\ohmm$), a 600\,m deep water layer ($\rho_\text{sea}=\num{0.3}\,\ohmm$), followed by a 250\,m thick, isotropic layer of 1\,\ohmm, a 2.3\,km thick, anisotropic layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive, isotropic basement consisting of a lower halfspace of $1000\,\ohmm$.
+The layered (1D) model consists of an upper halfspace of air ($\rho_\text{air}=\num{e8}\,\ohmm$), a 600\,m deep water layer ($\rho_\text{sea}=\num{0.3}\,\ohmm$), followed by a 250\,m thick, isotropic layer of 1\,\ohmm, a 2.3\,km thick, anisotropic (vertical transverse isotropy, VTI) layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive, isotropic basement consisting of a lower halfspace of $1000\,\ohmm$.
 The survey consists of a 200\,m long and 800\,A strong source at a single position with frequency $f=1\,$Hz, and three receiver lines of 101 receivers each.
-The centre the $x$-directed source is at $x=y=0\,$m, 50\,m above the seafloor.
-The $x$-directed receivers are placed on the seafloor every 200\,m from $x=-10\,$km to $x=+10\,$km in three lines for $y=-3; 0; +3\,$km.
-(Note that for the layered model we only show results for the receiver lines $y=-3; 0\,$km, as the results for $y=\pm3\,$km are the same in the 1D case.)
+The centre of the $x$-directed source is at $x=y=0\,$m, 50\,m above the seafloor.
+The $x$-directed receivers are placed on the seafloor every 200\,m from $x=-10\,$km to $x=+10\,$km in three lines with $y=-3; 0; +3\,$km.
 
@@
 However, it is one of the few examples that can be compared to semi-analytical results, and is therefore still a valuable test.
-All semi-analytical responses are computed using the code \empymod\citep{GEO.17.Werthmuller}.
+All layered-model responses are compared to results computed with the semi-analytical code \empymod\citep{GEO.17.Werthmuller}.
 
-\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
-\rmk{$\Downarrow$ Re-arrange and re-write all this $\Downarrow$}
+Figure~\ref{fig:results-layered} shows the result of the layered model verification, where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values).
+The top row shows the actual, semi-analytically computed responses, and the second and the third rows show the relative error (in percent) of the inline and the broadside receivers, respectively (note that for the 1D case the two broadside lines for $y=\pm3\,$km are identical).
 
-Figures~\ref{fig:results-layered-0} and \ref{fig:results-layered--3} show the actual responses in the top rows, and the relative error in the bottom rows for the receiver lines $y=0\,$km and $y=\pm3\,$km, which are identical.
-
-Figure~\ref{fig:results-layered-0} illustrates the inline responses in the top-row for offsets $r>0.5\,$km.
-We only show the semi-analytical result for the real and imaginary amplitudes.
-The bottom row displays the relative error of the 3D codes.
-The results show that all codes are yielding accurate result with errors of around 1\,\% in most parts and overall below a few percent, disregarding locations affected by sign reversals.
-The differences can be mainly attributed to the chosen discretizations.
-The FE codes show the strongest misfits at large offsets, most likely caused by the utilised boundary mesh.
-Very low errors at large offsets are achieved by \emg3d, whereas it suffers at short offsets from a coarse grid.
 %
-\plot*{results-layered}{width=\textwidth}{
-   Comparison of the layered model for the inline receivers ($y=0\,$km).
-   Top row shows the semi-analytical responses from \empymod, and bottom row
-   shows the relative error (\%) of \custem, \emg3d, \petgem, and \simpeg.
-}
+\plot*{results-layered}{width=\textwidth}{Inline and broadside responses (top row) for the layered model.
+The relative error of the four 3D modellers are shown in the second and the third row for the inline and broadside responses, respectively.}
 %
 
+There are a few noteworthy points:
+\begin{enumerate}
+  \item The error plots of the real and imaginary responses are  dominated by the zero-crossings, which blows the error up as is the nature of the relative error formula, it has no real-world implications.
+  \item However, it can be seen from the absolute-values errors that the error is generally in the order of 1\,\% or less.
+  \item The relative errors close to the source are getting huge, particularly for the inline receivers and particularly for the results of \emg3d and \simpeg.
+These comparably huge errors are caused by a too coarse discretization around the source.
+They could be significantly reduced by choosing a finer discretization, at the cost of increased computation time.
+  \item The relative error of the responses from \custem and \petgem, on the hand, are relatively big at large offsets, particularly for the inline real responses.
+This has, again, its origin in the chosen discretization.
 The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretization.
-Therefore, the FE codes \custem and \petgem used the same tetrahedral mesh with a horizontal layered-earth extent of 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
+Therefore, the FE codes only extend this thin layer up to 30\,km for the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
 This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
-\imycom[RR]{Add short information about mesh design with \simpeg and \emg3d, including something like "comparatively coarse discretization in centre to minimise computation times" }
+\end{enumerate}
 
-\imycom[RR]{I suggest to show y-component for broadside and the errors of the
-  weak component (if not too bad), otherwise only broadside is required to save
-  a plot, because inline should be better for Ex in general.} The corresponding
-  broadside responses for $y=\pm3\,$km are shown in
-  Figure~\ref{fig:results-layered--3}. The runtime and memory requirements are listed
-  in Table~\ref{tbl:comp-layered}.
+Please not that \emg3d and \simpeg used the same tensor mesh in this example.
+\imycom[DW]{Lindsey: A sentence why Tensor over OcTree.}
+\imycom[DW]{Raphael/Octavio: A sentence about the differences in the meshes of
+\custem and \petgem.}
 
-\rmk{$\Uparrow$ Re-arrange and re-write all this $\Uparrow$}
+The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
+\imycom[DW]{Lindsey: A note about high RAM usage of \simpeg? About PARDISO or Mumps or similar. Could be used as a general note that it boils down to the underlying solver.}
 
 %
-\tabl[btp]{comp-layered}{Comparison of runtime, memory, and number of cells used to discretize the layered model.}{
+\tabl[btp]{comp-layered}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}{
   \centering
-\begin{tabular}{lS[table-format=6.0]rS[table-format=4.1]S[table-format=8.0]}
+\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
   \toprule
   %
-       & {Runtime (s)} & \#Procs & {Memory (GiB)}   & {\#dof} \\
+       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
   \midrule
   %
-  \custem &   118 & 24 &  97.8 & 1530808 \\ % dof: 3061616 / 2 (Real+Imag -> Complex)
-  \emg3d  &   116 &  1 &   0.4 & 4813216 \\
-  \petgem &    90 & 24 &  34.2 & 2455868 \\
-  \simpeg & 10089 &  4 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
+  \custem & 24 &   118 &  97.8 & 1530808 \\ % dof: 3061616 / 2 (Real+Imag -> Complex)
+  \emg3d  &  1 &   116 &   0.4 & 4813216 \\
+  \petgem & 24 &    90 &  34.2 & 2455868 \\
+  \simpeg &  4 & 10089 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
   %
@@
 The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
-We took the same layout of the blocks but adjusted the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}.
-We additionally added a layered background with vertical transverse isotropy (VTI).
+We use the same layout of the blocks but adjust the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}.
+Additionally, we add our \emph{Layered Model} as a VTI background.
+The three resistive blocks have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
 %
 \plot*{model-block}{width=.6\textwidth}{
-  Sketch of the block model.
-The layered model consists of an air layer, a water layer, a thin top-layer followed by a thick, anisotropic background layer, and at the bottom a resistive basement layer.
-All three blocks are embedded in the thick background layer, which has VTI with $\lambda=\sqrt{2}$.
+  Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{2}$.
 }
@@
 
-In a second step, three resistive blocks were added in the 2.3\,km-thick, anisotropic background layer as shown in Figure~\ref{fig:model-block}.
-They have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
-As there are no (semi-)analytical solutions for this model we use the normalised root-mean square difference (NRMSD) between different codes, where the NRMSD of two responses $p$ and $q$ is given by
+There are no (semi-)analytical solutions for such a model.
+We therefore use the normalised root-mean square difference (NRMSD) between the results of different codes, where the NRMSD of two responses $R_1$ and $R_2$ is given by
 %
 \begin{equation}
-  \mr{NRMSD~(\%)} = 200 \frac{|p - q|}{|p| + |q|}\ .
+  \mr{NRMSD~(\%)} = 200 \frac{|R_1 - R_2|}{|R_1| + |R_2|}\ .
   \label{eq:nrmsd}
@@
 %
-\imycom[DW]{NRMSD: Comparing all codes to all would make the figures too cluttered, and I don't think it would add a lot insights.
-My idea is therefore to compare \emg3d/\simpeg (the two FV ones), \custem/\petgem (the two FE ones), and \emg3d/\custem (a cross-comparison).
-What do you think?
 
-\imycom[RR]{Agreed. Another suggestion, I solved this visualisation problem
-  with a color coded matrix plot, showing 90th percentiles or median values of
-  all errors along the line as meaningful comprehensive number. Look in my
-  thesis - example 4. Comparison for real and imag could be in the lower and
-  upper triangles, or we show absolute magnitudes for layered earth in lower
-  triangle and for block model in upper triangle. With help of this plot, one
-  could easily say if differences are higher for block model and which codes
-  fit to each other well.}
-\imycom[RR]{If using the mentioned matrix plots, we would need only one of the
-  figures 4-6, and could show the other data comprehensively. I added a python
-  script to generate an example of my plotting suggestion in the model-block
-  directory and a new Figure 7 in the manuscript that illustrates what I mean.
-  Of course, any upgrade suggestion for this initial idea is welcome, aside
-  from making it looking nice with labels  and annotations.}
-\imycom[OCR]{I really liked this way of presenting the comparison, in addition to saving space, we gained in understanding. Looks really nice!}
+The results for the three receiver lines $y=-3,0,+3\,$km are shown in the left, middle, and right columns of Figure~\ref{fig:results-block}, respectively.
+The top row shows the result of \emg3d, as an example, and the bottom row shows the NRMSDs between the absolute responses of the codes.
+%
+\plot*{results-block}{width=\textwidth}{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the NRMSDs (\%) between the absolute responses ($|E_x|$) of the different codes are shown in the bottom row.}
+%
+\itodo{We might wait for the final \simpeg results before jumping to conclusions; but generally, the NRMSD differences is below 1-2\,\%, except for large offsets.}
 
-}
-
-The results for the three receiver lines $y=-3,0,3\,$km are shown in Figures~\ref{fig:results-block--3}, \ref{fig:results-block-0}, and \ref{fig:results-block-3}, respectively, and the corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
-We can conclude from the NRMSD that similar codes have a smaller NRMSD than cross-comparison, hence \emg3d and \simpeg are very similar, as well as are \custem and \petgem.
-\imycom[DW]{Write in detail when all results are available}
+The corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
 %
-\plot*{results-block}{width=\textwidth}{
-   Comparison of the block model for the broadside receivers at $y=-3\,$km.
-   Top row shows the responses and bottom row the NRMSDs (\%)
-   between \emg3d--\custem, \custem--\petgem, and \emg3d--\simpeg.
-}
-%
-
-%
-\tabl[btp]{comp-block}{Comparison of used runtime, memory, and number of cells
-  used to discretize the block model.}{
+\tabl[btp]{comp-block}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}{
   \centering
-\begin{tabular}{lS[table-format=6.0]rS[table-format=4.1]S[table-format=8.0]}
+\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
 \toprule
   %
-       & {Runtime (s)} & \#Procs & {Memory (GiB)}   & {\#dof} \\
+       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
   \midrule
   %
-  \custem &   158 & 24 & 115.9 & 1654242 \\ % dof: 3308484 / 2  (Real+Imag -> Complex)
-  \emg3d  &   115 &  1 &   0.4 & 4813216 \\
-  \petgem &    72 & 24 &  35.8 & 2455868 \\
-  \simpeg &  9993 &  4 & 280.6 & 4813216 \\ % nprocs: 1*4 threads
+  \custem & 24 &   158 & 115.9 & 1654242 \\ % dof: 3308484 / 2  (Real+Imag -> Complex)
+  \emg3d  &  1 &   115 &   0.4 & 4813216 \\
+  \petgem & 24 &    72 &  35.8 & 2455868 \\
+  \simpeg &  4 &  9993 & 280.6 & 4813216 \\ % nprocs: 1*4 threads
   %
@@
 %
-
-The difference becomes only significant at offsets larger than 8\,km.
-This is due to a practical difference in the meshing: This simple block model is advantageous for FV codes, as it consists of rectangular blocks and horizontal layers, simple geometric objects.
-While having a very thin, shallow layer is straight-forward for FV codes, it requires many cells for a FE code, and a similar approach as for the Block Model was used.
-This is the reason for the increased NRMSD at large offsets, and it has nothing to do with the accuracy of the computation itself.
 
@@
   the drawn survey line in that figure are plainly wrong.
+  \textbf{Air, water, and salt are isotropic, rest has $\lambda=\sqrt{2}$.}
 }
@@
 
-\imycom[DW]{There are some interesting features we should highlight. But again,
-we first need all results. E.g.}
 \begin{itemize}
@@
 %
-\tabl[btp]{comp-marlim}{Comparison of used runtime, memory, and number of cells
-  used to discretize the Marlim R3D model.}{
+\tabl[btp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the Marlim R3D model.}{
   \centering
-\begin{tabular}{lS[table-format=6.0]rS[table-format=4.1]S[table-format=8.0]}
+\begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
   \toprule
   %
-       & {Runtime (s)} & \#Procs & {Memory (GiB)}   & {\#dof} \\
+       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
   \midrule
   %
-  \custem & 4984 & 64 & 558.5 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
-  \emg3d  & 1200 &  1 &   0.5 & 5998992 \\
-  \petgem & 3527 & 96 & 437.8 & 4539474 \\
-  \simpeg &  422 &  4 &  12.8 &  720146 \\ % nprocs: 1*4 threads
+  \custem & 64 & 4984 & 558.5 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
+  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
+  \petgem & 96 & 3527 & 437.8 & 4539474 \\
+  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
   %
@@
 %
-
-\itodo{ADD cross section plots!}
 
@@
 
-\imycom[DW]{I would like to capture as many as possible of the (I) differences,
-  (II) difficulties, (III) advantages, and (IV) disadvantages, that we
-  encountered in this exercise. This includes differences from direct to
-  iterative solver and differences from FE to FD codes etc. Please just jot
-  down things that come to your mind.
-\imycom[OCR]{I think an important point is the user experience (modeller). I
-  know this is an intangible element but perhaps we could add a line about it.
-  It is my opinion}
-}
-
-\imycom[LH]{From the discussion in slack - also a TODO on adding points on if there were any changes (or new motivation for development) based on this exercise --> goal: highlight benefits of open source collaborations.
-
-Within SimPEG: This work has motivated feature development including: (a) interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and (b) new examples to include in the documentation for designing octree meshes.
-Furthermore, as a part of a broader development objective of inter-operating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
-% \citep{simpeg0.14.0}.
-}
-
+\clearpage~\newpage
+\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
 \section{TODOs}
 
+Touch on:
 \begin{itemize}
-    \item Add cross-section
+  \item (I) differences, (II) difficulties, (III) dis\\advantages
+  \item direct vs iterative solver
+  \item FE vs FD
+  \item Speed of computation vs user experience (modeller) vs time spent to
+    create a good mesh.
     \item Focus on the different open source tools that can deliver industry-standard results.
@@
     \end{itemize}
+  \item Lindsey:
+    Within SimPEG: This work has motivated feature development including: (a)
+    interpolation and averaging strategies from mapping physical properties on
+    a fine mesh to a coarser mesh for computation and (b) new examples to
+    include in the documentation for designing octree meshes. Furthermore, as a
+    part of a broader development objective of inter-operating with other
+    forward-simulation engines, connecting \emg3d and \simpeg provided a
+    motivating use-case for the latest refactor and release of \simpeg 0.14.0.
 \end{itemize}

### 2020-09-16 manuscript/Manuscript.tex
Marlim figures and captinos

@@
 %
-\plot*{model-block}{width=.6\textwidth}{
-  Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{2}$.
-}
+\plot*{model-block}{width=.6\textwidth}{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
 %
@@
 
+\clearpage
+\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
 \subsection{Marlim R3D}
@@
 %
-\plot*{model-marlim}{width=\textwidth}{
-  This figure obviously needs to be improved massively (at least a colorbar).
-  What would you like to show from the actual data here?
-  A nice figure would  be Figure 2 in the original paper; however, note that
-  the drawn survey line in that figure are plainly wrong.
-  \textbf{Air, water, and salt are isotropic, rest has $\lambda=\sqrt{2}$.}
-}
+\plot*{model-marlim}{width=\textwidth}{Marlim horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position.
+Air (not shown in the model), seawater, and the salt body are electrically isotropic, everything else has a VTI with $\lambda=\sqrt{2}$.}
 %
@@
 %
-\plot*{results-marlim-responses}{width=\textwidth}{
-}
+\plot*{results-marlim-responses}{width=\textwidth}{Marlim R3D comparison between our codes (grey lines) and the published data (coloured lines).
+The grey lines under the coloured lines are not visible in most areas, meaning they are very similar.
+However, there are three notable zones, (1) to (3), which are explained further in the text.}
 %
@@
 %
-\plot*{results-marlim_2published}{width=\textwidth}{
-  This is one heck of a figure. Just an idea, please make suggestions how to
-  improve it (currently, \petgem data is a copy of \custem data, and \simpeg
-  data is a copy of \emg3d data).
-}
+\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
+Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
 %
@@
 %
-\plot*{results-marlim_2ours}{width=\textwidth}{
-}
+\plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
+Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.}
 %
@@
 %
-\plot*{results-marlim_entire}{width=\textwidth}{
-}
+\plot*{results-marlim_entire}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the entire computational domain.}
 %
+
 %
-\plot*{results-marlim_survey}{width=\textwidth}{
-}
+\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}
 %
@@
 
-\clearpage~\newpage
-\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
 \section{TODOs}

### 2020-09-17 manuscript/Manuscript.tex
Re-worked Marlim; Disc/Conc missing

@@
 % (1) principal objectives and scope of the work
-Large-scale modelling of three-dimensional (3D) controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
+Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
 However, this has changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
@@
 % (2) methodology
-For the numerical comparison we choose three models, a layered background, ones on its own and ones containing three resistive blocks, and Marlim R3D, a complex, anisotropic, real-world and open-source resistivity model.
+For the numerical comparison we use three models: a simple layered model; a model containing three resistive blocks in a layered background; and a complex, real-world resistivity model.
+All three models are vertically transverse isotropic.
 The analysis includes three different mesh-types, simple tensor meshes, octree meshes, and unstructured tetrahedral meshes.
@@
 Current exceptions: Miensopust et al., 2013, is cited twice.
-    \item {\color{red}\bfseries Please let me know} if you think the order of authors should be different. The last thing we want in this collaboration is that someone feels unhappy about that.
-    \item  {\color{red}\bfseries Everyone: Please ensure the info in the tables is correct:}
+    \item Regarding submission, {\color{red}\bfseries please let me know}:
+      \begin{itemize}
+        \item If you think the \textbf{order of authors} should be different. The last thing we want in this collaboration is that someone feels unhappy about that.
+        \item If you have \textbf{another manuscript under revision with GJI}. When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI.
+        \item For the submission I will create a \textbf{new repository on swung-research}.
+The idea is to make a single, new commit with everything (without the git history, for various reasons).
+Please let me know if you would prefer to commit your files yourself as a PR instead.
+        \item \textbf{Wanted and not wanted reviewers:} Let me know if you have any names for these.
+I do not have any \emph{not wanted}, but I do have a few I will put on the \emph{wanted} list, mainly people I would be interested to have their feedback and that have knowledge about 3D modelling:
+          \begin{itemize}
+            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM});
+            \item Rune Mittet (domain knowledge; he will know what SBLwiz actually does, so it would be very interesting to have his feedback);
+            \item Dimitry Avdeev and Ralph-Uwe Börner (they both did extensive 3D code overview/review papers in 2005 and 2010, respectively, and it would be interesting to get their feedback).
+          \end{itemize}
+      \end{itemize}
+    \item  {\color{red}\bfseries Everyone: Please ensure that the tables have the correct info:}
       \begin{enumerate}
@@
 
-We simulate EM fields for a layered background model with vertical transverse isotropy, with and without three resistive blocks, as well as for the complex marine Marlim R3D model.
+We simulate EM fields for a layered background model with vertical transverse isotropy, with and without three resistive blocks, as well as for the complex marine, open-source MR3D model.
 These three models as well as the corresponding results from four different codes provide a benchmark for new (and existing) codes to be compared to and validated with.
@@
 The layered model serves also as background model for the second verification, where we add three resistive blocks into the subsurface.
-The final comparison is based on a realistic, anisotropic marine model.
-This is an open-source resistivity model which comes with computed CSEM responses.
+The final comparison is based on the realistic, anisotropic marine model MR3D, which is an open resistivity model which comes with computed CSEM responses.
 
@@
 
-\clearpage
-\itodo{HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE HERE}
 \subsection{Marlim R3D}
@@
 The Marlim oil field is a giant reservoir in a turbidite sandstone horizon in the north-eastern part of the Campos Basin, offshore Brazil, which was discovered in 1985.
-\cite{BJG.17.Carvalho} created from seismic data and well log data a realistic resistivity model with vertical transverse isotropy (VTI), Marlim R3D (MR3D), which they released under an open-source license.
-\cite{GEO.19.Correa} computed CSEM data for six frequencies from 0.125\,Hz to 1.25\,Hz, released under an open-source license.
-To compute the data they used a state-of-the-art code from the industry \citep{GEO.07.Maao}.
+\cite{BJG.17.Carvalho} created from seismic data and well log data a realistic, three-dimensional resistivity model with vertical transverse isotropy (VTI), called MR3D, which they released under the open creative common license \emph{CC BY 4.0}.
+\cite{GEO.19.Correa} computed CSEM data for MR3D for six frequencies from 0.125\,Hz to 1.25\,Hz, and released them under the same CC license.
+To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
 It is therefore an ideal case to verify our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
@@
 
-The detailed reservoir model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
+The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
 For the computation the model is upscaled to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
-
+Both the full model and the upscaled computational model are released openly.
 The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
-45 source-towlines were located on the same grid, 50\,m above the seafloor, with shots every 100\,m.
-In the original paper the actual responses for one receiver with the corresponding East-West inline and one East-West broadside acquisition line are shown, which is the data we chose for our comparison.
-The cross-section of the resistivity model along the chosen inline acquisition line is shown in Figure~\ref{fig:model-marlim}, together with the acquisition information.
+45 source-towlines were located on the same grid above each receiver line, 50\,m above the seafloor, with shots every 100\,m.
+The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original paper for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km).
+We reproduce the responses for this receiver and corresponding source-lines in our comparison.
+The $x$-$z$ cross-section of the horizontal resistivity model at the receiver position is shown in Figure~\ref{fig:model-marlim}, together with the receiver and sources positions.
+All layer have a VTI with $\lambda=\sqrt{2}$, except for the air layer, the seawater, and the salt layer, which are all isotropic.
 
 %
-\plot*{model-marlim}{width=\textwidth}{Marlim horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position.
-Air (not shown in the model), seawater, and the salt body are electrically isotropic, everything else has a VTI with $\lambda=\sqrt{2}$.}
+\plot*{model-marlim}{width=\textwidth}{MR3D horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position and with major formations annotated.
+Air (not shown in the model), seawater, and the salt layer are electrically isotropic, everything else has VTI with $\lambda=\sqrt{2}$.
+The receiver is located on the seafloor, and the sources fly 50\,m above the seafloor.}
 %
 
-We computed all all six frequencies for all components ($E_x$, $E_y$, $E_z$) for both inline and broadside acquisition lines.
-However, we show here only the three frequencies and the responses with the strongest amplitudes (which are generally used in processing), which are $E_x$ inline and broadside, and $E_y$ broadside.
-The comparison is shown in Figure~\ref{fig:results-marlim}.
-
+The responses for all six frequencies, both inline and broadside, for all three electric components are shown in Figure~\ref{fig:results-marlim-responses}.
+The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
 %
-\plot*{results-marlim-responses}{width=\textwidth}{Marlim R3D comparison between our codes (grey lines) and the published data (coloured lines).
+\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines).
 The grey lines under the coloured lines are not visible in most areas, meaning they are very similar.
@@
 %
+Two datasets were published, one containing clean responses, and one where realistic noise was added.
+For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m.
+It can be seen that the grey lines are not visible for most parts, which means that the data agree very well.
+However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
+\begin{enumerate}
+  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
+In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component.
+The published responses are not stable either, and therefore any of the responses is as bad as the other.
+Also, tiniest differences in meshing will have a huge effect here.
+  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
+The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
+  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components.
+The differences are related to the bathymetry.
+And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally.
+See the discussion around Figure~\ref{fig:results-marlim_survey}.
+\end{enumerate}
 
+Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
 %
@@
 %
+A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less, particularly for the inline $E_x$ component it is only a few \% or less.
+In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., negative offsets in the inline and broadside $E_x$ responses, in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
+Some NRMSD have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
 
+One might argue that 5-10\,\% NRMSD is a lot.
+We argue that this is probably as good as it gets, given that the code with which we compare is not open-source.
+This has been shown within the process of these results.
+Our first attempt were based on the originally published, fine MR3D model.
+This model is very detailed, but too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation.
+However, none of the codes were able to reproduce the published results.
+The reason is that there are many ways how you can extrapolate a model.
+We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model.
+It is only with this model that we were able to get comparable results, visually mostly the same as shown in Figure~\ref{fig:model-marlim}.
+
+However, even though the computational input model is know, we still do not know what the code SBLwiz exactly does inside.
+From the information we have we know that it computes the data in the time domain transforming them afterwards to the frequency domain, and it includes the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}.
+All our codes, on the other hand, compute in the frequency domain and include the air layer in the model (putting the boundaries sufficiently far away).
+
+The importance of the meshing to the result can be seen in Figure~\ref{fig:results-marlim_2ours}, where we compute the NRMSDs between our codes.
 %
@@
 %
+The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their NRMSD is generally below 0.03\,\%.
+The reason is simple: \custem and \petgem use the exactly same mesh for the computation, the only difference is therefore the solver.
+As they are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same.
+But in general the NRMSDs between our codes look similar as in the comparison with the published results, which is due to the different meshes in use.
 
+The differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_entire} for the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
 %
@@
 %
-
+The top rows show the tensor mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem.
+The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.
+\itodo{Write more once the other results are in the figures too.
+Points to compare: See if the different boundary conditions are visible.
+See and comment on the effects of the different, fast coarsening outside the domain of interest.}
 %
@@
 %
+\itodo{Most importantly, once all results are in the figures: Discuss about the effect of bathymetry, particularly on the $E_y$ field.
+Mark it with a number in the figure.
+Compare between the meshes.
+State that the results will not have a smaller NRMSD unless we know exactly how the bathymetry is treated.}
 
-\begin{itemize}
-  \item 0.125\,Hz: on the left side, \custem and \emg3d are almost identical,
-    but very different from MR3D. So there I actually trust more our
-    computation, or there is a difference in the model that we did not take
-    into account.
-  \item 0.125\,Hz: on the right side, \custem is very similar to MR3D, whereas
-    \emg3d is off.
-  \item 0.125\,Hz and 0.5\,Hz: on the right side, \custem seems to very similar
-    to MR3D.
-  \item FD needs comparably a lot of cells
-\end{itemize}
+The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}.
+The memory requirement varies from $0.5-558.5\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).
 
 %
-\tabl[btp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the Marlim R3D model.}{
+\tabl[btp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
   \centering
@@
 The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
-Aside from the idea of analysing an industrially relevant benchmark example, the Marlim R3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretization.
+Aside from the idea of analysing an industrially relevant benchmark example, the MR3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretization.
 At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
@@
 
-The real Marlim R3D model was, ironically, the ideal case for FE codes because it's structure was characterised by irregular lithological horizons obtained from seismic data.
+The real MR3D model was, ironically, the ideal case for FE codes because it's structure was characterised by irregular lithological horizons obtained from seismic data.
 Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
@@
 
-\section{TODOs}
+It is worth noting that the reported runtime is just one of the aspects.
+But to generate an appropriate mesh, with all the testing involved, can easily take days of work.
+As such the computation times becomes relative, and the ease of usability of a code has to be considered too.
+For \custem, \petgem, and \simpeg it is therefore also a question of how easy everything is to set-up, because after the set-up phase it depends largely on the used solver, which might change in the future; \simpeg, e.g., is looking at moving to similar solvers as currently are used by \custem and \petgem.
+It is, however, slightly different for \emg3d, as that is primarily a solver on its own.
+It is also important to state that while \emg3d, \custem, and \petgem are purely CSEM codes, \simpeg is a much bigger framework which includes other geophysical methods as well.
 
-Touch on:
-\begin{itemize}
-  \item (I) differences, (II) difficulties, (III) dis\\advantages
-  \item direct vs iterative solver
-  \item FE vs FD
-  \item Speed of computation vs user experience (modeller) vs time spent to
-    create a good mesh.
-    \item Focus on the different open source tools that can deliver industry-standard results.
-That there is choice.
-That these people work together (!).
-That the collaboration improved all codes.
-That you can do things with tetrahedrals or tensor meshes or octree meshes, some are better for one task, the other is better for another task.
-Because, as you mentioned Lindsey, in the end for SimPEG, custEM, and PETGEM speed and memory in the end falls a lot on the solver used (Fenics, petsc, pardiso), and not actually on the code.
-Swapping the solver might yield very different metrics.
-    \item Focus on Result Comparison, as this is the only way to verify 3D modellers.
-\end{itemize}
+The shown examples consider the geophysical problem of marine CSEM.
+However, the codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
+The current main applications of the different codes are mining (\custem), mining and environmental (\simpeg), oil and more recent medical and geothermal (\petgem), and
+oil, methane, and deep sea mining (\emg3d).
 
-Add what improvements were initiated by article (“But also, a plus-point of such collaboration is if it brings the realm as such further.
-So we should note down if this collaboration resulted in new features implemented in some codes, new releases etc.
-What did it push forward?
-It would be a motivation for further cross-project/community collaborations.
-Something for the discussion or conclusion part.”):
+A plus-point of a collaboration between different projects such as this is that it brings the realm as a whole further, which should be motivation enough for further collaborations.
 
 \begin{itemize}
-    \item Lindsey: For SimPEG - this will result in new utilities for volume averaging, and likely more documentation on tips for designing tree meshes.
-This could be a pretty compelling piece to bring in to the discussion
+    \item Lindsey: For SimPEG - this will result in new utilities for volume
+      averaging, and likely more documentation on tips for designing tree
+      meshes. This could be a pretty compelling piece to bring in to the
+      discussion
     \item Raphael:
@@
         \item multi-layer subsurface topography first time applied
-        \item reciprocity modeling (even though that has not too much to do with implementation)
+        \item reciprocity modeling (even though that has not too much to do
+          with implementation)
         \item mesh design (resolution, refinement, etc.)
@@
 
-Add somewhere Trivia: All codes could be used for a multitude of applications (oil, mining, geothermal, groundwater, environmental, even non-geophysical). The main work, however:
-\begin{itemize}
-    \item custEM: mining;
-    \item SimPEG: mining, environmental;
-    \item PETGEM: used to be oil, now medical and geothermal;
-    \item emg3d: developed for project dealing with oil, methane, and deep sea mining.
-\end{itemize}
-
 Many things to discuss and take into account
 \begin{itemize}
-    \item Examples are in favour of FD codes, (rectangle blocks, complex model provided as FD model)
-    \item Examples are in favour of iterative solver, as only one source was computed.
-Iterative solvers (\emg3d) will require the same amount of time for each new source, whereas direct solvers have additional source locations almost for free
-    \item Not possible to exactly reproduce published results unless the codes is also open-source, as one cannot know what internally is actually done (show example!)
-    \item In the end the codes (\custem, \emg3d, \petgem, \simpeg) define mainly, how easy the interaction is.
-How easy is it to set-up the mesh, to create sources and receivers, etc etc.
-The \emph{actual} computation time, however,
-    is mostly NOT defined by these codes, but by the underlying solver. (The exception to that is \emg3d, which is its own solver.)
-    \item In the end it comes down to the most important, crucial, difficult, AND TIME CONSUMING point: mesh generation.
-It took all of us MUCH more time to generate appropriate meshes, then to actually compute the responses.
-    \item very different application area.
-E.g.
-\emg3d is for f-domain, CSEM; not too low frequencies, as it becomes slow (null-space).
-\simpeg, on the other hand, has from 1D, 2D, 3D, DC, IP, Magnetic, TEM, inversion, you-name-it things; so from very specialist to very broad.
+    \item Examples are in favour of FD codes, (rectangle blocks, complex model
+      provided as FD model)
+    \item Examples are in favour of iterative solver, as only one source was
+      computed. Iterative solvers (\emg3d) will require the same amount of time
+      for each new source, whereas direct solvers have additional source
+      locations almost for free
+    \item Not possible to exactly reproduce published results unless the codes
+      is also open-source, as one cannot know what internally is actually done
+      (show example!)
+    \item In the end the codes (\custem, \emg3d, \petgem, \simpeg) define
+      mainly, how easy the interaction is. How easy is it to set-up the mesh,
+      to create sources and receivers, etc etc. The \emph{actual} computation
+      time, however, is mostly NOT defined by these codes, but by the
+      underlying solver. (The exception to that is \emg3d, which is its own
+      solver.)
+    \item In the end it comes down to the most important, crucial, difficult,
+      AND TIME CONSUMING point: mesh generation. It took all of us MUCH more
+      time to generate appropriate meshes, then to actually compute the
+      responses.
+    \item very different application area. E.g. \emg3d is for f-domain, CSEM;
+      not too low frequencies, as it becomes slow (null-space). \simpeg, on the
+      other hand, has from 1D, 2D, 3D, DC, IP, Magnetic, TEM, inversion,
+      you-name-it things; so from very specialist to very broad.
 \end{itemize}

### 2020-09-17 manuscript/Manuscript.tex
Update NumPy reference

@@
 The four codes under consideration are, in alphabetical order, \custem \citep{GEO.19.Rochlitz}, \emg3d \citep{JOSS.19.Werthmuller}, \petgem \citep{CAG.18.CastilloReyes, GJI.19.CastilloReyes}, and \simpeg \citep{CAG.15.Cockett, CAG.17.Heagy}.
-All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{CSE.11.VanDerWalt} and \texttt{SciPy} \citep{NM.20.Virtanen}.
+All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{NAT.20.Harris} and \texttt{SciPy} \citep{NM.20.Virtanen}.
 The four of them are not just open-source but follow the open model of development, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).

### 2020-09-17 manuscript/Manuscript.tex
2nd draft of everything

@@
 A plus-point of a collaboration between different projects such as this is that it brings the realm as a whole further, which should be motivation enough for further collaborations.
-
-\begin{itemize}
-    \item Lindsey: For SimPEG - this will result in new utilities for volume
-      averaging, and likely more documentation on tips for designing tree
-      meshes. This could be a pretty compelling piece to bring in to the
-      discussion
-    \item Raphael:
-    \begin{itemize}
-        \item cell-wise resistivity interpolation added
-        \item multi-layer subsurface topography first time applied
-        \item reciprocity modeling (even though that has not too much to do
-          with implementation)
-        \item mesh design (resolution, refinement, etc.)
-    \end{itemize}
-  \item Lindsey:
-    Within SimPEG: This work has motivated feature development including: (a)
-    interpolation and averaging strategies from mapping physical properties on
-    a fine mesh to a coarser mesh for computation and (b) new examples to
-    include in the documentation for designing octree meshes. Furthermore, as a
-    part of a broader development objective of inter-operating with other
-    forward-simulation engines, connecting \emg3d and \simpeg provided a
-    motivating use-case for the latest refactor and release of \simpeg 0.14.0.
-\end{itemize}
-
-Many things to discuss and take into account
-\begin{itemize}
-    \item Examples are in favour of FD codes, (rectangle blocks, complex model
-      provided as FD model)
-    \item Examples are in favour of iterative solver, as only one source was
-      computed. Iterative solvers (\emg3d) will require the same amount of time
-      for each new source, whereas direct solvers have additional source
-      locations almost for free
-    \item Not possible to exactly reproduce published results unless the codes
-      is also open-source, as one cannot know what internally is actually done
-      (show example!)
-    \item In the end the codes (\custem, \emg3d, \petgem, \simpeg) define
-      mainly, how easy the interaction is. How easy is it to set-up the mesh,
-      to create sources and receivers, etc etc. The \emph{actual} computation
-      time, however, is mostly NOT defined by these codes, but by the
-      underlying solver. (The exception to that is \emg3d, which is its own
-      solver.)
-    \item In the end it comes down to the most important, crucial, difficult,
-      AND TIME CONSUMING point: mesh generation. It took all of us MUCH more
-      time to generate appropriate meshes, then to actually compute the
-      responses.
-    \item very different application area. E.g. \emg3d is for f-domain, CSEM;
-      not too low frequencies, as it becomes slow (null-space). \simpeg, on the
-      other hand, has from 1D, 2D, 3D, DC, IP, Magnetic, TEM, inversion,
-      you-name-it things; so from very specialist to very broad.
-\end{itemize}
+Within \simpeg, this work has motivated feature development including interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and new examples to include in the documentation for designing octree meshes.
+Furthermore, as a part of a broader development objective of inter-operating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
+Within \emg3d, this work pushed a lot of the meshing functionality, and implementing of I/O utilities for different file formats.
+Within \custem, cell-wise resistivity interpolation was added for this work, multi-layer subsurface topography was the first time applied as well as first time reciprocity modelling, and also improved mesh design (resolution, refinement, etc.).
 

### 2020-09-21 manuscript/Manuscript.tex
Final SimPEG block-model results
Updates from Overleaf

@@
 
-Furthermore, we deal with the topic of verification.
+Furthermore, we deal with the topic of validation.
 Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
@@
 If different discretizations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
-\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the verification of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
+\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
 This is, to the best of our knowledge, the first comparison exercise for CSEM codes.
@@
 
-\section{Numerical Verification}
+\section{Numerical Validation}
 
-We computed the responses for three different models to verify that the four 3D CSEM codes yield the same electromagnetic responses and to compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, tensor, octree) in different scenarios.
+We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and to compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, tensor, octree) in different scenarios.
 The first model is an anisotropic layered model, which can be compared to semi-analytical solutions.
-The layered model serves also as background model for the second verification, where we add three resistive blocks into the subsurface.
+The layered model serves also as background model for the second validation, where we add three resistive blocks into the subsurface.
 The final comparison is based on the realistic, anisotropic marine model MR3D, which is an open resistivity model which comes with computed CSEM responses.
@@
 %
-\itodo{We might wait for the final \simpeg results before jumping to conclusions; but generally, the NRMSD differences is below 1-2\,\%, except for large offsets.}
+The NRMSD is generally below a few percent, except for large offsets.
+An interesting feature is that the NRMSD between \emg3d and \simpeg is very low except at the boundary.
+The reason is that the codes use the same tensor mesh for modelling, but while \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
+\mycom[DW]{Lindsey, what about the different formulations we use?}
+\todo{expand the analysis of the Block Model -- any ideas / inputs?}
 
@@
   \petgem & 24 &    72 &  35.8 & 2455868 \\
-  \simpeg &  4 &  9993 & 280.6 & 4813216 \\ % nprocs: 1*4 threads
+  \simpeg &  4 & 10295 & 280.4 & 4813216 \\ % nprocs: 1*4 threads
   %
@@
 To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
-It is therefore an ideal case to verify our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
+It is therefore an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
 Additionally, that code is a time-domain code, whereas the four codes under consideration here compute the results all in the frequency-domain.
@@
 Even if modelling results may look completely valid, they could not be correct at all.
-Verifying the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
+Validating the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
 Overall, we observed an excellent match between all solutions.
@@
 
+\itodo{Discussion poins from Evert: How can you attribute differences to the solver? There are mesh element effects as well and the way Maxwell's equations are discretized plays a role too.}
+
 \section{Conclusions \& Outlook}
@@
 All comparisons exhibited an excellent reliability of the solutions.
-Our data should make it very easy for new codes to have a readily available data set to test against and verify.
+Our data should make it very easy for new codes to have a readily available data set to test against and validate.
 We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.

### 2020-09-29 manuscript/Manuscript.tex
Tetrahedra plots
Updates from Overleaf

@@
 All our scripts to reproduce the shown results are open-source.
+%
+\\~\\ \# \# Alternative \# \# \\
+Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
+This has changed over the last few years, and today there exists a selection of different open-source codes.
+Using four different codes in the Python ecosystem we model responses for three increasingly complex models.
+The verification of the results with semi-analytical solutions for a simple case as well as the validation between the codes and with results from the industry for more complex models show that the open-source codes are able to compute CSEM responses for challenging, large-scale models.
+Our comparison includes finite-element and finite-volume codes, using structured tensor and octree meshes as well as unstructured tetrahedra meshes.
+Our results show further that accurate responses can be obtained independently of the chosen method and the chosen mesh.
+The difficult part, however, is to appropriately discretize the model.
+The runtime and memory requirements, however, vary greatly between different codes.
+But we have found that much more time was spent on creating the appropriate input files than running the actual computation.
+We provide the three models and the corresponding responses of four codes, which can be used for verification of new and existing codes.
+The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further.
+We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
 \end{abstract}
@@
 
-The shown examples consider the geophysical problem of marine CSEM.
-However, the codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
-The current main applications of the different codes are mining (\custem), mining and environmental (\simpeg), oil and more recent medical and geothermal (\petgem), and
-oil, methane, and deep sea mining (\emg3d).
+The shown examples consider the geophysical problem of marine CSEM with resistive bodies.
+We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography looking for conductive bodies.
+The used codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
+The current main applications of the different codes are mining (\custem), mining and environmental (\simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
 

### 2020-10-02 manuscript/Manuscript.tex

@@
 \begin{abstract}
-% The (points) are from Mahrer (1993), Geophysics, Some Considerations When Abstracting; DOI: 10.1190/1.58010001.1
-% (1) principal objectives and scope of the work
-Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
-However, this has changed over the last few years, and today there exists a selection of different open-source codes which are up to the task.
-We have a closer look at four different ones, where in all cases at least the user-facing functionality is written in Python.
-% (2) methodology
-For the numerical comparison we use three models: a simple layered model; a model containing three resistive blocks in a layered background; and a complex, real-world resistivity model.
-All three models are vertically transverse isotropic.
-The analysis includes three different mesh-types, simple tensor meshes, octree meshes, and unstructured tetrahedral meshes.
-Two of the codes use finite volumes and the other two use finite elements.
-% (3) results
-The comparison shows that all four codes are able to compute the different models to sufficient precision.
-The biggest difference between codes is actually the discretization and the ease of creating a suitable mesh, particularly as that part often takes much more time than the actual computation.
-The required runtime and memory varies greatly between the codes.
-However, these depend mainly on the underlying solver, and not on the actual CSEM codes.
-% (4) conclusions
-The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further.
-We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
-All our scripts to reproduce the shown results are open-source.
-%
-\\~\\ \# \# Alternative \# \# \\
 Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
@@
 Using four different codes in the Python ecosystem we model responses for three increasingly complex models.
-The verification of the results with semi-analytical solutions for a simple case as well as the validation between the codes and with results from the industry for more complex models show that the open-source codes are able to compute CSEM responses for challenging, large-scale models.
-Our comparison includes finite-element and finite-volume codes, using structured tensor and octree meshes as well as unstructured tetrahedra meshes.
+We first verify the results with semi-analytical solutions for a simple case.
+Then we validate the responses of more complex models between the different codes and with results from the industry.
+These validations show that the open-source codes are able to compute CSEM responses for challenging, large-scale models.
+Our comparison includes finite-element and finite-volume codes using structured tensor and octree meshes as well as unstructured tetrahedra meshes.
 Our results show further that accurate responses can be obtained independently of the chosen method and the chosen mesh.
-The difficult part, however, is to appropriately discretize the model.
-The runtime and memory requirements, however, vary greatly between different codes.
+The runtime and memory requirements vary greatly based on the choice of iterative or direct solvers.
 But we have found that much more time was spent on creating the appropriate input files than running the actual computation.
+The challenging task is to appropriately discretize the model, independently of the chosen mesh and the chosen solver.
 We provide the three models and the corresponding responses of four codes, which can be used for verification of new and existing codes.
 The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further.
-We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
 \end{abstract}
@@
 \begin{itemize}
-    \item {\color{red}\bfseries This version is quite different from the previous you revised.
-However, from now on we do not expect too many changes.
-To make it easier for everyone to see the new changes please make sure that from now on "Track Changes" is always on in Overleaf.}
     \item Notes on orthography: I settled on discretize with a «z».
@@
 Is that fine or any other opinions?
-    \item We probably should be careful to not mention the actual code names too often. E.g., I removed them from the abstract.
-    \item I tried to avoid double reference.
-E.g., SciPy, MUMPS, pyGIMLi: I referenced them the first time they are mentioned, and not afterwards.
-Current exceptions: Miensopust et al., 2013, is cited twice.
     \item Regarding submission, {\color{red}\bfseries please let me know}:
@@
           \begin{itemize}
-            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM});
+            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \imycom[RR]{Agreed}
             \item Rune Mittet (domain knowledge; he will know what SBLwiz actually does, so it would be very interesting to have his feedback);
             \item Dimitry Avdeev and Ralph-Uwe Börner (they both did extensive 3D code overview/review papers in 2005 and 2010, respectively, and it would be interesting to get their feedback).
+\imycom[RR]{Strongly Agreed}
           \end{itemize}
@@
 (Either way, the reader can make a quick estimation in one or the other direction; important is that we are consistent throughout the paper.)
+    \imycom[RR]{Agreed.}
 \end{itemize}
@@
 The continuous improvement of computing power and the CSEM boom in the early 2000's in the hydrocarbon industry led to a wealth of developed numerical solutions and according publications.
-The most common applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
+The most commonly applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
 There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or octree meshes \citep{ECP.07.Haber}.
@@
 One reason why there are so many publications about this topic results from the variety of techniques to solve the systems of linear equations (SLE).
-They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
+They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
 The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GJI.16.Jaysaval}.
+
+% The remaining paragraphs should be shortened/condensed
 
@@
 
-It is becoming more common for researchers in many domains of science to release source-code with an open license that allows use and modification (e.g., see the Open Source Initiative approved licenses: \href{https://opensource.org/licenses}{opensource.org/licenses}).
+Today it is becoming more common for researchers in many domains of science to release source-code with an open license that allows use and modification (e.g., see the Open Source Initiative approved licenses: \href{https://opensource.org/licenses}{opensource.org/licenses}).
 This is an important step for improving reproducibility of research, «\emph{to provide the means by which the reader can verify the validity of the results and make use of them in further research}» \citep{GEO.17.Broggini}.
@@
 
-We discuss the topic of open-source developments with respect to 3D CSEM modelling.
-Even though it comprises still the minority of developments, the open-source landscape in this field of research changed in the last five years quite dramatically.
-Previously, there existed only closed-source codes owned by companies and consortia, or individual projects that were only available directly from the authors upon request.
-These codes often came without proper documentation.
-But more importantly, they also often came without a proper license, which essentially means that they are not open source (no license means legally speaking that, in most countries of the world, all rights are reserved by the author; see, for instance, the \emph{Berne Convention}).
+The open-source landscape in this field of research changed in the last five years quite dramatically.
 We introduce and compare four recent open-source projects with a focus on 3D CSEM modelling.
 All presented codes are in the Python ecosystem and use either the FV method on structured grids or the FE method on unstructured tetrahedral meshes.
-
-Furthermore, we deal with the topic of validation.
+As such, we address the topic of validation.
 Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
@@
 
-\itodo{Ones were ready check if we should introduce Maxwell's equations or not. Miensopust et al., 2013, for instance, do not touch on any equation.}
-
 \section{Codes}
@@
 Newer package-management systems such as \texttt{conda}, \texttt{docker}, or \texttt{pip} significantly supported us to make our codes easily available and installable on any of the major operating system without any user-side compilations.
-Each one can be downloaded and installed with a \mycom[DW]{I guess this statement is currently a bit of a stretch for \petgem, correct Octavio?}single command.
 
@@
 The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
-\imycom[DW]{I took out «the weak formulation of», as it actually doesn't apply to \emg3d. Please make sure that everything stated above («have in common that...») actually applies to your code.}
-
+\imycom[DW]{I took out «the weak formulation of», as it actually doesn't apply to \emg3d. Please make sure that everything stated above («have in common that...») actually applies to your code.
+\imycom[RR]{everything fits to custEM}
+}
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations PEC and PMC, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
@@
 I mention it in the emg3d-section, if you want you can mention it in the SimPEG section too.
-\tabl[btp]{codecomparison}{Comparison of the four codes under consideration.
+\tabl[bthp]{codecomparison}{Comparison of the four codes under consideration.
 Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}{
@@
 %
-\tabl[btp]{machines}{List of hardware, software, and operator with which the different codes were run.\itodo{Could everyone check if their RAM is GB or GiB?}}{
+\tabl[bthp]{machines}{List of hardware, software, and operator with which the different codes were run.\itodo{Could everyone check if their RAM is GB or GiB?}}{
   \centering
@@
 The toolbox considers generally anisotropic petrophysical properties.
-Even though changes of the conductivity is mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
+Even though changes of the conductivity are mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
 Recently, induced polarisation parameters in frequency-domain and three methods for simulating time-domain responses were added to \custem.
 The provided meshing tools are based on \texttt{TetGen} \citep{TOM.15.Si} and functionalities of \texttt{pyGIMLi} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
-
-The \custem toolbox is under steady development and maintenance.
-Future enhancements comprise adding iterative solution techniques, provided by \texttt{FEniCS}, as well as further functionalities for automatically incorporating intersecting bodies such as folds or faults in meshes.
-Furthermore, current work is on using \custem for inverse modelling applications.
 
@@
 It features now routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and also to obtain time-domain responses.
-The most recent development added the possibility to compute the responses for entire surveys, and also to compute the misfit and the gradient of the misfit function, and \emg3d is as such ready to be used in inversion schemes.
-
-For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem. Interoperability between \simpeg and \emg3d is therefore straightforward.
+For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem.
+Interoperability between \simpeg and \emg3d is therefore straightforward.
 
@@
 
-Based on the current state of the \petgem project, there are many possibilities to improve or to add additional features.
+% Octavio: We removed the outlook part, we did the same for custEM and emg3d. I hope that is OK.
+% Based on the current state of the \petgem project, there are many possibilities to improve or to add additional features.
 For instance, in the short-term, more modelling routines and support for multi-source set-ups will be implemented.
@@
 \subsection{SimPEG}
-
+\todo{Please condense SimPEG a bit; the other codes use about 200-240 words, SimPEG currently close to 400.}
 \simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
@@
 Please not that \emg3d and \simpeg used the same tensor mesh in this example.
-\imycom[DW]{Lindsey: A sentence why Tensor over OcTree.}
-\imycom[DW]{Raphael/Octavio: A sentence about the differences in the meshes of
-\custem and \petgem.}
+\imycom[DW]{Lindsey: A sentence why Tensor was chosen over OcTree here?}
 
 The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
-\imycom[DW]{Lindsey: A note about high RAM usage of \simpeg? About PARDISO or Mumps or similar. Could be used as a general note that it boils down to the underlying solver.}
 
 %
-\tabl[btp]{comp-layered}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}{
+\tabl[bthp]{comp-layered}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}{
   \centering
@@
 %
-The NRMSD is generally below a few percent, except for large offsets.
-An interesting feature is that the NRMSD between \emg3d and \simpeg is very low except at the boundary.
-The reason is that the codes use the same tensor mesh for modelling, but while \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
-\mycom[DW]{Lindsey, what about the different formulations we use?}
-\todo{expand the analysis of the Block Model -- any ideas / inputs?}
+
+There are a few noteworthy points:
+
+\begin{enumerate}
+  \item The error levels are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
+  \item The NRMSD between the FV codes \emg3d and \simpeg is very low except at the boundary.
+The generally very low NRMSD is because these codes use the same rectilinear mesh for modelling.
+The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
+  \item The FE codes \custem and petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
+\end{enumerate}
 
@@
 %
-\tabl[btp]{comp-block}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}{
+\tabl[bthp]{comp-block}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}{
   \centering
@@
 
+\imycom[RR]{@ Octavio: I think you use your own mesh here? Do you use the iterative solver in this example? otherwise, the values in the table do not make too much sense for me...}
+
 \subsection{Marlim R3D}
+
+\imycom[RR]{Is it possible to force a placement of the tables in the corresponding section? (every table is shifted to the next section, quite unituitive to correlate to the models)}
 
@@
 However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
+
+\imycom[RR]{I'd state point 1 at last (most obvious and least important in my opinion)}
 \begin{enumerate}
@@
 
+\imycom[RR]{The following paragraph is rather discussion content. Before, we mainly restricted to show data only with observations, I would keep this style also here}
 One might argue that 5-10\,\% NRMSD is a lot.
@@
 
+\imycom[RR]{Mostlyx redundant content to the information introduced before, I think this paragraph can be removed compeltely}
 However, even though the computational input model is know, we still do not know what the code SBLwiz exactly does inside.
@@
 \plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}
+\imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
 %
@@
 
+\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use?}
+\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use?}
 %
-\tabl[btp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
+\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
   \centering
@@
   %
-  \custem & 64 & 4984 & 558.5 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
+  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
   \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
@@
 %
+\imycom[RR]{tested some new mumps parameters, still no consistent benefit, but the best run was about 15\% faster now and slightly less memory required as I removed some unnecessary interpolation-varaiables overhead}
 
@@
 The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+\imycom[RR]{9M real valued vs.
+4.5M complex-valued, what is correct here?
+Anyway, we should also state that even emg3d uses 6M only for the same setup, so why did they (over?)discretized this model so excessively?}
+\imycom[DD]{Add a note that the custEM/PETGEM mesh can handle the entire survey, not just this inline/broadline.}
 
@@
 For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
+\imycom[RR]{maybe add also another important argument: Direct solvers ALWAYS solve solvable systems, whereas iterative solvers with suited preconditioners heavily rely on the matrix structure and condition caused influenced by resitivitiy distributions and cell/element sizes/shapes.
+This is in my opinion also the most important point why most of the recent unstructured FE papers use direct solvers (new real-world problem and your preconditioner might be completely useless even if it worked for your paper example - @ Octavio - can you confirm this thought or am I telling nonsense?}
 
@@
 
-It is worth noting that the reported runtime is just one of the aspects.
-But to generate an appropriate mesh, with all the testing involved, can easily take days of work.
+It is worth noting that the reported runtime is just one of the aspects, and we would like to emphasise that neither the runtime nor the memory consumption are at the core of this comparison, but the validation of the results.
+As such no special efforts were undertaken to minimise either, as this is an entire different task.
+Another aspect is to generate an appropriate mesh, with all the testing involved, can easily take days of work.
 As such the computation times becomes relative, and the ease of usability of a code has to be considered too.
@@
 The used codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
-The current main applications of the different codes are mining (\custem), mining and environmental (\simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
+The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
+\imycom[RR]{changed last sentence to mining + environmental for custEM (actually we will focus way more on gorund/salt water investigations now at LIAG)}
 
@@
 \itodo{Discussion poins from Evert: How can you attribute differences to the solver? There are mesh element effects as well and the way Maxwell's equations are discretized plays a role too.}
-
+ We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
 \section{Conclusions \& Outlook}
@@
 We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, including a modification with three resistive blocks, and the realistic marine Marlim R3D model.
-All comparisons exhibited an excellent reliability of the solutions.
-Our data should make it very easy for new codes to have a readily available data set to test against and validate.
+All comparisons exhibited an excellent reliability of the solutions.\imycom[RR]{reliability of overall $\approx$1\% misfit for layered and blocky test model and $\approx$10\% for realy world model.} Our data should make it very easy for new codes to have a readily available data set to test against and validate.
 We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
@@
 
-The development of \custem as part of the DESMEX project was funded by the Germany Ministry for Education and Research (BMBF) in the framework of the research and development program Fona-r4 under grant 033R130D.
+The development of \custem by R.R.
+as part of the DESMEX/DESMEX II projects was funded by the Germany Ministry for Education and Research (BMBF) in the framework of the research and development program Fona-r4 under grants 033R130D/033R130DN.
 

### 2020-10-02 manuscript/Manuscript.tex
Updates from Overleaf

@@
   \item The error levels are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
-  \item The NRMSD between the FV codes \emg3d and \simpeg is very low except at the boundary.
-The generally very low NRMSD is because these codes use the same rectilinear mesh for modelling.
+  \item The NRMSD between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
+The generally low NRMSD is because these codes use the same rectilinear mesh for modelling.
 The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
-  \item The FE codes \custem and petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
+  \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
+  \item The agreement within the same differential equation method (FE or FV) is better than across methods. 
 \end{enumerate}
@@
 \subsection{Marlim R3D}
-
-\imycom[RR]{Is it possible to force a placement of the tables in the corresponding section? (every table is shifted to the next section, quite unituitive to correlate to the models)}
 
@@
 However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
-
-\imycom[RR]{I'd state point 1 at last (most obvious and least important in my opinion)}
 \begin{enumerate}
-  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
-In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component.
-The published responses are not stable either, and therefore any of the responses is as bad as the other.
-Also, tiniest differences in meshing will have a huge effect here.
   \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
@@
 See the discussion around Figure~\ref{fig:results-marlim_survey}.
+  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
+In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component.
+The published responses are not stable either, and therefore any of the responses is as bad as the other.
+Also, tiniest differences in meshing will have a huge effect here.
 \end{enumerate}

### 2020-10-02 manuscript/Manuscript.tex
Incorporated all suggestions and ideas from Raphael.

@@
 To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
-It is therefore an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
-Additionally, that code is a time-domain code, whereas the four codes under consideration here compute the results all in the frequency-domain.
+It is therefore on one hand an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
+On the other hand it is impossible to reproduce it exactly, as it is a closed-source code and we cannot know exactly what was done internally.
+Additionally, that code is a time-domain code, including the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}, whereas the four codes under consideration here compute the results all in the frequency-domain.
 
@@
 
-The responses for all six frequencies, both inline and broadside, for all three electric components are shown in Figure~\ref{fig:results-marlim-responses}.
+The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside.
 The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
@@
 For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m.
-It can be seen that the grey lines are not visible for most parts, which means that the data agree very well.
+It can be seen that the grey lines are not visible for most parts, which means that the data agree well.
 However, there are a few notable points where this is not the case, and they are marked with numbers in the figure.
 \begin{enumerate}
-  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
-The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
   \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components.
@@
 See the discussion around Figure~\ref{fig:results-marlim_survey}.
+  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
+The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
+This explains their smooth behaviour, without saying anything about their accuracy.
   \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
@@
 
-Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
+Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
 %
@@
 Some NRMSD have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
-
-\imycom[RR]{The following paragraph is rather discussion content. Before, we mainly restricted to show data only with observations, I would keep this style also here}
-One might argue that 5-10\,\% NRMSD is a lot.
-We argue that this is probably as good as it gets, given that the code with which we compare is not open-source.
-This has been shown within the process of these results.
-Our first attempt were based on the originally published, fine MR3D model.
-This model is very detailed, but too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation.
-However, none of the codes were able to reproduce the published results.
-The reason is that there are many ways how you can extrapolate a model.
-We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model.
-It is only with this model that we were able to get comparable results, visually mostly the same as shown in Figure~\ref{fig:model-marlim}.
-
-\imycom[RR]{Mostlyx redundant content to the information introduced before, I think this paragraph can be removed compeltely}
-However, even though the computational input model is know, we still do not know what the code SBLwiz exactly does inside.
-From the information we have we know that it computes the data in the time domain transforming them afterwards to the frequency domain, and it includes the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}.
-All our codes, on the other hand, compute in the frequency domain and include the air layer in the model (putting the boundaries sufficiently far away).
 
@@
 
-The differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_entire} for the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
+The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_entire} for the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
 %
@@
 The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.
-\itodo{Write more once the other results are in the figures too.
-Points to compare: See if the different boundary conditions are visible.
-See and comment on the effects of the different, fast coarsening outside the domain of interest.}
+
+\itodo{We have to decide which figures to include, please state your preference:
+\imycom[DW]{I would go for at least two figures, probably 9 and 10 (in reversed order); in my opinion these are the most interesting figures, and I have never seen a comparison like this.}
+\imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
+}
+
 %
 \plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}
-\imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
-%
-\itodo{Most importantly, once all results are in the figures: Discuss about the effect of bathymetry, particularly on the $E_y$ field.
-Mark it with a number in the figure.
-Compare between the meshes.
-State that the results will not have a smaller NRMSD unless we know exactly how the bathymetry is treated.}
+
+The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model.
+At, e.g., two kilometers below the seafloor there are already significant changes visible, purely due to meshing.
+This is an important insight that has to be taken into account when interpreting inversion results.
 
 The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}.
-The memory requirement varies from $0.5-558.5\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).
+The memory requirement varies from $0.5-520\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).
 
@@
 %
-\imycom[RR]{tested some new mumps parameters, still no consistent benefit, but the best run was about 15\% faster now and slightly less memory required as I removed some unnecessary interpolation-varaiables overhead}
+\todo{Update nc-file of custEM for new CPU/RAM.}
 
 \section{Discussion}
-%
-% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
-%
-% In order to make your discussion section engaging, you should include the
-% following information:
-% - The major findings of your study
-% - The meaning of those findings
-% - How these findings relate to what others have done
-% - Limitations of your findings
-% - An explanation for any surprising, unexpected, or inconclusive results
-% - Suggestions for further research
-%
-% Your discussion should NOT include any of the following information:
-% - New results or data not presented previously in the paper
-% - Unwarranted speculation
-% - Tangential issues
-% - Conclusions not supported by your data
-%
+\imycom[DW]{Currently still a collection of discussions. Needs better structuring.}
 
@@
 Nevertheless, we are confident that many observations would hold in a similar manner for land-based, airborne, or mixed setups.
+
+For the MR3D results one might argue that 5-10\,\% NRMSD is a lot.
+We argue that this is probably as good as it gets, given that the code with which we compare is not open-source.
+This has been shown within the process of these results.
+Our first attempt were based on the originally published, fine MR3D model.
+This model is very detailed, but too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation.
+However, none of the codes were able to reproduce the published results.
+The reason is that there are many ways how you can extrapolate a model.
+We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model.
+It is only with this model that we were able to get comparable results, visually mostly the same as shown in Figure~\ref{fig:model-marlim}.
 
@@
 The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
-\imycom[RR]{9M real valued vs.
-4.5M complex-valued, what is correct here?
-Anyway, we should also state that even emg3d uses 6M only for the same setup, so why did they (over?)discretized this model so excessively?}
-\imycom[DD]{Add a note that the custEM/PETGEM mesh can handle the entire survey, not just this inline/broadline.}
+It is important to state that the FE mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and two source lines.
 
@@
 For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
-\imycom[RR]{maybe add also another important argument: Direct solvers ALWAYS solve solvable systems, whereas iterative solvers with suited preconditioners heavily rely on the matrix structure and condition caused influenced by resitivitiy distributions and cell/element sizes/shapes.
-This is in my opinion also the most important point why most of the recent unstructured FE papers use direct solvers (new real-world problem and your preconditioner might be completely useless even if it worked for your paper example - @ Octavio - can you confirm this thought or am I telling nonsense?}
+\imycom[RR]{maybe add also another important argument: Direct solvers ALWAYS solve solvable systems, whereas iterative solvers with suited preconditioners heavily rely on the matrix structure and condition caused influenced by resistivity distributions and cell/element sizes/shapes.
+This is in my opinion also the most important point why most of the recent unstructured FE papers use direct solvers (new real-world problem and your preconditioner might be completely useless even if it worked for your paper example - @ Octavio - can you confirm this thought or am I telling nonsense?
+\imycom[DW]{If this is true we should definitely include it. However, this is new to me (and I currently doubt it), we would need a reference confirming this.}
+}
 
@@
 The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
-\imycom[RR]{changed last sentence to mining + environmental for custEM (actually we will focus way more on gorund/salt water investigations now at LIAG)}
 
@@
 
-\itodo{Discussion poins from Evert: How can you attribute differences to the solver? There are mesh element effects as well and the way Maxwell's equations are discretized plays a role too.}
 We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
+
 \section{Conclusions \& Outlook}
-%
-% enago.com/academy/discussion-conclusion-know-difference-drafting-manuscript/
-%
-% Your conclusion should:
-% - Restate your hypothesis or research question
-% - Restate your major findings
-% - Tell the reader what contribution your study has made to the existing
-%   literature
-% - Highlight any limitations of your study
-% - State future directions for research/recommendations
-%
-% Your conclusion should NOT:
-% - Introduce new arguments
-% - Introduce new data
-% - Fail to include your research question
-% - Fail to state your major results
-%
+\imycom[DW]{Not really conclusions, but a mix with discussions. Make pure conclusions.}
 
-We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, including a modification with three resistive blocks, and the realistic marine Marlim R3D model.
-All comparisons exhibited an excellent reliability of the solutions.\imycom[RR]{reliability of overall $\approx$1\% misfit for layered and blocky test model and $\approx$10\% for realy world model.} Our data should make it very easy for new codes to have a readily available data set to test against and validate.
+We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, a model containing three resistive blocks, and the realistic marine Marlim R3D model.
+All comparisons exhibited an excellent reliability of the solutions, in the order of $\approx1\,\%$ misfit for the layered and the block model, and $\approx10\,\%$ for the real world model.
+Our data should make it very easy for new codes to have a readily available data set to test against and validate.
 We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.

### 2020-10-09 manuscript/Manuscript.tex

@@
       \begin{itemize}
-        \item If you think the \textbf{order of authors} should be different. The last thing we want in this collaboration is that someone feels unhappy about that.
-        \item If you have \textbf{another manuscript under revision with GJI}. When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI.
+        \item If you think the \textbf{order of authors} should be different.
+The last thing we want in this collaboration is that someone feels unhappy about that: \itodo{No comment from RR; OCR said OK}
+        \item If you have \textbf{another manuscript under revision with GJI}.
+When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI: \itodo{No comments from Raphael; Octavio}
         \item For the submission I will create a \textbf{new repository on swung-research}.
@@
 Please let me know if you would prefer to commit your files yourself as a PR instead.
+        \imycom[OCR]{I have no problem with showing the entire history of the repo (in some way it could justify the way of working collaboratively that is discussed in the abstract), but I would also agree to create a new repo.
+        \imycom[DW]{This is actually a good idea, if everyone is up for it. I think we should have a quick call before submitting, and discuss these little points so everyone is happy.}
+        }
         \item \textbf{Wanted and not wanted reviewers:} Let me know if you have any names for these.
@@
           \begin{itemize}
-            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \imycom[RR]{Agreed}
+            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \itodo{RR and QCR agreed}
             \item Rune Mittet (domain knowledge; he will know what SBLwiz actually does, so it would be very interesting to have his feedback);
             \item Dimitry Avdeev and Ralph-Uwe Börner (they both did extensive 3D code overview/review papers in 2005 and 2010, respectively, and it would be interesting to get their feedback).
-\imycom[RR]{Strongly Agreed}
+\itodo{RR and QCR agreed}
           \end{itemize}
@@
 Publications regarding three-dimensional (3D) modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
-These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient EM measurements \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient electromagnetic (EM) measurements  \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
 \cite{B.SEG.88.Ward} assemble many of these solutions in \emph{Electromagnetic Theory for Geophysical Applications}, which is widely viewed as an authoritative publication on electromagnetic geophysics.
@@
 The continuous improvement of computing power and the CSEM boom in the early 2000's in the hydrocarbon industry led to a wealth of developed numerical solutions and according publications.
-The most commonly applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RSC.94.Mackie, RS.94.Druskin, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
+The most commonly applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RS.94.Druskin, RSC.94.Mackie, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
 There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or octree meshes \citep{ECP.07.Haber}.
@@
 \imycom[RR]{everything fits to custEM}
+\imycom[OCR]{ok for petgem}
 }
@@
 Another abbreviation used in the tables is dof for degree of freedom, which is equivalent to the size of the SLE we are solving.
-Finally, we use \emph{runtime} as the wall time or elapsed real time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
+Finally, we use runtime as the wall time or elapsed real time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
 Note that the actual computation or CPU time is therefore much higher than the reported runtime for the codes that run in parallel.
@@
        & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
-  License & GPL-3.0 & Apache-2.0 & GPL-3.0 & MIT \\
+  License & GPL-3.0 & Apache-2.0 & BSD 3-Clause & MIT \\
   Installation & \texttt{conda}
@@
 \petgem is a parallel code for frequency-domain 3D CSEM data for marine and land surveys.
-The high-order edge FE method (HEFEM) is used for the discretization of the governing equations in its diffusive form.
-This technique provides a suitable mechanism to obtain stable numerical solutions as well as a good trade-off between number of dof and computational effort.
+The high-order edge FE method (HEFEM) is used to discretize the governing equations in its diffusive form.
+This technique provides a suitable mechanism to obtain stable numerical solutions and a good trade-off between the number of dof and computational effort.
 The current implementation supports up to sixth-order tetrahedral vector basis functions.
-Moreover, because the HEFEM belongs to the FE family, the unstructured meshes can be used efficiently on complex geometries, e.g., models with topography and bathymetry.
+Moreover, because the HEFEM belongs to the FE family, the unstructured meshes can be used efficiently on complex geometries (e.g., models with topography and bathymetry).
 
@@
 For the parallel forward modelling computations, a highly scalable MPI (message passing interface) domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
-This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing architectures).
+This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing (HPC) architectures).
 
@@
 
-We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and to compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, tensor, octree) in different scenarios.
+We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, tensor, octree) in different scenarios.
 The first model is an anisotropic layered model, which can be compared to semi-analytical solutions.
-The layered model serves also as background model for the second validation, where we add three resistive blocks into the subsurface.
-The final comparison is based on the realistic, anisotropic marine model MR3D, which is an open resistivity model which comes with computed CSEM responses.
+The layered model also serves as background model for the second validation, where we add three resistive blocks into the subsurface.
+The final comparison is based on the realistic, anisotropic marine model MR3D.
+It is an open resistivity model which comes with computed CSEM responses.
 
@@
   \item The error plots of the real and imaginary responses are  dominated by the zero-crossings, which blows the error up as is the nature of the relative error formula, it has no real-world implications.
-  \item However, it can be seen from the absolute-values errors that the error is generally in the order of 1\,\% or less.
+  \item However, it can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.
   \item The relative errors close to the source are getting huge, particularly for the inline receivers and particularly for the results of \emg3d and \simpeg.
@@
   \emg3d  &  1 &   116 &   0.4 & 4813216 \\
-  \petgem & 24 &    90 &  34.2 & 2455868 \\
+  \petgem & 24 &   252 & 151.7 & 2455868 \\
   \simpeg &  4 & 10089 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
@@
   \emg3d  &  1 &   115 &   0.4 & 4813216 \\
-  \petgem & 24 &    72 &  35.8 & 2455868 \\
+  \petgem & 24 &    238 &  152.8 & 2455868 \\
   \simpeg &  4 & 10295 & 280.4 & 4813216 \\ % nprocs: 1*4 threads
@@
 %
-
-\imycom[RR]{@ Octavio: I think you use your own mesh here? Do you use the iterative solver in this example? otherwise, the values in the table do not make too much sense for me...}
 
@@
 \imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
+\imycom[OCR]{I also suggest keeping only figure 9. The rest provide little details/specifications}
 }
@@
 %
-\todo{Update nc-file of custEM for new CPU/RAM.}
+\itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}
 
@@
 Overall, we observed an excellent match between all solutions.
-The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation.
+The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation strategy.
 Considering this satisfactory result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
@@
 Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
-The p2 FE solution required only $\approx$9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+The p2 FE solution required only $\approx$9\,M dof \todo{Update this number if we decide compute the fields for the new FE mesh} instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
 It is important to state that the FE mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and two source lines.
 
-The codes under consideration use direct and indirect solvers.
+The codes under consideration use direct and iterative solvers.
 In general, the biggest advantage of iterative solvers with appropriate preconditioners are the comparatively small memory requirements.
@@
 \imycom[DW]{If this is true we should definitely include it. However, this is new to me (and I currently doubt it), we would need a reference confirming this.}
-}
+\imycom[OCR]{I agree entirely with @Raphael.
+The reality is that most FE papers use direct solvers because there is no iterative solver that is capable of offering good convergence and scalability.
+Most iterative solvers (petsc for example) are general purpose and are not adapted to deal with the particularities imposed by the CSEM problem, therefore they offer the "best effort" approach (depending on user experience, model, computational architecture) .
+Perhaps the easiest way to justify this point is to review the recent literature and verify that the majority of FE discretizations use direct solvers.}}
 
@@
 The used codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
-The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent medical and geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
+The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
 
@@
 Within \custem, cell-wise resistivity interpolation was added for this work, multi-layer subsurface topography was the first time applied as well as first time reciprocity modelling, and also improved mesh design (resolution, refinement, etc.).
+Within \petgem, this work has promoted the inclusion of magnetic field computation, improving the generation of adapted meshes based on a semi-automatic approach that reduces user intervention.
+Also added was the continuous integration functionality and improved its test suite.
 

### 2020-10-09 manuscript/Manuscript.tex

@@
 %
-\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.}
+\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.
+(Vertical exaggeration: 5.45)}
 
 The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model.
-At, e.g., two kilometers below the seafloor there are already significant changes visible, purely due to meshing.
+At, e.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing.
 This is an important insight that has to be taken into account when interpreting inversion results.
@@
 
-\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use?}
-\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use?}
+\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use? (Vertical exaggeration: 1.33)}
+\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use? (Vertical exaggeration: 4.0)}
 %
@@
   \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
-  \petgem & 96 & 3527 & 437.8 & 4539474 \\
+  \petgem & 96 &  524 & 175.4 & 1918106 \\
   \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads

### 2020-10-11 model-block/custEM/export_netcdf.py
final custem changes and results and performance data, tested on independent system with custEM version 0.99.16
performance data hard copied from original architecture (slightly faster)

@@ -22,8 +22,11 @@ import numpy as np
 ds = xr.load_dataset('../block_model_and_survey.nc', engine='h5netcdf')
 lines = ['l1m_line_x', 'l2m_line_x', 'l3m_line_x']
 
+runtimes = ['118 s', '158 s']
+memory = ['97.8 GiB', '115.9 GiB']
+
 # export everything to netcdf
-for p in ['1', '2']:
+for p in ['2']:
     for model in ['layered', 'block']:
 
         # load interpolated modeling results on observation line
@@ -49,9 +52,9 @@ for p in ['1', '2']:
                  P.line_data['t3_E_t'][:, 0].imag]).ravel('F') 
     
         # Add info
-        ds.attrs['runtime'] = str(int(P.solution_time)) + ' s'
-        ds.attrs['n_procs'] = P.mpi_procs * P.omp_threads
-        ds.attrs['max_ram'] = f"{P.max_mem :5.1f} GiB"
+        ds.attrs['runtime'] = runtimes
+        ds.attrs['n_procs'] = '24'
+        ds.attrs['max_ram'] = memory
         ds.attrs['n_cells'] = P.cells
         ds.attrs['n_nodes'] = P.nodes
         ds.attrs['n_dof'] = P.dof
@@ -66,8 +69,8 @@ for p in ['1', '2']:
         ds.attrs['version'] = "custEM v" + ce.__version__
         ds.attrs['date'] = datetime.today().isoformat()
  
-        # These are quasi final results
-        ds.attrs['NOTE'] = 'Quasi final'
+        # These are final results
+        ds.attrs['NOTE'] = 'final'
     
         # Save it under <{model}_{code}_{p}.nc>
         code = 'custEM_p' + p

### 2020-10-11 model-block/custEM/mesh_layered.py

@@ -14,39 +14,6 @@ from custEM.meshgen.meshgen_tools import BlankWorld
 import numpy as np
 
 
-# ######################### mesh for p1 computations ######################## #
-
-# Define refinement-paths around receiver lcoations
-points = np.concatenate((
-    mu.line_x(-1e4, 1e4, n_segs=100, y=-3e3),
-    mu.line_x(-1e4, 1e4, n_segs=100),
-    mu.line_x(-1e4, 1e4, n_segs=100, y=3e3)))
-rx = mu.refine_rx(points, 1., 30.)
-
-# create world
-M = BlankWorld(name='layered_earth_p1',
-               m_dir='./meshes',
-               x_dim=[-3e4, 3e4],
-               y_dim=[-3e4, 3e4],
-               z_dim=[-5e4, 5e4],
-               preserve_edges=True)
-
-# include water surface
-M.build_surface()
-
-# build halfspace mesh and extend 2D surface mesh to 3D world
-M.build_layered_earth_mesh(4, [-600., -850., -3150.],
-                           insert_struct=rx)
-
-# add transmitter in water layer at -550 m depth
-M.add_tx(mu.line_x(-100., 100., n_segs=10, z=-550.))
-
-M.there_is_always_a_bigger_world(10., 10., 10.)
-
-# call TetGen
-M.call_tetgen(tet_param='-pq1.2aA', export_vtk=True)
-
-
 # ######################### mesh for p2 computations ######################## #
 
 # Define refinement-paths around receiver lcoations
@@ -79,3 +46,37 @@ M.there_is_always_a_bigger_world(10., 10., 10.)
 
 # call TetGen
 M.call_tetgen(tet_param='-pq1.6aA', export_vtk=True)
+
+
+# ######################### mesh for p1 computations ######################## #
+
+# Define refinement-paths around receiver lcoations
+points = np.concatenate((
+    mu.line_x(-1e4, 1e4, n_segs=100, y=-3e3),
+    mu.line_x(-1e4, 1e4, n_segs=100),
+    mu.line_x(-1e4, 1e4, n_segs=100, y=3e3)))
+rx = mu.refine_rx(points, 1., 30.)
+
+# create world
+M = BlankWorld(name='layered_earth_p1',
+               m_dir='./meshes',
+               x_dim=[-3e4, 3e4],
+               y_dim=[-3e4, 3e4],
+               z_dim=[-5e4, 5e4],
+               preserve_edges=True)
[…]

### 2020-10-11 model-block/custEM/run_block.py

@@ -60,5 +60,5 @@ for p in [2, 1]:
                             n_segs=100, line_name='l3m')
 
     for line in ['l1m_line_x', 'l2m_line_x', 'l3m_line_x']:
-        M.IB.interpolate('E_t', line)
+        M.IB.interpolate(line, 'E_t')
     M.IB.synchronize()  # synchronize all processes after interpolation

### 2020-10-11 model-block/custEM/run_layered.py

@@ -55,5 +55,5 @@ for p in [2, 1]:
                             n_segs=100, line_name='l3m')
 
     for line in ['l1m_line_x', 'l2m_line_x', 'l3m_line_x']:
-        M.IB.interpolate('E_t', line)
+        M.IB.interpolate(line, 'E_t')
     M.IB.synchronize()  # synchronize all processes after interpolation

### 2020-10-11 model-block/custEM/export_netcdf.py
Update to final custEM results

@@ -27,7 +27,7 @@ memory = ['97.8 GiB', '115.9 GiB']
 
 # export everything to netcdf
 for p in ['2']:
-    for model in ['layered', 'block']:
+    for mm, model in enumerate(['layered', 'block']):
 
         # load interpolated modeling results on observation line
         mod = 'p' + str(p)
@@ -37,28 +37,28 @@ for p in ['2']:
             mesh = 'block_model_p' + p
 
         P = PlotFD(mod=mod, mesh=mesh, approach='E_t', r_dir='./results')
-        for i, line in enumerate(lines):            
+        for i, line in enumerate(lines):
             P.import_line_data(line, key='t' + str(i+1), EH='E')
 
         # save the three lines
         ds.line_1.data = np.vstack(
-                [P.line_data['t1_E_t'][:, 0].real, 
-                 P.line_data['t1_E_t'][:, 0].imag]).ravel('F') 
+                [P.line_data['t1_E_t'][:, 0].real,
+                 P.line_data['t1_E_t'][:, 0].imag]).ravel('F')
         ds.line_2.data = np.vstack(
-                [P.line_data['t2_E_t'][:, 0].real, 
-                 P.line_data['t2_E_t'][:, 0].imag]).ravel('F') 
+                [P.line_data['t2_E_t'][:, 0].real,
+                 P.line_data['t2_E_t'][:, 0].imag]).ravel('F')
         ds.line_3.data = np.vstack(
-                [P.line_data['t3_E_t'][:, 0].real, 
-                 P.line_data['t3_E_t'][:, 0].imag]).ravel('F') 
-    
+                [P.line_data['t3_E_t'][:, 0].real,
+                 P.line_data['t3_E_t'][:, 0].imag]).ravel('F')
+
         # Add info
-        ds.attrs['runtime'] = runtimes
+        ds.attrs['runtime'] = runtimes[mm]
         ds.attrs['n_procs'] = '24'
-        ds.attrs['max_ram'] = memory
+        ds.attrs['max_ram'] = memory[mm]
         ds.attrs['n_cells'] = P.cells
         ds.attrs['n_nodes'] = P.nodes
         ds.attrs['n_dof'] = P.dof
-        ds.attrs['extent'] = ("x = -100000 - 100000; " 
+        ds.attrs['extent'] = ("x = -100000 - 100000; "
                               "y = -100000 - 100000; "
                               "z = -100000 - 100000")
[…]

### 2020-10-11 manuscript/Manuscript.tex
Updates from Overleaf

@@
   %
-  \custem & 24 &   118 &  97.8 & 1530808 \\ % dof: 3061616 / 2 (Real+Imag -> Complex)
+  \custem & 24 &   118 &  97.8 & 1531824 \\ % dof: 3063648 / 2 (Real+Imag -> Complex)
   \emg3d  &  1 &   116 &   0.4 & 4813216 \\
@@
   %
-  \custem & 24 &   158 & 115.9 & 1654242 \\ % dof: 3308484 / 2  (Real+Imag -> Complex)
+  \custem & 24 &   158 & 115.9 & 1646736 \\ % dof: 3293472 / 2  (Real+Imag -> Complex)
   \emg3d  &  1 &   115 &   0.4 & 4813216 \\
@@
   %
-  \custem & 64 & 4034 & 522.7 & 4539474 \\ % dof: 9078948 / 2 (Real+Imag -> Complex)
+  \custem & 64 &  872 & 230.1 & 1918106 \\ % dof: 3836212 / 2 (Real+Imag -> Complex)
   \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
@@
 \itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}
+
+\paragraph{TODOs:}
+Figure \ref{fig:results-marlim_allmodels} is just added; integrate properly. Also, the following info should be integrated:
+\begin{itemize}
+    \item Model interpolation: \simpeg and \emg3d use volume averaging on log10(rho)-space; \custem and \petgem use linear interpolation on log10(rho)-space.
+    \item Fields interpolation: \simpeg uses ???\mycom[DW]{Lindsey, what did you use in the end?}; \emg3d uses spline interpolation; the FE codes custEM and PETGEM use the second-order basis functions for the interpolation within elements.
+\end{itemize}
+\plot*{results-marlim_allmodels}{width=\textwidth}{TODO}
 

### 2020-10-12 manuscript/Manuscript.tex
Updates from Overleaf

@@
 %     manuscript,
-%     twocolumn,
-%     twoside,
+     twocolumn,
+     twoside,
 %     revised,
@@
 \begin{abstract}
-Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) responses used to be feasible only for large companies and research consortia.
+Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) surveys used to be feasible only for large companies and research consortia.
 This has changed over the last few years, and today there exists a selection of different open-source codes.
-Using four different codes in the Python ecosystem we model responses for three increasingly complex models.
-We first verify the results with semi-analytical solutions for a simple case.
-Then we validate the responses of more complex models between the different codes and with results from the industry.
+Using four different codes in the Python ecosystem, we perform simulations for increasingly complex models.
+We first verify the results with semi-analytical solutions for a simple layered model.
+Then we validate the responses of a more complex block model between the different codes.
+Finally we compare the responses of a real world model with results from the industry.
 These validations show that the open-source codes are able to compute CSEM responses for challenging, large-scale models.
-Our comparison includes finite-element and finite-volume codes using structured tensor and octree meshes as well as unstructured tetrahedra meshes.
-Our results show further that accurate responses can be obtained independently of the chosen method and the chosen mesh.
+Our comparison includes finite-element and finite-volume codes using structured rectilinear and octree meshes as well as unstructured tetrahedral meshes.
+Accurate responses can be obtained independently of the chosen method and the chosen mesh.
 The runtime and memory requirements vary greatly based on the choice of iterative or direct solvers.
-But we have found that much more time was spent on creating the appropriate input files than running the actual computation.
-The challenging task is to appropriately discretize the model, independently of the chosen mesh and the chosen solver.
-We provide the three models and the corresponding responses of four codes, which can be used for verification of new and existing codes.
-The collaboration of four code maintainer trying to achieve the same task brought in the end all four codes a significant step further.
+However, we have found that much more time was spent on creating the appropriate input files than running the actual computation.
+The challenging task is, irrespective of the chosen code, to appropriately discretize the model.
+We provide three models, each with their corresponding discretization and responses of four codes, which can be used for validation of new and existing codes.
+The collaboration of four code maintainers trying to achieve the same task brought in the end all four codes a significant step further.
+This includes improved meshing and interpolation capabilities, resulting in shorter runtimes for the same accuracy.
+We hope that these results may be useful for the CSEM community at large, and we invite and encourage the community to make more codes, modelling scripts, and results publicly available.
 \end{abstract}
@@
 \begin{itemize}
-    \item Notes on orthography: I settled on discretize with a «z».
+    \item Notes on orthography: As we submit to GJI it should be British English.
+But I settled on discretize with a «z».
 My dictionary says that discreti{\color{red}\bfseries z}e is AE and discreti{\color{red}\bfseries s}e is BE, but that «z» is also used in BE in mathematical contexts.
 Is that fine or any other opinions?
+    \imycom[LJH]{discretize is good with me}
     \item Regarding submission, {\color{red}\bfseries please let me know}:
@@
         \item If you think the \textbf{order of authors} should be different.
-The last thing we want in this collaboration is that someone feels unhappy about that: \itodo{No comment from RR; OCR said OK}
+The last thing we want in this collaboration is that someone feels unhappy about that: \itodo{No comment from RR; OCR said OK, LJH: +1 looks good to me :)}
         \item If you have \textbf{another manuscript under revision with GJI}.
-When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI: \itodo{No comments from Raphael; Octavio}
+When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI: \itodo{No comments from Raphael; Octavio, No from Lindsey}
         \item For the submission I will create a \textbf{new repository on swung-research}.
@@
         \imycom[DW]{This is actually a good idea, if everyone is up for it. I think we should have a quick call before submitting, and discuss these little points so everyone is happy.}
+        \imycom[LJH]{+1, fine by me to transfer the whole repo over with git history (either way is fine by me) }
         }
@@
           \begin{itemize}
-            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \itodo{RR and QCR agreed}
+            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \itodo{RR and QCR and LJH agreed}
             \item Rune Mittet (domain knowledge; he will know what SBLwiz actually does, so it would be very interesting to have his feedback);
@@
 
-The 3D CSEM code \emg3d is a multigrid solver \citep{CMMP.64.Fedorenko} for electromagnetic diffusion following \cite{GP.06.Mulder}, with tri-axial electrical anisotropy, isotropic electric permittivity, and isotropic magnetic permeability.
-The matrix-free solver can be used as main solver, or alternatively as preconditioner for one of the Krylov subspace methods implemented in SciPy.
+The 3D CSEM code \emg3d is a multigrid solver \citep{CMMP.64.Fedorenko} for electromagnetic diffusion following \cite{GP.06.Mulder}, including tri-axial electrical anisotropy.
+The matrix-free solver can be used as main solver, or as preconditioner for one of the Krylov subspace methods implemented in SciPy.
 The governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalisation of a Yee grid.
@@
 
-As such the code is, contrary to the other three, primarily a solver, which solves the Maxwell's equation for a single frequency and a single, electric source.
-However, recent developments added functionalities such that \emg3d can be used directly as a more general EM modeller too.
-It features now routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and also to obtain time-domain responses.
+As such the code is primarily a solver, which solves Maxwell's equations for a single frequency and a single, electric source.
+Recent developments added functionalities such that \emg3d can be used directly as a more general EM modeller too.
+It features now routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses.
 For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem.
-Interoperability between \simpeg and \emg3d is therefore straightforward.
 
@@
 \subsection{SimPEG}
-\todo{Please condense SimPEG a bit; the other codes use about 200-240 words, SimPEG currently close to 400.}
+\todo{Please condense SimPEG a bit; the other codes use about 190-220 words, SimPEG currently roughly 350.}
 \simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
@@
 
-Meshes and finite volume differential operators are implemented in the \discretize package, which currently includes tensor, octree, cylindrical, and logically rectangular meshes.
+Meshes and finite volume differential operators are implemented in the \discretize package, which currently includes rectilinear, octree, cylindrical, and logically rectangular meshes.
 Each mesh type inherits from a common structure and uses the same naming conventions for methods and properties.
@@
 
-We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, tensor, octree) in different scenarios.
+We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, rectilinear, octree) in different scenarios.
 The first model is an anisotropic layered model, which can be compared to semi-analytical solutions.
@@
 
-Please not that \emg3d and \simpeg used the same tensor mesh in this example.
-\imycom[DW]{Lindsey: A sentence why Tensor was chosen over OcTree here?}
+Please not that \emg3d and \simpeg used the same rectilinear mesh in this example.
+\imycom[DW]{Lindsey: A sentence why a rectilinear mesh was chosen over octree here?}
 
@@
 
-The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_entire} for the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
+The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_medium} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
+The dimension of the computational domain varies for the different meshes:
+% emg3d:         x = 327 to 454 km; z =  -57 to 83 km
+% SimPEG:        x = 288 to 492 km; z = -123 to 41 km
+% custEM/PETGEM: as shown in the image (+/- 25 km)
+\plot*{results-marlim_medium}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row).
+The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.
+(Vertical exaggeration: 1.1.)}
 %
-\plot*{results-marlim_entire}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the entire computational domain.}
-%
-The top rows show the tensor mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem.
+The top rows show the rectilinear mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem.
 The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.
 
-\itodo{We have to decide which figures to include, please state your preference:
-\imycom[DW]{I would go for at least two figures, probably 9 and 10 (in reversed order); in my opinion these are the most interesting figures, and I have never seen a comparison like this.}
-\imycom[RR]{only keep this figure in my opinion (Figure 9), remove 8, 10 \& 11. One figure should be enough for an illustrative field and mesh representation.}
-\imycom[OCR]{I also suggest keeping only figure 9. The rest provide little details/specifications}
-}
-
 %
-\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a tensor mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.
-(Vertical exaggeration: 5.45)}
+\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.
+(Vertical exaggeration: 4.1.)}
 
@@
 
-\plot*{results-marlim_medium}{width=\textwidth}{Additional zoom “medium”; which ones should we use? (Vertical exaggeration: 1.33)}
-\plot*{results-marlim_small}{width=\textwidth}{Additional zoom “small”; which ones should we use? (Vertical exaggeration: 4.0)}
 %
@@
 %
-\itodo{Update nc-file of custEM and PETGEM for new CPU/RAM.}
 
@@
 \end{itemize}
-\plot*{results-marlim_allmodels}{width=\textwidth}{TODO}
+\plot*{results-marlim_allmodels}{width=\textwidth}{TODO (Vertical exaggeration: 3.6.)}
 
@@
 Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
-The p2 FE solution required only $\approx$9\,M dof \todo{Update this number if we decide compute the fields for the new FE mesh} instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+\imycom[DW]{Rethink the previous and next phrases. Correa could have chosen a different discretization. Also, OcTree uses even less cells, so this statement is wrong.}
+The p2 FE solution required only $\approx$1.9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
 It is important to state that the FE mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and two source lines.
@@
 In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d.
-Even though not shown here, direct solvers exhibit their strongest advantage in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain.
+Even though not shown here, direct solvers exhibit their strongest advantage, besides stability, in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain.
 As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d.
 For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
-\imycom[RR]{maybe add also another important argument: Direct solvers ALWAYS solve solvable systems, whereas iterative solvers with suited preconditioners heavily rely on the matrix structure and condition caused influenced by resistivity distributions and cell/element sizes/shapes.
-This is in my opinion also the most important point why most of the recent unstructured FE papers use direct solvers (new real-world problem and your preconditioner might be completely useless even if it worked for your paper example - @ Octavio - can you confirm this thought or am I telling nonsense?
-\imycom[DW]{If this is true we should definitely include it. However, this is new to me (and I currently doubt it), we would need a reference confirming this.}
-\imycom[OCR]{I agree entirely with @Raphael.
-The reality is that most FE papers use direct solvers because there is no iterative solver that is capable of offering good convergence and scalability.
-Most iterative solvers (petsc for example) are general purpose and are not adapted to deal with the particularities imposed by the CSEM problem, therefore they offer the "best effort" approach (depending on user experience, model, computational architecture) .
-Perhaps the easiest way to justify this point is to review the recent literature and verify that the majority of FE discretizations use direct solvers.}}
 
@@
 
-All files to rerun the different models with the four codes and reproduce the shown results are available at \dots.
-\itodo{Put up on Zenodo, link here.}
+All files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
+For the review process we refer to the github page \href{https://github.com/prisae/3d-csem-open-source-landscape}{github.com/prisae/3d-csem-open-source-landscape}.
 

### 2020-10-12 manuscript/Manuscript.tex

@@
 %     manuscript,
-     twocolumn,
-     twoside,
+%     twocolumn,
+%     twoside,
 %     revised,
@@
 
-The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_medium} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
+The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_big} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
 The dimension of the computational domain varies for the different meshes:
@@
 % custEM/PETGEM: as shown in the image (+/- 25 km)
-\plot*{results-marlim_medium}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row).
-The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.
-(Vertical exaggeration: 1.1.)}
+\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row).
+The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
 %
@@
 %
-\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain.
-(Vertical exaggeration: 4.1.)}
+\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain (3$\times$ vertical exaggeration).}
 
@@
 \end{itemize}
-\plot*{results-marlim_allmodels}{width=\textwidth}{TODO (Vertical exaggeration: 3.6.)}
+\plot*{results-marlim_allmodels}{width=\textwidth}{TODO (3$\times$ vertical exaggeration).}
 
@@
 
-We would like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
+We had help of several colleagues for different tasks, and would therefore like to thank Bane Sullivan (plotting of tetrahedra in matplotlib through PyVista), Seogi Kang (octree meshes), \mycom[DW]{please add if someone helped with something}.
+We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
 

### 2020-10-13 manuscript/Manuscript.tex
Incorporating new resistivity figure.

@@
   \footnotemark[1]TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL);\\
-  \footnotemark[2]Leibniz Institut for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE);\\
+  \footnotemark[2]Leibniz Institute for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE);\\
   \footnotemark[3]Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES);\\
@@
 \newpage
-\itodo{\hfill$\Downarrow$\hfill$\Downarrow$\hfill List of things ToDo, Notes, etc\hfill$\Downarrow$\hfill$\Downarrow$\hfill~}
+\subsection*{Discussed items re manuscript}
 \begin{itemize}
-    \item Notes on orthography: As we submit to GJI it should be British English.
-But I settled on discretize with a «z».
-My dictionary says that discreti{\color{red}\bfseries z}e is AE and discreti{\color{red}\bfseries s}e is BE, but that «z» is also used in BE in mathematical contexts.
-Is that fine or any other opinions?
-    \imycom[LJH]{discretize is good with me}
-    \item Regarding submission, {\color{red}\bfseries please let me know}:
-      \begin{itemize}
-        \item If you think the \textbf{order of authors} should be different.
-The last thing we want in this collaboration is that someone feels unhappy about that: \itodo{No comment from RR; OCR said OK, LJH: +1 looks good to me :)}
-        \item If you have \textbf{another manuscript under revision with GJI}.
-When submitting to GJI one has to indicate when you have other manuscripts currently under review with GJI: \itodo{No comments from Raphael; Octavio, No from Lindsey}
-        \item For the submission I will create a \textbf{new repository on swung-research}.
-The idea is to make a single, new commit with everything (without the git history, for various reasons).
-Please let me know if you would prefer to commit your files yourself as a PR instead.
-        \imycom[OCR]{I have no problem with showing the entire history of the repo (in some way it could justify the way of working collaboratively that is discussed in the abstract), but I would also agree to create a new repo.
-        \imycom[DW]{This is actually a good idea, if everyone is up for it. I think we should have a quick call before submitting, and discuss these little points so everyone is happy.}
-        \imycom[LJH]{+1, fine by me to transfer the whole repo over with git history (either way is fine by me) }
-        }
-        \item \textbf{Wanted and not wanted reviewers:} Let me know if you have any names for these.
-I do not have any \emph{not wanted}, but I do have a few I will put on the \emph{wanted} list, mainly people I would be interested to have their feedback and that have knowledge about 3D modelling:
-          \begin{itemize}
-            \item Kerry Key (domain knowledge with \texttt{MARE3DEM}, also experience with open-sourcing with \texttt{MARE2DEM}); \itodo{RR and QCR and LJH agreed}
-            \item Rune Mittet (domain knowledge; he will know what SBLwiz actually does, so it would be very interesting to have his feedback);
-            \item Dimitry Avdeev and Ralph-Uwe Börner (they both did extensive 3D code overview/review papers in 2005 and 2010, respectively, and it would be interesting to get their feedback).
-\itodo{RR and QCR agreed}
+  \item Orthography: BE for GJI; using discretize.
+  \item Author order is fine by everyone.
+  \item Everyone is responsible that the info of their codes is correct (machine info, runtime, memory, dof, etc) and agrees with the info in the \texttt{*.nc}-files.
+  \item The runtime in the table is real-world time. So actual computation time is roughly `nprocs x runtime`; also, nprocs includes processes and threads.
+  \item Regarding submission:
+    \begin{description}
+      \item[Current submission] RR, OCR, LH have no submission with GJI currently.
+      \item[History] We will keep all git history.
+      \item[Repo] \href{https://github.com/swung-research/3d-csem-open-source-landscape/}{github.com/swung-research/3d-csem-open-source-landscape}.
+      \item[Suggested reviewers] We suggest the following reviewers, mainly because they have the relevant experience and it would be interesting for us to have their feedback: \emph{Kerry Key} (domain knowledge as developer of \texttt{MARE3DEM}); \emph{Rune Mittet} (domain knowledge; he will know what SBLwiz actually does); \emph{Dimitry Avdeev} and \emph{Ralph-Uwe Börner} (both did extensive 3D code overview/review papers in 2005 and 2010, respectively).
+    \end{description}
 \end{itemize}
-      \end{itemize}
-    \item  {\color{red}\bfseries Everyone: Please ensure that the tables have the correct info:}
-      \begin{enumerate}
-          \item machine info;
-          \item runtime;
-          \item memory;
-          \item nproc;
-          \item dof.
-      \end{enumerate}
-    I got all the info out of the ".nc" files, so make sure you wrote the correct info into the nc-files. Further notes:
-      \begin{description}
-        \item[runtime] Should only include the wall time (or elapsed real time, \href{https://en.wikipedia.org/wiki/Elapsed_real_time}{wikipedia.org/\-wiki/\-Elapsed\-\_real\-\_time}) of solving the SLE, for ALL frequencies (in \emg3d some frequencies are slower than others, but in any case, we report the sum of all of them); any pre-/postprocessing such as mesh generation or model interpolation can be ignored.
-        \item[memory] It should be the maximum memory increase when solving the SLE (again, ignoring any pre-/postprocessing).
-Again, of all frequencies.
-In \emg3d some frequencies require more RAM than others (more iterations), but we only report the "worst", the heaviest consumer.
-        \item[nproc] Not sure we reached agreement on Slack, but I took no everything in here (threads and (virtual) processes); please note here if you think it should be different.
-        \item[dof] Similarly, not sure we reached agreement on Slack. I put it here now for complex value, hence halving the dof of custEM. Again, please write here if we should change it.
-    \end{description}
-    We could discuss if we should report CPU time instead (hence summing all parallel processes); but I think for the user of interest is the real-world time, how long do I have to wait, so I think it is good as we do it now.
-(Either way, the reader can make a quick estimation in one or the other direction; important is that we are consistent throughout the paper.)
-    \imycom[RR]{Agreed.}
-\end{itemize}
-\itodo{\hfill$\Uparrow$\hfill$\Uparrow$\hfill List of things ToDo, Notes, etc\hfill$\Uparrow$\hfill$\Uparrow$\hfill~}
-\newpage
 
@@
 
-Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geo-hazards.
+Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geohazards.
 Modelling these electromagnetic fields is therefore of great interest to design survey layouts, to understand the measured data, and for inversion purposes.
@@
 The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
-\imycom[DW]{I took out «the weak formulation of», as it actually doesn't apply to \emg3d. Please make sure that everything stated above («have in common that...») actually applies to your code.
-\imycom[RR]{everything fits to custEM}
-\imycom[OCR]{ok for petgem}
-}
-A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations PEC and PMC, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
-Another abbreviation used in the tables is dof for degree of freedom, which is equivalent to the size of the SLE we are solving.
-Finally, we use runtime as the wall time or elapsed real time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
-Note that the actual computation or CPU time is therefore much higher than the reported runtime for the codes that run in parallel.
+
+A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
+Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving.
+Finally, we use \emph{runtime} as the wall time or elapsed real-world time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
+Note that the actual computation time or CPU time is therefore much higher than the reported runtime for the codes that run in parallel, with an upper limit of \#Procs$\times$Runtime.
 Memory refers to the maximum memory increase at any point of solving the SLE.
@@
        & \href{https://docs.simpeg.xyz}{simpeg.xyz} \\
-  License & GPL-3.0 & Apache-2.0 & BSD 3-Clause & MIT \\
+  License & GPL-3.0 & Apache-2.0 & BSD-3-Clause & MIT \\
   Installation & \texttt{conda}
@@
 
-% Octavio: We removed the outlook part, we did the same for custEM and emg3d. I hope that is OK.
-% Based on the current state of the \petgem project, there are many possibilities to improve or to add additional features.
-For instance, in the short-term, more modelling routines and support for multi-source set-ups will be implemented.
-For the long-term, the obvious next step is to move to 3D CSEM data inversion.
+\subsection{SimPEG}
 
-\subsection{SimPEG}
 \todo{Please condense SimPEG a bit; the other codes use about 190-220 words, SimPEG currently roughly 350.}
@@
 The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces.
-%(for an overview of discretizing Maxwell's equations, we recommend \cite{B.SIAM.14.Haber}).
 There are two different discretization strategies implemented for Maxwell's equations: (I) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (II) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces.
@@
 The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
-For the computation the model is upscaled to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
+The model was upscaled for the computation to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
 Both the full model and the upscaled computational model are released openly.
@@
 45 source-towlines were located on the same grid above each receiver line, 50\,m above the seafloor, with shots every 100\,m.
-The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original paper for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km).
+The computed responses for one of the receivers, \texttt{04Rx251a}, are shown in the original publication for the East-West inline-source \texttt{04Tx013a} and the East-West broadside-source \texttt{04Tx014a} (broadside offset of 1\,km).
 We reproduce the responses for this receiver and corresponding source-lines in our comparison.
@@
 The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside.
-The published responses are shown in color (and with markers), and the responses from our codes are shown beneath in grey colours in this overview plot.
+The published responses are shown in colour with markers for the frequency, and the responses from our codes are shown beneath in grey colours in this overview plot.
 %
 \plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines).
-The grey lines under the coloured lines are not visible in most areas, meaning they are very similar.
+The grey lines under the coloured lines are not visible in most areas, meaning that they are very similar.
 However, there are three notable zones, (1) to (3), which are explained further in the text.}
 %
-Two datasets were published, one containing clean responses, and one where realistic noise was added.
+Two data-sets were published, one containing clean responses, and one where realistic noise was added.
 For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m.
@@
 \begin{enumerate}
-  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components.
-The differences are related to the bathymetry.
-And the reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally.
+  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components, which are related to the bathymetry.
+The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally.
 See the discussion around Figure~\ref{fig:results-marlim_survey}.
@@
   \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
-In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here come from 3D effects, but they are very low, roughly two orders of magnitude lower than the $E_x$ component.
+In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here comes from 3D effects.
+These responses are very low, roughly two orders of magnitude lower than the $E_x$ component.
 The published responses are not stable either, and therefore any of the responses is as bad as the other.
-Also, tiniest differences in meshing will have a huge effect here.
+Also, tiniest differences in meshing will have a huge effect here, as well as the boundary condition of the air-water interface of the published results.
 \end{enumerate}
 
+As there is no \emph{true} solution we cannot verify the results, but validate by different results using the NRMSD.
+It is important to not that not the published results nor any of our results is correct, but the closer they agree with each other the more certain we can be of the outcomes.
 Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
@@
 %
-A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less, particularly for the inline $E_x$ component it is only a few \% or less.
-In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., negative offsets in the inline and broadside $E_x$ responses, in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
-Some NRMSD have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
+A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less.
+In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
+Some NRMSDs have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
 
@@
 \plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
-Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.}
+Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
+This also shows that the biggest impart in 3D forward modelling comes from the discretization.}
 %
@@
 The reason is simple: \custem and \petgem use the exactly same mesh for the computation, the only difference is therefore the solver.
-As they are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same.
+This exemplifies that the big difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result.
+As these two are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same.
 But in general the NRMSDs between our codes look similar as in the comparison with the published results, which is due to the different meshes in use.
 
-The actual differences in meshing is shown in the next two figures, in Figure~\ref{fig:results-marlim_big} for almost the entire computational domain, and in Figure~\ref{fig:results-marlim_survey} a zoom-in to the survey domain, the domain of interest.
-The dimension of the computational domain varies for the different meshes:
-% emg3d:         x = 327 to 454 km; z =  -57 to 83 km
-% SimPEG:        x = 288 to 492 km; z = -123 to 41 km
-% custEM/PETGEM: as shown in the image (+/- 25 km)
-\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row).
+The actual differences in meshing is shown in the next two figures.
+Figure~\ref{fig:results-marlim_big} shows on the top row the rectilinear mesh of \emg3d, on the middle row the octree mesh of \simpeg, and on the bottom row the tetrahedral mesh of \custem and \petgem.
+The actual mesh, the broadside $|E_x|$ field, and the broadside $|E_y|$ field are shown in the left, middle, and right columns, respectively.
+The extent of the plot includes the entire computational domain for the tetrahedral mesh; the rectilinear and octree mesh extents are larger (rectilinear: $x=327$ to 454\,km, $z=-57$ to 83\,km; octree: $x=288$ to 492\,km, $z=-123$ to 41\,km).
+%
+\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for the rectilinear mesh / \emg3d (top row), octree mesh / \simpeg (middle row), and tetrahedra mesh / \custem \& \petgem (bottom row).
 The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
 %
-The top rows show the rectilinear mesh of \emg3d, the middle rows the octree mesh of \simpeg, and the bottom rows the tetrahedra mesh of \custem and \petgem.
-The actual mesh, the $|E_x|$ field, and the $|E_y|$ field are shown in the left, middle, and right columns, respectively.
+This figure is interesting for various points: The differences between the different meshes are very obvious.
+Particularly the advantage of octree and tetrahedra, which can create huge cells at the boundary to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
+The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.
 
+Figure~\ref{fig:results-marlim_survey} shows a zoom-in to the survey domain, the domain of interest, which shows how the different codes discretized the zones of interest.
 %
-\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for a rectilinear mesh (top row), octree mesh (middle row), and tetrahedra mesh (bottom row) for the survey domain (3$\times$ vertical exaggeration).}
-
+\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for the rectilinear mesh / \emg3d (top row), octree mesh / \simpeg (middle row), and tetrahedra mesh / \custem \& \petgem (bottom row) (3$\times$ vertical exaggeration).}
+%
 The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model.
-At, e.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing.
+E.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing.
 This is an important insight that has to be taken into account when interpreting inversion results.
@@
 The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}.
-The memory requirement varies from $0.5-520\,$GiB, and the runtime from roughly 7\,min to 1h\,23\,min, where the codes were run on very different machines from servers to supercomuters (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel).
-
+The memory requirement varies from $0.5-230\,$GiB, and the runtime from roughly 7\,min to 20\,min, where the codes were run on very different machines from servers to supercomputers (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel.
 %
@@
 
-\paragraph{TODOs:}
-Figure \ref{fig:results-marlim_allmodels} is just added; integrate properly. Also, the following info should be integrated:
-\begin{itemize}
-    \item Model interpolation: \simpeg and \emg3d use volume averaging on log10(rho)-space; \custem and \petgem use linear interpolation on log10(rho)-space.
-    \item Fields interpolation: \simpeg uses ???\mycom[DW]{Lindsey, what did you use in the end?}; \emg3d uses spline interpolation; the FE codes custEM and PETGEM use the second-order basis functions for the interpolation within elements.
-\end{itemize}
-\plot*{results-marlim_allmodels}{width=\textwidth}{TODO (3$\times$ vertical exaggeration).}
+The actual discretized resistivity model of the three mesh types are shown in Figure~\ref{fig:results-marlim_allmodels}.
+%
+\plot*{results-marlim_allmodels}{width=\textwidth}{The resistivity model as obtained from the three different discretizations using rectilinear, octree, and tetrahedral meshes (3$\times$ vertical exaggeration).}
+%
+The models where obtained using volume averaging (\emg3d, \simpeg) and linear interpolation (\custem, \petgem) on $\log_{10}{\rho}$ values.
+The actual responses at the receivers (field interpolation) are obtained by spline interpolation (\emg3d), ???\mycom[DW]{Lindsey, what did you use in the end?} (\simpeg), and through the second-order basis functions (\custem, \petgem).
 
@@
 
-We had help of several colleagues for different tasks, and would therefore like to thank Bane Sullivan (plotting of tetrahedra in matplotlib through PyVista), Seogi Kang (octree meshes), \mycom[DW]{please add if someone helped with something}.
+We had help of several colleagues for different tasks, and would therefore like to thank Bane Sullivan (plotting of tetrahedra meshes in matplotlib through PyVista), Seogi Kang (creation of octree meshes), \dots\mycom[DW]{please add if someone helped with something}.
 We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.

### 2020-10-18 manuscript/Manuscript.tex
Merged first round of inputs from Lindsey.

@@
   \footnotemark[4]University of California Berkeley, Department of Statistics (USA).\\
-  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org};\\
-  \textbf{Keywords}: CSEM, Open-Source, 3D modelling, FV, FE.
+  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org}.
 }
@@
 Using four different codes in the Python ecosystem, we perform simulations for increasingly complex models.
-We first verify the results with semi-analytical solutions for a simple layered model.
-Then we validate the responses of a more complex block model between the different codes.
+We first verify the computed fields with semi-analytical solutions for a simple layered model.
+Then we validate the responses of a more complex block model by comparing results obtained from each code.
 Finally we compare the responses of a real world model with results from the industry.
-These validations show that the open-source codes are able to compute CSEM responses for challenging, large-scale models.
+These validations show that the open-source codes are able to compute comparable CSEM responses for challenging, large-scale models.
 Our comparison includes finite-element and finite-volume codes using structured rectilinear and octree meshes as well as unstructured tetrahedral meshes.
-Accurate responses can be obtained independently of the chosen method and the chosen mesh.
+Accurate responses can be obtained independently of the chosen method and the chosen mesh type.
 The runtime and memory requirements vary greatly based on the choice of iterative or direct solvers.
-However, we have found that much more time was spent on creating the appropriate input files than running the actual computation.
+However, we have found that much more time was spent on designing the mesh and setting up the simulations than running the actual computation.
 The challenging task is, irrespective of the chosen code, to appropriately discretize the model.
@@
 This includes improved meshing and interpolation capabilities, resulting in shorter runtimes for the same accuracy.
-We hope that these results may be useful for the CSEM community at large, and we invite and encourage the community to make more codes, modelling scripts, and results publicly available.
+%
+% https://academic.oup.com/DocumentLibrary/GJI/gji%20keyword%20list%20updated2017.pdf
+\\[1cm] \textbf{Keywords}: Controlled source electromagnetics (CSEM), Numerical modelling, Electrical properties
 \end{abstract}
@@
 
-Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various geophysical exploration fields, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geohazards.
+Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various areas of geophysical exploration, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geohazards.
 Modelling these electromagnetic fields is therefore of great interest to design survey layouts, to understand the measured data, and for inversion purposes.
-Publications regarding three-dimensional (3D) modelling in electromagnetic methods started to appear as early as the 1970's and 1980's.
-These early publications were integral equation (IE) methods, having an anomaly embedded within a layered medium, mostly for loop-loop type transient electromagnetic (EM) measurements  \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
+Publications regarding three-dimensional (3D) modelling in electromagnetic (EM) methods started to appear as early as the 1970's and 1980's.
+These early publications were integral equation (IE) methods for simulating an anomaly embedded within a layered medium, mostly for loop-loop type transient EM measurements  \citep{GJI.74.Raiche, GEO.75.Hohmann, GJI.82.Das, GEO.86.Newman} and magnetotelluric (MT) measurements \citep{GEO.84.Wannamaker}.
 \cite{B.SEG.88.Ward} assemble many of these solutions in \emph{Electromagnetic Theory for Geophysical Applications}, which is widely viewed as an authoritative publication on electromagnetic geophysics.
 
-In the 1990's, computer became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
-This symposium resulted eventually in the book \emph{Three-Dimensional Electromagnetics} by the SEG \citep{B.SEG.99.Oristaglio}, and another book by \cite{B.02.Wannamaker} with the exactly same title came out only three years later.
+In the 1990's, computers became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
+This symposium resulted eventually in the book \emph{Three-Dimensional Electromagnetics} \citep{B.SEG.99.Oristaglio}, and another book by \cite{B.02.Wannamaker} with the exactly same title came out only three years later.
 Often cited publications from that time are \cite{RSC.94.Mackie} for 3D MT computation; \cite{RS.94.Druskin} for frequency- and time-domain modelling using a Yee grid and a global Krylov subspace approximation; and \cite{RS.96.Alumbaugh, GJI.97.Newman} for low-to-high frequency computation on massively parallel computers.
@@
 
-Very well written overviews about the different approaches to 3D EM modelling are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
+Very well written overviews about the different approaches to 3D EM modelling (and inversion) are given by \cite{SG.05.Avdeev} and \cite{SG.10.Borner}.
 But there was also a tremendous publications output with regards to 3D EM modelling in the last 10-15 years, at least partly driven by the ever increasing computing power.
@@
 The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GJI.16.Jaysaval}.
-
-% The remaining paragraphs should be shortened/condensed
 
@@
 In the aforementioned review on EM modelling and inversion Dmitry Avdeev concludes with the following statement: «\emph{The most important challenge that faces the EM community today is to convince software developers to put their 3-D EM forward and inverse solutions into the public domain, at least after some time.
-This would have a strong impact on the whole subject and the developers would benefit from feedback regarding the real needs of the end-users.}» Further, \cite{EXG.19.Oldenburg} argue that an open-source paradigm has the potential to accelerate multidisciplinary research by encouraging the development of modular, interoperable tools that are supported by a community of researchers.
+This would have a strong impact on the whole subject and the developers would benefit from feedback regarding the real needs of the end-users.}» Similarly, \cite{EXG.19.Oldenburg} argue that an open-source paradigm has the potential to accelerate multidisciplinary research by encouraging the development of modular, interoperable tools that are supported by a community of researchers.
 
@@
 
-The open-source landscape in this field of research changed in the last five years quite dramatically.
-We introduce and compare four recent open-source projects with a focus on 3D CSEM modelling.
+The open-source landscape in the field of 3D CSEM modelling changed in the last five years quite dramatically, and here we introduce and compare four recent open-source projects.
 All presented codes are in the Python ecosystem and use either the FV method on structured grids or the FE method on unstructured tetrahedral meshes.
-As such, we address the topic of validation.
+Having different codes which use different methods and different meshes is ideal to address the topic of validation.
 Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
-Beyond these simple models, the only objective possibility to ensure the accuracy of solutions is by comparing results from different modellers.
+The only objective possibility to ensure the accuracy of solutions beyond these simple models is by comparing results from different modellers.
 If different discretizations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
-\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of magnetotelluric forward and inversion codes, but we are not aware of any comparable study or benchmark suite for CSEM data.
-This is, to the best of our knowledge, the first comparison exercise for CSEM codes.
+\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of MT forward and inversion codes, but we are not aware of any comparable comparison study or benchmark suite for CSEM data.
 We hope our efforts help to ensure the reliability of simulations for any new or existing, open-source or closed-source 3D CSEM project.
@@
 All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{NAT.20.Harris} and \texttt{SciPy} \citep{NM.20.Virtanen}.
-The four of them are not just open-source but follow the open model of development, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+The four of them follow the open model of development, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
 All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
-Newer package-management systems such as \texttt{conda}, \texttt{docker}, or \texttt{pip} significantly supported us to make our codes easily available and installable on any of the major operating system without any user-side compilations.
+Newer package-management systems such as \texttt{conda}, \texttt{docker}, or \texttt{pip} simplify installation for all of these codes on any major operating system
 
-In the following, we provide a quick overview of the codes.
+We briefly present our codes in this section.
 It is, however, beyond the scope of this article to go into every detail of the different modellers, and we refer to their documentations for more details.
-An overview comparison of the different codes is given in Table~\ref{tbl:codecomparison}.
-All codes have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
+An overview comparison of the codes is given in Table~\ref{tbl:codecomparison}.
+All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
 The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
-
-A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor and perfect magnetic conductor, respectively.
+A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
+% ($\vec{n}\times\vec{E} = 0; \vec{n}\cdot\vec{H} = 0$)
+and perfect magnetic conductor%
+% ($\vec{n}\cdot\vec{E} = 0; \vec{n}\times\vec{H} = 0$)
+, respectively.
 Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving.
@@
 
-% Lindsey, I leave the SciPy solvers out.
-You mention that in practice they are not often used.
-emg3d can also use those solvers, and then multigrid is used as preconditioner.
-However, we cite SciPy, and as you say, SimPEG mostly uses PARDISO or MUMPS.
-To keep it simply I think we can leave SciPy out on the solver side.
-I mention it in the emg3d-section, if you want you can mention it in the SimPEG section too.
 \tabl[bthp]{codecomparison}{Comparison of the four codes under consideration.
@@
   %
-  Home & \href{https://custem.rtfd.io}{custem.rtfd.io}
+  Website & \href{https://custem.rtfd.io}{custem.rtfd.io}
           & \href{https://empymod.github.io}{empymod.github.io}
@@
 %
-\tabl[bthp]{machines}{List of hardware, software, and operator with which the different codes were run.\itodo{Could everyone check if their RAM is GB or GiB?}}{
+\tabl[bthp]{machines}{List of hardware, software, and operator with which the different codes were run.}{
   \centering
@@
 The 3D CSEM code \emg3d is a multigrid solver \citep{CMMP.64.Fedorenko} for electromagnetic diffusion following \cite{GP.06.Mulder}, including tri-axial electrical anisotropy.
-The matrix-free solver can be used as main solver, or as preconditioner for one of the Krylov subspace methods implemented in SciPy.
+The matrix-free solver can be used as main solver or as preconditioner for one of the Krylov subspace methods implemented in SciPy.
 The governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalisation of a Yee grid.
@@
 
-\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyse the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type, among others).
+\petgem permits to locate the source and receivers anywhere in the computational domain (e.g., sediments, seafloor, sea, ground), allowing to analyse the physical environment of the electric responses and how parameters impact them (e.g., frequency, conductivity, dependence on mesh setup, basis order, solver type).
 Furthermore, \petgem implements a semi-adaptive mesh strategy ($hp$ mesh refinement) based on physical parameters and on polynomial order to satisfy quality criteria chosen by the user.
@@
 
-\todo{Please condense SimPEG a bit; the other codes use about 190-220 words, SimPEG currently roughly 350.}
 \simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
-Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, electromagnetics (time and frequency, controlled and natural sources such as magnetotellurics), and fluid flow (Richards equation).
-It is a community driven project that aims to support researchers and \mycom[DW]{I added «and practitioners», as I think «support researchers» downplays the fact that \simpeg is used by various companies as well\dots}practitioners by providing a flexible, extensible framework and to facilitate integration of data sets from a variety of geophysical methods, including joint inversions \citep{GJI.20.Astic}, by providing a common interface to each method.
+Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, EM (time and frequency, as well as natural sources), and fluid flow.
+It is a community driven project that aims to support researchers and practitioners by providing a flexible, extensible framework, and common interface to a variety of geophysical methods.
 
@@
 The electromagnetic implementations use a staggered grid finite volume approach where physical properties are discretized at cell centres, fields on cell edges and fluxes on cell faces.
-There are two different discretization strategies implemented for Maxwell's equations: (I) the EB-formulation, which discretizes the electric field ($\vec{e}$) on cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (II) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell edges and the current density ($\vec{j}$) on cell faces.
-The physical properties electrical conductivity / resistivity and magnetic permeability are discretized in both cases at cell centres.
+There are two different discretization strategies implemented for Maxwell's equations: (I) the EB-formulation, which discretizes the electric field ($\vec{e}$) and the magnetic flux density ($\vec{b}$) and (II) the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) and the current density ($\vec{j}$).
 Having multiple implementations allows for testing that compares results from each approach, as well as the representation of both electrical and magnetic sources on cylindrically symmetric meshes.
 \simpeg supports variable magnetic permeability and full-tensor anisotropy for the physical properties.
-
 \simpeg interfaces to various solvers including \texttt{PARDISO} and \texttt{MUMPS}, and also to some implemented in SciPy.
-For problems with many sources (e.g.
-airborne EM), \simpeg contains machinery for domain-decomposition approaches; see for example \cite{GEO.20.Fournier}.
 
@@
 
-We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FD) and different mesh types (unstructured tetrahedra, rectilinear, octree) in different scenarios.
+We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FV) and different mesh types (unstructured tetrahedra, rectilinear, octree) in different scenarios.
 The first model is an anisotropic layered model, which can be compared to semi-analytical solutions.
@@
 The layered (1D) model consists of an upper halfspace of air ($\rho_\text{air}=\num{e8}\,\ohmm$), a 600\,m deep water layer ($\rho_\text{sea}=\num{0.3}\,\ohmm$), followed by a 250\,m thick, isotropic layer of 1\,\ohmm, a 2.3\,km thick, anisotropic (vertical transverse isotropy, VTI) layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive, isotropic basement consisting of a lower halfspace of $1000\,\ohmm$.
-The survey consists of a 200\,m long and 800\,A strong source at a single position with frequency $f=1\,$Hz, and three receiver lines of 101 receivers each.
-The centre of the $x$-directed source is at $x=y=0\,$m, 50\,m above the seafloor.
+The survey uses a 200\,m long, 800\,A source  with frequency $f=1\,$Hz at a single position, and three receiver lines of 101 receivers each.
+The centre of the $x$-oriented source is at $x=y=0\,$m, 50\,m above the seafloor.
 The $x$-directed receivers are placed on the seafloor every 200\,m from $x=-10\,$km to $x=+10\,$km in three lines with $y=-3; 0; +3\,$km.
@@
 A layered model fails to show the strength of 3D modellers, and in reality one would not choose a 3D code to compute responses for a layered model.
-However, it is one of the few examples that can be compared to semi-analytical results, and is therefore still a valuable test.
-All layered-model responses are compared to results computed with the semi-analytical code \empymod\citep{GEO.17.Werthmuller}.
-
-Figure~\ref{fig:results-layered} shows the result of the layered model verification, where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values).
-The top row shows the actual, semi-analytically computed responses, and the second and the third rows show the relative error (in percent) of the inline and the broadside receivers, respectively (note that for the 1D case the two broadside lines for $y=\pm3\,$km are identical).
+However, it is one of the few examples that can be verified with semi-analytical results, and is therefore still a valuable test.
+The results are shown in Figure~\ref{fig:results-layered}, where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values).
+The top row shows the actual, semi-analytically computed responses, for which we used \empymod\citep{GEO.17.Werthmuller}.
+The second and the third row show the relative percentage error of the inline and the broadside receivers, respectively; note that for the 1D case the two broadside lines for $y=\pm3\,$km are identical.
 
 %
-\plot*{results-layered}{width=\textwidth}{Inline and broadside responses (top row) for the layered model.
-The relative error of the four 3D modellers are shown in the second and the third row for the inline and broadside responses, respectively.}
+\plot*{results-layered}{width=\textwidth}{Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
+The relative percentage error of the four 3D modellers are shown in the second and the third row for the inline and broadside responses, respectively.}
 %
@@
 \begin{enumerate}
-  \item The error plots of the real and imaginary responses are  dominated by the zero-crossings, which blows the error up as is the nature of the relative error formula, it has no real-world implications.
-  \item However, it can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.
-  \item The relative errors close to the source are getting huge, particularly for the inline receivers and particularly for the results of \emg3d and \simpeg.
-These comparably huge errors are caused by a too coarse discretization around the source.
-They could be significantly reduced by choosing a finer discretization, at the cost of increased computation time.
-  \item The relative error of the responses from \custem and \petgem, on the hand, are relatively big at large offsets, particularly for the inline real responses.
+  \item The error of the real and imaginary responses are dominated by their zero-crossings, which blows up the error as is the nature of the relative error formula, it has no real-world implications.
+  \item It can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.
+  \item The errors become substantial towards zero offset, particularly for the results of the FV codes.
+These comparably significant errors could be significantly reduced by choosing a finer discretization around the source, at the cost of increased computation time.
+  \item The error of the responses from the FE codes, on the hand, are relatively big at large offsets, particularly for the inline real responses.
 This has, again, its origin in the chosen discretization.
 The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretization.
-Therefore, the FE codes only extend this thin layer up to 30\,km for the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
-This approximation significantly reduced the problem size compared to considering the layered-earth geometry for the whole computational domain.
+Therefore, the FE codes only extend this thin layer up to 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
+This approximation significantly reduces the problem size compared to considering the layered-earth geometry for the whole computational domain.
 \end{enumerate}
 
-Please not that \emg3d and \simpeg used the same rectilinear mesh in this example.
-\imycom[DW]{Lindsey: A sentence why a rectilinear mesh was chosen over octree here?}
+Note that \emg3d and \simpeg used the same rectilinear mesh in this example.
+The use of an octree mesh in \simpeg could greatly reduce the size of the mesh and resultant computation time, but at the cost of accuracy, which is reduced when averaging over layer interfaces to coarsen cells and because of the factor-of-two expansion rate of coarsened cells.
+As the aim of this study is to focus on accuracy of the simulations and compare discretization approaches, we chose to use the same mesh as in the \emg3d simulation.
 
@@
 
-There are no (semi-)analytical solutions for such a model.
-We therefore use the normalised root-mean square difference (NRMSD) between the results of different codes, where the NRMSD of two responses $R_1$ and $R_2$ is given by
+There are no semi-analytical solutions for such a model to verify our results, and we can only validate them by comparing different results.
+For this we use the normalised root-mean square difference (NRMSD) between two responses $R_1$ and $R_2$, given by
 %
@@
 
-The results for the three receiver lines $y=-3,0,+3\,$km are shown in the left, middle, and right columns of Figure~\ref{fig:results-block}, respectively.
+The results for the three receiver lines $y=-3;0;+3\,$km are shown in the left, middle, and right columns of Figure~\ref{fig:results-block}, respectively.
 The top row shows the result of \emg3d, as an example, and the bottom row shows the NRMSDs between the absolute responses of the codes.
 %
-\plot*{results-block}{width=\textwidth}{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the NRMSDs (\%) between the absolute responses ($|E_x|$) of the different codes are shown in the bottom row.}
+\plot*{results-block}{width=\textwidth}{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the NRMSDs (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
 %
@@
 \begin{enumerate}
-  \item The error levels are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
+  \item The error levels between the different codes are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
   \item The NRMSD between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
 The generally low NRMSD is because these codes use the same rectilinear mesh for modelling.
-The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition.
+The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition in this example.
   \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
@@
 To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
-It is therefore on one hand an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
+It is therefore, on one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
 On the other hand it is impossible to reproduce it exactly, as it is a closed-source code and we cannot know exactly what was done internally.
-Additionally, that code is a time-domain code, including the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}, whereas the four codes under consideration here compute the results all in the frequency-domain.
+Additionally, that code is a time-domain code obtaining the frequency-domain responses through a transform, and it includes the air layer via a non-local boundary condition at the water-air interface \citep{GEO.10.Mittet}.
+We compute all the results in this study in the frequency domain, where we model the entire domain including the air layer by putting the boundaries of the computational domain far away.
 
@@
 \begin{enumerate}
-  \item There are some noticeable differences in the positive offsets of the broadside $E_y$ and $E_z$ components, which are related to the bathymetry.
+  \item There are some noticeable differences for positive offsets of the broadside $E_y$ and $E_z$ components, which are likely related to the bathymetry.
 The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally.
 See the discussion around Figure~\ref{fig:results-marlim_survey}.
-  \item The highest three frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
+  \item The three highest frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
 The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
@@
 The published responses are not stable either, and therefore any of the responses is as bad as the other.
-Also, tiniest differences in meshing will have a huge effect here, as well as the boundary condition of the air-water interface of the published results.
+Also, tiniest differences in meshing or different interpolation algorithms will have a huge effect here, as well as the boundary condition of the air-water interface of the published results.
 \end{enumerate}
 
-As there is no \emph{true} solution we cannot verify the results, but validate by different results using the NRMSD.
-It is important to not that not the published results nor any of our results is correct, but the closer they agree with each other the more certain we can be of the outcomes.
+It is important to note that note the published results nor any of our results is correct, but the closer they agree with each other the more certain we can be of the outcomes.
 Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
@@
 %
-A few general conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less.
-In some cases the regular meshes with \emg3d and \simpeg have a smaller NRMSD, such as, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in some cases the unstructured tetrahedral meshes with \custem and \petgem have a smaller NRMSD, such as, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
-Some NRMSDs have an interesting step-pattern, which is more pronounced for \emg3d and \simpeg than for \custem and \petgem; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
+A few conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less.
+The structured meshes have in some cases a smaller NRMSD, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in other cases the unstructured tetrahedral meshes, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
+Some NRMSDs have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
 
@@
 \plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
-Good visible is that \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
-This also shows that the biggest impart in 3D forward modelling comes from the discretization.}
+\custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
+This also shows that the biggest impact in 3D forward modelling comes from the discretization.}
 %
@@
 The reason is simple: \custem and \petgem use the exactly same mesh for the computation, the only difference is therefore the solver.
-This exemplifies that the big difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result.
+This exemplifies that the biggest difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result.
 As these two are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same.
@@
 The actual mesh, the broadside $|E_x|$ field, and the broadside $|E_y|$ field are shown in the left, middle, and right columns, respectively.
-The extent of the plot includes the entire computational domain for the tetrahedral mesh; the rectilinear and octree mesh extents are larger (rectilinear: $x=327$ to 454\,km, $z=-57$ to 83\,km; octree: $x=288$ to 492\,km, $z=-123$ to 41\,km).
+The extent of the plot includes the entire computational domain for the tetrahedral mesh (in x and z direction); the rectilinear and octree mesh extents are larger than what is shown (rectilinear: $x=327$ to 454\,km, $z=-57$ to 83\,km; octree: $x=288$ to 492\,km, $z=-123$ to 41\,km).
 %
-\plot*{results-marlim_big}{width=\textwidth}{Meshes (left column), broadside $E_x$ field (middle column), and broadside $E_y$ field (right column) for the rectilinear mesh / \emg3d (top row), octree mesh / \simpeg (middle row), and tetrahedra mesh / \custem \& \petgem (bottom row).
+\plot*{results-marlim_big}{width=\textwidth}{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively.
 The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
@@
 This figure is interesting for various points: The differences between the different meshes are very obvious.
-Particularly the advantage of octree and tetrahedra, which can create huge cells at the boundary to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
+Particularly the advantage of octree and tetrahedra, which can create large cells outside of the region of interest to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
 The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.
@@
 %
-\plot*{results-marlim_survey}{width=\textwidth}{Meshes (left column), $E_x$ field (middle column), and $E_y$ field (right column) for the rectilinear mesh / \emg3d (top row), octree mesh / \simpeg (middle row), and tetrahedra mesh / \custem \& \petgem (bottom row) (3$\times$ vertical exaggeration).}
+\plot*{results-marlim_survey}{width=\textwidth}{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
 %
@@
 %
-The models where obtained using volume averaging (\emg3d, \simpeg) and linear interpolation (\custem, \petgem) on $\log_{10}{\rho}$ values.
-The actual responses at the receivers (field interpolation) are obtained by spline interpolation (\emg3d), ???\mycom[DW]{Lindsey, what did you use in the end?} (\simpeg), and through the second-order basis functions (\custem, \petgem).
+The models where obtained using volume averaging (\emg3d, \simpeg) and linear interpolation (\custem, \petgem), in both cases on $\log_{10}{\rho}$ values.
+The actual responses at the receivers (field interpolation) are obtained by spline interpolation (\emg3d), linear interpolation (\simpeg), and through the second-order basis functions (\custem, \petgem).
 
 \section{Discussion}
-\imycom[DW]{Currently still a collection of discussions. Needs better structuring.}
 
-Even if modelling results may look completely valid, they could not be correct at all.
-Validating the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
+It is easy to run a simulation and obtain reasonable-looking results.
+Though we may be able to confirm the accuracy of codes in some simple scenarios, validating the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
 Overall, we observed an excellent match between all solutions.
 The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation strategy.
-Considering this satisfactory result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
+Considering this result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
 The following arguments are based on a comparison of only marine CSEM models, which are the focus of industry applications.
@@
 Our first attempt were based on the originally published, fine MR3D model.
-This model is very detailed, but too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation.
+This model is very detailed, but its extent is too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation.
 However, none of the codes were able to reproduce the published results.
@@
 We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model.
-It is only with this model that we were able to get comparable results, visually mostly the same as shown in Figure~\ref{fig:model-marlim}.
+It is only with this model that we were able to get comparable results.
 
-We point out that making a synthetic and a real benchmark model available to cross-validate any 3D CSEM code was the determining reason for their choice, regardless of the suitability of the considered FD and FE codes for these problems.
+We point out that making a synthetic and a real benchmark model available to cross-validate any 3D CSEM code was the determining reason for their choice, regardless of the suitability of the considered FV and FE codes for these problems.
 The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
@@
 At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
-Hence, the chosen examples favoured the FD codes, since they used either regular grids or octree-meshes, whereas the two FE codes were required to tetrahedralise the model geometries.
+Hence, the chosen examples favoured the FV codes, since they used either regular grids or octree-meshes, whereas the two FE codes were required to tetrahedralize the model geometries.
 
@@
 FE codes with unstructured meshes were probably the poorest choice of all commonly used methods for this setup in terms of computational performance.
-However, thinking about introducing just one slight irregularity such as bathymetry, a thin dipping plate or an anticline, the performance behaviour could likely switch.
-All of these changes would barely change the problem size for the FE codes, but significantly increase it for the FD codes if the true geometry should be approximated sufficiently accurate.
+Similar challenges arise when considering an octree mesh.
+However, if we introduce just one slight irregularity such as bathymetry, a thin dipping plate or an anticline, the performance behaviour could likely switch.
+All of these changes would barely change the problem size for the FE codes, but significantly increase it for the FV codes if the true geometry should be approximated sufficiently accurate.
 
@@
 Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
-\imycom[DW]{Rethink the previous and next phrases. Correa could have chosen a different discretization. Also, OcTree uses even less cells, so this statement is wrong.}
-The p2 FE solution required only $\approx$1.9\,M dof instead of $\approx$90\,M dof for the FD system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
+The p2 FE solution required only $\approx$1.9\,M dof instead of $\approx$90\,M dof for the FV system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
 It is important to state that the FE mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and two source lines.
@@
 We found that the meshing task, which is most performance determining, is particularly difficult and relevant, choosing cells small enough to appropriately represent the model yet to be as coarse as possible still achieving the desired precision.
-The required model extent has to be considered as well, thinking also about effects of the so-called airwave in marine setups or boundary meshes in general.
+The required model extent has to be considered, as do the effects of the so-called airwave in marine setups or boundary meshes in general.
 This is not a new finding but rather well known fact.
@@
 It is worth noting that the reported runtime is just one of the aspects, and we would like to emphasise that neither the runtime nor the memory consumption are at the core of this comparison, but the validation of the results.
-As such no special efforts were undertaken to minimise either, as this is an entire different task.
-Another aspect is to generate an appropriate mesh, with all the testing involved, can easily take days of work.
+As such, no special efforts were undertaken to minimise either, as this is an entire different task.
+Another aspect is to generate an appropriate mesh; with all the testing involved, this step can easily take days of work.
 As such the computation times becomes relative, and the ease of usability of a code has to be considered too.
-For \custem, \petgem, and \simpeg it is therefore also a question of how easy everything is to set-up, because after the set-up phase it depends largely on the used solver, which might change in the future; \simpeg, e.g., is looking at moving to similar solvers as currently are used by \custem and \petgem.
+For \custem, \petgem, and \simpeg it is therefore also a question of how easy everything is to set-up, because after the set-up phase it depends largely on the solver used, which might change in the future; \simpeg, e.g., is looking at also interfacing to similar solvers as currently are used by \custem and \petgem.
 It is, however, slightly different for \emg3d, as that is primarily a solver on its own.
-It is also important to state that while \emg3d, \custem, and \petgem are purely CSEM codes, \simpeg is a much bigger framework which includes other geophysical methods as well.
+It is also important to state that while \emg3d, \custem, and \petgem are purely CSEM codes, \simpeg is a larger framework which includes other geophysical methods as well.
 
-The shown examples consider the geophysical problem of marine CSEM with resistive bodies.
+The examples shown consider the geophysical problem of marine CSEM with resistive bodies.
 We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography looking for conductive bodies.
-The used codes could, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
-The current main applications of the different codes are mining and environmental (\custem, \simpeg), oil and more recent geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
+The codes we demonstrated could be, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
+The current main applications of the different codes are: mining and environmental (\custem, \simpeg), oil and more recent geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
 
-A plus-point of a collaboration between different projects such as this is that it brings the realm as a whole further, which should be motivation enough for further collaborations.
-Within \simpeg, this work has motivated feature development including interpolation and averaging strategies from mapping physical properties on a fine mesh to a coarser mesh for computation and new examples to include in the documentation for designing octree meshes.
+A positive outcome of a collaboration between different projects such as this is that it brings the realm as a whole further, which should be motivation enough for further collaborations.
+Within \simpeg, this work has motivated feature development including averaging strategies to map physical properties on a fine mesh to a coarser mesh for computation and new examples to be included in the documentation for designing octree meshes.
 Furthermore, as a part of a broader development objective of inter-operating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
@@
 
-We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
-
 \section{Conclusions \& Outlook}
-\imycom[DW]{Not really conclusions, but a mix with discussions. Make pure conclusions.}
 
 We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, a model containing three resistive blocks, and the realistic marine Marlim R3D model.
-All comparisons exhibited an excellent reliability of the solutions, in the order of $\approx1\,\%$ misfit for the layered and the block model, and $\approx10\,\%$ for the real world model.
+All comparisons exhibited an excellent reliability of the solutions, in the order of $\approx1\,\%$ relative error for the layered and the block model, and $\approx10\,\%$ NRMSD for the real world model.
 Our data should make it very easy for new codes to have a readily available data set to test against and validate.
@@
 Reasonable extensions include providing benchmark models for land, airborne, or mixed CSEM environments as well as time-domain data.
-Another addition to this work would be focusing on complex irregular  models, tailored for an FE or FV code based on unstructured meshes, and to compare how the FD codes can cope with it.
+Another addition to this work would be focusing on complex irregular  models, tailored for an FE or FV code based on unstructured meshes, and to compare how the FV codes can cope with it.
 
@@
 
+Our study is one example of a collaboration facilitated by open practices including sharing of code and data.
+We hope that these results may be useful for the entire CSEM community at large, and we invite and encourage the community to make more code, modelling scripts, and results publicly available.
+
 \section{Acknowledgement}
 
-We had help of several colleagues for different tasks, and would therefore like to thank Bane Sullivan (plotting of tetrahedra meshes in matplotlib through PyVista), Seogi Kang (creation of octree meshes), \dots\mycom[DW]{please add if someone helped with something}.
+We had help from several colleagues for different tasks, and would like to thank Bane Sullivan (plotting of tetrahedra meshes in matplotlib through PyVista), Seogi Kang (input and octree mesh design for the \simpeg layer and block models), and Joseph Capriotti (octree mesh implementation and volume averaging in \simpeg).
 We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
@@
 
+The work of L.H. received funding from the National Science Foundation EarthCube program under award 1928406.
+
 \section{Data}

### 2020-10-19 manuscript/Manuscript.tex
Final draft for review to co-authors.

@@
 The governing equations are discretized on a staggered grid by the finite-integration technique \citep{AEU.77.Weiland}, which is a finite-volume generalisation of a Yee grid.
-The code is written completely in Python using the NumPy and SciPy stacks, where the most time- and memory-consuming parts are sped up through jitted (just-in-time compiled) functions using Numba \citep{LLVM.15.Lam}.
+The code is written completely in Python using the \texttt{NumPy} and \texttt{SciPy} stacks, where the most time- and memory-consuming parts are sped up through jitted (just-in-time compiled) functions using \texttt{Numba} \citep{LLVM.15.Lam}.
 The strength of \emg3d is the matrix-free multigrid implementation, which is characterised by almost linear scaling both in terms of runtime and memory usage, and it is therefore a solver that uses comparably very little memory.
@@
 \simpeg supports variable magnetic permeability and full-tensor anisotropy for the physical properties.
-\simpeg interfaces to various solvers including \texttt{PARDISO} and \texttt{MUMPS}, and also to some implemented in SciPy.
+\simpeg interfaces to various solvers including \texttt{PARDISO} and \texttt{MUMPS}, and also to some implemented in \texttt{SciPy}.
 
@@
 
-It is easy to run a simulation and obtain reasonable-looking results.
-Though we may be able to confirm the accuracy of codes in some simple scenarios, validating the performance of 3D CSEM codes for real 3D problems is only possible by cross-validating multiple solutions.
-Overall, we observed an excellent match between all solutions.
-The relative misfits, almost always smaller than 10\,\%, were related to the either weak or strong amplitudes of real or imaginary parts and can be attributed to particularities regarding the discretization, boundary effects, and interpolation strategy.
-Considering this result in terms of accuracy and robustness, it is more interesting to discuss the characteristics of the four considered codes with focus on the demand of computational resources and the capability of handling the investigated CSEM geometries, including the very important underlying mesh design.
-The following arguments are based on a comparison of only marine CSEM models, which are the focus of industry applications.
-Nevertheless, we are confident that many observations would hold in a similar manner for land-based, airborne, or mixed setups.
+%% 0. What we did and why %%
+Today we are in the fortunate situation where we have several open-source codes available to model CSEM data for arbitrarily sized complex 3D models.
+It is therefore comparably easy for anyone to run a simulation and obtain reasonable-looking, robust and precise results, something that was impossible a few years ago.
+However, just because one obtains a good-looking result does not say anything about its accuracy.
+Though we may be able to confirm the accuracy of codes in some simple scenarios, validating the performance of 3D CSEM codes for complex problems is only possible by cross-validating multiple solutions.
+This is the core motivation for this study.
 
-For the MR3D results one might argue that 5-10\,\% NRMSD is a lot.
-We argue that this is probably as good as it gets, given that the code with which we compare is not open-source.
-This has been shown within the process of these results.
+%% 1. Results: good agreement %%
+Overall, we observed an excellent match between the solutions.
+The amplitudes of the layered model have mostly a relative error of less than $1-2\,$\%.
+Looking individually at the real or imaginary part results in much higher error values, but those are related to the zero crossings of the responses.
+The cross-validation of the results for the block model yields a similar picture, with NRMSD values within a few percents.
+For the large, complex MR3D model it is a bit different.
+First it can be noted that the errors seem to be higher for higher frequencies.
+For the lowest frequency, 0.125\,Hz, the NRMSD is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
+For higher frequencies these numbers rise to the order of $\pm10\,$\%.
+The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategy.
+While one might argue that $5-10\,$\% NRMSD is a lot, we argue that this is probably as good as it gets, given that the code with which the responses we compare to were computed is not open-source.
+This has been shown within the process of this study.
 Our first attempt were based on the originally published, fine MR3D model.
-This model is very detailed, but its extent is too small in x- and y-direction for CSEM computation, and each of our codes did its own extrapolation.
+This model is very detailed, but its extent is too small in x- and y-directions for CSEM computations, and each of our codes did its own extrapolation.
 However, none of the codes were able to reproduce the published results.
@@
 
-We point out that making a synthetic and a real benchmark model available to cross-validate any 3D CSEM code was the determining reason for their choice, regardless of the suitability of the considered FV and FE codes for these problems.
-The first model, including the block-anomalies variation, is exactly reproducible by using any numerical method with either regular or irregular computational domains.
-Aside from the idea of analysing an industrially relevant benchmark example, the MR3D model was also considered since the primary design from \cite{GEO.19.Correa} uses a regular discretization.
-At least theoretically, the exact geometry might be reconstructed with unstructured meshes, but it is never possible to convert an irregular geometry to a regular grid without approximations.
-Hence, the chosen examples favoured the FV codes, since they used either regular grids or octree-meshes, whereas the two FE codes were required to tetrahedralize the model geometries.
+%% 2. Discretization %%
+One of the key insights we gained from this study is that creating appropriate meshes is a difficult and time-consuming task.
+While there exist now several open-source 3D CSEM codes the capability for automatic meshing lacks behind and currently remains a largely manual task requiring experience in the field.
+It is important to state that the chosen models favour structured meshes.
+The first two examples can easily and accurately be represented by regular meshes.
+Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes.
+MR3D would be ideal an scenario for unstructured meshes, as it is based on also published irregular lithological horizons.
+Since the corresponding resistivity model, however, was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
+We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
+Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling.
+Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour.
+It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
 
-In the first model, the necessity of discretizing regular structures with tetrahedra, especially thin layers, led to comparatively large FE problem sizes and computational resource demands.
-FE codes with unstructured meshes were probably the poorest choice of all commonly used methods for this setup in terms of computational performance.
-Similar challenges arise when considering an octree mesh.
-However, if we introduce just one slight irregularity such as bathymetry, a thin dipping plate or an anticline, the performance behaviour could likely switch.
-All of these changes would barely change the problem size for the FE codes, but significantly increase it for the FV codes if the true geometry should be approximated sufficiently accurate.
+%% 3. Iterative vs direct solvers; runtime and memory %%
+Whereas proper discretization is the main driver for accurate results, the used solver is the main discriminator in terms of runtime and memory.
+Both iterative and direct solvers are used in this study, however, the chosen models clearly favour iterative solvers.
+The biggest advantage of iterative solvers are the comparatively small memory requirements, even more so if the iterative solver is matrix free.
+Direct solvers exhibit their strongest advantage, besides stability and robustness, in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain.
+As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, whereas it would come at the same cost as the first source for iterative solvers.
+Independently of the solver there is a trade-off between high accuracy and runtime.
+As an example, the octree mesh made for a very fast computation in the MR3D example thanks to the low number of dof, even though a direct solver was used.
+But the octree mesh has, due to its 2:1 aspect ratio, some limitations on the accuracy, why it was not used in the first two examples.
+Having discussed the discretization and the solver it is important to state that the reported runtime and memory is just one of the aspects, and we would like to emphasise that neither was at the core of this comparison, but the validation of the results.
+As such, no special efforts were undertaken to minimise either, as this is an entire different task.
 
-The real MR3D model was, ironically, the ideal case for FE codes because it's structure was characterised by irregular lithological horizons obtained from seismic data.
-Since the corresponding published resistivity model was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
-We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
-Nevertheless, the chosen tetrahedral discretization, especially in combination with second order basis functions, showed clearly the intrinsic strength of the FE codes, requiring significantly less dof for meshing irregular geometries in general.
-The p2 FE solution required only $\approx$1.9\,M dof instead of $\approx$90\,M dof for the FV system by \citet{GEO.19.Correa}, disregarding the structure of the system matrices.
-It is important to state that the FE mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and two source lines.
-
-The codes under consideration use direct and iterative solvers.
-In general, the biggest advantage of iterative solvers with appropriate preconditioners are the comparatively small memory requirements.
-Direct solvers can be considered as most robust to solve any ill-conditioned SLE, which is most important for systems of the FE method on unstructured meshes.
-As the consumed computational resources indicate, a more powerful machine than a laptop is required for most 3D CSEM problems, but no high-performance-computing architecture.
-
-The computation times can differ significantly for specific simulations, but there is no clear general advantage for one of the solver types.
-In our models, the runtime comparison favoured the iterative solver and therefore, \emg3d.
-Even though not shown here, direct solvers exhibit their strongest advantage, besides stability, in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain.
-As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, i.e., MUMPS, whereas it would come at the same cost as the first source for \emg3d.
-For the sake of completeness, note that there are also advanced techniques for iterative solvers to make use of preconditioners, factorisations, or intermediate solutions of the previous SLE to speed up the computation for multiple sources, but this argumentation is beyond the scope of this work.
-
-We see this work as the start for future elaboration on the validation of modelling codes, not necessarily restricted to CSEM problems.
-Much more comparisons and examples are required which not only result in the finding that a sufficient accuracy was observed.
-3D CSEM modelling is a difficult task, which requires many considerations.
-It starts with the selection of the right code for the problem.
-We found that the meshing task, which is most performance determining, is particularly difficult and relevant, choosing cells small enough to appropriately represent the model yet to be as coarse as possible still achieving the desired precision.
-The required model extent has to be considered, as do the effects of the so-called airwave in marine setups or boundary meshes in general.
-This is not a new finding but rather well known fact.
-We are surprised that only the minority of publications in the field of 3D EM modelling considers a sufficiently detailed elaboration of the meshing process.
-
-A completely objective evaluation of codes is only possible by cross-validation.
-Nevertheless, we point out that using different discretizations or formulations of the numerical approach, e.g.
-by choosing field or potential approaches, second or total field formulations, different polynomial order basis functions, and others, is a suitable alternative to the cross-comparison of multiple codes for self-validating complex 3D results.
-This is a very powerful method to confirm the general functionality of codes for any modelling problem, which might not be covered by existing cross-validation benchmark examples.
-Considering for instance  this study, it would be very optimistic to estimate the accuracy of the utilised codes for a land-based mineral exploration setup with a highly-conductive, steeply-dipping conductor.
-However, each modeller could run multiple simulations with different configurations to increase the reliability of the obtained results.
-
-It is worth noting that the reported runtime is just one of the aspects, and we would like to emphasise that neither the runtime nor the memory consumption are at the core of this comparison, but the validation of the results.
-As such, no special efforts were undertaken to minimise either, as this is an entire different task.
-Another aspect is to generate an appropriate mesh; with all the testing involved, this step can easily take days of work.
-As such the computation times becomes relative, and the ease of usability of a code has to be considered too.
-For \custem, \petgem, and \simpeg it is therefore also a question of how easy everything is to set-up, because after the set-up phase it depends largely on the solver used, which might change in the future; \simpeg, e.g., is looking at also interfacing to similar solvers as currently are used by \custem and \petgem.
-It is, however, slightly different for \emg3d, as that is primarily a solver on its own.
-It is also important to state that while \emg3d, \custem, and \petgem are purely CSEM codes, \simpeg is a larger framework which includes other geophysical methods as well.
-
-The examples shown consider the geophysical problem of marine CSEM with resistive bodies.
-We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography looking for conductive bodies.
-The codes we demonstrated could be, and many frequently are, applied to very different applications, including any other geophysical exploration in the sea or on land (oil, mining, geothermal, groundwater, environmental) and also non-geophysical tasks.
-The current main applications of the different codes are: mining and environmental (\custem, \simpeg), oil and more recent geothermal (\petgem), and oil, methane, and deep sea mining (\emg3d).
-
+%% 4. Focus here on marine CSEM; gains through collaboration %%
+The shown examples consider the geophysical problem of marine CSEM with resistive bodies in the frequency domain.
+We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
 A positive outcome of a collaboration between different projects such as this is that it brings the realm as a whole further, which should be motivation enough for further collaborations.
@@
 Furthermore, as a part of a broader development objective of inter-operating with other forward-simulation engines, connecting \emg3d and \simpeg provided a motivating use-case for the latest refactor and release of \simpeg 0.14.0.
-Within \emg3d, this work pushed a lot of the meshing functionality, and implementing of I/O utilities for different file formats.
+Within \emg3d, this work pushed a lot of the meshing functionality, and implementation of I/O utilities for different file formats.
 Within \custem, cell-wise resistivity interpolation was added for this work, multi-layer subsurface topography was the first time applied as well as first time reciprocity modelling, and also improved mesh design (resolution, refinement, etc.).
@@
 
-\section{Conclusions \& Outlook}
+\section{Conclusions}
 
-We compared four different open-source 3D CSEM modellers by computing responses for a layered, anisotropic model, a model containing three resistive blocks, and the realistic marine Marlim R3D model.
-All comparisons exhibited an excellent reliability of the solutions, in the order of $\approx1\,\%$ relative error for the layered and the block model, and $\approx10\,\%$ NRMSD for the real world model.
-Our data should make it very easy for new codes to have a readily available data set to test against and validate.
-We are confident that the discussions about runtimes, memory consumption, solver choices, and, most important, discretizations of the 3D CSEM problems help potential users not only to decide which modeller is best suited for specific tasks, but also to support their individual projects.
-
-As none of the considered methods is best suited for all problems, it is important to have more test models for various scenarios in future.
-Our study is limited to marine CSEM cases in the frequency-domain.
-Reasonable extensions include providing benchmark models for land, airborne, or mixed CSEM environments as well as time-domain data.
-Another addition to this work would be focusing on complex irregular  models, tailored for an FE or FV code based on unstructured meshes, and to compare how the FV codes can cope with it.
-
-We encourage the community to not only work on new open-source code developments but also to create a landscape of easily accessible benchmark models for increasing the number of reliable and reproducible solutions.
-Our study could provide one of the primary inputs for this task.
-We are confident that the mentioned development will and should be taking place, taking into account the current general trend in science to open-source papers, codes or data.
-
+We compare the computed fields and underlying meshes of four different open-source 3D CSEM codes by means of three increasingly complex resistivity models.
+A layered marine, anisotropic model is used as first example to verify our results with semi-analytical responses.
+All codes show excellent accuracy with a relative error in the order of a few percents.
+Three resistive blocks are added to the layered model to increase complexity in the second example.
+The cross-validation of the outcomes of the different codes shows a NRMSD of a few percent, hence in a similar range as the relative error in the layered model.
+The third example is Marlim R3D, a realistic, complex, marine resistivity model.
+The model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
+In this scenario the NRMSD is in the order of $5-10$\,\%, where the main source can be attributed to differences in discretization.
+The required runtime and memory consumption is primarily controlled by the used solver.
+The accuracy, on the other hand, depends to a large degree on the discretization.
+A proper discretization is therefore key for an accurate result, which makes this step the most time-consuming task, not the actual computation of the responses itself.
+Validating the correctness of a 3D code is a difficult task, and it is essential to have easily accessible benchmark models with reliable and reproducible solutions.
 Our study is one example of a collaboration facilitated by open practices including sharing of code and data.
@@
 
-We had help from several colleagues for different tasks, and would like to thank Bane Sullivan (plotting of tetrahedra meshes in matplotlib through PyVista), Seogi Kang (input and octree mesh design for the \simpeg layer and block models), and Joseph Capriotti (octree mesh implementation and volume averaging in \simpeg).
+We had help from several colleagues for different tasks, and would like to thank Bane Sullivan (plotting of tetrahedra meshes in \texttt{matplotlib} through \texttt{PyVista}), Seogi Kang (input and octree mesh design for the \simpeg layer and block models), and Joseph Capriotti (octree mesh implementation and volume averaging in \simpeg).
 We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.

### 2020-10-21 manuscript/Manuscript.tex
Feedback RR

@@
 The models where obtained using volume averaging (\emg3d, \simpeg) and linear interpolation (\custem, \petgem), in both cases on $\log_{10}{\rho}$ values.
+The actual representation of the original resistivities in the tetrahedra mesh is not as smooth as in the other meshes since this would require significantly smaller tetrahedra and more dof on top of the inclusion of subsurface layer constraints.
+However, note that the combination of slicing through tetrahedra and the vertical exaggeration lead to a very distorted view of the tetrahedral mesh which is barely representative for the overall averaged approximation of resistivities.
 The actual responses at the receivers (field interpolation) are obtained by spline interpolation (\emg3d), linear interpolation (\simpeg), and through the second-order basis functions (\custem, \petgem).
@@
 Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes.
-MR3D would be ideal an scenario for unstructured meshes, as it is based on also published irregular lithological horizons.
+MR3D would be an ideal scenario for unstructured meshes, as it is based on also published irregular lithological horizons.
 Since the corresponding resistivity model, however, was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
@@
 
-We had help from several colleagues for different tasks, and would like to thank Bane Sullivan (plotting of tetrahedra meshes in \texttt{matplotlib} through \texttt{PyVista}), Seogi Kang (input and octree mesh design for the \simpeg layer and block models), and Joseph Capriotti (octree mesh implementation and volume averaging in \simpeg).
+We would like to thank Bane Sullivan for plotting of tetrahedra meshes in \texttt{matplotlib} through \texttt{PyVista}, Seogi Kang for the input and octree mesh design for the \simpeg layer and block models, and Joseph Capriotti for the octree mesh implementation and volume averaging in \simpeg.
 We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.

### 2020-10-23 manuscript/Manuscript.tex
Before moving to GJI template

@@
 \usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}
+\frenchspacing
 
@@
 This includes improved meshing and interpolation capabilities, resulting in shorter runtimes for the same accuracy.
+We hope that these results may be useful for the CSEM community at large and that we can build over time a suite of benchmarks that will help to increase the confidence in existing and new 3D CSEM codes.
 %
@@
 \end{abstract}
-
-\newpage
-\subsection*{Discussed items re manuscript}
-\begin{itemize}
-  \item Orthography: BE for GJI; using discretize.
-  \item Author order is fine by everyone.
-  \item Everyone is responsible that the info of their codes is correct (machine info, runtime, memory, dof, etc) and agrees with the info in the \texttt{*.nc}-files.
-  \item The runtime in the table is real-world time. So actual computation time is roughly `nprocs x runtime`; also, nprocs includes processes and threads.
-  \item Regarding submission:
-    \begin{description}
-      \item[Current submission] RR, OCR, LH have no submission with GJI currently.
-      \item[History] We will keep all git history.
-      \item[Repo] \href{https://github.com/swung-research/3d-csem-open-source-landscape/}{github.com/swung-research/3d-csem-open-source-landscape}.
-      \item[Suggested reviewers] We suggest the following reviewers, mainly because they have the relevant experience and it would be interesting for us to have their feedback: \emph{Kerry Key} (domain knowledge as developer of \texttt{MARE3DEM}); \emph{Rune Mittet} (domain knowledge; he will know what SBLwiz actually does); \emph{Dimitry Avdeev} and \emph{Ralph-Uwe Börner} (both did extensive 3D code overview/review papers in 2005 and 2010, respectively).
-    \end{description}
-\end{itemize}
 
@@
 \cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of MT forward and inversion codes, but we are not aware of any comparable comparison study or benchmark suite for CSEM data.
-We hope our efforts help to ensure the reliability of simulations for any new or existing, open-source or closed-source 3D CSEM project.
 
@@
 An overview comparison of the codes is given in Table~\ref{tbl:codecomparison}.
-All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range commonly applied in CSEM.
+All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM.
 The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
+% We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
 % ($\vec{n}\times\vec{E} = 0; \vec{n}\cdot\vec{H} = 0$)
@@
   Method & FE & FV & FE & FV \\
-  Mesh & tetrahedral & rectilinear & tetrahedral & recti- \& curvilinear \\
+  Mesh & tetrahedral & rectilinear & tetrahedral & recti-/curvilinear, octree \\
   BC & PEC; PMC & PEC & PEC & PEC; PMC \\
@@
 
-There are a few noteworthy points:
-
+I few interesting points stand out:
 \begin{enumerate}
@@
 %
-Two data-sets were published, one containing clean responses, and one where realistic noise was added.
+Two CSEM data-sets were published with MR3D, one containing clean responses, and one responses where realistic noise was added.
 For the comparison we use the clean data, but we indicate the chosen noise level by the horizontal line at \num{2e-15}\,V/m.
@@
 The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally.
-See the discussion around Figure~\ref{fig:results-marlim_survey}.
-  \item The three highest frequencies became noisy at large offsets for all of our codes (well below any real-world noise level).
+See the discussion around Figure~\ref{fig:results-marlim_2published}.
+  \item The three highest frequencies become noisy at large offsets for all of our codes (well below any real-world noise level).
 The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
@@
 These responses are very low, roughly two orders of magnitude lower than the $E_x$ component.
-The published responses are not stable either, and therefore any of the responses is as bad as the other.
-Also, tiniest differences in meshing or different interpolation algorithms will have a huge effect here, as well as the boundary condition of the air-water interface of the published results.
+Not the published nor our responses are stable, and any of the responses is as bad as the other.
+Tiniest differences in meshing or different interpolation algorithms will have a huge effect here.
 \end{enumerate}
 
-It is important to note that note the published results nor any of our results is correct, but the closer they agree with each other the more certain we can be of the outcomes.
+It is important to note that the published results nor any of our results is the \emph{thruth}, but the closer they agree with each other the more certain we can be of the outcomes.
 Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
@@
 The structured meshes have in some cases a smaller NRMSD, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in other cases the unstructured tetrahedral meshes, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
-Some NRMSDs have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}, and will be discussed in more detail with Figure~\ref{fig:results-marlim_survey}.
+Some NRMSDs have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
+The origin of this zigg-zagg pattern is most likely the bathymetry.
+We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
+This would explain why the codes using the tetrahedra mesh, which uses the bathymetry as well, does not show this feature.
 
@@
 The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their NRMSD is generally below 0.03\,\%.
-The reason is simple: \custem and \petgem use the exactly same mesh for the computation, the only difference is therefore the solver.
+The reason is simple: \custem and \petgem use the exactly same mesh for the computation of this example, the only difference is therefore the solver.
 This exemplifies that the biggest difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result.
 As these two are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same.
-But in general the NRMSDs between our codes look similar as in the comparison with the published results, which is due to the different meshes in use.
+But in general the NRMSDs between our codes look similar as in the comparison with the published results, and the principal source of the difference must be in the different discretizations.
 
@@
 Figure~\ref{fig:results-marlim_big} shows on the top row the rectilinear mesh of \emg3d, on the middle row the octree mesh of \simpeg, and on the bottom row the tetrahedral mesh of \custem and \petgem.
-The actual mesh, the broadside $|E_x|$ field, and the broadside $|E_y|$ field are shown in the left, middle, and right columns, respectively.
-The extent of the plot includes the entire computational domain for the tetrahedral mesh (in x and z direction); the rectilinear and octree mesh extents are larger than what is shown (rectilinear: $x=327$ to 454\,km, $z=-57$ to 83\,km; octree: $x=288$ to 492\,km, $z=-123$ to 41\,km).
+The actual mesh and the broadside $|E_x|$ and $|E_y|$ fields are shown in the left, middle, and right columns, respectively.
+The extent of the plot includes the entire computational domain for the tetrahedral mesh (in x and z direction); the rectilinear and octree mesh extents are larger than what is shown (rectilinear: $x=327$ to 454\,km, $z=-57$ to 66\,km; octree: $x=288$ to 492\,km, $z=-123$ to 41\,km).
 %
@@
 %
-This figure is interesting for various points: The differences between the different meshes are very obvious.
-Particularly the advantage of octree and tetrahedra, which can create large cells outside of the region of interest to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
+This figure is interesting for various points, and the differences between the three meshes are very obvious.
+Particularly visible is the advantage of octree and tetrahedra to create large cells outside of the region of interest to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
 The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.
@@
 %
-The most striking point of these mesh comparison plots is that, while the overall fields are similar and particularly the responses at receiver locations are the same, the fields can vary quite a lot in different parts of the model.
-E.g., two kilometres below the seafloor there are already significant changes visible, purely due to meshing.
+The most striking point of these mesh comparison plots is that, while the overall fields are similar and the responses at receiver locations agree well, the fields can vary quite a lot in different parts of the model.
+Two kilometres below the seafloor, as an example, there are already significant changes visible, purely due to meshing.
 This is an important insight that has to be taken into account when interpreting inversion results.
@@
   \custem & 64 &  872 & 230.1 & 1918106 \\ % dof: 3836212 / 2 (Real+Imag -> Complex)
-  \emg3d  &  1 & 1200 &   0.5 & 5998992 \\
+  \emg3d  &  1 & 1254 &   0.6 & 5998992 \\
   \petgem & 96 &  524 & 175.4 & 1918106 \\
@@
 %
-The models where obtained using volume averaging (\emg3d, \simpeg) and linear interpolation (\custem, \petgem), in both cases on $\log_{10}{\rho}$ values.
+The models where obtained using volume averaging (\emg3d, \simpeg) and linear interpolation (\custem, \petgem), in both cases on $\log_{10}(\rho)$ values.
 The actual representation of the original resistivities in the tetrahedra mesh is not as smooth as in the other meshes since this would require significantly smaller tetrahedra and more dof on top of the inclusion of subsurface layer constraints.
-However, note that the combination of slicing through tetrahedra and the vertical exaggeration lead to a very distorted view of the tetrahedral mesh which is barely representative for the overall averaged approximation of resistivities.
+However, note that the combination of slicing through tetrahedra and the vertical exaggeration leads to a very distorted view of the tetrahedral mesh which is barely representative for the overall averaged approximation of resistivities.
 The actual responses at the receivers (field interpolation) are obtained by spline interpolation (\emg3d), linear interpolation (\simpeg), and through the second-order basis functions (\custem, \petgem).
+It is worth mentioning as a final note that we used frequency independent meshes in this study.
+Creating frequency dependent meshes could potentially improve both the result and the runtime.
 
@@
 Overall, we observed an excellent match between the solutions.
-The amplitudes of the layered model have mostly a relative error of less than $1-2\,$\%.
+The amplitudes of the layered model have mostly a relative error of less than 1--2\,\%.
 Looking individually at the real or imaginary part results in much higher error values, but those are related to the zero crossings of the responses.
@@
 For the large, complex MR3D model it is a bit different.
-First it can be noted that the errors seem to be higher for higher frequencies.
+First it can be noted that the misfits are higher for higher frequencies.
 For the lowest frequency, 0.125\,Hz, the NRMSD is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
@@
 The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategy.
-While one might argue that $5-10\,$\% NRMSD is a lot, we argue that this is probably as good as it gets, given that the code with which the responses we compare to were computed is not open-source.
+While one might argue that 5--10\,\% NRMSD is a lot, we argue that this is probably as good as it gets, given that the code with which the responses we compare to were computed is not open-source.
 This has been shown within the process of this study.
@@
 Direct solvers exhibit their strongest advantage, besides stability and robustness, in terms of computation times if responses of multiple CSEM transmitters need to be computed in the same computational domain.
-As the system matrix factorisation requires 98-99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, whereas it would come at the same cost as the first source for iterative solvers.
+As the system matrix factorisation requires 98--99\,\% of the solution time, computations for additional sources come at almost no cost for direct solvers, whereas it would come at the same cost as the first source for iterative solvers.
 Independently of the solver there is a trade-off between high accuracy and runtime.
@@
 
-%% 4. Focus here on marine CSEM; gains through collaboration %%
-The shown examples consider the geophysical problem of marine CSEM with resistive bodies in the frequency domain.
-We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
+%% 4. Gains through collaboration; focus here on marine CSEM %%
 A positive outcome of a collaboration between different projects such as this is that it brings the realm as a whole further, which should be motivation enough for further collaborations.
@@
 Within \custem, cell-wise resistivity interpolation was added for this work, multi-layer subsurface topography was the first time applied as well as first time reciprocity modelling, and also improved mesh design (resolution, refinement, etc.).
-Within \petgem, this work has promoted the inclusion of magnetic field computation, improving the generation of adapted meshes based on a semi-automatic approach that reduces user intervention.
-Also added was the continuous integration functionality and improved its test suite.
+Within \petgem, this work has promoted the inclusion of routines for magnetic field computation and the implementation of continuous integration functions.
+It has also improved its test suite and work-flow for the generation of adapted meshes based on a semi-automatic approach that reduces user intervention.
+
+The shown examples consider the geophysical problem of marine CSEM with resistive bodies in the frequency domain.
+We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
 
@@
 The model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
-In this scenario the NRMSD is in the order of $5-10$\,\%, where the main source can be attributed to differences in discretization.
+In this scenario the NRMSD is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization.
 The required runtime and memory consumption is primarily controlled by the used solver.
-The accuracy, on the other hand, depends to a large degree on the discretization.
+The accuracy, on the other hand, depends to a large degree on the mesh.
 A proper discretization is therefore key for an accurate result, which makes this step the most time-consuming task, not the actual computation of the responses itself.
@@
 All files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
-For the review process we refer to the github page \href{https://github.com/prisae/3d-csem-open-source-landscape}{github.com/prisae/3d-csem-open-source-landscape}.
+For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}.
 

### 2020-10-23 manuscript/Manuscript.tex
Change from geophysics to GJI template

@@
-\documentclass[
-    paper,
-%     manuscript,
-%     twocolumn,
-%     twoside,
-%     revised,
-  ]{geophysics}
-
-% TODO's
-\usepackage[color=cyan, textsize=footnotesize, textwidth=2.8cm]{todonotes}
+% \documentclass[onecolumn,extra,referee,camera]{gji}
+\documentclass[onecolumn,extra,camera]{gji}
+\usepackage{timet}
 
 % Additional packages
-\usepackage[UKenglish]{babel}
+% \usepackage[UKenglish]{babel}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amssymb, amsmath, amsfonts}
+\usepackage{booktabs}
+\usepackage{xspace}
+\usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}
+\usepackage[pdftex]{graphicx}
+
+% workaround siunitx clashes unfortunately with gji
+% https://tex.stackexchange.com/a/412886
+\makeatletter
+\let\zz@tabular\@tabular
+\let\zzendtabular\endtabular
+\let\zz@xtabularcr\@xtabularcr
+\let\zz@tabclassz\@tabclassz
+\let\zz@tabclassiv \@tabclassiv 
+\let\zz@tabarray\@tabarray
+\makeatother
+
+\let\tablenum\relax
 \usepackage{siunitx}
 \usepackage{tabularx}
-\usepackage{booktabs}
-\usepackage{xspace}
-\usepackage{flafter}
-\usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}
-\frenchspacing
 
-% Figures
-\renewcommand{\figdir}{./figures}
+% To fix clash of gji with hyperref
+% https://tex.stackexchange.com/a/384969
+\AtBeginDocument{
+  \label{CorrectFirstPageLabel}
+  \def\fpage{\pageref{CorrectFirstPageLabel}}
+}
 
@@
 \newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
-
 \newcommand{\rmk}[1]{{\color{red}\bfseries #1}}
 
-% TODO's
-% For comments in the margin, use:   \mycom[YOURINITIALS]{comment}
-% and for inline comments, use:      \imycom[YOURINITIALS]{comment}
-\newcommand{\mycom}[2][]{\todo{\textbf{\uppercase{[#1]}}:~#2}}
-\newcommand{\imycom}[2][]{\todo[inline]{\textbf{\uppercase{[#1]}}:~#2}}
-\newcommand{\itodo}[1]{\todo[inline]{\sffamily #1}}
+\title[Open-source 3D CSEM modelling]{Open-source landscape for 3D CSEM modelling}
 
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\author[D. Werthmüller \emph{et al.}]
+  {\Large Dieter Werthmüller$^1$,        % orcid: 0000-0002-8575-2484
+   Raphael Rochlitz$^2$,          % orcid: 0000-0002-5132-916X
+   Octavio Castillo-Reyes$^3$ and % orcid: 0000-0003-4271-5015
+   Lindsey Heagy$^4$              % orcid: 0000-0002-1551-5926
+   \\
+   \footnotesize
+  $^1$ TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL).
+  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org}\\[-.3em]
+   \footnotesize
+  $^2$ Leibniz Institute for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE)\\[-.3em]
+   \footnotesize
+   $^3$ Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES)\\[-.3em]
+   \footnotesize
+  $^4$ University of California Berkeley, Department of Statistics (USA)
+  }
+
+\date{Received 202Y MMMM DD; in original form 2020 October 23}
+\pagerange{\pageref{firstpage}--\pageref{lastpage}}
+\volume{VVV}
+\pubyear{202Y}
+
+% Authors with AMS fonts and mssymb.tex can comment out the following
+% line to get the correct symbol for Geophysical Journal International.
+\let\leqslant=\leq
+
+\newtheorem{theorem}{Theorem}[section]
 
@@
 
-% META INFO
-\title{Open-source landscape for 3D CSEM modelling}
+\label{firstpage}
 
-% ARTICLE-ID
-\ms{}
+% workaround siunitx clashes unfortunately with gji
+% https://tex.stackexchange.com/a/412886
+{\makeatletter
+\let\@tabular\zz@tabular
+\let\endtabular\zzendtabular
+\let\@xtabularcr\zz@xtabularcr
+\let\@tabclassz\zz@tabclassz
+\let\@tabclassiv \zz@tabclassiv 
+\let\@tabarray\zz@tabarray
+\maketitle
+}
+% \maketitle
 
-% ADDRESSES
-\address{
-  \footnotemark[1]TU Delft, Building 23, Stevinweg 1 / PO-box 5048, 2628 CN Delft (NL);\\
-  \footnotemark[2]Leibniz Institute for Applied Geophysics, Stilleweg 2, 30655 Hannover (DE);\\
-  \footnotemark[3]Barcelona Supercomputing Center (BSC), Nexus II Building c/Jordi Girona, 29, 08034 Barcelona (ES);\\
-  \footnotemark[4]University of California Berkeley, Department of Statistics (USA).\\
-  E-mail: \href{mailto:Dieter@Werthmuller.org}{Dieter@Werthmuller.org}.
-}
-% AUTHORS
-\author{%
-  Dieter Werthmüller\footnotemark[1],          % orcid: 0000-0002-8575-2484
-  Raphael Rochlitz\footnotemark[2],            % orcid: 0000-0002-5132-916X
-  Octavio Castillo-Reyes\footnotemark[3], and  % orcid: 0000-0003-4271-5015
-  Lindsey Heagy\footnotemark[4]                % orcid: 0000-0002-1551-5926
-}
-
-% HEADER / FOOTER
-\footer{}
-\lefthead{Werthmüller et al.}
-\righthead{Open-source 3D CSEM modelling}
-
-\maketitle
-
-\begin{abstract}
+\begin{summary}
 Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) surveys used to be feasible only for large companies and research consortia.
@@
 We hope that these results may be useful for the CSEM community at large and that we can build over time a suite of benchmarks that will help to increase the confidence in existing and new 3D CSEM codes.
-%
+\end{summary}
+
 % https://academic.oup.com/DocumentLibrary/GJI/gji%20keyword%20list%20updated2017.pdf
-\\[1cm] \textbf{Keywords}: Controlled source electromagnetics (CSEM), Numerical modelling, Electrical properties
-\end{abstract}
+\begin{keywords}
+  Controlled source electromagnetics (CSEM); Numerical modelling; Electrical
+  properties.
+\end{keywords}
 
@@
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
-% We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
+We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
 % ($\vec{n}\times\vec{E} = 0; \vec{n}\cdot\vec{H} = 0$)
@@
 
-\tabl[bthp]{codecomparison}{Comparison of the four codes under consideration.
-Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}{
+%
+\begin{table*}
+\begin{minipage}{.9\linewidth}
   \centering
-  \footnotesize
+  \caption{Comparison of the four codes under consideration.
+Note that \emg3d is a solver on its own, while the other codes implement third-package solvers such as \texttt{PETSc} \citep{Preprint.Abhyankar}, \texttt{MUMPS} \citep{SIAM.01.Amestoy}, or \texttt{PARDISO} \citep{FGCS.04.Schenk}.}
+\label{tbl:codecomparison}
   \begin{tabularx}{\linewidth}{lXXXX}
@@
   \bottomrule
-\end{tabularx}}%
+\end{tabularx}
+\end{minipage}
+\end{table*}
 %
@@
 %
-\tabl[bthp]{machines}{List of hardware, software, and operator with which the different codes were run.}{
+\begin{table*}
+\begin{minipage}{14cm}
   \centering
-  \footnotesize
+  \caption{List of hardware, software, and operator with which the different codes were run.}
+\label{tbl:machines}
   \begin{tabularx}{\linewidth}{lXl}
   \toprule
-  %
   Code & Computer and Operating System & Operator \\
@@
   \petgem & \textbf{Marenostrum4 (supercomputer)}             & Octavio Castillo-Reyes \\
-          & - Intel Xeon Platinum from Skylake generation; 2 sockets Intel Xeon Platinum 8160 CPU with 24 cores each @2.10GHz for a total of 48 cores per node & \\
+          & - 2 sockets Intel Xeon Platinum (Skylake generation) 8160 CPU & \\
+          & \phantom{-} with 24 cores each @2.10GHz for a total of 48 cores per node & \\
           & - 386 GB DDR4 RAM per node                        & \\
@@
 
-The layered (1D) model consists of an upper halfspace of air ($\rho_\text{air}=\num{e8}\,\ohmm$), a 600\,m deep water layer ($\rho_\text{sea}=\num{0.3}\,\ohmm$), followed by a 250\,m thick, isotropic layer of 1\,\ohmm, a 2.3\,km thick, anisotropic (vertical transverse isotropy, VTI) layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive, isotropic basement consisting of a lower halfspace of $1000\,\ohmm$.
+The layered (1D) model consists of an upper halfspace of air ($\rho_\text{air}=\num{e8}\,\ohmm$), a 600\,m deep water layer ($\rho_\text{sea}=0.3\,\ohmm$), followed by a 250\,m thick, isotropic layer of 1\,\ohmm, a 2.3\,km thick, anisotropic (vertical transverse isotropy, VTI) layer of $\rho_\text{h}=2\,\ohmm$ and $\rho_\text{v}=4\,\ohmm$, and finally a resistive, isotropic basement consisting of a lower halfspace of $1000\,\ohmm$.
 The survey uses a 200\,m long, 800\,A source  with frequency $f=1\,$Hz at a single position, and three receiver lines of 101 receivers each.
@@
 The second and the third row show the relative percentage error of the inline and the broadside receivers, respectively; note that for the 1D case the two broadside lines for $y=\pm3\,$km are identical.
-
 %
-\plot*{results-layered}{width=\textwidth}{Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-layered}
+  \caption{Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
 The relative percentage error of the four 3D modellers are shown in the second and the third row for the inline and broadside responses, respectively.}
+  \label{fig:results-layered}
+\end{figure*}
 %
@@
 As the aim of this study is to focus on accuracy of the simulations and compare discretization approaches, we chose to use the same mesh as in the \emg3d simulation.
-
+%
 The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
-
 %
-\tabl[bthp]{comp-layered}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}{
+\begin{table*}
+\begin{minipage}{10cm}
   \centering
+  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
+\label{tbl:comp-layered}
   \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
   \toprule
-  %
-       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
+  Code & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
   \midrule
-  %
   \custem & 24 &   118 &  97.8 & 1531824 \\ % dof: 3063648 / 2 (Real+Imag -> Complex)
@@
   \simpeg &  4 & 10089 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
-  %
   \bottomrule
-\end{tabular}}%
+\end{tabular}
+\end{minipage}
+\end{table*}
 %
@@
 %
-\plot*{model-block}{width=.6\textwidth}{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
+\begin{figure*}
+  \centering
+  \includegraphics[width=.6\linewidth]{figures/model-block}
+  \caption{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
+  \label{fig:model-block}
+\end{figure*}
 %
@@
 %
-\plot*{results-block}{width=\textwidth}{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the NRMSDs (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-block}
+  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the NRMSDs (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+  \label{fig:results-block}
+\end{figure*}
 %
 
-I few interesting points stand out:
+A few interesting points stand out:
 \begin{enumerate}
@@
 %
-\tabl[bthp]{comp-block}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}{
+\begin{table*}
+\begin{minipage}{10cm}
   \centering
+  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}
+\label{tbl:comp-block}
   \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
   \toprule
-  %
-       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
+  Code & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
   \midrule
-  %
   \custem & 24 &   158 & 115.9 & 1646736 \\ % dof: 3293472 / 2  (Real+Imag -> Complex)
@@
   \simpeg &  4 & 10295 & 280.4 & 4813216 \\ % nprocs: 1*4 threads
-  %
   \bottomrule
-\end{tabular}}%
+\end{tabular}
+\end{minipage}
+\end{table*}
 %
@@
 %
-\plot*{model-marlim}{width=\textwidth}{MR3D horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position and with major formations annotated.
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/model-marlim}
+  \caption{MR3D horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position and with major formations annotated.
 Air (not shown in the model), seawater, and the salt layer are electrically isotropic, everything else has VTI with $\lambda=\sqrt{2}$.
 The receiver is located on the seafloor, and the sources fly 50\,m above the seafloor.}
+  \label{fig:model-marlim}
+\end{figure*}
 %
@@
 %
-\plot*{results-marlim-responses}{width=\textwidth}{MR3D comparison between our codes (grey lines) and the published data (coloured lines).
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-marlim-responses}
+  \caption{MR3D comparison between our codes (grey lines) and the published data (coloured lines).
 The grey lines under the coloured lines are not visible in most areas, meaning that they are very similar.
 However, there are three notable zones, (1) to (3), which are explained further in the text.}
+  \label{fig:results-marlim-responses}
+\end{figure*}
 %
@@
 %
-\plot*{results-marlim_2published}{width=\textwidth}{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_2published}
+  \caption{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
 Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
+  \label{fig:results-marlim_2published}
+\end{figure*}
 %
@@
 %
-\plot*{results-marlim_2ours}{width=\textwidth}{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours}
+  \caption{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
 \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
 This also shows that the biggest impact in 3D forward modelling comes from the discretization.}
+  \label{fig:results-marlim_2ours}
+\end{figure*}
 %
@@
 %
-\plot*{results-marlim_big}{width=\textwidth}{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively.
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_big}
+  \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively.
 The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
+  \label{fig:results-marlim_big}
+\end{figure*}
 %
@@
 %
-\plot*{results-marlim_survey}{width=\textwidth}{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_survey}
+  \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
+  \label{fig:results-marlim_survey}
+\end{figure*}
 %
@@
 %
-\tabl[bthp]{comp-marlim}{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}{
+\begin{table*}
+\begin{minipage}{10cm}
   \centering
+  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}
+\label{tbl:comp-marlim}
   \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
   \toprule
-  %
-       & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
+  Code & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
   \midrule
-  %
   \custem & 64 &  872 & 230.1 & 1918106 \\ % dof: 3836212 / 2 (Real+Imag -> Complex)
@@
   \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
-  %
   \bottomrule
-\end{tabular}}%
+\end{tabular}
+\end{minipage}
+\end{table*}
 %
@@
 %
-\plot*{results-marlim_allmodels}{width=\textwidth}{The resistivity model as obtained from the three different discretizations using rectilinear, octree, and tetrahedral meshes (3$\times$ vertical exaggeration).}
+\begin{figure*}
+  \centering
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_allmodels}
+  \caption{The resistivity model as obtained from the three different discretizations using rectilinear, octree, and tetrahedral meshes (3$\times$ vertical exaggeration).}
+  \label{fig:results-marlim_allmodels}
+\end{figure*}
 %
@@
 
-\section{Acknowledgement}
+\section{Data}
+
+All files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
+For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}.
+
+\begin{acknowledgments}
 
@@
 The work of L.H. received funding from the National Science Foundation EarthCube program under award 1928406.
-
-\section{Data}
-
-All files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
-For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}.
+\end{acknowledgments}
 
 % REFERENCES
-\bibliographystyle{Refs}  % Modified SEG bibliography style.
+\bibliographystyle{gji}
 \bibliography{Refs}
 
+\label{lastpage}
+
 \end{document}

### 2020-10-23 manuscript/Manuscript.tex
Submission version

@@
 
-\title[Open-source 3D CSEM modelling]{Open-source landscape for 3D CSEM modelling}
+\title[3D CSEM Open-Source Landscape]{Open-source landscape for 3D CSEM modelling}
 
@@
 \begin{keywords}
-  Controlled source electromagnetics (CSEM); Numerical modelling; Electrical
-  properties.
+  Controlled source electromagnetics (CSEM); Numerical modelling; Electrical properties.
 \end{keywords}
@@
 The most commonly applied methods to solve Maxwell's equation are the IE method \citep{GJI.74.Raiche, RS.02.Hursan, GEO.06.Zhdanov, GP.10.Tehrani, CAG.16.Kruglyakov, MGS.17.Kruglyakov} and different variations of the differential equation (DE) method, such as finite differences (FD) \citep{GEO.93.Wang, RS.94.Druskin, RSC.94.Mackie, GEO.09.Streich, CAG.13.Sommer}, finite elements (FE) \citep{GEO.04.Commer, GJI.11.Schwarzbach,GEO.12.daSilva, GJI.13.Grayver, GJI.13.Puzyrev, SEG.16.Zhang}, and finite volumes (FV) \citep{EM.90.Madsen, SIAM.01.Haber, PIER.01.Clemens, GEO.14.Jahandari}.
-There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or octree meshes \citep{ECP.07.Haber}.
+There are also many different types of discretization, where the most common ones are regular grids (Cartesian, rectilinear, curvilinear), mostly using a Yee grid \citep{IEEE.66.Yee} or a Lebedev grid \citep{CMMP.64.Lebedev}, but also unstructured tetrahedral grids \citep{SEG.16.Zhang, CAG.17.Cai}, hexagonal meshes \citep{CAG.14.Cai}, or octree meshes \citep{ECP.07.Haber}.
 
@@
 As a result, in many areas of the geosciences, we are seeing a shift away from a one-way distribution of (open-source) code towards building global communities around open projects.
-Other notable Python projects with an open model of development within the same realm as the codes under considerations are \texttt{pyGIMLi} \citep{CAG.17.Rucker}, \texttt{Fatiando} \citep{JOSS.18.Uieda}, \texttt{GemPy} \citep{GMD.19.DeLaVarga}, and \texttt{PyVista} \citep{JOSS.19.Sullivan}.
+Other notable Python projects with an open model of development within the same realm as the codes under consideration are \texttt{pyGIMLi} \citep{CAG.17.Rucker}, \texttt{Fatiando} \citep{JOSS.18.Uieda}, \texttt{GemPy} \citep{GMD.19.DeLaVarga}, and \texttt{PyVista} \citep{JOSS.19.Sullivan}.
 
@@
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
-We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
+% We could add maths here; but we would need to introduce all the symbols. For now, we leave it out.
 % ($\vec{n}\times\vec{E} = 0; \vec{n}\cdot\vec{H} = 0$)
@@
 For the parallel forward modelling computations, a highly scalable MPI (message passing interface) domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
-This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing (HPC) architectures).
+This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing [HPC] architectures).
 
@@
 As the aim of this study is to focus on accuracy of the simulations and compare discretization approaches, we chose to use the same mesh as in the \emg3d simulation.
-%
+
 The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
@@
 \begin{equation}
-  \mr{NRMSD~(\%)} = 200 \frac{|R_1 - R_2|}{|R_1| + |R_2|}\ .
+  \mr{NRMSD~(\%)} = 200\,\frac{|R_1 - R_2|}{|R_1| + |R_2|}\ ,
   \label{eq:nrmsd}
@@
 %
+to which we refer as simply the \emph{normalised difference} throughout the paper.
 
 The results for the three receiver lines $y=-3;0;+3\,$km are shown in the left, middle, and right columns of Figure~\ref{fig:results-block}, respectively.
-The top row shows the result of \emg3d, as an example, and the bottom row shows the NRMSDs between the absolute responses of the codes.
+The top row shows the result of \emg3d, as an example, and the bottom row shows the normalised differences between the absolute responses of the codes.
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-block}
-  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the NRMSDs (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
   \label{fig:results-block}
@@
 \begin{enumerate}
-  \item The error levels between the different codes are overall comparable; the NRMSD is generally below a few percent, increasing towards larger offsets.
-  \item The NRMSD between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
-The generally low NRMSD is because these codes use the same rectilinear mesh for modelling.
-The increasing NRMSD towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition in this example.
+  \item The error levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
+  \item The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
+The generally low normalised difference is because these codes use the same rectilinear mesh for modelling.
+The increasing normalised difference towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition in this example.
   \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
@@
   \item There are some noticeable differences for positive offsets of the broadside $E_y$ and $E_z$ components, which are likely related to the bathymetry.
-The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not exactly know what it does internally.
+The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not know in detail what it does internally.
 See the discussion around Figure~\ref{fig:results-marlim_2published}.
@@
 It is important to note that the published results nor any of our results is the \emph{thruth}, but the closer they agree with each other the more certain we can be of the outcomes.
-Figure~\ref{fig:results-marlim_2published} shows the NRMSDs between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
+Figure~\ref{fig:results-marlim_2published} shows the normalised differences between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_2published}
-  \caption{NRMSDs for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
+  \caption{Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
 Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
@@
 %
-A few conclusions can be drawn from this figure: In general the NRMSD is roughly 10\,\% or less.
-The structured meshes have in some cases a smaller NRMSD, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in other cases the unstructured tetrahedral meshes, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
-Some NRMSDs have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
-The origin of this zigg-zagg pattern is most likely the bathymetry.
+A few conclusions can be drawn from this figure: In general the normalised difference is roughly 10\,\% or less.
+The structured meshes have in some cases a smaller normalised difference, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in other cases the unstructured tetrahedral meshes, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
+Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
+The origin of this zigzag pattern is most likely the bathymetry.
 We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
@@
 
-The importance of the meshing to the result can be seen in Figure~\ref{fig:results-marlim_2ours}, where we compute the NRMSDs between our codes.
+The importance of the meshing to the result can be seen in Figure~\ref{fig:results-marlim_2ours}, where we compute the normalised differences between our codes.
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours}
-  \caption{NRMSDs, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
+  \caption{Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
 \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
@@
 %
-The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their NRMSD is generally below 0.03\,\%.
+The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their normalised difference is generally below 0.03\,\%.
 The reason is simple: \custem and \petgem use the exactly same mesh for the computation of this example, the only difference is therefore the solver.
@@
 As these two are so similar we compare \emg3d and \simpeg only to \custem in Figure~\ref{fig:results-marlim_2ours}, as the comparisons to \petgem would look the same.
-But in general the NRMSDs between our codes look similar as in the comparison with the published results, and the principal source of the difference must be in the different discretizations.
+But in general the normalised differences between our codes look similar as in the comparison with the published results, and the principal source of the difference must be in the different discretizations.
 
@@
 %
-This figure is interesting for various points, and the differences between the three meshes are very obvious.
-Particularly visible is the advantage of octree and tetrahedra to create large cells outside of the region of interest to push away the boundary, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
+This figure is interesting for various points, as the differences between the three meshes are clearly visible.
+Particularly the advantage of octree and tetrahedra to create large cells outside of the region of interest to push away the boundary can be seen, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
 The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.
@@
 Two kilometres below the seafloor, as an example, there are already significant changes visible, purely due to meshing.
-This is an important insight that has to be taken into account when interpreting inversion results.
+This is an important insight that has to be taken into account when interpreting modelling results and the feasibility for inversions.
 
@@
 Looking individually at the real or imaginary part results in much higher error values, but those are related to the zero crossings of the responses.
-The cross-validation of the results for the block model yields a similar picture, with NRMSD values within a few percents.
+The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
 For the large, complex MR3D model it is a bit different.
 First it can be noted that the misfits are higher for higher frequencies.
-For the lowest frequency, 0.125\,Hz, the NRMSD is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
+For the lowest frequency, 0.125\,Hz, the normalised difference is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
 For higher frequencies these numbers rise to the order of $\pm10\,$\%.
@@
 This has been shown within the process of this study.
-Our first attempt were based on the originally published, fine MR3D model.
-This model is very detailed, but its extent is too small in x- and y-directions for CSEM computations, and each of our codes did its own extrapolation.
-However, none of the codes were able to reproduce the published results.
-The reason is that there are many ways how you can extrapolate a model.
+Our first attempts were based on the originally published, fine MR3D model.
+This model is very detailed, but its extent is too small in x- and y-directions for CSEM computations.
+In order to represent the fine-scale model on a mesh suitable for computation, each of our codes did its own upscaling and extrapolation.
+However, we were unsuccessful in our attempt to reproduce the published results.
+The reason is that there are many ways how you can extrapolate a model, and without knowing the details of how MR3D represents the model on the computational mesh, we could not re-produce this step.
 We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model.
-It is only with this model that we were able to get comparable results.
+It is only with this model that we were able to obtain comparable results.
 
@@
 One of the key insights we gained from this study is that creating appropriate meshes is a difficult and time-consuming task.
-While there exist now several open-source 3D CSEM codes the capability for automatic meshing lacks behind and currently remains a largely manual task requiring experience in the field.
+While there now exist several open-source 3D CSEM codes the capability for automatic meshing lacks behind and currently remains a largely manual task requiring experience in the field.
 It is important to state that the chosen models favour structured meshes.
@@
 MR3D would be an ideal scenario for unstructured meshes, as it is based on also published irregular lithological horizons.
-Since the corresponding resistivity model, however, was defined on a regular grid, we were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
+Since the corresponding resistivity model, however, was defined on a regular grid, the FE codes were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
 We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
@@
 Three resistive blocks are added to the layered model to increase complexity in the second example.
-The cross-validation of the outcomes of the different codes shows a NRMSD of a few percent, hence in a similar range as the relative error in the layered model.
+The cross-validation of the outcomes of the different codes shows a normalised difference of a few percent, hence in a similar range as the relative error in the layered model.
 The third example is Marlim R3D, a realistic, complex, marine resistivity model.
 The model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
-In this scenario the NRMSD is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization.
+In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization.
 The required runtime and memory consumption is primarily controlled by the used solver.
@@
 
-All files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
+The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
 For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}.

### 2020-11-20 presentation/2020-12-14_Presentation.tex
AGU2020

\documentclass[xcolor=svgnames, aspectratio=169]{beamer}
\usepackage{pgfpages}
\setbeameroption{
  hide notes
  % show notes
  % show notes on second screen=right  % requires pgfpages
  % show only notes
}

\definecolor{mygreen}{rgb}{.125,.5,.25}

\setbeamertemplate{note page}{
  \vspace{.5cm}\hspace{.8\textwidth}
  \vspace{-2.7cm}
  \fbox{\insertslideintonotes{.2}}
  \pagecolor{white}
  \LARGE
  \begin{tikzpicture}[remember picture,overlay]
    \node [color=mygreen, opacity=0.8, xshift=-.3cm, yshift=-1.9cm, rotate=90] (current page.north west) {\bfseries N O T E S};
  \end{tikzpicture}
  \footnotesize
  \insertnote
}

% --- THEME ---
\usetheme[progressbar=frametitle]{metropolis}

\useoutertheme{metropolis}
\useinnertheme{metropolis}
\usefonttheme{metropolis}
\usecolortheme{spruce}  % spruce, metropolis, dove, crane, beaver, seagull
\setbeamercolor{background canvas}{bg=white}
\usecolortheme[named=mygreen]{structure}
\usefonttheme[onlymath]{serif}

% --- HACKS ---
% Hide numbers on standout slides.
\setbeamertemplate{frame numbering}{
    \ifbool{metropolis@standout}{}{
        \insertframenumber
    }
}
\setbeamertemplate{frame numbering}[counter]  % none, counter, fraction

% Avoid font-warning with itemize bullets.
\renewcommand\textbullet{\ensuremath{\bullet}}

% --- PACKAGES ---
\usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

% \usepackage{appendixnumberbeamer}
\usepackage{upquote}
\usetikzlibrary{positioning}
% \usepackage{minted}
\usepackage{multicol}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{siunitx}

% --- SETTINGS ---
\graphicspath{{./figures/}}
\setlength{\fboxsep}{0pt}

% --- OWN COMMANDS ---
\newcommand{\bdra}{\ensuremath{\boldsymbol \Rightarrow }~}
\newcommand{\dra}{\ensuremath{\Rightarrow }~}
\newcommand{\mr}[1]{\mathrm{#1}}
\newcommand{\emg}[2]{\texttt{emg#1#2}\xspace}
\newcommand{\empymod}{\texttt{empymod}\xspace}
\newcommand{\simpeg}{\texttt{SimPEG}\xspace}
\newcommand{\discretize}{\texttt{discretize}\xspace}
\newcommand{\custem}{\texttt{custEM}\xspace}
\newcommand{\petgem}{\texttt{PETGEM}\xspace}
\newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
\newcommand{\rmk}[1]{{\color{red}\bfseries #1}}
\newcommand{\maybe}[1]{{\color{gray} #1}}
\newcommand{\todo}{{\color{red}\texttt{TODO:}}\xspace}

% --- TITLE-STUFF ---
\title{Open-Source Landscape for Three-Dimensional Controlled-Source Electromagnetic Modeling\vspace{-1em}}
% \subtitle{}
\author{\vspace{-1em}
  Dieter Werthmüller\\
  Raphael Rochlitz\\
  Octavio Castillo Reyes\\
  Lindsey Heagy\\[1em]
  \includegraphics[height=.7cm]{Logo-TUD}
  \includegraphics[height=.5cm]{Logo-LIAG}\\
  \includegraphics[height=.6cm]{Logo-BSC}
  \includegraphics[height=.4cm]{Logo-BUC}\\
}
\date{\scriptsize 14th December 2020\\
  \maybe{\tiny
  \emph{Paper Number} GP005-06;
  \emph{Session} Frontiers in Electromagnetic (EM) Geophysics I;
  10:00--11:00 PST
 }
}

\institute{%
  \begin{tikzpicture}[remember picture,overlay]
    \node[xshift=.5\paperwidth, yshift=.66cm] at (current page.south west) {\includegraphics[width=\paperwidth]{Logo-AGU}};
  \end{tikzpicture}
  \begin{tikzpicture}[remember picture,overlay]
    \node[xshift=.67\paperwidth, yshift=4.1cm] at (current page.south west) {\includegraphics[width=.6\paperwidth]{model-marlim}};
  \end{tikzpicture}
}

% Title slide is one, so I want it to start at number 2 after the title.
\addtocounter{framenumber}{1}

% --- SLIDES ---
\begin{document}
\metroset{block=fill}  % Fills the block-environment

% guvcview for small video
% pdfpc for presenting
% - pdfpc 2020-12-14_Presentation.pdf --notes right -c  # Fails; then
% - pdfpc 2020-12-14_Presentation.pdf  -d 15
% vokoscreenNG for recording

% --------------------------------------------------------------------------- %
% - Presentation uploaded by Friday, 20/11                                    %
% - Max 15 minutes                                                            %
% - Maximum resolution: 1920x1080 pixels                                      %
% - Minimum resolution: 854x480 pixels                                        %
% - File format: MP4 (preferred), MOV, MPEG-2 or WebM                         %
% - Aspect ratio: 16:9 horizontal                                             %
% - reducing its size                                                         %
% - Maximum file size: 1 GB                                                   %
% --------------------------------------------------------------------------- %

% 01 -    01 : Title - Overview
% 02 -    02 : Intro to codes, problem
% 03 - 03-06 : Layered results
% 04 - 07-08 : Block results
% 05 -   -   : Marlim results
% 06 -       : Discussion
% 07 -       : Conclusions & Outlook
% 08 -       : References

\maketitle % ---------------------------------------------------------------- %
\note{
  \begin{itemize}
    \item Who am I, who are my co-authors
    \item What we have been working -- see MarlimR3D section:
      \begin{itemize}
        \item Open-source, huge resistivity model, 466 million cells
        \item 10, even 5 yrs ago impossible to simulate data\\
          with easily available open-source codes
        \item We look at four recent, open-source 3D CSEM codes; changes in the
          last years
        \item Able to model large-/industry-scale models
      \end{itemize}
    \item However, these new possibility open-up many more questions: How
      accurate are the results, what is the influence of the mesh type, etc.
    \item I will walk through the steps from
      \begin{itemize}
        \item verification (analytical solution),
        \item validation amongst codes (block), and
        \item validation with code from industry (MarlimR3D);
        \item discussion about mesh type;
        \item setting up simulation vs computation
      \end{itemize}
  \end{itemize}
}

\begin{frame}[c]%
  {Validation of large-scale 3D CSEM modelling using the\\
   open-source codes \custem, \emg3d, \petgem, and \simpeg}
  \vspace{.3cm}
  \begin{columns}[c]
    \column{.25\textwidth}
      \centering
      \includegraphics[width=2.5cm]{Logo-emg3d}\\
      \href{https://empymod.github.io}{empymod.github.io}\\[.5cm]
      \includegraphics[width=2.5cm]{Logo-SimPEG}\\[-.4cm]
      \href{https://simpeg.xyz}{simpeg.xyz}\\[1cm]
    \column{.25\textwidth}
      \centering
      \includegraphics[width=3.0cm]{Logo-PETGEM}\\
      \href{http://petgem.bsc.es}{petgem.bsc.es}\\[1cm]
      \includegraphics[width=2.5cm]{Logo-custEM}\\
      \href{https://custem.rtfd.io}{custem.rtfd.io}\\[.5cm]~

    \column{.4\textwidth}
      \centering
      \includegraphics[width=\textwidth, trim=0 600 0 0, clip]{CSEM_Method3}
      \begin{tikzpicture}[remember picture,overlay]
        \node [color=white, xshift=1.5cm, yshift=1.4cm, rotate=60] (current page.south west) {\small \copyright\ emgs.com};
      \end{tikzpicture}
  \end{columns}
  \vspace{-.3cm}
  \small \alert{Werthmüller, Rochlitz, Castillo-Reyes, and Heagy, 2020},
  submitted to GJI; \href{https://arxiv.org/abs/2010.12926}{arXiv:~2010.12926}
  \note{
    \begin{itemize}
      \item We are core-devs of the four codes under consideration
      \item \custem and \petgem are finite element CSEM codes; both work in
        the\\ frequency domain, \custem also in the time domain; using
        tetrahedral meshes
      \item \simpeg is a more general framework for geophysical modelling and
        inversion:\\ Gravity, Magnetics, DC resistivity, IP, EM ($t$- and
        $f$-domain; controlled- and natural-src),\\ and more; contains
        1D, 2D, and 3D rectilinear, curvilinear, and octree meshes
      \item \emg3d is a matrix-free multigrid solver for 3D EM diffusion using
        rectilinear meshes.
      \item \custem, \petgem, and \simpeg use third party direct solvers such
        as MUMPS or PARDISO to solve the system of linear equations, \emg3d is
        a, iterative, solver on its own
      \item SimPEG is a community effort, other codes are currently mostly
        one-man shows
      \item Note: We look at the marine CSEM case as shown in the right figure;
        we are looking for resistive bodies in a conductive environment;
        node-based, using reciprocity; so just at one, tightly limited
        scenario; we will come back to that at the end
      \item Submitted to Geophysical Journal International, preprint on arXiv
      \item All are open-source: \simpeg MIT, \emg3d Apache-2.0, \petgem
        BSD-3-Clause, \custem GPL-3.0
    \end{itemize}
  }
\end{frame}

\section{Numerical Results} % ----------------------------------------------- %

\begin{frame}[t]%
  {Verification for layered model using semi-analytical solutions\\
   shows a relative amplitude error in the order of 1\,\% or less}
  %
  \begin{columns}[c]
    %
    \column{.45\textwidth}
    %
      \centering
      \includegraphics[width=\textwidth]{model-layered}\\
      \hspace{1cm}\includegraphics[width=.5\textwidth]{model-layered-src}
    %
    \column{.6\textwidth}
    %
      \includegraphics[width=\textwidth]{results-layered}
    %
  \end{columns}
  %
  \note{
    \begin{itemize}
      \item Source at x=8, 50\,m above seafloor; 200\,m, 800\,A, receivers on
        the seafloor
      \item Results of the four codes can visually not be distinguished
      \item Relative error from 0.01\,\% to 100\,\%
      \item Black lines mark the 1\,\% line
      \item The relative error of the amplitude is mostly below 1\,\%
      \item Looking at the absolute error plot now:
        \begin{itemize}
          \item Big relative errors can be observed close to the source
          \item Differences in how the source is defined
          \item Higher errors for \custem at the edges: explain the
            gridding approach of the thin layer of \custem
          \item Differences between PEC and PMC boundary conditions:
            \petgem and \emg3d used PEC, which seems to work better in this
            case, \simpeg and \custem used PMC
        \end{itemize}
      \item In paper also broadside; CPU/RAM/dof
      \item For the semi-analytical solutions we used \empymod
    \end{itemize}
  }
  %
\end{frame}

\begin{frame}[t]%
  {Adding three resistive blocks to the layered model requires\\
   the normalised difference instead of the relative error}
  %
  \begin{columns}[c]
    %
    \column{.6\textwidth}
      \includegraphics[width=.9\textwidth]{model-block}
    %
    \column{.4\textwidth}
      \centering
      \alert{Normalised Root-Mean Square Difference} (NRMSD) in
      percent:\\
      %
      \begin{equation}
        200\,\frac{|R_1 - R_2|}{|R_1| + |R_2|} \nonumber
      \end{equation}
      %
      \vspace{.5cm}\\
      %
      {\footnotesize After \emph{Dublin Test Model 1},\\
      \alert{Miensopust et al., 2013}, GJI}
    %
  \end{columns}
  %
  \note{
    \begin{itemize}
      \item Background model is the layered model from before
      \item We embed three resistive blocks and look at three acquisition
        lines
      \item The blocks are an adaption of the Dublin Test Model 1 from\\
        Miensopust et al., 2013; similar study for MT data
      \item As there are no analytical solutions we have to compare codes;\\
        hence \emph{validation}, not \emph{verification}
      \item Instead of the relative error we use therefore the NRMSD (and a
        conservative version thereof)
    \end{itemize}
  }
\end{frame}

% \begin{frame}[t]%
%   {Results from different meshes and different\\
%    codes can visually not be distinguished}
%   %
%   \vspace{.5cm}
%   \begin{columns}[c]
%     %
%     \column{.35\textwidth}
%       \includegraphics[width=.9\textwidth, trim=0 0 123.5 0, clip]{model-block}
%     %
%     \column{.65\textwidth}
%     %
%       \centering
%       \includegraphics[width=\textwidth]{results-block-all}\\
%       %
%       \vspace{ .5cm}
%       \begin{table}
%         \footnotesize %small %tiny
%         \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
%           % \begin{tabular}{lrrrr}
%           % \toprule
%           Code & \#Procs & {CPU (s)} & {RAM (GiB)}   & {\#dof} \\
%           \midrule
%           \custem & 24 &   158 & 115.9 & 1646736 \\
%           \emg3d  &  1 &   115 &   0.4 & 4813216 \\
%           \petgem & 24 &    238 &  152.8 & 2455868 \\
%           \simpeg &  4 & 10295 & 280.4 & 4813216 \\
%           % \bottomrule
%         \end{tabular}
%       \end{table}
%     %
%   \end{columns}
%   %
%   \note{
%     \begin{itemize}
%       \item Responses: Absolute values plotted
%       \item Plotted all results on top of each other: no differences visible
%       \item The responses of the resistive cubes are visible
%       \item Regarding computational costs:
%         \begin{itemize}
%           \item First: Comparison was not phrased as a comp. competition;
%             entire different exercise
%           \item Second: Ran on very different machines, from laptop to
%             supercomputers
%           \item The objective is: what can we do with different codes
%           \item How do we obtain good results with different codes
%           \item Much more time invested in model building than computation
%           \item \simpeg: fine grid (precision); later taking advantage of
%             octree meshes
%           \item Other three $\pm$ same speed in real-world
%             time, but \custem/\petgem used 24 processes
%           \item It can be directly seen for the direct solvers: more \#doc,
%             more RAM
%           \item Rectilinear grids required the most dofs
%           \item Layered model is basically identical
%         \end{itemize}
%     \end{itemize}
%   }
% \end{frame}

\begin{frame}[t]%
  {Validation between the codes shows a\\
   normalised difference of 1--2\,\% or less}
  %
  \vspace{.5cm}
  \begin{columns}[c]
    %
    \column{.35\textwidth}
      \includegraphics[width=.9\textwidth, trim=0 0 123.5 0, clip]{model-block}
    %
    \column{.65\textwidth}
    %
      % \includegraphics[width=\textwidth]{results-block-all-2}
      \includegraphics[width=\textwidth]{results-block}
    %
  \end{columns}
  %
  \note{
    \begin{itemize}
      \item Because they are basically identical, we just show the
        response of one code
      \item The responses of the resistive cubes are visible
      \item Shows also real and imaginary contributions
      \item The NRMSD is generally around 1\,\% or less
      \item Not surprising, as we could not see a visual difference
      \item There are 6 combinations for the normalized difference
        of the four codes
      \item Only middle plot shows all six
      \item On the left are three, on the right the other three
      \item \simpeg and \emg3d use same grid, so lower differences
      \item We use four different codes, two different mesh types, and the
        results are basically identical, which is a good first result
      \item Now we move to a huge model\ldots
    \end{itemize}
  }
\end{frame}

\begin{frame}[c]
  {Marlim R3D model: Responses at receiver locations\\
   look visually the same for all relevant responses}
  %
  \begin{columns}[c]
    \column{.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{model-marlim}\\
      %
      {\footnotesize Marlim R3D:\\
        \alert{Correa and Menezes, 2019}, Geophysics}
    \column{.55\textwidth}
      \centering
      \includegraphics[width=\textwidth]{results-marlim-responses}
  \end{columns}
  \note{
    \begin{itemize}
      \item IMPORTANT: Reciprocity, hence source-receiver swap
      \item Very complex resistivity model
      \item Responses modelled with software from EMGS, in the time domain
      \item The responses look visually the same, except\ldots
      \item \ldots $E_x$ inline, which is about 2 orders of magnitudes lower
      \item Full grid of sources and receivers for 6 frequencies
      \item We modelled 1 receiver \dra source, two source \dra receiver lines
    \end{itemize}
  }
\end{frame}

\begin{frame}[c]
  {Normalised difference to published data is mostly\\
   below 10\,\% and very different from code to code}
  \centering
  %
  ~\vfill
  \includegraphics[width=\textwidth]{results-marlim_2published}
  %
  \note{
    \begin{itemize}
      \item $E_x$ inline, strongest component, a few percents
      \item Others up to 10 percent, higher frequencies more
      \item Some codes are more similar in different places
      \item funny shape due to bathymetry
    \end{itemize}
  }
\end{frame}

\begin{frame}[c]
  {Normalised difference between our codes\\
   is very similar and mostly below 10\,\%}
  \centering
  %
  ~\vfill
  \includegraphics[width=\textwidth]{results-marlim_2ours}
  %
  \note{
    \begin{itemize}
      \item Comparison between our codes looks very similar
      \item Noteworthy is \custem and \petgem, because of same grid
      \item Also \emg3d and \simpeg, even though not same mesh
    \end{itemize}
  }
\end{frame}

% \begin{frame}
%   {Very insightful is to look at the entire\\
%    meshes and their different behaviours}
%   \centering
%   %
%   ~\vfill
%   \includegraphics[width=.9\textwidth]{results-marlim_big}
%   %
%   \note{
%     \begin{itemize}
%       \item Computational domain very different
%       \item \simpeg and emg3d could probably reduce their domains
%       \item Advantages of Octree and Tetrahedra in comparison to Rectilinear
%     \end{itemize}
%   }
% \end{frame}

\begin{frame}
  {Very insightful is to look at the entire\\
   meshes and their different behaviours}
%   {While the responses at receiver locations are identical,\\
%    the fields start to vary greatly when moving away}
  \centering
  %
  ~\vfill
  \includegraphics[width=.9\textwidth]{results-marlim_survey}
  %
  \note{
    \begin{itemize}
      \item White band includes the receiver lines
      \item Responses are very similar there
      \item Outside not so much!
      \item Very insightful for inversions etc
    \end{itemize}
  }
\end{frame}

\begin{frame}
  {A look at the models in different mesh yields interesting\\
   insights with regards to recoverability in inversions}
  \centering
  \includegraphics[width=\textwidth]{results-marlim_allmodels}
    \begin{table}
      \footnotesize %small %tiny
      \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
        % \begin{tabular}{lrrrr}
        % \toprule
        Code & \#Procs & {CPU (s)} & {RAM (GiB)}   & {\#dof} \\
        \midrule
        \custem & 64 &  872 & 230.1 & 1918106 \\
        \emg3d  &  1 & 1254 &   0.6 & 5998992 \\
        \petgem & 96 &  524 & 175.4 & 1918106 \\
        \simpeg &  4 &  422 &  12.8 &  720146 \\
        % \bottomrule
      \end{tabular}
    \end{table}
    \note{
      \begin{itemize}
        \item Models show clearly what we have seen before
        \item dof: tetrahedra about 2 million dofs, rectil. about 2 million
          cells; octree only about 240,000 cells
      \end{itemize}
    }
\end{frame}

\section{Conclusions and Outlook} % ----------------------------------------- %

\begin{frame}%
  {References}
  \tiny
  %
  \begin{columns}
    \column{1.1\textwidth}
  %
  \setlength{\columnseprule}{0.4pt}
  % \setlength{\columnsep}{3em}
  \begin{multicols}{2}
  A more extensive reference list can be found in:\\[.5em]
  {\bfseries \alert{Werthmüller, D., R. Rochlitz, O. Castillo-Reyes, and L.
  Heagy, 2020}, Open-source landscape for 3D CSEM modelling},\\
  submitted to Geophysical Journal International,
  \href{https://arxiv.org/abs/2010.12926}{arXiv:~2010.12926}.\\[.5cm]
  %
  {\bfseries Modelling codes: \custem, \emg3d, \petgem, \simpeg, and
  \empymod:}
  \begin{description}[2cm]
    %
    % \item[Castillo-Reyes et al., 2019,] {\bfseries Parallel 3D marine
    %   controlled-source electromagnetic modeling using high-order
    %   tetrahedral Nédélec elements}, Geophysical Journal International,
    %   219, 39--65,
    %   \href{https://doi.org/10.1093/gji/ggz285}{doi:~10.1093/gji/ggz285}.
    \item[Castillo-Reyes et al., 2018,] {\bfseries PETGEM: A parallel code
      for 3D CSEM forward modeling using edge finite elements}, Computers \&
      Geosciences, 119, 126--136,
      \href{https://doi.org/10.1016/j.cageo.2018.07.005}%
      {doi:~10.1016/j.cageo.2018.07.005}.
    %
    \item[Cockett et al., 2015,] {\bfseries SimPEG: An open source framework
      for simulation and gradient based parameter estimation in geophysical
      applications}, Computers \& Geosciences, 85, 142--154,
      \href{https://doi.org/10.1016/j.cageo.2015.09.015}%
      {doi:~10.1016/j.cageo.2015.09.015}.
    %
    \item[Rochlitz et al., 2019,] {\bfseries custEM: customizable finite
      element simulation of complex controlled-source electromagnetic data},
      Geophysics, 84, F17--F33,
      \href{https://doi.org/10.1190/geo2018-0208.1}%
      {doi:~10.1190/geo2018-0208.1}.
    %
    \item[Werthmüller, 2017,] {\bfseries An open-source full 3D
      electromagnetic modeler for 1D VTI media in Python: empymod},
      Geophysics, 82(6), WB9--WB19;
      \href{https://doi.org/10.1190/geo2016-0626.1}%
      {doi:~10.1190/geo2016-0626.1}.
    %
    \item[Werthmüller et al., 2019,] {\bfseries emg3d: A multigrid solver for
      3D electromagnetic diffusion}, Journal of Open Source Software, 4(39),
      1463;
      \href{https://doi.org/10.21105/joss.01463}{doi:~10.21105/joss.01463}.
    %
  \end{description}
  \columnbreak
  %
  {\bfseries Solvers \texttt{PETSc}, \texttt{MUPMS}, \texttt{FEniCS}, and
  \texttt{PARDISO}:}
  %
  \begin{description}[2cm]
    %
    \item[Abhyankar et al., 2018,] {\bfseries PETSc/TS: A modern scalable
      ODE/DAE solver library},
      \href{https://arxiv.org/abs/1806.01437}{arXiv:~1806.01437}.
    %
    \item[Amestoy et al., 2001,] {\bfseries A fully asynchronous multifrontal
      solver using distributed dynamic scheduling:} SIAM Journal on Matrix
      Analysis and Applications, 23, 15--41,
      \href{https://doi.org/10.1137/S0895479899358194}%
      {doi:~10.1137/S0895479899358194}.
    %
    \item[Langtangen et al., 2016,] {\bfseries Solving PDEs in Python: The
      FEniCS Tutorial I}, vol. 3 of Simula SpringerBriefs on Computing,
      Springer International Publishing,
      \href{https://doi.org/10.1007/978-3-319-52462-7}%
      {doi:~10.1007/978-3-319-52462-7}.
    %
    \item[Schenk and Gärtner, 2004,] {\bfseries Solving unsymmetric sparse
      systems of linear equations with PARDISO}, Future Generation Computer
      Systems, 20, 475--487,
      \href{https://doi.org/10.1016/j.future.2003.07.011}%
      {doi:~10.1016/j.future.2003.07.011}.
    %
  \end{description}
  %
  {\bfseries Marlim R3D model:}
  %
  \begin{description}[2cm]
    %
    \item[Correa and Menezes, 2019,] {\bfseries Marlim R3D: A realistic model
      for controlled-source electromagnetic simulations--Phase 2: The
      controlled-source electromagnetic data set}, Geophysics, 84,
      E293--E299, \href{https://doi.org/10.1190/geo2018-0452.1}%
      {doi:~10.1190/geo2018-0452.1}.
    %
  \end{description}
  %
  {\bfseries MT comparison study:}
  %
  \begin{description}[2cm]
    %
    \item[Miensopust et al., 2013,] {\bfseries Magnetotelluric 3-D inversion--a
      review of two successful workshops on forward and inversion code testing
      and comparison}, Geophysical Journal International, 193, 1216--1238,
      \href{https://doi.org/10.1093/gji/ggt066}{doi: 10.1093/gji/ggt066}.
    %
  \end{description}
  %
\end{multicols}
\end{columns}
\end{frame}

\begin{frame}[c]%  {}
  {More Comparisons \& Benchmarks\\
   Other Scenarios, other programming languages}
  %
  \begin{columns}
      %
    \column{.2\textwidth}
    \centering
      %
      ~\\[.5cm]
      \includegraphics[width=2.0cm]{Logo-emg3d}\\[.5cm]
      %
      \includegraphics[width=\textwidth, trim=0 500 0 0, clip]{CSEM_Method3}\\[1cm]
      %
      \includegraphics[width=2.0cm]{Logo-custEM}
      %
    \column{.5\textwidth}
    \centering
      %
    \phantom{~}\\[.5cm]
    \includegraphics[width=\textwidth, trim=40 235 150 0, clip]{results-marlim_big}\\[.5cm]
      %
      \includegraphics[width=\textwidth, trim=70 095 0 160, clip]{results-block}
      %
    \column{.3\textwidth}
    \centering
      %
      \includegraphics[width=3cm]{Logo-SimPEG2}\\[.5cm]
      %
      \includegraphics[width=\textwidth, trim=65 242 50 20, clip]{results-marlim-responses}\\[.5cm]
      %
      \includegraphics[width=2.5cm]{Logo-PETGEM}
      %
  \end{columns}
  %
  \note{
    \begin{itemize}
      \item See you \alert{14th December}!
      \item Shown: Analytical verification; simple validation; complex
        validation
      \item Four codes, three different mesh types
      \item It is all about the discretization, the solvers themselves do
        basically the same
      \item Most time is spent in creating the appropriate discretization
      \item Performance depends mostly on the used solver
      \item Examples favoured rectilinear and octree meshes, as they were all
        regular cubes
      \item Examples favoured iterative solvers, as we only used one source;
        when computing many sources the direct solvers could re-use the
        factorisations
      \item We need more validations and benchmarks like this for CSEM
      \item More scenarios: air borne, strong topography, loops, conductor in
        a resistor, etc
      \item Reference model which is delivered on horizons and as functions
        instead of cubes
      \item More codes, other languages
    \end{itemize}
  }
\end{frame}

\end{document}

### 2020-12-07 presentation/2020-12-14_Intro.tex

--- 2020-11-20 presentation/2020-12-14_Presentation.tex
@@
 \newcommand{\bdra}{\ensuremath{\boldsymbol \Rightarrow }~}
+\newcommand{\bdla}{\ensuremath{\boldsymbol \Leftarrow }~}
 \newcommand{\dra}{\ensuremath{\Rightarrow }~}
+\newcommand{\dla}{\ensuremath{\Leftarrow }~}
 \newcommand{\mr}[1]{\mathrm{#1}}
@@
 
-% --- TITLE-STUFF ---
-\title{Open-Source Landscape for Three-Dimensional Controlled-Source Electromagnetic Modeling\vspace{-1em}}
-% \subtitle{}
-\author{\vspace{-1em}
-  Dieter Werthmüller\\
-  Raphael Rochlitz\\
-  Octavio Castillo Reyes\\
-  Lindsey Heagy\\[1em]
-  \includegraphics[height=.7cm]{Logo-TUD}
-  \includegraphics[height=.5cm]{Logo-LIAG}\\
-  \includegraphics[height=.6cm]{Logo-BSC}
-  \includegraphics[height=.4cm]{Logo-BUC}\\
-}
-\date{\scriptsize 14th December 2020\\
-  \maybe{\tiny
-  \emph{Paper Number} GP005-06;
-  \emph{Session} Frontiers in Electromagnetic (EM) Geophysics I;
-  10:00--11:00 PST
- }
-}
-
-\institute{%
-  \begin{tikzpicture}[remember picture,overlay]
-    \node[xshift=.5\paperwidth, yshift=.66cm] at (current page.south west) {\includegraphics[width=\paperwidth]{Logo-AGU}};
-  \end{tikzpicture}
-  \begin{tikzpicture}[remember picture,overlay]
-    \node[xshift=.67\paperwidth, yshift=4.1cm] at (current page.south west) {\includegraphics[width=.6\paperwidth]{model-marlim}};
-  \end{tikzpicture}
-}
-
-% Title slide is one, so I want it to start at number 2 after the title.
-\addtocounter{framenumber}{1}
-
 % --- SLIDES ---
@@
 
-% guvcview for small video
-% pdfpc for presenting
-% - pdfpc 2020-12-14_Presentation.pdf --notes right -c  # Fails; then
-% - pdfpc 2020-12-14_Presentation.pdf  -d 15
-% vokoscreenNG for recording
-
-% --------------------------------------------------------------------------- %
-% - Presentation uploaded by Friday, 20/11                                    %
-% - Max 15 minutes                                                            %
-% - Maximum resolution: 1920x1080 pixels                                      %
-% - Minimum resolution: 854x480 pixels                                        %
-% - File format: MP4 (preferred), MOV, MPEG-2 or WebM                         %
-% - Aspect ratio: 16:9 horizontal                                             %
-% - reducing its size                                                         %
-% - Maximum file size: 1 GB                                                   %
-% --------------------------------------------------------------------------- %
-
-% 01 -    01 : Title - Overview
-% 02 -    02 : Intro to codes, problem
-% 03 - 03-06 : Layered results
-% 04 - 07-08 : Block results
-% 05 -   -   : Marlim results
-% 06 -       : Discussion
-% 07 -       : Conclusions & Outlook
-% 08 -       : References
-
-\maketitle % ---------------------------------------------------------------- %
-\note{
-  \begin{itemize}
-    \item Who am I, who are my co-authors
-    \item What we have been working -- see MarlimR3D section:
-      \begin{itemize}
-        \item Open-source, huge resistivity model, 466 million cells
-        \item 10, even 5 yrs ago impossible to simulate data\\
-          with easily available open-source codes
-        \item We look at four recent, open-source 3D CSEM codes; changes in the
-          last years
-        \item Able to model large-/industry-scale models
-      \end{itemize}
-    \item However, these new possibility open-up many more questions: How
-      accurate are the results, what is the influence of the mesh type, etc.
-    \item I will walk through the steps from
-      \begin{itemize}
-        \item verification (analytical solution),
-        \item validation amongst codes (block), and
-        \item validation with code from industry (MarlimR3D);
-        \item discussion about mesh type;
-        \item setting up simulation vs computation
-      \end{itemize}
-  \end{itemize}
-}
-
 \begin{frame}[c]%
-  {Validation of large-scale 3D CSEM modelling using the\\
-   open-source codes \custem, \emg3d, \petgem, and \simpeg}
+  {Open-Source Landscape for Three-Dimensional CSEM Modeling}
   \vspace{.3cm}
   \begin{columns}[c]
-    \column{.25\textwidth}
+    \column{.3\textwidth}
       \centering
-      \includegraphics[width=2.5cm]{Logo-emg3d}\\
-      \href{https://empymod.github.io}{empymod.github.io}\\[.5cm]
-      \includegraphics[width=2.5cm]{Logo-SimPEG}\\[-.4cm]
-      \href{https://simpeg.xyz}{simpeg.xyz}\\[1cm]
-    \column{.25\textwidth}
-      \centering
-      \includegraphics[width=3.0cm]{Logo-PETGEM}\\
-      \href{http://petgem.bsc.es}{petgem.bsc.es}\\[1cm]
-      \includegraphics[width=2.5cm]{Logo-custEM}\\
-      \href{https://custem.rtfd.io}{custem.rtfd.io}\\[.5cm]~
-
-    \column{.4\textwidth}
-      \centering
-      \includegraphics[width=\textwidth, trim=0 600 0 0, clip]{CSEM_Method3}
+      \includegraphics[width=2.0cm]{Logo-emg3d}\\[.5cm]
+      \includegraphics[width=2.0cm]{Logo-custEM}\\[.5cm]
+      \includegraphics[width=2.2cm]{Logo-PETGEM}\\[.5cm]
+      \includegraphics[width=3.0cm]{Logo-SimPEG2}
+    %
+    \column{.7\textwidth}
+      ~\\\vspace{.4cm}
+      \includegraphics[width=.9\textwidth]{model-marlim}\\[.5cm]
       \begin{tikzpicture}[remember picture,overlay]
+        \node [color=white, xshift=8cm, yshift=5.5cm] (current page.south west) {\includegraphics[width=3cm, trim=200 800 200 150, clip]{CSEM_Method3}};
         \node [color=white, xshift=1.5cm, yshift=1.4cm, rotate=60] (current page.south west) {\small \copyright\ emgs.com};
       \end{tikzpicture}
+      %
+      \centering
+      \small \alert{Werthmüller, Rochlitz, Castillo-Reyes, and Heagy, 2020},\\
+      submitted to GJI;
+      \href{https://arxiv.org/abs/2010.12926}{arXiv:~2010.12926}
   \end{columns}
-  \vspace{-.3cm}
-  \small \alert{Werthmüller, Rochlitz, Castillo-Reyes, and Heagy, 2020},
-  submitted to GJI; \href{https://arxiv.org/abs/2010.12926}{arXiv:~2010.12926}
+  %
   \note{
+    \phantom{~}\\\hspace{1cm} \alert{\bfseries Summary Slide 1: Project Motivation}
     \begin{itemize}
-      \item We are core-devs of the four codes under consideration
-      \item \custem and \petgem are finite element CSEM codes; both work in
-        the\\ frequency domain, \custem also in the time domain; using
-        tetrahedral meshes
-      \item \simpeg is a more general framework for geophysical modelling and
-        inversion:\\ Gravity, Magnetics, DC resistivity, IP, EM ($t$- and
-        $f$-domain; controlled- and natural-src),\\ and more; contains
-        1D, 2D, and 3D rectilinear, curvilinear, and octree meshes
-      \item \emg3d is a matrix-free multigrid solver for 3D EM diffusion using
-        rectilinear meshes.
-      \item \custem, \petgem, and \simpeg use third party direct solvers such
-        as MUMPS or PARDISO to solve the system of linear equations, \emg3d is
-        a, iterative, solver on its own
-      \item SimPEG is a community effort, other codes are currently mostly
-        one-man shows
-      \item Note: We look at the marine CSEM case as shown in the right figure;
-        we are looking for resistive bodies in a conductive environment;
-        node-based, using reciprocity; so just at one, tightly limited
-        scenario; we will come back to that at the end
-      \item Submitted to Geophysical Journal International, preprint on arXiv
-      \item All are open-source: \simpeg MIT, \emg3d Apache-2.0, \petgem
-        BSD-3-Clause, \custem GPL-3.0
+      \item Large scale CSEM modelling with open-source software
+      \item Opens new questions: validation; importance of mesh; repeatibility
     \end{itemize}
@@
 
-\section{Numerical Results} % ----------------------------------------------- %
-
-\begin{frame}[t]%
-  {Verification for layered model using semi-analytical solutions\\
-   shows a relative amplitude error in the order of 1\,\% or less}
+\begin{frame}[c]
+  {Successful cross-validation between different codes and mesh types}
   %
   \begin{columns}[c]
-    %
     \column{.45\textwidth}
-    %
       \centering
-      \includegraphics[width=\textwidth]{model-layered}\\
-      \hspace{1cm}\includegraphics[width=.5\textwidth]{model-layered-src}
-    %
-    \column{.6\textwidth}
-    %
-      \includegraphics[width=\textwidth]{results-layered}
-    %
+      \includegraphics[width=\textwidth]{results-marlim-responses}
+    \column{.55\textwidth}
+      \centering
+      \includegraphics[width=\textwidth, trim=0 0 170 0, clip]{results-marlim_2ours}\\[.2cm]
+      \includegraphics[width=.3\textwidth, trim=640 160 0 100, clip]{results-marlim_2ours}
   \end{columns}
@@
   \note{
+    \phantom{~}\\\hspace{1cm} \alert{\bfseries Summary Slide 2: Key Results}
     \begin{itemize}
-      \item Source at x=8, 50\,m above seafloor; 200\,m, 800\,A, receivers on
-        the seafloor
-      \item Results of the four codes can visually not be distinguished
-      \item Relative error from 0.01\,\% to 100\,\%
-      \item Black lines mark the 1\,\% line
-      \item The relative error of the amplitude is mostly below 1\,\%
-      \item Looking at the absolute error plot now:
-        \begin{itemize}
-          \item Big relative errors can be observed close to the source
-          \item Differences in how the source is defined
-          \item Higher errors for \custem at the edges: explain the
-            gridding approach of the thin layer of \custem
-          \item Differences between PEC and PMC boundary conditions:
-            \petgem and \emg3d used PEC, which seems to work better in this
-            case, \simpeg and \custem used PMC
-        \end{itemize}
-      \item In paper also broadside; CPU/RAM/dof
-      \item For the semi-analytical solutions we used \empymod
+      \item Successfully modelled and validated different models
+      \item Cross-validating 3D CSEM results with other codes is the\\
+        only possible check
     \end{itemize}
@@
 
-\begin{frame}[t]%
-  {Adding three resistive blocks to the layered model requires\\
-   the normalised difference instead of the relative error}
+\begin{frame}
+  {Comparisons, Validations, Benchmarks; Open-Source}
+  \centering
   %
-  \begin{columns}[c]
+  \includegraphics[width=.8\textwidth]{results-marlim_survey}\\[.5cm]
   %
-    \column{.6\textwidth}
-      \includegraphics[width=.9\textwidth]{model-block}
-    %
-    \column{.4\textwidth}
-      \centering
-      \alert{Normalised Root-Mean Square Difference} (NRMSD) in
-      percent:\\
-      %
-      \begin{equation}
-        200\,\frac{|R_1 - R_2|}{|R_1| + |R_2|} \nonumber
-      \end{equation}
-      %
-      \vspace{.5cm}\\
-      %
-      {\footnotesize After \emph{Dublin Test Model 1},\\
-      \alert{Miensopust et al., 2013}, GJI}
-    %
-  \end{columns}
+  \href{mailto:d.werthmuller@tudelft.nl}{D.Werthmuller@TUDelft.nl}\\
+  \alert{\bdra
+    \href{https://github.com/swung-research/3d-csem-open-source-landscape}%
+         {github.com/swung-research/3d-csem-open-source-landscape}
+       \bdla}
   %
   \note{
+    \phantom{~}\\\hspace{1cm} \alert{\bfseries Summary Slide 3: Significance}
     \begin{itemize}
-      \item Background model is the layered model from before
-      \item We embed three resistive blocks and look at three acquisition
-        lines
-      \item The blocks are an adaption of the Dublin Test Model 1 from\\
-        Miensopust et al., 2013; similar study for MT data
-      \item As there are no analytical solutions we have to compare codes;\\
-        hence \emph{validation}, not \emph{verification}
-      \item Instead of the relative error we use therefore the NRMSD (and a
-        conservative version thereof)
+      \item Comparisons, validations, and benchmarks are crucial for 3D
+        modelling
+      \item We need many more of them, which would benefit the community
+      \item Other scenarios: air borne, topography, conductor, other sources
+      \item Everything is on GitHub
     \end{itemize}
   }
-\end{frame}
-
-% \begin{frame}[t]%
-%   {Results from different meshes and different\\
-%    codes can visually not be distinguished}
-%   %
-%   \vspace{.5cm}
-%   \begin{columns}[c]
-%     %
-%     \column{.35\textwidth}
-%       \includegraphics[width=.9\textwidth, trim=0 0 123.5 0, clip]{model-block}
-%     %
-%     \column{.65\textwidth}
-%     %
-%       \centering
-%       \includegraphics[width=\textwidth]{results-block-all}\\
-%       %
-%       \vspace{ .5cm}
-%       \begin{table}
-%         \footnotesize %small %tiny
-%         \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
-%           % \begin{tabular}{lrrrr}
-%           % \toprule
-%           Code & \#Procs & {CPU (s)} & {RAM (GiB)}   & {\#dof} \\
-%           \midrule
-%           \custem & 24 &   158 & 115.9 & 1646736 \\
-%           \emg3d  &  1 &   115 &   0.4 & 4813216 \\
-%           \petgem & 24 &    238 &  152.8 & 2455868 \\
-%           \simpeg &  4 & 10295 & 280.4 & 4813216 \\
-%           % \bottomrule
-%         \end{tabular}
-%       \end{table}
-%     %
-%   \end{columns}
-%   %
-%   \note{
-%     \begin{itemize}
-%       \item Responses: Absolute values plotted
-%       \item Plotted all results on top of each other: no differences visible
-%       \item The responses of the resistive cubes are visible
-%       \item Regarding computational costs:
-%         \begin{itemize}
-%           \item First: Comparison was not phrased as a comp. competition;
-%             entire different exercise
-%           \item Second: Ran on very different machines, from laptop to
-%             supercomputers
-%           \item The objective is: what can we do with different codes
-%           \item How do we obtain good results with different codes
-%           \item Much more time invested in model building than computation
-%           \item \simpeg: fine grid (precision); later taking advantage of
-%             octree meshes
-%           \item Other three $\pm$ same speed in real-world
-%             time, but \custem/\petgem used 24 processes
-%           \item It can be directly seen for the direct solvers: more \#doc,
-%             more RAM
-%           \item Rectilinear grids required the most dofs
-%           \item Layered model is basically identical
-%         \end{itemize}
-%     \end{itemize}
-%   }
-% \end{frame}
-
-\begin{frame}[t]%
-  {Validation between the codes shows a\\
-   normalised difference of 1--2\,\% or less}
   %
-  \vspace{.5cm}
-  \begin{columns}[c]
-    %
-    \column{.35\textwidth}
-      \includegraphics[width=.9\textwidth, trim=0 0 123.5 0, clip]{model-block}
-    %
-    \column{.65\textwidth}
-    %
-      % \includegraphics[width=\textwidth]{results-block-all-2}
-      \includegraphics[width=\textwidth]{results-block}
-    %
-  \end{columns}
-  %
-  \note{
-    \begin{itemize}
-      \item Because they are basically identical, we just show the
-        response of one code
-      \item The responses of the resistive cubes are visible
-      \item Shows also real and imaginary contributions
-      \item The NRMSD is generally around 1\,\% or less
-      \item Not surprising, as we could not see a visual difference
-      \item There are 6 combinations for the normalized difference
-        of the four codes
-      \item Only middle plot shows all six
-      \item On the left are three, on the right the other three
-      \item \simpeg and \emg3d use same grid, so lower differences
-      \item We use four different codes, two different mesh types, and the
-        results are basically identical, which is a good first result
-      \item Now we move to a huge model\ldots
-    \end{itemize}
-  }
-\end{frame}
-
-\begin{frame}[c]
-  {Marlim R3D model: Responses at receiver locations\\
-   look visually the same for all relevant responses}
-  %
-  \begin{columns}[c]
-    \column{.5\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{model-marlim}\\
-      %
-      {\footnotesize Marlim R3D:\\
-        \alert{Correa and Menezes, 2019}, Geophysics}
-    \column{.55\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{results-marlim-responses}
-  \end{columns}
-  \note{
-    \begin{itemize}
-      \item IMPORTANT: Reciprocity, hence source-receiver swap
-      \item Very complex resistivity model
-      \item Responses modelled with software from EMGS, in the time domain
-      \item The responses look visually the same, except\ldots
-      \item \ldots $E_x$ inline, which is about 2 orders of magnitudes lower
-      \item Full grid of sources and receivers for 6 frequencies
-      \item We modelled 1 receiver \dra source, two source \dra receiver lines
-    \end{itemize}
-  }
-\end{frame}
-
-\begin{frame}[c]
-  {Normalised difference to published data is mostly\\
-   below 10\,\% and very different from code to code}
-  \centering
-  %
-  ~\vfill
-  \includegraphics[width=\textwidth]{results-marlim_2published}
-  %
-  \note{
-    \begin{itemize}
-      \item $E_x$ inline, strongest component, a few percents
-      \item Others up to 10 percent, higher frequencies more
-      \item Some codes are more similar in different places
-      \item funny shape due to bathymetry
-    \end{itemize}
-  }
-\end{frame}
-
-\begin{frame}[c]
-  {Normalised difference between our codes\\
-   is very similar and mostly below 10\,\%}
-  \centering
-  %
-  ~\vfill
-  \includegraphics[width=\textwidth]{results-marlim_2ours}
-  %
-  \note{
-    \begin{itemize}
-      \item Comparison between our codes looks very similar
-      \item Noteworthy is \custem and \petgem, because of same grid
-      \item Also \emg3d and \simpeg, even though not same mesh
-    \end{itemize}
-  }
-\end{frame}
-
-% \begin{frame}
-%   {Very insightful is to look at the entire\\
-%    meshes and their different behaviours}
-%   \centering
-%   %
-%   ~\vfill
-%   \includegraphics[width=.9\textwidth]{results-marlim_big}
-%   %
-%   \note{
-%     \begin{itemize}
-%       \item Computational domain very different
-%       \item \simpeg and emg3d could probably reduce their domains
-%       \item Advantages of Octree and Tetrahedra in comparison to Rectilinear
-%     \end{itemize}
-%   }
-% \end{frame}
-
-\begin{frame}
-  {Very insightful is to look at the entire\\
-   meshes and their different behaviours}
-%   {While the responses at receiver locations are identical,\\
-%    the fields start to vary greatly when moving away}
-  \centering
-  %
-  ~\vfill
-  \includegraphics[width=.9\textwidth]{results-marlim_survey}
-  %
-  \note{
-    \begin{itemize}
-      \item White band includes the receiver lines
-      \item Responses are very similar there
-      \item Outside not so much!
-      \item Very insightful for inversions etc
-    \end{itemize}
-  }
-\end{frame}
-
-\begin{frame}
-  {A look at the models in different mesh yields interesting\\
-   insights with regards to recoverability in inversions}
-  \centering
-  \includegraphics[width=\textwidth]{results-marlim_allmodels}
-    \begin{table}
-      \footnotesize %small %tiny
-      \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
-        % \begin{tabular}{lrrrr}
-        % \toprule
-        Code & \#Procs & {CPU (s)} & {RAM (GiB)}   & {\#dof} \\
-        \midrule
-        \custem & 64 &  872 & 230.1 & 1918106 \\
-        \emg3d  &  1 & 1254 &   0.6 & 5998992 \\
-        \petgem & 96 &  524 & 175.4 & 1918106 \\
-        \simpeg &  4 &  422 &  12.8 &  720146 \\
-        % \bottomrule
-      \end{tabular}
-    \end{table}
-    \note{
-      \begin{itemize}
-        \item Models show clearly what we have seen before
-        \item dof: tetrahedra about 2 million dofs, rectil. about 2 million
-          cells; octree only about 240,000 cells
-      \end{itemize}
-    }
-\end{frame}
-
-\section{Conclusions and Outlook} % ----------------------------------------- %
-
-\begin{frame}%
-  {References}
-  \tiny
-  %
-  \begin{columns}
-    \column{1.1\textwidth}
-  %
-  \setlength{\columnseprule}{0.4pt}
-  % \setlength{\columnsep}{3em}
-  \begin{multicols}{2}
-  A more extensive reference list can be found in:\\[.5em]
-  {\bfseries \alert{Werthmüller, D., R. Rochlitz, O. Castillo-Reyes, and L.
-  Heagy, 2020}, Open-source landscape for 3D CSEM modelling},\\
-  submitted to Geophysical Journal International,
-  \href{https://arxiv.org/abs/2010.12926}{arXiv:~2010.12926}.\\[.5cm]
-  %
-  {\bfseries Modelling codes: \custem, \emg3d, \petgem, \simpeg, and
-  \empymod:}
-  \begin{description}[2cm]
-    %
-    % \item[Castillo-Reyes et al., 2019,] {\bfseries Parallel 3D marine
-    %   controlled-source electromagnetic modeling using high-order
-    %   tetrahedral Nédélec elements}, Geophysical Journal International,
-    %   219, 39--65,
-    %   \href{https://doi.org/10.1093/gji/ggz285}{doi:~10.1093/gji/ggz285}.
-    \item[Castillo-Reyes et al., 2018,] {\bfseries PETGEM: A parallel code
-      for 3D CSEM forward modeling using edge finite elements}, Computers \&
-      Geosciences, 119, 126--136,
-      \href{https://doi.org/10.1016/j.cageo.2018.07.005}%
-      {doi:~10.1016/j.cageo.2018.07.005}.
-    %
-    \item[Cockett et al., 2015,] {\bfseries SimPEG: An open source framework
-      for simulation and gradient based parameter estimation in geophysical
-      applications}, Computers \& Geosciences, 85, 142--154,
-      \href{https://doi.org/10.1016/j.cageo.2015.09.015}%
-      {doi:~10.1016/j.cageo.2015.09.015}.
-    %
-    \item[Rochlitz et al., 2019,] {\bfseries custEM: customizable finite
-      element simulation of complex controlled-source electromagnetic data},
-      Geophysics, 84, F17--F33,
-      \href{https://doi.org/10.1190/geo2018-0208.1}%
-      {doi:~10.1190/geo2018-0208.1}.
-    %
-    \item[Werthmüller, 2017,] {\bfseries An open-source full 3D
-      electromagnetic modeler for 1D VTI media in Python: empymod},
-      Geophysics, 82(6), WB9--WB19;
-      \href{https://doi.org/10.1190/geo2016-0626.1}%
-      {doi:~10.1190/geo2016-0626.1}.
-    %
-    \item[Werthmüller et al., 2019,] {\bfseries emg3d: A multigrid solver for
-      3D electromagnetic diffusion}, Journal of Open Source Software, 4(39),
-      1463;
-      \href{https://doi.org/10.21105/joss.01463}{doi:~10.21105/joss.01463}.
-    %
-  \end{description}
-  \columnbreak
-  %
-  {\bfseries Solvers \texttt{PETSc}, \texttt{MUPMS}, \texttt{FEniCS}, and
-  \texttt{PARDISO}:}
-  %
-  \begin{description}[2cm]
-    %
-    \item[Abhyankar et al., 2018,] {\bfseries PETSc/TS: A modern scalable
-      ODE/DAE solver library},
-      \href{https://arxiv.org/abs/1806.01437}{arXiv:~1806.01437}.
-    %
-    \item[Amestoy et al., 2001,] {\bfseries A fully asynchronous multifrontal
-      solver using distributed dynamic scheduling:} SIAM Journal on Matrix
-      Analysis and Applications, 23, 15--41,
-      \href{https://doi.org/10.1137/S0895479899358194}%
-      {doi:~10.1137/S0895479899358194}.
-    %
-    \item[Langtangen et al., 2016,] {\bfseries Solving PDEs in Python: The
-      FEniCS Tutorial I}, vol. 3 of Simula SpringerBriefs on Computing,
-      Springer International Publishing,
-      \href{https://doi.org/10.1007/978-3-319-52462-7}%
-      {doi:~10.1007/978-3-319-52462-7}.
-    %
-    \item[Schenk and Gärtner, 2004,] {\bfseries Solving unsymmetric sparse
-      systems of linear equations with PARDISO}, Future Generation Computer
-      Systems, 20, 475--487,
-      \href{https://doi.org/10.1016/j.future.2003.07.011}%
-      {doi:~10.1016/j.future.2003.07.011}.
-    %
-  \end{description}
-  %
-  {\bfseries Marlim R3D model:}
-  %
-  \begin{description}[2cm]
-    %
-    \item[Correa and Menezes, 2019,] {\bfseries Marlim R3D: A realistic model
-      for controlled-source electromagnetic simulations--Phase 2: The
-      controlled-source electromagnetic data set}, Geophysics, 84,
-      E293--E299, \href{https://doi.org/10.1190/geo2018-0452.1}%
-      {doi:~10.1190/geo2018-0452.1}.
-    %
-  \end{description}
-  %
-  {\bfseries MT comparison study:}
-  %
-  \begin{description}[2cm]
-    %
-    \item[Miensopust et al., 2013,] {\bfseries Magnetotelluric 3-D inversion--a
-      review of two successful workshops on forward and inversion code testing
-      and comparison}, Geophysical Journal International, 193, 1216--1238,
-      \href{https://doi.org/10.1093/gji/ggt066}{doi: 10.1093/gji/ggt066}.
-    %
-  \end{description}
-  %
-\end{multicols}
-\end{columns}
-\end{frame}
-
-\begin{frame}[c]%  {}
-  {More Comparisons \& Benchmarks\\
-   Other Scenarios, other programming languages}
-  %
-  \begin{columns}
-      %
-    \column{.2\textwidth}
-    \centering
-      %
-      ~\\[.5cm]
-      \includegraphics[width=2.0cm]{Logo-emg3d}\\[.5cm]
-      %
-      \includegraphics[width=\textwidth, trim=0 500 0 0, clip]{CSEM_Method3}\\[1cm]
-      %
-      \includegraphics[width=2.0cm]{Logo-custEM}
-      %
-    \column{.5\textwidth}
-    \centering
-      %
-    \phantom{~}\\[.5cm]
-    \includegraphics[width=\textwidth, trim=40 235 150 0, clip]{results-marlim_big}\\[.5cm]
-      %
-      \includegraphics[width=\textwidth, trim=70 095 0 160, clip]{results-block}
-      %
-    \column{.3\textwidth}
-    \centering
-      %
-      \includegraphics[width=3cm]{Logo-SimPEG2}\\[.5cm]
-      %
-      \includegraphics[width=\textwidth, trim=65 242 50 20, clip]{results-marlim-responses}\\[.5cm]
-      %
-      \includegraphics[width=2.5cm]{Logo-PETGEM}
-      %
-  \end{columns}
-  %
-  \note{
-    \begin{itemize}
-      \item See you \alert{14th December}!
-      \item Shown: Analytical verification; simple validation; complex
-        validation
-      \item Four codes, three different mesh types
-      \item It is all about the discretization, the solvers themselves do
-        basically the same
-      \item Most time is spent in creating the appropriate discretization
-      \item Performance depends mostly on the used solver
-      \item Examples favoured rectilinear and octree meshes, as they were all
-        regular cubes
-      \item Examples favoured iterative solvers, as we only used one source;
-        when computing many sources the direct solvers could re-use the
-        factorisations
-      \item We need more validations and benchmarks like this for CSEM
-      \item More scenarios: air borne, strong topography, loops, conductor in
-        a resistor, etc
-      \item Reference model which is delivered on horizons and as functions
-        instead of cubes
-      \item More codes, other languages
-    \end{itemize}
-  }
 \end{frame}

### 2021-01-05 manuscript/Manuscript.tex
Add notes re feedback
Push in case there were changes.

@@
-% \documentclass[onecolumn,extra,referee,camera]{gji}
-\documentclass[onecolumn,extra,camera]{gji}
+\documentclass[extra, camera,%
+    % onecolumn,   % comment for two columns
+    % referee,     % uncomment for double lines
+    % final,       % uncomment for changes
+]{gji}
 \usepackage{timet}
@@
 \usepackage{xspace}
+\usepackage[final]{graphicx}
+\usepackage[position=top]{subfig}
+\usepackage{ifthen}
+\usepackage[addedmarkup=bf]{changes}
+% \usepackage[final]{changes}
 \usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}
-\usepackage[pdftex]{graphicx}
 
@@
 \makeatother
+
+% Figures
+% To print widths put this in text:
+% \the\textwidth
+% \the\columnwidth
+%
+% Widths:   textwidth  columnwidth  tablewidth
+%       1-c   504pt        252pt       504pt
+%       2-c   504pt        240pt       240pt
+%       ref   468pt        234pt       468pt
+%
+\newlength{\fwidth}
+\newlength{\cwidth}
+\newlength{\twidth}
+\ifthenelse{\boolean{GJ@referee}}{%
+  \setlength{\cwidth}{234pt}%
+  \setlength{\fwidth}{468pt}%
+  \setlength{\twidth}{468pt}}{%
+  \setlength{\fwidth}{504pt}%
+  \ifthenelse{\boolean{@twocolumn}}{%
+    \setlength{\cwidth}{240pt}%
+    \setlength{\twidth}{240pt}}{%
+    \setlength{\cwidth}{252pt}%
+    \setlength{\twidth}{504pt}%
+  }
+}
+\graphicspath{{./figures/}}
+
+% Change default colour of «changes» package
+\definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
+\definecolor{mygreen}{rgb}{0, .5, 0}
+\setaddedmarkup{\color{mygreen}{\uline{#1}}}
+\setdeletedmarkup{\color{alizarin}{\uwave{#1}}}
 
@@
 \newcommand{\petgem}{\texttt{PETGEM}\xspace}
+
+% Remove once done
+% \newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
+% \newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
+% \newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
+\newcommand{\dul}[1]{\underline{\underline{#1}}}
+\newcommand{\ul}[1]{\underline{#1}}
+\newcommand{\rmk}[1]{{\color{red}{#1}}}
 \newcommand{\ohmm}{\ensuremath{\Omega\,}\text{m}\xspace}
-\newcommand{\rmk}[1]{{\color{red}\bfseries #1}}
 
@@
 \newtheorem{theorem}{Theorem}[section]
+
+% % == Notes from Wim; to incorporate ==
+%
+% All implemented
+%
+% % == Notes form Paulo ==
+%
+% Very good to know that the Ex responses are well represented. For most of the inversions done in the industry, we use these fields only.
+%
+% Ez: the mismatch occurs at the longer offsets and below the noise threshold 10-15.
+EMGS argues now that with the new source, the threshold is pushed to 10-16.
+But in practice, if the curve follows a smooth decay, we use this data for inversion, and we get meaningful geological results compared to seismic images.
+%
+% Ey: the broadside component is quite close,  with small differences at long offsets.
+For the inline component, I've noted that your responses are up to two orders of magnitude higher than MR3D.
+The four programs you tested give the same amplitudes?
+It may be a problem with the EMGS software, as EY is always neglected we may have ignored that issue.
+Simultaneously, it looks that your inline responses are at the same level as the broadside ones.
+%
+% Bathymetry is also a big issue. It must be well represented to avoid problems.
+%
+% % == Notes from Evert ==
+%
+% [T]he fact that the solutions in the four codes are roughly correct with an expected error between 1\% and 10\% makes it totally understandable that the field that is one to two orders of magnitude smaller has no accuracy.
+You could test this by driving the overall error down by a factor 100.
+Not sure that is feasible with all codes but if you can do it with one it can be enough when all codes agree sufficiently on the strong field components.
+Another option can be to increase the cross line component in the error computation.
 
@@
 
+\begin{itemize}
+  \item \deleted{old}: \texttt{\textbackslash deleted\{old\}}
+  \item \added{new}: \texttt{\textbackslash added\{new\}}
+  \item \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
+\end{itemize}
+
 Controlled-source electromagnetic (CSEM) measurements are a frequently applied method in various areas of geophysical exploration, such as geothermal, groundwater, oil and gas, mining, civil engineering, or geohazards.
@@
 
-In the 1990's, computers became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
+In the \replaced{1990s}{1990's}, computers became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
 This symposium resulted eventually in the book \emph{Three-Dimensional Electromagnetics} \citep{B.SEG.99.Oristaglio}, and another book by \cite{B.02.Wannamaker} with the exactly same title came out only three years later.
@@
 One reason why there are so many publications about this topic results from the variety of techniques to solve the systems of linear equations (SLE).
-They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, indirect solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
+They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, \replaced{iterative}{indirect} solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
 The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GJI.16.Jaysaval}.
@@
 All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{NAT.20.Harris} and \texttt{SciPy} \citep{NM.20.Virtanen}.
-The four of them follow the open model of development, meaning that they come with both, an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+The four of them follow the open model of development, meaning that they come with both\deleted{,} an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
 All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
@@
 To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
-It is therefore, on one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
+It is therefore, on \added{the} one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
 On the other hand it is impossible to reproduce it exactly, as it is a closed-source code and we cannot know exactly what was done internally.
@@
 The model was upscaled for the computation to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
-Both the full model and the upscaled computational model are released openly.
+Both the full model and the upscaled computational model are released \replaced{as open source}{openly}.
 The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
@@
   \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively.
-The shown dimensions shows the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
+The shown dimensions \replaced{display}{shows} the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
   \label{fig:results-marlim_big}
@@
 %
-This figure is interesting for various points, as the differences between the three meshes are clearly visible.
+This figure is interesting for various \replaced{reasons}{points}, as the differences between the three meshes are clearly visible.
 Particularly the advantage of octree and tetrahedra to create large cells outside of the region of interest to push away the boundary can be seen, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
@@
 For the lowest frequency, 0.125\,Hz, the normalised difference is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
-For higher frequencies these numbers rise to the order of $\pm10\,$\%.
+For higher frequencies these numbers \replaced{increase}{rise} to the order of $\pm10\,$\%.
 The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategy.
@@
 Our first attempts were based on the originally published, fine MR3D model.
-This model is very detailed, but its extent is too small in x- and y-directions for CSEM computations.
+This model is very detailed, but its extent is too small in \added{the} x- and y-directions for CSEM computations.
 In order to represent the fine-scale model on a mesh suitable for computation, each of our codes did its own upscaling and extrapolation.
@@
 Independently of the solver there is a trade-off between high accuracy and runtime.
-As an example, the octree mesh made for a very fast computation in the MR3D example thanks to the low number of dof, even though a direct solver was used.
+\replaced{For}{As an} example, the octree mesh made for a very fast computation in the MR3D example thanks to the low number of dof, even though a direct solver was used.
 But the octree mesh has, due to its 2:1 aspect ratio, some limitations on the accuracy, why it was not used in the first two examples.

### 2021-01-05 manuscript/Manuscript.tex
Start revision seriously

@@
 
-\title[3D CSEM Open-Source Landscape]{Open-source landscape for 3D CSEM modelling}
+\title[3D CSEM Open-Source Landscape]{\replaced{Towards an open-source landscape for 3D CSEM modelling}{Open-source landscape for 3D CSEM modelling}}
 
@@
    Octavio Castillo-Reyes$^3$ and % orcid: 0000-0003-4271-5015
-   Lindsey Heagy$^4$              % orcid: 0000-0002-1551-5926
-   \\
+   Lindsey Heagy$^4$\\            % orcid: 0000-0002-1551-5926
    \footnotesize
@@
 \newtheorem{theorem}{Theorem}[section]
-
-% % == Notes from Wim; to incorporate ==
-%
-% All implemented
-%
-% % == Notes form Paulo ==
-%
-% Very good to know that the Ex responses are well represented. For most of the inversions done in the industry, we use these fields only.
-%
-% Ez: the mismatch occurs at the longer offsets and below the noise threshold 10-15.
-EMGS argues now that with the new source, the threshold is pushed to 10-16.
-But in practice, if the curve follows a smooth decay, we use this data for inversion, and we get meaningful geological results compared to seismic images.
-%
-% Ey: the broadside component is quite close,  with small differences at long offsets.
-For the inline component, I've noted that your responses are up to two orders of magnitude higher than MR3D.
-The four programs you tested give the same amplitudes?
-It may be a problem with the EMGS software, as EY is always neglected we may have ignored that issue.
-Simultaneously, it looks that your inline responses are at the same level as the broadside ones.
-%
-% Bathymetry is also a big issue. It must be well represented to avoid problems.
-%
-% % == Notes from Evert ==
-%
-% [T]he fact that the solutions in the four codes are roughly correct with an expected error between 1\% and 10\% makes it totally understandable that the field that is one to two orders of magnitude smaller has no accuracy.
-You could test this by driving the overall error down by a factor 100.
-Not sure that is feasible with all codes but if you can do it with one it can be enough when all codes agree sufficiently on the strong field components.
-Another option can be to increase the cross line component in the error computation.
 
@@
 
+% TODO delete before re-submission
 \begin{itemize}
@@
 All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM.
-The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
+\added{For the shown numerical examples all codes use the total-field formulation for the electric field.} The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor

### 2021-01-28 model-block/custEM/run_layered.py
Update Figures (#40)

@@ -44,7 +44,7 @@ for p in [2, 1]:
     #                        stop=[100., 0., -550.])
 
     # Call solver, skip H-field computation, and export results
-    M.solve_main_problem(convert_to_H=False)
+    M.solve_main_problem()
 
     # create regular inteprolation lines in x-direction at sea floor
     M.IB.create_line_meshes('x',  x0=-1e4, x1=1e4, y=-3e3, z=-600.1,
@@ -54,6 +54,17 @@ for p in [2, 1]:
     M.IB.create_line_meshes('x',  x0=-1e4, x1=1e4, y=3e3, z=-600.1,
                             n_segs=100, line_name='l3m')
 
+    M.IB.create_line_meshes('x',  x0=-1e4, x1=1e4, y=-3e3, z=-599.9,
+                            n_segs=100, line_name='l1p')
+    M.IB.create_line_meshes('x',  x0=-1e4, x1=1e4, y=0., z=-599.9,
+                            n_segs=100, line_name='l2p')
+    M.IB.create_line_meshes('x',  x0=-1e4, x1=1e4, y=3e3, z=-599.9,
+                            n_segs=100, line_name='l3p')
+
     for line in ['l1m_line_x', 'l2m_line_x', 'l3m_line_x']:
         M.IB.interpolate(line, 'E_t')
+        M.IB.interpolate(line, 'H_t')
+    for line in ['l1p_line_x', 'l2p_line_x', 'l3p_line_x']:
+        M.IB.interpolate(line, 'E_t')
+        M.IB.interpolate(line, 'H_t')
     M.IB.synchronize()  # synchronize all processes after interpolation

### 2021-01-28 manuscript/Manuscript.tex

@@
 \usepackage{tabularx}
+\usepackage{tcolorbox}
 
@@
 \newcommand{\petgem}{\texttt{PETGEM}\xspace}
+\newcommand{\ymark}[1]{%
+  \begin{tcolorbox}[colback=yellow!40!white]#1\end{tcolorbox}}
 
 % Remove once done
-% \newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
+\newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
 % \newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
-% \newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
+\newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
 \newcommand{\dul}[1]{\underline{\underline{#1}}}
@@
 
-\title[3D CSEM Open-Source Landscape]{\replaced{Towards an open-source landscape for 3D CSEM modelling}{Open-source landscape for 3D CSEM modelling}}
+\title[3D CSEM Open-Source Landscape]{\replaced{Towards an o}{O}pen-source landscape for 3D CSEM modelling}
 
@@
 
-\date{Received 202Y MMMM DD; in original form 2020 October 23}
+\date{Received 2021 MMMM DD; in original form 2020 October 23}
 \pagerange{\pageref{firstpage}--\pageref{lastpage}}
@@
 
-\section{Introduction}
+\clearpage
 
-% TODO delete before re-submission
+\subsection*{Correction commands}
 \begin{itemize}
@@
 \end{itemize}
+
+\subsection*{Revise entire manuscript re:}
+\ymark{Intro/Discussion: Take into account «To make this manuscript publishable within GJI, it requires some serious effort to focus more on the bigger picture and make this story more pronounced within your manuscript.»}
+
+\listoftodos
+
+\clearpage
+
+\section{Introduction}
 
@@
 Many of the advancements made in the EM modelling community over the past decades have required that authors develop new implementations from scratch.
-These codes often provided the research group or company with a competitive advantage for a time, and thus the source codes were often kept internal.
+These codes often provided the research group or company with a competitive advantage for a time, and thus the source codes were \replaced{normally}{often} kept internal.
 In some cases, executables have been made available for academic purposes upon request or to sponsoring consortium members.
@@
 
-The open-source landscape in the field of 3D CSEM modelling changed in the last five years quite dramatically, and here we introduce and compare four recent open-source projects.
+The landscape in the field of 3D CSEM modelling changed in the last five years quite dramatically.
+This paper introduces and compares four projects which make all source code openly available for use and adaptation.
 All presented codes are in the Python ecosystem and use either the FV method on structured grids or the FE method on unstructured tetrahedral meshes.
-Having different codes which use different methods and different meshes is ideal to address the topic of validation.
+Having different codes which use different methods and different meshes is ideal to address the topic of validation, and having all openly available facilitates reproducibility of our results.
 Analytical and semi-analytical solutions only exist for simple halfspace or layered-Earth models, which served mostly to verify new codes.
@@
 Beyond that, we extensively discuss important points that control the performance and suitability of our FV and FE codes, including considerations about the mesh design and the choice of solvers.
+Such a comparison reveals avenues for further development for each of the codes.
 We conclude with a discussion and conclusions, and a motivation for the EM community at large to not only continue to extend the landscape of open-source codes but to also create a landscape of open-source benchmark models.
@@
 All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
-Newer package-management systems such as \texttt{conda}, \texttt{docker}, or \texttt{pip} simplify installation for all of these codes on any major operating system
+Newer package-management systems such as \texttt{conda}, \texttt{docker}, or \texttt{pip} simplify installation for all of these codes on any major operating system.
 
@@
 An overview comparison of the codes is given in Table~\ref{tbl:codecomparison}.
-All four have in common that they solve Maxwell's equation in its differential form (DE) under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM.
-\added{For the shown numerical examples all codes use the total-field formulation for the electric field.} The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
+All four have in common that they solve Maxwell's equation in its differential form \deleted{(DE)} under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM.
+\added{For the numerical examples we show, all codes use the total-field formulation for the electric field.} The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
@@
 , respectively.
-Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving.
+\added{PEC (PMC) implies that the tangential electric (magnetic) field vector components are zero at the boundary.} Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving.
 Finally, we use \emph{runtime} as the wall time or elapsed real-world time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
@@
   Website & \href{https://custem.rtfd.io}{custem.rtfd.io}
-          & \href{https://empymod.github.io}{empymod.github.io}
+          & \href{https://emsig.github.io}{emsig.github.io}
           & \href{http://petgem.bsc.es}{petgem.bsc.es}
@@
           & - 15.5 GiB RAM                                    & \\
-          & - Ubuntu 18.04                                    & \\[.5em]
+          & - Ubuntu 20.04                                    & \\[.5em]
   \petgem & \textbf{Marenostrum4 (supercomputer)}             & Octavio Castillo-Reyes \\
@@
 Even though changes of the conductivity are mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
-Recently, induced polarisation parameters in frequency-domain and three methods for simulating time-domain responses were added to \custem.
+Recently, induced polarisation parameters in frequency-domain \added{computations} and three methods for simulating time-domain responses were added to \custem.
 The provided meshing tools are based on \texttt{TetGen} \citep{TOM.15.Si} and functionalities of \texttt{pyGIMLi} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
@@
 Recent developments added functionalities such that \emg3d can be used directly as a more general EM modeller too.
-It features now routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses.
+It features now \replaced{besides arbitrarily rotated electric sources and receivers also routines for magnetic sources and receivers, to model time-domain responses, and to obtain the gradient of the misfit function which can be used by inversion algorithms}{routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses}.
 For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem.
@@
 For the parallel forward modelling computations, a highly scalable MPI (message passing interface) domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
-This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters (e.g., High-Performance Computing [HPC] architectures).
+This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters \replaced{such as}{(e.g.,} High-Performance Computing (HPC) architectures\deleted{)}.
 
@@
 \simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
-Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, EM (time and frequency, as well as natural sources), and fluid flow.
+Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, EM (time and frequency \added{domain}, \replaced{controlled and}{as well as} natural sources), and fluid flow.
 It is a community driven project that aims to support researchers and practitioners by providing a flexible, extensible framework, and common interface to a variety of geophysical methods.
@@
 We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FV) and different mesh types (unstructured tetrahedra, rectilinear, octree) in different scenarios.
-The first model is an anisotropic layered model, which can be compared to semi-analytical solutions.
+The first model is an anisotropic\added{,} layered model, which can be compared to semi-analytical solutions.
 The layered model also serves as background model for the second validation, where we add three resistive blocks into the subsurface.
 The final comparison is based on the realistic, anisotropic marine model MR3D.
-It is an open resistivity model which comes with computed CSEM responses.
+It is a\deleted{n open} resistivity model \replaced{that is openly released, together}{which comes} with computed CSEM responses.
 
@@
 However, it is one of the few examples that can be verified with semi-analytical results, and is therefore still a valuable test.
-The results are shown in Figure~\ref{fig:results-layered}, where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values).
+\itodo{Adjust everything here in section 3.1 for new figures}The results are shown in Figure~\ref{fig:results-layered}, where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values).
 The top row shows the actual, semi-analytically computed responses, for which we used \empymod\citep{GEO.17.Werthmuller}.
@@
   \includegraphics[width=.9\linewidth]{figures/results-layered}
-  \caption{Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
+  \caption{\itodo{Adjust Figures 1 (Amplitude/Phase) and corresponding text in manuscript.} Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
 The relative percentage error of the four 3D modellers are shown in the second and the third row for the inline and broadside responses, respectively.}
@@
 \begin{enumerate}
-  \item The error of the real and imaginary responses are dominated by their zero-crossings, which blows up the error as is the nature of the relative error formula, it has no real-world implications.
+  \item \itodo{adjust}The error of the real and imaginary responses are dominated by their zero-crossings, which blows up the error as is the nature of the relative error formula, it has no real-world implications.
   \item It can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.
@@
 These comparably significant errors could be significantly reduced by choosing a finer discretization around the source, at the cost of increased computation time.
-  \item The error of the responses from the FE codes, on the hand, are relatively big at large offsets, particularly for the inline real responses.
+\itodo{Add a sentence re close offsets FV codes, Rune's comment (or above in point ii).}
+  \item~\\ \itodo{Adjust re changes of Raphael.} The error of the responses from the FE codes, on the hand, are relatively big at large offsets, particularly for the inline real responses.
 This has, again, its origin in the chosen discretization.
@@
   \centering
-  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
+  \caption{\itodo{Check all}Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
 \label{tbl:comp-layered}
@@
 
+\itodo{Explain/clarify re interpolation and re vertical fields in the manuscript.}
+
 \subsection{Block Model}
 
-The block model is a derivation of the \emph{Dublin Test Model 1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
+The block model is a derivation of the \emph{Dublin Test Model~1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
 We use the same layout of the blocks but adjust the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}.
@@
 %
-\begin{figure*}
+\begin{figure}
   \centering
-  \includegraphics[width=.6\linewidth]{figures/model-block}
+  \includegraphics[width=\linewidth]{figures/model-block}
   \caption{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
   \label{fig:model-block}
-\end{figure*}
+\end{figure}
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-block}
-  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+  \caption{\itodo{Adjust Figures 3 (\emg3d-\simpeg; \custem-\petgem; FV-FE) and corresponding text in manuscript.}Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
   \label{fig:results-block}
@@
   \centering
-  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}
+  \caption{\itodo{Check all}Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}
 \label{tbl:comp-block}
@@
 
-The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside.
+The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside \added{(we only show the amplitude, as the conclusions for the phase are very similar)}.
 The published responses are shown in colour with markers for the frequency, and the responses from our codes are shown beneath in grey colours in this overview plot.
@@
 
-It is important to note that the published results nor any of our results is the \emph{thruth}, but the closer they agree with each other the more certain we can be of the outcomes.
+It is important to note that the published results nor any of our results is the \emph{truth}, but the closer they agree with each other the more certain we can be of the outcomes.
 Figure~\ref{fig:results-marlim_2published} shows the normalised differences between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_2published}
-  \caption{Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
+  \caption{\itodo{Improve figure.}Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
 Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
@@
 Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
-The origin of this zigzag pattern is most likely the bathymetry.
-We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
+The origin of this zigzag pattern is most likely the bathymetry.\itodo{Rune confirmed this; adjust} We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
 This would explain why the codes using the tetrahedra mesh, which uses the bathymetry as well, does not show this feature.
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours}
-  \caption{Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
+  \caption{\itodo{Improve figure.}Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
 \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
@@
 The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}.
-The memory requirement varies from $0.5-230\,$GiB, and the runtime from roughly 7\,min to 20\,min, where the codes were run on very different machines from servers to supercomputers (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel.
+The memory requirement varies from \itodo{Check at end again} $0.5-230\,$GiB, and the runtime from roughly 7\,min to 20\,min, where the codes were run on very different machines from servers to supercomputers (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel.
 %
@@
   \centering
-  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}
+  \caption{\itodo{Check all}Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}
 \label{tbl:comp-marlim}
@@
 
+\itodo{SOMEWHERE: Address NRMSD of MR3D results better; EMGS code elan uses bathymetry file; difference not error; very strong NRMSD; although visually identical.}
+
 \section{Discussion}
@@
 %% 1. Results: good agreement %%
+\itodo{Adjust/check text for amplitude/phase plots.}
 Overall, we observed an excellent match between the solutions.
@@
 The reason is that there are many ways how you can extrapolate a model, and without knowing the details of how MR3D represents the model on the computational mesh, we could not re-produce this step.
-We reached out to the authors of MR3D, and they kindly agreed to also published the upscaled and extended computational model.
+We reached out to the authors of MR3D, and they kindly agreed to also publish\deleted{ed} the upscaled and extended computational model.
 It is only with this model that we were able to obtain comparable results.
@@
 We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
-Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling.
+Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \citep{GJI.11.Schwarzbach,GJI.16.Key}.
 Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour.
 It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
+\itodo{Add comment: FV mesh creation much easier / faster; FE have then the advantage of better interpolation and easier possibility for adaptive grids.}
 
@@
 The shown examples consider the geophysical problem of marine CSEM with resistive bodies in the frequency domain.
-We hope to see in the future similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
+\added{Marlim R3D is a rare example of an open-source resistivity model that also comes with CSEM data.
+The spectrum of geophysical EM methods is much wider than marine CSEM.} We hope to see in the future \added{more open-source models with accompanying data and} similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
+\added{An ideal realistic model should be defined as a function resistivity(x, y, z) which returns the resistivity for any location in the domain of interest.}
 
@@
 \section{Data}
-
+\itodo{Zenodo DOI: Upload and link here.}
 The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.

### 2021-01-29 manuscript/Manuscript.tex

@@
   \centering
-  \caption{\itodo{Check all}Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
+  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
 \label{tbl:comp-layered}
@@
   \midrule
-  \custem & 24 &   118 &  97.8 & 1531824 \\ % dof: 3063648 / 2 (Real+Imag -> Complex)
-  \emg3d  &  1 &   116 &   0.4 & 4813216 \\
+  \custem & 48 &   232 & 244.1 & 5899578 \\ % dof: 11799156 / 2 (Real+Imag -> Complex)
+  \emg3d  &  1 &   123 &   0.4 & 4813216 \\
   \petgem & 24 &   252 & 151.7 & 2455868 \\
@@
   \centering
-  \caption{\itodo{Check all}Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}
+  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the block model.}
 \label{tbl:comp-block}
@@
   \midrule
-  \custem & 24 &   158 & 115.9 & 1646736 \\ % dof: 3293472 / 2  (Real+Imag -> Complex)
-  \emg3d  &  1 &   115 &   0.4 & 4813216 \\
+  \custem & 48 &   312 & 281.8 & 6014440 \\ % dof: 12,028,880 / 2  (Real+Imag -> Complex)
+  \emg3d  &  1 &   119 &   0.4 & 4813216 \\
   \petgem & 24 &   238 & 152.8 & 2455868 \\
@@
   \centering
-  \caption{\itodo{Check all}Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}
+  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the MR3D model.}
 \label{tbl:comp-marlim}
@@
   \custem & 64 &  872 & 230.1 & 1918106 \\ % dof: 3836212 / 2 (Real+Imag -> Complex)
-  \emg3d  &  1 & 1254 &   0.6 & 5998992 \\
+  \emg3d  &  1 & 1246 &   0.5 & 5998992 \\
   \petgem & 96 &  524 & 175.4 & 1918106 \\

### 2021-01-29 manuscript/Manuscript.tex
Updates from Overleaf

@@
 However, it is one of the few examples that can be verified with semi-analytical results, and is therefore still a valuable test.
-\itodo{Adjust everything here in section 3.1 for new figures}The results are shown in Figure~\ref{fig:results-layered}, where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values).
+The results are shown in Figure~\ref{fig:results-layered}, \replaced{in the left column the amplitudes and in the right column the phases}{where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values)}.
 The top row shows the actual, semi-analytically computed responses, for which we used \empymod\citep{GEO.17.Werthmuller}.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-layered}
+  \includegraphics[width=.9\linewidth]{figures/results-layered.png}
   \caption{\itodo{Adjust Figures 1 (Amplitude/Phase) and corresponding text in manuscript.} Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
@@
 
-There are a few noteworthy points:
-\begin{enumerate}
-  \item \itodo{adjust}The error of the real and imaginary responses are dominated by their zero-crossings, which blows up the error as is the nature of the relative error formula, it has no real-world implications.
-  \item It can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.
-  \item The errors become substantial towards zero offset, particularly for the results of the FV codes.
-These comparably significant errors could be significantly reduced by choosing a finer discretization around the source, at the cost of increased computation time.
-\itodo{Add a sentence re close offsets FV codes, Rune's comment (or above in point ii).}
-  \item~\\ \itodo{Adjust re changes of Raphael.} The error of the responses from the FE codes, on the hand, are relatively big at large offsets, particularly for the inline real responses.
+\added{The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes.
+The errors become substantial towards zero offset, particularly for the results of the FV codes.
+These comparably significant errors could be eliminated by choosing a finer discretization around the source, at the cost of increased computation time.
+Another possibility is to have a finer mesh for short offsets, and a coarser mesh for large offsets.}
+
+\deleted{There are a few noteworthy points:\\
+\phantom{\hspace{1em}}(i) The error of the real and imaginary responses are dominated by their zero-crossings, which blows up the error as is the nature of the relative error formula, it has no real-world implications.\\
+\phantom{\hspace{1em}}(ii) It can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.\\
+\phantom{\hspace{1em}}(iii) The errors become substantial towards zero offset, particularly for the results of the FV codes.
+These comparably significant errors could be significantly reduced by choosing a finer discretization around the source, at the cost of increased computation time.\\
+\phantom{\hspace{1em}}(iv) The error of the responses from the FE codes, on the hand, are relatively big at large offsets, particularly for the inline real responses.
 This has, again, its origin in the chosen discretization.
@@
 Therefore, the FE codes only extend this thin layer up to 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
-This approximation significantly reduces the problem size compared to considering the layered-earth geometry for the whole computational domain.
-\end{enumerate}
+This approximation significantly reduces the problem size compared to considering the layered-earth geometry for the whole computational domain.\\
+}
 
@@
 As the aim of this study is to focus on accuracy of the simulations and compare discretization approaches, we chose to use the same mesh as in the \emg3d simulation.
+\added{Although we only show the x-directed field in this comparison, the y-directed field yields a similar result with respect to the misfit.
+A different story in this scenario are the z-directed fields, which is not continues across the boundary on the seafloor.
+Having receivers close to such a non-continues boundary requires advanced interpolation routine} \citep[e.g., ][]{GJI.15.Shantsev, GP.11.Wirianto}\added{.
+This is no problem for the used FE codes within their basis functions, but the used FV codes do currently not have such routines implemented.
+}
 
@@
 
-\itodo{Explain/clarify re interpolation and re vertical fields in the manuscript.}
-
 \subsection{Block Model}
@@
   \centering
-  \includegraphics[width=\linewidth]{figures/model-block}
+  \includegraphics[width=\linewidth]{figures/model-block.png}
   \caption{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-block}
+  \includegraphics[width=.9\linewidth]{figures/results-block.png}
   \caption{\itodo{Adjust Figures 3 (\emg3d-\simpeg; \custem-\petgem; FV-FE) and corresponding text in manuscript.}Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/model-marlim}
+  \includegraphics[width=.9\linewidth]{figures/model-marlim.png}
   \caption{MR3D horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position and with major formations annotated.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim-responses}
+  \includegraphics[width=.9\linewidth]{figures/results-marlim-responses.png}
   \caption{MR3D comparison between our codes (grey lines) and the published data (coloured lines).
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_2published}
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_2published.png}
   \caption{\itodo{Improve figure.}Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours}
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours.png}
   \caption{\itodo{Improve figure.}Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_big}
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_big.png}
   \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_survey}
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_survey.png}
   \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_allmodels}
+  \includegraphics[width=.9\linewidth]{figures/results-marlim_allmodels.png}
   \caption{The resistivity model as obtained from the three different discretizations using rectilinear, octree, and tetrahedral meshes (3$\times$ vertical exaggeration).}

### 2021-01-30 manuscript/Manuscript.tex
Revision Draft; now to co-authors.

@@
 The top row shows the actual, semi-analytically computed responses, for which we used \empymod\citep{GEO.17.Werthmuller}.
-The second and the third row show the relative percentage error of the inline and the broadside receivers, respectively; note that for the 1D case the two broadside lines for $y=\pm3\,$km are identical.
+The second and the third row show the relative percentage error of the inline and the broadside receivers, respectively; note that for the 1D case the \added{x-directed electric fields for the} two broadside lines for $y=\pm3\,$km are identical.
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-layered.png}
-  \caption{\itodo{Adjust Figures 1 (Amplitude/Phase) and corresponding text in manuscript.} Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
+  \caption{Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
 The relative percentage error of the four 3D modellers are shown in the second and the third row for the inline and broadside responses, respectively.}
@@
 %
-
-\added{The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes.
-The errors become substantial towards zero offset, particularly for the results of the FV codes.
-These comparably significant errors could be eliminated by choosing a finer discretization around the source, at the cost of increased computation time.
-Another possibility is to have a finer mesh for short offsets, and a coarser mesh for large offsets.}
+\added{The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes.}
 
@@
 
+\itodo{Expand and adjust, wait for final result \simpeg (same mesh or different mesh?); some of this might be outdated.}
 Note that \emg3d and \simpeg used the same rectilinear mesh in this example.
@@
 \added{Although we only show the x-directed field in this comparison, the y-directed field yields a similar result with respect to the misfit.
-A different story in this scenario are the z-directed fields, which is not continues across the boundary on the seafloor.
+A different story in this scenario is the z-directed field, which is not continues across the boundary on the seafloor.
 Having receivers close to such a non-continues boundary requires advanced interpolation routine} \citep[e.g., ][]{GJI.15.Shantsev, GP.11.Wirianto}\added{.
 This is no problem for the used FE codes within their basis functions, but the used FV codes do currently not have such routines implemented.
-}
+The grid for the FV codes in this first example with a focus on precision is created in such a way that  the receivers are located on the corresponding nodes, so no interpolation is required to obtain the responses.}
 
@@
   \custem & 48 &   232 & 244.1 & 5899578 \\ % dof: 11799156 / 2 (Real+Imag -> Complex)
-  \emg3d  &  1 &   123 &   0.4 & 4813216 \\
+  \emg3d  &  1 &   216 &   0.5 & 6004144 \\
   \petgem & 24 &   252 & 151.7 & 2455868 \\
@@
 
-The block model is a derivation of the \emph{Dublin Test Model~1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
+The block model is a \replaced{CSEM adaption}{derivation} of the \added{MT} \emph{Dublin Test Model~1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
 We use the same layout of the blocks but adjust the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}.
@@
 \begin{equation}
-  \mr{NRMSD~(\%)} = 200\,\frac{|R_1 - R_2|}{|R_1| + |R_2|}\ ,
+  \mr{NRMSD~(\%)} = \replaced{100\,\frac{|R_1 - R_2|}{(|R_1| + |R_2|)/2}}
+                             {200\,\frac{|R_1 - R_2|}{|R_1| + |R_2|}}\ ,
   \label{eq:nrmsd}
@@
 The top row shows the result of \emg3d, as an example, and the bottom row shows the normalised differences between the absolute responses of the codes.
+\added{Note that for visual reasons we only show the normalised differences between the two FV codes, the two FE codes, and between \emg3d and \custem as an example of a cross-FV-FE comparison; the three other cross-method comparisons look quantitatively similar.}
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-block.png}
-  \caption{\itodo{Adjust Figures 3 (\emg3d-\simpeg; \custem-\petgem; FV-FE) and corresponding text in manuscript.}Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
   \label{fig:results-block}
@@
   \item The error levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
-  \item The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
+  \item \itodo{Adjust with final \simpeg results; conclusion does currently not hold.} The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
 The generally low normalised difference is because these codes use the same rectilinear mesh for modelling.
@@
 The corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
+\ymark{We could remove Table 4, as \#procs and \#doc are equal, and runtime and memory are almost identical for all codes in these two examples.
+What do you think?
+I would then replace it in the following way:
+«The corresponding required runtime and memory are \added{almost identical to the ones for the layered model} listed in Table~\replaced{\ref{tbl:comp-layered}}{\ref{tbl:comp-block}}.»}
 %
@@
   \custem & 48 &   312 & 281.8 & 6014440 \\ % dof: 12,028,880 / 2  (Real+Imag -> Complex)
-  \emg3d  &  1 &   119 &   0.4 & 4813216 \\
+  \emg3d  &  1 &   213 &   0.5 & 6004144 \\
   \petgem & 24 &   238 & 152.8 & 2455868 \\
@@
 
-The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of 25 by 75 by 5\,m.
-The model was upscaled for the computation to 515 by 563 by 310 cells, totalling to almost 90 million cells, where each cell has dimensions of 100 by 100 by 20\,m.
+The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of $25$\replaced{$\times$}{by}$75$\replaced{$\times$}{by}$5$\,m.
+The model was upscaled for the computation to $515$\replaced{$\times$}{by}$563$\replaced{$\times$}{by}$310$ cells, totalling to almost 90 million cells, where each cell has dimensions of $100$\replaced{$\times$}{by}$100$\replaced{$\times$}{by}$20$\,m.
 Both the full model and the upscaled computational model are released \replaced{as open source}{openly}.
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_2published.png}
-  \caption{\itodo{Improve figure.}Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
+  \caption{Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
 Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
@@
 Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
-The origin of this zigzag pattern is most likely the bathymetry.\itodo{Rune confirmed this; adjust} We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
+The origin of this zigzag pattern is most likely the bathymetry.
+We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
 This would explain why the codes using the tetrahedra mesh, which uses the bathymetry as well, does not show this feature.
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours.png}
-  \caption{\itodo{Improve figure.}Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
+  \caption{Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
 \custem and \petgem produce very similar results, which is due to the fact that they use the same mesh.
@@
 The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their normalised difference is generally below 0.03\,\%.
-The reason is simple: \custem and \petgem use the exactly same mesh for the computation of this example, the only difference is therefore the solver.
+\added{This is why they are shown as one case in Figure~\ref{fig:results-marlim_2published}.} The reason is simple: \custem and \petgem use the exactly same mesh for the computation of this example, the only difference is therefore the solver.
 This exemplifies that the biggest difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result.
@@
 The required runtime and memory to compute the shown MR3D responses for the four codes are listed in Table~\ref{tbl:comp-marlim}.
-The memory requirement varies from \itodo{Check at end again} $0.5-230\,$GiB, and the runtime from roughly 7\,min to 20\,min, where the codes were run on very different machines from servers to supercomputers (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel.
+The memory requirement varies from $0.5-230\,$GiB, and the runtime from roughly 7\,min to 20\,min, where the codes were run on very different machines from servers to supercomputers (see Table \ref{tbl:machines}) and use between 1 and 96 processes in parallel.
 %
@@
 
-\itodo{SOMEWHERE: Address NRMSD of MR3D results better; EMGS code elan uses bathymetry file; difference not error; very strong NRMSD; although visually identical.}
-
 \section{Discussion}
@@
 %% 1. Results: good agreement %%
-\itodo{Adjust/check text for amplitude/phase plots.}
 Overall, we observed an excellent match between the solutions.
-The amplitudes of the layered model have mostly a relative error of less than 1--2\,\%.
-Looking individually at the real or imaginary part results in much higher error values, but those are related to the zero crossings of the responses.
-The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
+The amplitudes \added{and phases} of the layered model have mostly a relative error of less than 1--2\,\%.
+\deleted{Looking individually at the real or imaginary part results in much higher error values, but those are related to the zero crossings of the responses.} The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
 For the large, complex MR3D model it is a bit different.
@@
 We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
-Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \citep{GJI.11.Schwarzbach,GJI.16.Key}.
+Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \added{\mbox{\citep{GJI.11.Schwarzbach,GJI.16.Key}}}.
 Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour.
 It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
-\itodo{Add comment: FV mesh creation much easier / faster; FE have then the advantage of better interpolation and easier possibility for adaptive grids.}
+\ymark{I added this last sentence. Let me know what you think, we can take it out again or adjust/modify it:}
+\added{Also, creating FV meshes is much simpler than creating FE meshes.
+However, having a FE mesh yields a lot o flexibility with regards to interpolation and refinement and adaption, making it more powerful once created.}
 

### 2021-02-08 manuscript/Manuscript.tex

@@
 Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes.
-MR3D would be an ideal scenario for unstructured meshes, as it is based on also published irregular lithological horizons.
+MR3D would be an ideal scenario for unstructured meshes, \added{as they are best suited to represent the irregular geometry provided by the} \deleted{as it is based on also published irregular} lithological horizons.
 Since the corresponding resistivity model, however, was defined on a regular grid, the FE codes were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.

### 2021-02-08 manuscript/Manuscript.tex
After draft cover letter.

--- 2021-01-30 manuscript/Manuscript.tex
@@
 
+\ymark{RR: here my thoughts to strengthen the manuscript:\\
+- Marlim clearly shows that more than two independent codes are needed to say which one might produce the most reliable results in case of greater differences (like 10\%).
+Our work shows that having the choice of multiple usable codes is the only chance to see how good our codes are for realistic scenarios.\\
+- even though our examples are not suited for FE, we discuss important pros and cons of the different methods, mainly related to the discretization, which helps other modellers to make the correct choice for their application.
+AS Dieter mentioned, I'm not aware of anything comparable for CSEM.\\
+- Not everything is perfect in our paper - actually, we must rather argue that this is a unique benefit of our work.
+Every modeller will experience the same issues if he wants to go for realistic geometries, but none talks about it.
+As we go open-source, we are forced to mention and explain every issue and problem in the application for common examples every reader can learn from our negative experiences.
+In the common practice, none talk about the issues and weaknesses of his code but says "I have a few \% errors for two examples so my code is super".\\
+- I think so far none mentioned the importance of a proper resistivity description in 3D, in the best case as function(x, y, z), which is an important general finding for designing any non-blocky model.}
+
 \listoftodos
@@
           & - Intel Cascade Lake, 8 vCPUs                     & \\
-          & - 355 GB RAM                                      & \\
+          & - 420 GB RAM                                      & \\
           & - Ubuntu 16.04                                    & \\
@@
 
-\itodo{Expand and adjust, wait for final result \simpeg (same mesh or different mesh?); some of this might be outdated.}
 Note that \emg3d and \simpeg used the same rectilinear mesh in this example.
@@
 
-The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
+\deleted{The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
+[Note to reviewers: we removed the runtime table of the layered model; there is not much difference in RAM/Runtime of the layered and block models.]
 %
-\begin{table*}
-\begin{minipage}{10cm}
-  \centering
-  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
-\label{tbl:comp-layered}
-  \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
-  \toprule
-  Code & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
-  \midrule
-  \custem & 48 &   232 & 244.1 & 5899578 \\ % dof: 11799156 / 2 (Real+Imag -> Complex)
-  \emg3d  &  1 &   216 &   0.5 & 6004144 \\
-  \petgem & 24 &   252 & 151.7 & 2455868 \\
-  \simpeg &  4 & 10089 & 280.3 & 4813216 \\ % nprocs: 1*4 threads
-  \bottomrule
-\end{tabular}
-\end{minipage}
-\end{table*}
+%\begin{table*}
+%\begin{minipage}{10cm}
+%  \centering
+%  \caption{Comparison of number of processes, runtime, and memory, as well as the degree of freedom of the discretization used by the different codes for the layered model.}
+% \label{tbl:comp-layered}
+%  \begin{tabular}{lrS[table-format=6.0]S[table-format=4.1]S[table-format=8.0]}
+%  \toprule
+%  Code & \#Procs & {Runtime (s)} & {Memory (GiB)}   & {\#dof} \\
+%  \midrule
+%  \custem & 48 &   232 & 244.1 & 5899578 \\ % dof: 11799156 / 2 (Real+Imag -> Complex)
+%  \emg3d  &  1 &   216 &   0.5 & 6004144 \\
+%  \petgem & 24 &   252 & 151.7 & 2455868 \\
+%  \simpeg &  4 & 37131 & 392.2 & 6004144 \\ % nprocs: 1x4 vCPUs
+%  \bottomrule
+%\end{tabular}
+%\end{minipage}
+%\end{table*}
 %
+}
 
@@
   \item The error levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
-  \item \itodo{Adjust with final \simpeg results; conclusion does currently not hold.} The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
+  \item The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
 The generally low normalised difference is because these codes use the same rectilinear mesh for modelling.
@@
 The corresponding required runtime and memory are listed in Table~\ref{tbl:comp-block}.
-\ymark{We could remove Table 4, as \#procs and \#doc are equal, and runtime and memory are almost identical for all codes in these two examples.
-What do you think?
-I would then replace it in the following way:
-«The corresponding required runtime and memory are \added{almost identical to the ones for the layered model} listed in Table~\replaced{\ref{tbl:comp-layered}}{\ref{tbl:comp-block}}.»}
 %
@@
   \petgem & 24 &   238 & 152.8 & 2455868 \\
-  \simpeg &  4 & 10295 & 280.4 & 4813216 \\ % nprocs: 1*4 threads
+  \simpeg &  4 & 20000 & 387.9 & 6004144 \\ % nprocs: 1x4 vCPUs
   \bottomrule
@@
   \petgem & 96 &  524 & 175.4 & 1918106 \\
-  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 threads
+  \simpeg &  4 &  422 &  12.8 &  720146 \\ % nprocs: 1*4 vCPU
   \bottomrule
@@
 Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes.
-MR3D would be an ideal scenario for unstructured meshes, as it is based on also published irregular lithological horizons.
+MR3D would be an ideal scenario for unstructured meshes, \replaced{as they are best suited to represent the irregular geometry provided by the}{as it is based on also published irregular} lithological horizons.
 Since the corresponding resistivity model, however, was defined on a regular grid, the FE codes were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
@@
 It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
-\ymark{I added this last sentence. Let me know what you think, we can take it out again or adjust/modify it:}
 \added{Also, creating FV meshes is much simpler than creating FE meshes.
-However, having a FE mesh yields a lot o flexibility with regards to interpolation and refinement and adaption, making it more powerful once created.}
+However, having a FE mesh yields a lot of flexibility with regards to interpolation and local refinement, making it more powerful once created.}
 

### 2021-02-11 manuscript/Manuscript.tex
Updates from Overleaf
Draft 1 for resubmission; to co-authors.

@@
    Raphael Rochlitz$^2$,           % orcid: 0000-0002-5132-916X
-   Octavio Castillo-Reyes$^3$ and % orcid: 0000-0003-4271-5015
+   Octavio Castillo-Reyes$^3$, and % orcid: 0000-0003-4271-5015
    Lindsey Heagy$^4$\\             % orcid: 0000-0002-1551-5926
@@
 Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) surveys used to be feasible only for large companies and research consortia.
-This has changed over the last few years, and today there exists a selection of different open-source codes.
-Using four different codes in the Python ecosystem, we perform simulations for increasingly complex models.
+This has changed over the last few years, and today there exists a selection of different open-source codes \added{available to everyone}.
+Using four different codes in the Python ecosystem, we perform simulations for increasingly complex models \added{in a shallow marine setting}.
 We first verify the computed fields with semi-analytical solutions for a simple layered model.
@@
 
-\clearpage
+% \deleted{old}: \texttt{\textbackslash deleted\{old\}}
+% \added{new}: \texttt{\textbackslash added\{new\}}
+% \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
 
-\subsection*{Correction commands}
-\begin{itemize}
-  \item \deleted{old}: \texttt{\textbackslash deleted\{old\}}
-  \item \added{new}: \texttt{\textbackslash added\{new\}}
-  \item \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
-\end{itemize}
+% Intro/Discussion: Take into account «To make this manuscript publishable within GJI, it requires some serious effort to focus more on the bigger picture and make this story more pronounced within your manuscript.»}
 
-\subsection*{Revise entire manuscript re:}
-\ymark{Intro/Discussion: Take into account «To make this manuscript publishable within GJI, it requires some serious effort to focus more on the bigger picture and make this story more pronounced within your manuscript.»}
-
-\ymark{RR: here my thoughts to strengthen the manuscript:\\
-- Marlim clearly shows that more than two independent codes are needed to say which one might produce the most reliable results in case of greater differences (like 10\%).
+% RR: here my thoughts to strengthen the manuscript:\\
+% - Marlim clearly shows that more than two independent codes are needed to say which one might produce the most reliable results in case of greater differences (like 10\%).
 Our work shows that having the choice of multiple usable codes is the only chance to see how good our codes are for realistic scenarios.\\
-- even though our examples are not suited for FE, we discuss important pros and cons of the different methods, mainly related to the discretization, which helps other modellers to make the correct choice for their application.
+% - even though our examples are not suited for FE, we discuss important pros and cons of the different methods, mainly related to the discretization, which helps other modellers to make the correct choice for their application.
 AS Dieter mentioned, I'm not aware of anything comparable for CSEM.\\
-- Not everything is perfect in our paper - actually, we must rather argue that this is a unique benefit of our work.
+% - Not everything is perfect in our paper - actually, we must rather argue that this is a unique benefit of our work.
 Every modeller will experience the same issues if he wants to go for realistic geometries, but none talks about it.
@@
 In the common practice, none talk about the issues and weaknesses of his code but says "I have a few \% errors for two examples so my code is super".\\
-- I think so far none mentioned the importance of a proper resistivity description in 3D, in the best case as function(x, y, z), which is an important general finding for designing any non-blocky model.}
-
-\listoftodos
-
-\clearpage
+% - I think so far none mentioned the importance of a proper resistivity description in 3D, in the best case as function(x, y, z), which is an important general finding for designing any non-blocky model.}
 
@@
 We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FV) and different mesh types (unstructured tetrahedra, rectilinear, octree) in different scenarios.
-The first model is an anisotropic\added{,} layered model, which can be compared to semi-analytical solutions.
+The first model is an anisotropic\added{,} layered model, which can be \replaced{verified with}{compared to} semi-analytical solutions.
 The layered model also serves as background model for the second validation, where we add three resistive blocks into the subsurface.
 The final comparison is based on the realistic, anisotropic marine model MR3D.
-It is a\deleted{n open} resistivity model \replaced{that is openly released, together}{which comes} with computed CSEM responses.
+It is a\replaced{ large-scale}{n open} resistivity model \replaced{that is openly released, together}{which comes} with computed CSEM responses.
 
@@
 
-A layered model fails to show the strength of 3D modellers, and in reality one would not choose a 3D code to compute responses for a layered model.
-However, it is one of the few examples that can be verified with semi-analytical results, and is therefore still a valuable test.
+A layered model fails to show the strength of 3D modellers \added{in general and FE codes in particular}, and in reality one would not choose a 3D code to compute responses for \replaced{such a problem}{a layered model}.
+However, it is one of the few examples that can be verified with semi-analytical results, and \added{it} is therefore \replaced{an important first}{still a valuable} test.
 The results are shown in Figure~\ref{fig:results-layered}, \replaced{in the left column the amplitudes and in the right column the phases}{where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values)}.
@@
 %
-\added{The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes.}
+\added{The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes associated to amplitudes having a dip towards zero.
+The increased errors towards the location of the 200\,m long source are related to the gridding, and finer discretizations (resulting in longer runtime and higher memory consumption) would reduce these errors.}
 
@@
 Note that \emg3d and \simpeg used the same rectilinear mesh in this example.
-The use of an octree mesh in \simpeg could greatly reduce the size of the mesh and resultant computation time, but at the cost of accuracy, which is reduced when averaging over layer interfaces to coarsen cells and because of the factor-of-two expansion rate of coarsened cells.
+The use of an octree mesh in \simpeg could greatly reduce the size of the mesh and resultant computation time, but at the cost of accuracy, which is reduced when averaging over layer interfaces to coarsen cells and because of the factor-of-two expansion rate of coarsened cells\added{ in an octree mesh}.
 As the aim of this study is to focus on accuracy of the simulations and compare discretization approaches, we chose to use the same mesh as in the \emg3d simulation.
@@
 \deleted{The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
-[Note to reviewers: we removed the runtime table of the layered model; there is not much difference in RAM/Runtime of the layered and block models.]
+[Note to reviewers: we removed the runtime table of the layered model; there is not much difference in RAM/Runtime of the layered and block models, and we considered it now redundant.]
 %
@@
 %  \petgem & 24 &   252 & 151.7 & 2455868 \\
-%  \simpeg &  4 & 37131 & 392.2 & 6004144 \\ % nprocs: 1x4 vCPUs
+%  \simpeg &  4 & 23002 & 389.5 & 6004144 \\ % nprocs: 1x4 vCPUs / 400 %
 %  \bottomrule
@@
 Additionally, we add our \emph{Layered Model} as a VTI background.
-The three resistive blocks have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
+The three resistive blocks have resistivities of \deleted{$\rho=$}$10\,\ohmm$ (shallow beam perpendicular to survey lines), \deleted{$\rho=$}$100\,\ohmm$ (thin plate, South-East), and \deleted{$\rho=$}$500\,\ohmm$ (cube, North-West).
 %
@@
   \includegraphics[width=.9\linewidth]{figures/results-block.png}
-  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the \replaced{amplitudes}{absolute responses $|E_x|$} of the different codes are shown in the bottom row.}
   \label{fig:results-block}
@@
 \begin{enumerate}
-  \item The error levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
+  \item The \replaced{misfit}{error} levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
   \item The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
@@
 The increasing normalised difference towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition in this example.
-  \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
-  \item The agreement within the same differential equation method (FE or FV) is better than across methods.
+\added{This difference from the boundary condition can also be seen in the relative error of the layered model in Figure~\ref{fig:results-layered}.}
+  \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher \replaced{misfits over the anomalous blocks}{errors on right side and now unsymmetrical error distribution}).
+  \item The agreement within the same differential equation method (FE or FV) is \added{mostly} better than across methods.
 \end{enumerate}
@@
   \petgem & 24 &   238 & 152.8 & 2455868 \\
-  \simpeg &  4 & 20000 & 387.9 & 6004144 \\ % nprocs: 1x4 vCPUs
+  \simpeg &  4 & 20000 & 387.9 & 6004144 \\ % nprocs: 1x4 vCPUs / 400 %
   \bottomrule
@@
 \begin{enumerate}
-  \item There are some noticeable differences for positive offsets of the broadside $E_y$ and $E_z$ components, which are likely related to the bathymetry.
+  \item[(1)] There are some noticeable differences for positive offsets of the broadside $E_y$ and $E_z$ components, which are likely related to the bathymetry.
 The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not know in detail what it does internally.
 See the discussion around Figure~\ref{fig:results-marlim_2published}.
-  \item The three highest frequencies become noisy at large offsets for all of our codes (well below any real-world noise level).
+  \item[(2)] The three highest frequencies \added{of the $E_z$ fields} become noisy at large offsets for all of our codes (well below any real-world noise level).
 The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
 This explains their smooth behaviour, without saying anything about their accuracy.
-  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
+  \item[(3)] The responses for the $E_y$ component of the inline acquisition line do not agree at all.
 In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here comes from 3D effects.
@@
 
-It is important to note that the published results nor any of our results is the \emph{truth}, but the closer they agree with each other the more certain we can be of the outcomes.
-Figure~\ref{fig:results-marlim_2published} shows the normalised differences between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
+It is important to note that \added{not} the published results nor any of our results is the \emph{truth}, but the closer they agree with each other the more certain we can be of the outcomes.
+\added{This emphasises the importance of comparing 3D results and one of our main objectives, as there is no other way to check the results of 3D codes for complex models.}  Figure~\ref{fig:results-marlim_2published} shows the normalised differences between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
 %
@@
   \caption{Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
-Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
+Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.
+\added{The results of the two FE codes are almost identical, see Figure~\ref{fig:results-marlim_2ours}, and are therefore combined here.}}
   \label{fig:results-marlim_2published}
@@
 The structured meshes have in some cases a smaller normalised difference, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in other cases the unstructured tetrahedral meshes, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
-Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
-The origin of this zigzag pattern is most likely the bathymetry.
-We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
-This would explain why the codes using the tetrahedra mesh, which uses the bathymetry as well, does not show this feature.
+Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (\replaced{1}{3}) in Figure~\ref{fig:model-marlim}.
+The origin of this zigzag pattern is most likely the bathymetry\replaced{, as}{.
+We suspect that} the code of the published data \deleted{did probably} use\added{s} the bathymetry information in addition to the resistivity cube \added{(Mittet, pers.
+com.)}.
+This \deleted{would} explain\added{s} why the codes using the tetrahedra mesh, which use\deleted{s} the bathymetry as well, do\deleted{es} not show this feature.
 
@@
 The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.
+\added{Also visible is that there is more energy close to the boundary in the tetrahedral mesh, due to the smaller computational domain with corresponding reflections.
+However, this seems not to have influenced the responses at the receiver locations, as the misfit between the FE and FV codes does not increase particularly for receivers with larger offsets.}
 
@@
   \includegraphics[width=.9\linewidth]{figures/results-marlim_survey.png}
-  \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
+  \caption{Meshes and broadside $E_x$ and $E_y$ fields \added{of the survey domain} in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
   \label{fig:results-marlim_survey}
@@
 Though we may be able to confirm the accuracy of codes in some simple scenarios, validating the performance of 3D CSEM codes for complex problems is only possible by cross-validating multiple solutions.
-This is the core motivation for this study.
+This\replaced{, plus the necessity for more reproducible modelling results, are}{ is} the core motivation\added{s} for this study.
 
@@
 The spectrum of geophysical EM methods is much wider than marine CSEM.} We hope to see in the future \added{more open-source models with accompanying data and} similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
-\added{An ideal realistic model should be defined as a function resistivity(x, y, z) which returns the resistivity for any location in the domain of interest.}
+\added{An ideal realistic model should be defined as a function \texttt{resistivity(x, y, z)} which returns the resistivity for any location in the domain of interest.}
+
+\added{It was a fruitful path to get four different CSEM codes to work together, and it included a steep learning curve for all involved parties.
+Our comparison and our results are far from perfect.
+The chosen models favour regular grids, and the chosen surveys favour iterative solvers.
+We only consider one particular CSEM case, the shallow marine setting looking for a resistor.
+Our comparison probably raised more questions regarding the accuracy of 3D CSEM modelling than answered.
+We consider this as an important, initial step which we believe yields already many insights to the reader.
+We have shown similarities and differences in FV and FE codes.
+And our results show that ideally the CSEM responses of a complex model should be computed with various codes, as there is not a single code that will provide very accurate results.
+Focusing on reproducibility and open-source forced us to show the misfit between the codes brutally honest, there is no hiding.
+We think this should be done more often.
+We do not claim that our codes are superior to other codes in any way.
+It is the current status of our codes, and we hope that we can build on this and that many similar comparisons will follow.}
 
@@
 The third example is Marlim R3D, a realistic, complex, marine resistivity model.
-The model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
-In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization.
+The \added{MR3D} model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
+In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization\added{ and handling of the bathymetry}.
 The required runtime and memory consumption is primarily controlled by the used solver.
@@
 \section{Data}
-\itodo{Zenodo DOI: Upload and link here.}
-The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
-For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}.
+The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (\replaced{\href{https://doi.org/10.5281/zenodo.4535603}{10.5281/zenodo.4535603}}{DOI})\deleted{ \emph{with the final submission}.
+For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}}.
 
@@
 The work of D.W.
-was conducted within the Gitaro.JIM project funded through MarTERA, a \emph{European Union's Horizon 2020} research and innovation programme, grant agreement N$^\circ$~728053; \href{https://www.martera.eu}{martera.eu}.
+was conducted within the Gitaro.JIM project funded through MarTERA, a \emph{European Union's Horizon 2020} research and innovation programme, grant agreement N$^\circ$~728053\deleted{; \href{https://www.martera.eu}{martera.eu}}.
 

### 2021-02-11 model-marlim/loadmarlim.py
Update creation scripts

@@ -58,8 +58,8 @@ def extract_model(model='orig'):
         txt += f"{s}- Vertical_Resistivity.sgy\n"
         txt += f"{s}from https://doi.org/10.5281/zenodo.400233\n\n"
         txt += f"{s}For model='comp' you need\n"
-        txt += f"{s}- novo_mrl3d_H_Z_meters.segy\n"
-        txt += f"{s}- novo_mrl3d_Zmeters.segy\n"
+        txt += f"{s}- Mrl3d_Rh_20metersmesh.segy\n"
+        txt += f"{s}- Mrl3d_Rv_20metersmesh.segy\n"
         txt += f"{s}from https://doi.org/10.5281/zenodo.3748492\n"
         print(txt)
         return None, None

### 2021-02-15 manuscript/Manuscript.tex
Last change from Overleaf for Revision 1.

@@
 Finally we compare the responses of a real world model with results from the industry.
-These validations show that the open-source codes are able to compute comparable CSEM responses for challenging, large-scale models.
-Our comparison includes finite-element and finite-volume codes using structured rectilinear and octree meshes as well as unstructured tetrahedral meshes.
+\replaced{On the one hand, t}{T}hese validations show that the open-source codes are able to compute comparable CSEM responses for challenging, large-scale models.
+\added{On the other hand, they show many general and method-dependent problems that need to be faced for obtaining accurate results.} Our comparison includes finite-element and finite-volume codes using structured rectilinear and octree meshes as well as unstructured tetrahedral meshes.
 Accurate responses can be obtained independently of the chosen method and the chosen mesh type.
@@
 If different discretizations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
-\cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of MT forward and inversion codes, but we are not aware of any comparable comparison study or benchmark suite for CSEM data.
+\added{This is the principal motivation of our study, together with the necessity for more reproducible models and modelling results in the realm of 3D CSEM computations.} \cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of MT forward and inversion codes, but we are not aware of any comparable comparison study or benchmark suite for CSEM data.
 
@@
 Recent developments added functionalities such that \emg3d can be used directly as a more general EM modeller too.
-It features now \replaced{besides arbitrarily rotated electric sources and receivers also routines for magnetic sources and receivers, to model time-domain responses, and to obtain the gradient of the misfit function which can be used by inversion algorithms}{routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses}.
+\replaced{In addition to functionality for modelling arbitrarily rotated electric sources and receivers, it also can simulate magnetic sources and receivers as well as model time-domain responses.
+It further has routines for obtaining the gradient of the misfit function which can be used by inversion algorithms.}{It features now routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses}.
 For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem.
@@
 A different story in this scenario is the z-directed field, which is not continues across the boundary on the seafloor.
-Having receivers close to such a non-continues boundary requires advanced interpolation routine} \citep[e.g., ][]{GJI.15.Shantsev, GP.11.Wirianto}\added{.
-This is no problem for the used FE codes within their basis functions, but the used FV codes do currently not have such routines implemented.
+Having receivers close to such a non-continues boundary requires advanced interpolation routines} \citep[e.g., ][]{GJI.15.Shantsev, GP.11.Wirianto}\added{.
+The FE codes handle this problem automatically with the used basis functions, but the used FV codes do currently not have such routines implemented.
 The grid for the FV codes in this first example with a focus on precision is created in such a way that the receivers are located on the corresponding nodes, so no interpolation is required to obtain the responses.}
@@
 
-It is important to note that \added{not} the published results nor any of our results is the \emph{truth}, but the closer they agree with each other the more certain we can be of the outcomes.
+It is important to note that \replaced{there is no \emph{true solution};}{the published results nor any of our results is the \emph{truth},} but the closer \replaced{that the previously published results and the results obtained from the four codes run here agree, the more confident}{they agree with each other the more certain} we can be of the outcomes.
 \added{This emphasises the importance of comparing 3D results and one of our main objectives, as there is no other way to check the results of 3D codes for complex models.}  Figure~\ref{fig:results-marlim_2published} shows the normalised differences between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
@@
 The origin of this zigzag pattern is most likely the bathymetry\replaced{, as}{.
-We suspect that} the code of the published data \deleted{did probably} use\added{s} the bathymetry information in addition to the resistivity cube \added{(Mittet, pers.
-com.)}.
+We suspect that} the code of the published data \deleted{did probably} use\added{s} the bathymetry information in addition to the resistivity cube.
 This \deleted{would} explain\added{s} why the codes using the tetrahedra mesh, which use\deleted{s} the bathymetry as well, do\deleted{es} not show this feature.
@@
 We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
-Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \added{\mbox{\citep{GJI.11.Schwarzbach,GJI.16.Key}}}.
+Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \added{\mbox{\citep{GJI.11.Schwarzbach,GJI.16.Key,GJI.19.CastilloReyes}}}.
 Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour.
@@
 The shown examples consider the geophysical problem of marine CSEM with resistive bodies in the frequency domain.
-\added{Marlim R3D is a rare example of an open-source resistivity model that also comes with CSEM data.
+\added{Marlim R3D is a rare example of an open-source resistivity model that also comes with simulated CSEM data.
 The spectrum of geophysical EM methods is much wider than marine CSEM.} We hope to see in the future \added{more open-source models with accompanying data and} similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
-\added{An ideal realistic model should be defined as a function \texttt{resistivity(x, y, z)} which returns the resistivity for any location in the domain of interest.}
+\added{An ideal realistic model should be defined as a function \texttt{resistivity(x, y, z)} which returns the resistivity for any location in the domain of interest, preferably with the horizons of the major formations.
+This would allow any meshing strategy to extract its optimal resistivity model.}
 
@@
 We only consider one particular CSEM case, the shallow marine setting looking for a resistor.
-Our comparison probably raised more questions regarding the accuracy of 3D CSEM modelling than answered.
+Our comparison raised probably more questions regarding the accuracy of 3D CSEM modelling than it answered.
 We consider this as an important, initial step which we believe yields already many insights to the reader.
-We have shown similarities and differences in FV and FE codes.
-And our results show that ideally the CSEM responses of a complex model should be computed with various codes, as there is not a single code that will provide very accurate results.
-Focusing on reproducibility and open-source forced us to show the misfit between the codes brutally honest, there is no hiding.
+We have shown similarities and differences in FV and FE codes and our results show that ideally the CSEM responses of a complex model should be computed with various codes, as there is not a single code that will provide very accurate results.
+Focusing on reproducibility and open-source software and data forced us to show the misfit between the codes brutally honest, there is no hiding.
 We think this should be done more often.
 We do not claim that our codes are superior to other codes in any way.
-It is the current status of our codes, and we hope that we can build on this and that many similar comparisons will follow.}
+It is our codes' current status, and we hope that we can build on this and that many similar comparisons will follow.}
 
@@
 We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
+\added{We would further like to thank the editor Ute Weckmann and assistant editor Fern Story as well as the reviewers Colin Farquharson and Rune Mittet for many helpful comments, which improved this manuscript considerably.}
 

### 2021-02-15 manuscript/Manuscript.tex
Revision I

--- 2021-02-08 manuscript/Manuscript.tex
@@
 \usepackage{ifthen}
-\usepackage[addedmarkup=bf]{changes}
+% \usepackage[addedmarkup=bf]{changes}
 % \usepackage[final]{changes}
@@
 % Change default colour of «changes» package
-\definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
-\definecolor{mygreen}{rgb}{0, .5, 0}
-\setaddedmarkup{\color{mygreen}{\uline{#1}}}
-\setdeletedmarkup{\color{alizarin}{\uwave{#1}}}
+% \definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
+% \definecolor{mygreen}{rgb}{0, .5, 0}
+% \setaddedmarkup{\color{mygreen}{\uline{#1}}}
+% \setdeletedmarkup{\color{alizarin}{\uwave{#1}}}
 
@@
 
-\title[3D CSEM Open-Source Landscape]{\replaced{Towards an o}{O}pen-source landscape for 3D CSEM modelling}
+\title[3D CSEM Open-Source Landscape]{Towards an open-source landscape for 3D CSEM modelling}
 
@@
 Large-scale modelling of three-dimensional controlled-source electromagnetic (CSEM) surveys used to be feasible only for large companies and research consortia.
-This has changed over the last few years, and today there exists a selection of different open-source codes.
-Using four different codes in the Python ecosystem, we perform simulations for increasingly complex models.
+This has changed over the last few years, and today there exists a selection of different open-source codes available to everyone.
+Using four different codes in the Python ecosystem, we perform simulations for increasingly complex models in a shallow marine setting.
 We first verify the computed fields with semi-analytical solutions for a simple layered model.
@@
 Finally we compare the responses of a real world model with results from the industry.
-These validations show that the open-source codes are able to compute comparable CSEM responses for challenging, large-scale models.
+On the one hand, these validations show that the open-source codes are able to compute comparable CSEM responses for challenging, large-scale models.
+On the other hand, they show many general and method-dependent problems that need to be faced for obtaining accurate results.
 Our comparison includes finite-element and finite-volume codes using structured rectilinear and octree meshes as well as unstructured tetrahedral meshes.
@@
 
-\clearpage
-
-\subsection*{Correction commands}
-\begin{itemize}
-  \item \deleted{old}: \texttt{\textbackslash deleted\{old\}}
-  \item \added{new}: \texttt{\textbackslash added\{new\}}
-  \item \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
-\end{itemize}
-
-\subsection*{Revise entire manuscript re:}
-\ymark{Intro/Discussion: Take into account «To make this manuscript publishable within GJI, it requires some serious effort to focus more on the bigger picture and make this story more pronounced within your manuscript.»}
-
-\ymark{RR: here my thoughts to strengthen the manuscript:\\
-- Marlim clearly shows that more than two independent codes are needed to say which one might produce the most reliable results in case of greater differences (like 10\%).
-Our work shows that having the choice of multiple usable codes is the only chance to see how good our codes are for realistic scenarios.\\
-- even though our examples are not suited for FE, we discuss important pros and cons of the different methods, mainly related to the discretization, which helps other modellers to make the correct choice for their application.
-AS Dieter mentioned, I'm not aware of anything comparable for CSEM.\\
-- Not everything is perfect in our paper - actually, we must rather argue that this is a unique benefit of our work.
-Every modeller will experience the same issues if he wants to go for realistic geometries, but none talks about it.
-As we go open-source, we are forced to mention and explain every issue and problem in the application for common examples every reader can learn from our negative experiences.
-In the common practice, none talk about the issues and weaknesses of his code but says "I have a few \% errors for two examples so my code is super".\\
-- I think so far none mentioned the importance of a proper resistivity description in 3D, in the best case as function(x, y, z), which is an important general finding for designing any non-blocky model.}
-
-\listoftodos
-
-\clearpage
+% \deleted{old}: \texttt{\textbackslash deleted\{old\}}
+% \added{new}: \texttt{\textbackslash added\{new\}}
+% \replaced{new}{old}: \texttt{\textbackslash replaced\{new\}\{old\}}
 
@@
 
-In the \replaced{1990s}{1990's}, computers became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
+In the 1990s, computers became sufficiently powerful that 3D modelling gained traction, and in 1995 the first International Symposium on Three-Dimensional Electromagnetics took place.
 This symposium resulted eventually in the book \emph{Three-Dimensional Electromagnetics} \citep{B.SEG.99.Oristaglio}, and another book by \cite{B.02.Wannamaker} with the exactly same title came out only three years later.
@@
 One reason why there are so many publications about this topic results from the variety of techniques to solve the systems of linear equations (SLE).
-They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, \replaced{iterative}{indirect} solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
+They can be distinguished between direct solvers \citep{GEO.09.Streich, GP.14.Chung, GEO.14.Jaysaval, GEO.15.Grayver, SEG.15.Oh, GJI.18.Wang}, iterative solvers \citep{GP.06.Mulder, GJI.15.Jaysaval}, or a combination of both, so-called hybrid solvers \citep{GEO.18.Liu}.
 The solvers often use preconditioners such as the multigrid method \citep{SIAM.02.Aruliah, GJI.16.Jaysaval}.
@@
 Many of the advancements made in the EM modelling community over the past decades have required that authors develop new implementations from scratch.
-These codes often provided the research group or company with a competitive advantage for a time, and thus the source codes were \replaced{normally}{often} kept internal.
+These codes often provided the research group or company with a competitive advantage for a time, and thus the source codes were normally kept internal.
 In some cases, executables have been made available for academic purposes upon request or to sponsoring consortium members.
@@
 If different discretizations and implementations of Maxwell's equations yield the same result, it gives confidence in their accuracy.
+This is the principal motivation of our study, together with the necessity for more reproducible models and modelling results in the realm of 3D CSEM computations.
 \cite{GJI.13.Miensopust} presents a review of two workshops dealing with the validation of MT forward and inversion codes, but we are not aware of any comparable comparison study or benchmark suite for CSEM data.
@@
 All four codes have their user-facing routines written in Python, and all of them make heavy use of \texttt{NumPy} \citep{NAT.20.Harris} and \texttt{SciPy} \citep{NM.20.Virtanen}.
-The four of them follow the open model of development, meaning that they come with both\deleted{,} an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
+The four of them follow the open model of development, meaning that they come with both an open-source license and an online-hosted version-control system with tracking possibilities (raising issues, filing pull requests).
 All developments comprise an extensive online documentation with many examples and have continuous integration to some degree.
@@
 An overview comparison of the codes is given in Table~\ref{tbl:codecomparison}.
-All four have in common that they solve Maxwell's equation in its differential form \deleted{(DE)} under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM.
-\added{For the numerical examples we show, all codes use the total-field formulation for the electric field.} The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
+All four have in common that they solve Maxwell's equation in its differential form under the quasi-static or diffusive approximation, hence neglecting displacement currents, which is a common approximation for the low frequency range usually applied in CSEM.
+For the numerical examples we show, all codes use the total-field formulation for the electric field.
+The machines on which the different codes were run are listed in Table~\ref{tbl:machines} together with the responsible operator.
 A few clarifying words on abbreviations and definitions: For the boundary conditions (BC) in the comparison table we use the abbreviations \emph{PEC} and \emph{PMC}, which stand for perfect electric conductor
@@
 , respectively.
-\added{PEC (PMC) implies that the tangential electric (magnetic) field vector components are zero at the boundary.} Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving.
+PEC (PMC) implies that the tangential electric (magnetic) field vector components are zero at the boundary.
+Another abbreviation used in the tables is \emph{dof} for degree of freedom, which is equivalent to the size of the SLE we are solving.
 Finally, we use \emph{runtime} as the wall time or elapsed real-world time from start to end of solving the SLE; pre- and post-processing (e.g., mesh generation) is not measured.
@@
 Even though changes of the conductivity are mainly of interest for CSEM modelling, the electric permittivity and magnetic permeability can be taken into account using the preferred electric field approach on Nédélec elements.
-Recently, induced polarisation parameters in frequency-domain \added{computations} and three methods for simulating time-domain responses were added to \custem.
+Recently, induced polarisation parameters in frequency-domain computations and three methods for simulating time-domain responses were added to \custem.
 The provided meshing tools are based on \texttt{TetGen} \citep{TOM.15.Si} and functionalities of \texttt{pyGIMLi} facilitate the generation of tetrahedral meshes including layered-earth geometries with topography or bathymetry and anomalous bodies which are allowed to be connected or to reach the surface.
@@
 Recent developments added functionalities such that \emg3d can be used directly as a more general EM modeller too.
-It features now \replaced{besides arbitrarily rotated electric sources and receivers also routines for magnetic sources and receivers, to model time-domain responses, and to obtain the gradient of the misfit function which can be used by inversion algorithms}{routines to obtain the magnetic field due to an electric source, to obtain the electric and magnetic fields due to a magnetic source, and to obtain time-domain responses}.
+In addition to functionality for modelling arbitrarily rotated electric sources and receivers, it also can simulate magnetic sources and receivers as well as model time-domain responses.
+It further has routines for obtaining the gradient of the misfit function which can be used by inversion algorithms.
 For the underlying discretization the Python package \discretize is used, which is part of the larger \simpeg ecosystem.
@@
 For the parallel forward modelling computations, a highly scalable MPI (message passing interface) domain decomposition allows reducing runtimes and the solution of large-scale modelling cases.
-This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters \replaced{such as}{(e.g.,} High-Performance Computing (HPC) architectures\deleted{)}.
+This strategy is capable of exploiting the parallelism offered by both modest multi-core computers and cutting-edge clusters such as High-Performance Computing (HPC) architectures.
 
@@
 \simpeg is a modular toolbox for simulations and gradient based inversions in geophysics.
-Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, EM (time and frequency \added{domain}, \replaced{controlled and}{as well as} natural sources), and fluid flow.
+Current functionality includes modelling and inversion capabilities for gravity, magnetics, direct current resistivity, induced polarisation, EM (time and frequency domain, controlled and natural sources), and fluid flow.
 It is a community driven project that aims to support researchers and practitioners by providing a flexible, extensible framework, and common interface to a variety of geophysical methods.
@@
 We computed the responses for three different models to validate that the four 3D CSEM codes yield the same electromagnetic responses and compare different solver types (FE, FV) and different mesh types (unstructured tetrahedra, rectilinear, octree) in different scenarios.
-The first model is an anisotropic\added{,} layered model, which can be compared to semi-analytical solutions.
+The first model is an anisotropic, layered model, which can be verified with semi-analytical solutions.
 The layered model also serves as background model for the second validation, where we add three resistive blocks into the subsurface.
 The final comparison is based on the realistic, anisotropic marine model MR3D.
-It is a\deleted{n open} resistivity model \replaced{that is openly released, together}{which comes} with computed CSEM responses.
+It is a large-scale resistivity model that is openly released, together with computed CSEM responses.
 
@@
 
-A layered model fails to show the strength of 3D modellers, and in reality one would not choose a 3D code to compute responses for a layered model.
-However, it is one of the few examples that can be verified with semi-analytical results, and is therefore still a valuable test.
-The results are shown in Figure~\ref{fig:results-layered}, \replaced{in the left column the amplitudes and in the right column the phases}{where the left, middle, and right columns are for the real part, imaginary part, and absolute value, respectively (dashed lines indicate negative values)}.
+A layered model fails to show the strength of 3D modellers in general and FE codes in particular, and in reality one would not choose a 3D code to compute responses for such a problem.
+However, it is one of the few examples that can be verified with semi-analytical results, and it is therefore an important first test.
+The results are shown in Figure~\ref{fig:results-layered}, in the left column the amplitudes and in the right column the phases.
 The top row shows the actual, semi-analytically computed responses, for which we used \empymod\citep{GEO.17.Werthmuller}.
-The second and the third row show the relative percentage error of the inline and the broadside receivers, respectively; note that for the 1D case the \added{x-directed electric fields for the} two broadside lines for $y=\pm3\,$km are identical.
+The second and the third row show the relative percentage error of the inline and the broadside receivers, respectively; note that for the 1D case the x-directed electric fields for the two broadside lines for $y=\pm3\,$km are identical.
 %
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-layered.png}
+  \includegraphics[width=.9\fwidth]{figures/results-layered.png}
   \caption{Results of the layered model: The semi-analytical inline and broadside responses are shown in the top row.
@@
 %
-\added{The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes.}
-
-\deleted{There are a few noteworthy points:\\
-\phantom{\hspace{1em}}(i) The error of the real and imaginary responses are dominated by their zero-crossings, which blows up the error as is the nature of the relative error formula, it has no real-world implications.\\
-\phantom{\hspace{1em}}(ii) It can be seen from the absolute-value errors that the misfit is generally in the order of 1\,\% or less.\\
-\phantom{\hspace{1em}}(iii) The errors become substantial towards zero offset, particularly for the results of the FV codes.
-These comparably significant errors could be significantly reduced by choosing a finer discretization around the source, at the cost of increased computation time.\\
-\phantom{\hspace{1em}}(iv) The error of the responses from the FE codes, on the hand, are relatively big at large offsets, particularly for the inline real responses.
-This has, again, its origin in the chosen discretization.
-The thin isotropic layer beneath the water requires many tetrahedra for a good-quality discretization.
-Therefore, the FE codes only extend this thin layer up to 30\,km from the origin, surrounded by a ten times larger halfspace-like boundary mesh with water conductivities assigned to the subsurface.
-This approximation significantly reduces the problem size compared to considering the layered-earth geometry for the whole computational domain.\\
-}
+The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes associated to amplitudes having a dip towards zero.
+The increased errors towards the location of the 200\,m long source are related to the gridding, and finer discretizations (resulting in longer runtime and higher memory consumption) would reduce these errors.
 
 Note that \emg3d and \simpeg used the same rectilinear mesh in this example.
-The use of an octree mesh in \simpeg could greatly reduce the size of the mesh and resultant computation time, but at the cost of accuracy, which is reduced when averaging over layer interfaces to coarsen cells and because of the factor-of-two expansion rate of coarsened cells.
+The use of an octree mesh in \simpeg could greatly reduce the size of the mesh and resultant computation time, but at the cost of accuracy, which is reduced when averaging over layer interfaces to coarsen cells and because of the factor-of-two expansion rate of coarsened cells in an octree mesh.
 As the aim of this study is to focus on accuracy of the simulations and compare discretization approaches, we chose to use the same mesh as in the \emg3d simulation.
-\added{Although we only show the x-directed field in this comparison, the y-directed field yields a similar result with respect to the misfit.
+Although we only show the x-directed field in this comparison, the y-directed field yields a similar result with respect to the misfit.
 A different story in this scenario is the z-directed field, which is not continues across the boundary on the seafloor.
-Having receivers close to such a non-continues boundary requires advanced interpolation routine} \citep[e.g., ][]{GJI.15.Shantsev, GP.11.Wirianto}\added{.
-This is no problem for the used FE codes within their basis functions, but the used FV codes do currently not have such routines implemented.
-The grid for the FV codes in this first example with a focus on precision is created in such a way that  the receivers are located on the corresponding nodes, so no interpolation is required to obtain the responses.}
+Having receivers close to such a non-continues boundary requires advanced interpolation routines \citep[e.g., ][]{GJI.15.Shantsev, GP.11.Wirianto}.
+The FE codes handle this problem automatically with the used basis functions, but the used FV codes do currently not have such routines implemented.
+The grid for the FV codes in this first example with a focus on precision is created in such a way that the receivers are located on the corresponding nodes, so no interpolation is required to obtain the responses.
 
-\deleted{The runtime and memory requirements for the layered model are listed in Table~\ref{tbl:comp-layered}.
-[Note to reviewers: we removed the runtime table of the layered model; there is not much difference in RAM/Runtime of the layered and block models.]
-%
 %\begin{table*}
@@
 %
-}
 
@@
 
-The block model is a \replaced{CSEM adaption}{derivation} of the \added{MT} \emph{Dublin Test Model~1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
+The block model is a CSEM adaption of the MT \emph{Dublin Test Model~1} from the first EM modelling workshop described by \cite{GJI.13.Miensopust}.
 We use the same layout of the blocks but adjust the dimensions and resistivities to a typical marine CSEM problem, as shown in Figure~\ref{fig:model-block}.
 Additionally, we add our \emph{Layered Model} as a VTI background.
-The three resistive blocks have resistivities of $\rho=10\,\ohmm$ (shallow beam perpendicular to survey lines), $\rho=100\,\ohmm$ (thin plate, South-East), and $\rho=500\,\ohmm$ (cube, North-West).
+The three resistive blocks have resistivities of $10\,\ohmm$ (shallow beam perpendicular to survey lines), $100\,\ohmm$ (thin plate, South-East), and $500\,\ohmm$ (cube, North-West).
 %
@@
   \centering
-  \includegraphics[width=\linewidth]{figures/model-block.png}
+  \includegraphics[width=\cwidth]{figures/model-block.png}
   \caption{Sketch of the block model, consisting of the layered background model with three resistive blocks, embedded in the thick background layer which has VTI with $\lambda=\sqrt{\rho_\textrm{v}/\rho_\textrm{h}}=\sqrt{2}$.}
@@
 \begin{equation}
-  \mr{NRMSD~(\%)} = \replaced{100\,\frac{|R_1 - R_2|}{(|R_1| + |R_2|)/2}}
-                             {200\,\frac{|R_1 - R_2|}{|R_1| + |R_2|}}\ ,
+  \mr{NRMSD~(\%)} = 100\,\frac{|R_1 - R_2|}{(|R_1| + |R_2|)/2} \ ,
   \label{eq:nrmsd}
@@
 The top row shows the result of \emg3d, as an example, and the bottom row shows the normalised differences between the absolute responses of the codes.
-\added{Note that for visual reasons we only show the normalised differences between the two FV codes, the two FE codes, and between \emg3d and \custem as an example of a cross-FV-FE comparison; the three other cross-method comparisons look quantitatively similar.}
+Note that for visual reasons we only show the normalised differences between the two FV codes, the two FE codes, and between \emg3d and \custem as an example of a cross-FV-FE comparison; the three other cross-method comparisons look quantitatively similar.
 %
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-block.png}
-  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the absolute responses $|E_x|$ of the different codes are shown in the bottom row.}
+  \includegraphics[width=.9\fwidth]{figures/results-block.png}
+  \caption{Results of the block model comparison: The responses of \emg3d, as an example, are shown in the top row, and the normalised differences (\%) between the amplitudes of the different codes are shown in the bottom row.}
   \label{fig:results-block}
@@
 \begin{enumerate}
-  \item The error levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
+  \item The misfit levels between the different codes are overall comparable; the normalised difference is generally below a few percent, increasing towards larger offsets.
   \item The normalised difference between the FV codes \emg3d and \simpeg is comparably low except at the boundary.
@@
 The increasing normalised difference towards the boundary is because \emg3d uses the PEC boundary condition, while \simpeg uses the PMC boundary condition in this example.
-  \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher errors on right side and now unsymmetrical error distribution).
-  \item The agreement within the same differential equation method (FE or FV) is better than across methods.
+This difference from the boundary condition can also be seen in the relative error of the layered model in Figure~\ref{fig:results-layered}.
+  \item The FE codes \custem and \petgem show similar boundary effects, but are influenced by the anomaly response (higher misfits over the anomalous blocks).
+  \item The agreement within the same differential equation method (FE or FV) is mostly better than across methods.
 \end{enumerate}
@@
 To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
-It is therefore, on \added{the} one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
+It is therefore, on the one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
 On the other hand it is impossible to reproduce it exactly, as it is a closed-source code and we cannot know exactly what was done internally.
@@
 
-The full MR3D model consists of $1022 \times 371 \times 1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of $25$\replaced{$\times$}{by}$75$\replaced{$\times$}{by}$5$\,m.
-The model was upscaled for the computation to $515$\replaced{$\times$}{by}$563$\replaced{$\times$}{by}$310$ cells, totalling to almost 90 million cells, where each cell has dimensions of $100$\replaced{$\times$}{by}$100$\replaced{$\times$}{by}$20$\,m.
-Both the full model and the upscaled computational model are released \replaced{as open source}{openly}.
+The full MR3D model consists of $1022\times371\times1229$ cells, totalling to almost 466 million cells, where each cell has dimensions of $25\times75\times5$\,m.
+The model was upscaled for the computation to $515\times563\times310$ cells, totalling to almost 90 million cells, where each cell has dimensions of $100\times100\times20$\,m.
+Both the full model and the upscaled computational model are released as open source.
 The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/model-marlim.png}
+  \includegraphics[width=.9\fwidth]{figures/model-marlim.png}
   \caption{MR3D horizontal resistivity model, $x$-$z$-slice through the receiver $y$-position and with major formations annotated.
@@
 
-The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside \added{(we only show the amplitude, as the conclusions for the phase are very similar)}.
+The responses for all six frequencies and all three electric components are shown in Figure~\ref{fig:results-marlim-responses}, both inline and broadside (we only show the amplitude, as the conclusions for the phase are very similar).
 The published responses are shown in colour with markers for the frequency, and the responses from our codes are shown beneath in grey colours in this overview plot.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim-responses.png}
+  \includegraphics[width=.9\fwidth]{figures/results-marlim-responses.png}
   \caption{MR3D comparison between our codes (grey lines) and the published data (coloured lines).
@@
 \begin{enumerate}
-  \item There are some noticeable differences for positive offsets of the broadside $E_y$ and $E_z$ components, which are likely related to the bathymetry.
+  \item[(1)] There are some noticeable differences for positive offsets of the broadside $E_y$ and $E_z$ components, which are likely related to the bathymetry.
 The reason why we cannot reproduce the published results exactly is that the code is not open-source, and we do not know in detail what it does internally.
 See the discussion around Figure~\ref{fig:results-marlim_2published}.
-  \item The three highest frequencies become noisy at large offsets for all of our codes (well below any real-world noise level).
+  \item[(2)] The three highest frequencies of the $E_z$ fields become noisy at large offsets for all of our codes (well below any real-world noise level).
 The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
 This explains their smooth behaviour, without saying anything about their accuracy.
-  \item The responses for the $E_y$ component of the inline acquisition line do not agree at all.
+  \item[(3)] The responses for the $E_y$ component of the inline acquisition line do not agree at all.
 In the 1D case, the inline $E_y$ component would be zero, and the only response we can measure here comes from 3D effects.
@@
 
-It is important to note that the published results nor any of our results is the \emph{truth}, but the closer they agree with each other the more certain we can be of the outcomes.
+It is important to note that there is no \emph{true solution}; but the closer that the previously published results and the results obtained from the four codes run here agree, the more confident we can be of the outcomes.
+This emphasises the importance of comparing 3D results and one of our main objectives, as there is no other way to check the results of 3D codes for complex models.
 Figure~\ref{fig:results-marlim_2published} shows the normalised differences between the published results and our codes for the three strongest components, the inline $E_x$ and the broadside $E_x$ and $E_y$ components, for three frequencies.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_2published.png}
+  \includegraphics[width=.9\fwidth]{figures/results-marlim_2published.png}
   \caption{Normalised differences for all four codes in comparison with the published data, for the inline $E_x$ field and the broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively.
-Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.}
+Shown are the three frequencies 0.125\,Hz, 0.5\,Hz, and 1.0\,Hz in the top, middle, and bottom row, respectively.
+The results of the two FE codes are almost identical, see Figure~\ref{fig:results-marlim_2ours}, and are therefore combined here.}
   \label{fig:results-marlim_2published}
@@
 The structured meshes have in some cases a smaller normalised difference, e.g., for negative offsets in the inline and broadside $E_x$ responses, and in other cases the unstructured tetrahedral meshes, e.g., for positive offsets for all broadside $E_y$ responses, and often they have a comparable NRMSD.
-Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (3) in Figure~\ref{fig:model-marlim}.
-The origin of this zigzag pattern is most likely the bathymetry.
-We suspect that the code of the published data did probably use the bathymetry information in addition to the resistivity cube.
-This would explain why the codes using the tetrahedra mesh, which uses the bathymetry as well, does not show this feature.
+Some normalised differences have an interesting step-pattern, which is more pronounced for the structured meshes than for the unstructured meshes; this is related to the annotated point (1) in Figure~\ref{fig:model-marlim}.
+The origin of this zigzag pattern is most likely the bathymetry, as the code of the published data uses the bathymetry information in addition to the resistivity cube.
+This explains why the codes using the tetrahedra mesh, which use the bathymetry as well, do not show this feature.
 
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_2ours.png}
+  \includegraphics[width=.9\fwidth]{figures/results-marlim_2ours.png}
   \caption{Normalised differences, just as in Figure~\ref{fig:results-marlim_2published}, but comparing some of the four codes with each other.
@@
 The most obvious result in that figure is that \custem and \petgem produce results that are almost identical, their normalised difference is generally below 0.03\,\%.
-\added{This is why they are shown as one case in Figure~\ref{fig:results-marlim_2published}.} The reason is simple: \custem and \petgem use the exactly same mesh for the computation of this example, the only difference is therefore the solver.
+This is why they are shown as one case in Figure~\ref{fig:results-marlim_2published}.
+The reason is simple: \custem and \petgem use the exactly same mesh for the computation of this example, the only difference is therefore the solver.
 This exemplifies that the biggest difference between different codes is the discretization; the solver is important when it comes to runtime and memory, but not for the accuracy of the result.
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_big.png}
+  \includegraphics[width=.9\fwidth]{figures/results-marlim_big.png}
   \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively.
-The shown dimensions \replaced{display}{shows} the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
+The shown dimensions display the entire computational domain for the tetrahedra mesh, whereas the entire rectilinear and octree meshes are bigger.}
   \label{fig:results-marlim_big}
@@
 %
-This figure is interesting for various \replaced{reasons}{points}, as the differences between the three meshes are clearly visible.
+This figure is interesting for various reasons, as the differences between the three meshes are clearly visible.
 Particularly the advantage of octree and tetrahedra to create large cells outside of the region of interest to push away the boundary can be seen, whereas a rectilinear grid, even though stretched, has to compute many cells far away of the zone of interest.
 The different boundary condition also play a part, where the top row used PEC, and the other two rows PMC.
+Also visible is that there is more energy close to the boundary in the tetrahedral mesh, due to the smaller computational domain with corresponding reflections.
+However, this seems not to have influenced the responses at the receiver locations, as the misfit between the FE and FV codes does not increase particularly for receivers with larger offsets.
 
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_survey.png}
-  \caption{Meshes and broadside $E_x$ and $E_y$ fields in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
+  \includegraphics[width=.9\fwidth]{figures/results-marlim_survey.png}
+  \caption{Meshes and broadside $E_x$ and $E_y$ fields of the survey domain in the left, middle, and right column, respectively, for the rectilinear, octree, and tetrahedral meshes in the top, middle, and bottom row, respectively (3$\times$ vertical exaggeration).}
   \label{fig:results-marlim_survey}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{figures/results-marlim_allmodels.png}
+  \includegraphics[width=.9\fwidth]{figures/results-marlim_allmodels.png}
   \caption{The resistivity model as obtained from the three different discretizations using rectilinear, octree, and tetrahedral meshes (3$\times$ vertical exaggeration).}
@@
 Though we may be able to confirm the accuracy of codes in some simple scenarios, validating the performance of 3D CSEM codes for complex problems is only possible by cross-validating multiple solutions.
-This is the core motivation for this study.
+This, plus the necessity for more reproducible modelling results, are the core motivations for this study.
 
@@
 Overall, we observed an excellent match between the solutions.
-The amplitudes \added{and phases} of the layered model have mostly a relative error of less than 1--2\,\%.
-\deleted{Looking individually at the real or imaginary part results in much higher error values, but those are related to the zero crossings of the responses.} The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
+The amplitudes and phases of the layered model have mostly a relative error of less than 1--2\,\%.
+The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
 For the large, complex MR3D model it is a bit different.
@@
 For the lowest frequency, 0.125\,Hz, the normalised difference is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
-For higher frequencies these numbers \replaced{increase}{rise} to the order of $\pm10\,$\%.
+For higher frequencies these numbers increase to the order of $\pm10\,$\%.
 The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategy.
@@
 Our first attempts were based on the originally published, fine MR3D model.
-This model is very detailed, but its extent is too small in \added{the} x- and y-directions for CSEM computations.
+This model is very detailed, but its extent is too small in the x- and y-directions for CSEM computations.
 In order to represent the fine-scale model on a mesh suitable for computation, each of our codes did its own upscaling and extrapolation.
@@
 The reason is that there are many ways how you can extrapolate a model, and without knowing the details of how MR3D represents the model on the computational mesh, we could not re-produce this step.
-We reached out to the authors of MR3D, and they kindly agreed to also publish\deleted{ed} the upscaled and extended computational model.
+We reached out to the authors of MR3D, and they kindly agreed to also publish the upscaled and extended computational model.
 It is only with this model that we were able to obtain comparable results.
@@
 Using, for instance, a dipping layer instead of three resistive cubes would turn it around and make the model more favourable for unstructured meshes.
-MR3D would be an ideal scenario for unstructured meshes, \replaced{as they are best suited to represent the irregular geometry provided by the}{as it is based on also published irregular} lithological horizons.
+MR3D would be an ideal scenario for unstructured meshes, as they are best suited to represent the irregular geometry provided by the lithological horizons.
 Since the corresponding resistivity model, however, was defined on a regular grid, the FE codes were forced to approximate the comparatively fine regular discretization by an unstructured one and interpolate the resistivity data for being able to apply the FE codes to this problem.
 We are completely aware about the ineptness of this re-approximation procedure, unless it served for the cross-validation purposes.
-Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \added{\mbox{\citep{GJI.11.Schwarzbach,GJI.16.Key}}}.
+Both cases show that automatic and adaptive meshing capabilities are needed, which will increase the flexibility of 3D CSEM modelling \citep{GJI.11.Schwarzbach,GJI.16.Key,GJI.19.CastilloReyes}.
 Such meshing codes should also take into account the physics of CSEM computation with its diffusive behaviour.
 It is also important to state that the unstructured mesh used for the MR3D model incorporates the entire domain and could be used for all source and receiver positions, whereas the rectilinear and octree meshes were designed for the shown receiver and corresponding source lines.
-\added{Also, creating FV meshes is much simpler than creating FE meshes.
-However, having a FE mesh yields a lot of flexibility with regards to interpolation and local refinement, making it more powerful once created.}
+Also, creating FV meshes is much simpler than creating FE meshes.
+However, having a FE mesh yields a lot of flexibility with regards to interpolation and local refinement, making it more powerful once created.
 
@@
 Independently of the solver there is a trade-off between high accuracy and runtime.
-\replaced{For}{As an} example, the octree mesh made for a very fast computation in the MR3D example thanks to the low number of dof, even though a direct solver was used.
+For example, the octree mesh made for a very fast computation in the MR3D example thanks to the low number of dof, even though a direct solver was used.
 But the octree mesh has, due to its 2:1 aspect ratio, some limitations on the accuracy, why it was not used in the first two examples.
@@
 The shown examples consider the geophysical problem of marine CSEM with resistive bodies in the frequency domain.
-\added{Marlim R3D is a rare example of an open-source resistivity model that also comes with CSEM data.
-The spectrum of geophysical EM methods is much wider than marine CSEM.} We hope to see in the future \added{more open-source models with accompanying data and} similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
-\added{An ideal realistic model should be defined as a function resistivity(x, y, z) which returns the resistivity for any location in the domain of interest.}
+Marlim R3D is a rare example of an open-source resistivity model that also comes with simulated CSEM data.
+The spectrum of geophysical EM methods is much wider than marine CSEM.
+We hope to see in the future more open-source models with accompanying data and similar comparisons for other cases, such as land CSEM with strong topography; airborne and mixed air-ground surveys; looking for conductive bodies; time domain; and models based on horizons instead of blocks which pose a challenge for structured grids and favour unstructured meshes.
+An ideal realistic model should be defined as a function \texttt{resistivity(x, y, z)} which returns the resistivity for any location in the domain of interest, preferably with the horizons of the major formations.
+This would allow any meshing strategy to extract its optimal resistivity model.
+
+It was a fruitful path to get four different CSEM codes to work together, and it included a steep learning curve for all involved parties.
+Our comparison and our results are far from perfect.
+The chosen models favour regular grids, and the chosen surveys favour iterative solvers.
+We only consider one particular CSEM case, the shallow marine setting looking for a resistor.
+Our comparison raised probably more questions regarding the accuracy of 3D CSEM modelling than it answered.
+We consider this as an important, initial step which we believe yields already many insights to the reader.
+We have shown similarities and differences in FV and FE codes and our results show that ideally the CSEM responses of a complex model should be computed with various codes, as there is not a single code that will provide very accurate results.
+Focusing on reproducibility and open-source software and data forced us to show the misfit between the codes brutally honest, there is no hiding.
+We think this should be done more often.
+We do not claim that our codes are superior to other codes in any way.
+It is our codes' current status, and we hope that we can build on this and that many similar comparisons will follow.
 
@@
 The third example is Marlim R3D, a realistic, complex, marine resistivity model.
-The model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
-In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization.
+The MR3D model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
+In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization and handling of the bathymetry.
 The required runtime and memory consumption is primarily controlled by the used solver.
@@
 \section{Data}
-\itodo{Zenodo DOI: Upload and link here.}
-The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (DOI) \emph{with the final submission}.
-For the review process we refer to the github page \href{https://github.com/swung-research/3d-csem-open-source-landscape}{github.com/swung-research/3d-csem-open-source-landscape}.
+The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (\href{https://doi.org/10.5281/zenodo.4535603}{10.5281/zenodo.4535603}).
 
@@
 We would also like to thank Paulo Menezes for the help and explanations with regards to the Marlim R3D model and corresponding CSEM data, and for making their actual computation model available under an open-source license.
+We would further like to thank the editor Ute Weckmann and assistant editor Fern Story as well as the reviewers Colin Farquharson and Rune Mittet for many helpful comments, which improved this manuscript considerably.
 
-The work of D.W.
-was conducted within the Gitaro.JIM project funded through MarTERA, a \emph{European Union's Horizon 2020} research and innovation programme, grant agreement N$^\circ$~728053; \href{https://www.martera.eu}{martera.eu}.
+The work of D.W. was conducted within the Gitaro.JIM project funded through MarTERA, a \emph{European Union's Horizon 2020} research and innovation programme, grant agreement N$^\circ$~728053.
 

### 2021-04-09 manuscript/Manuscript.tex
Fix paper to A4
Start revision II

@@
-\documentclass[extra, camera,%
+\documentclass[a4paper, extra, camera,%
     % onecolumn,   % comment for two columns
@@
 \usepackage{ifthen}
-% \usepackage[addedmarkup=bf]{changes}
+\usepackage[addedmarkup=bf]{changes}
 % \usepackage[final]{changes}
@@
 % Change default colour of «changes» package
-% \definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
-% \definecolor{mygreen}{rgb}{0, .5, 0}
-% \setaddedmarkup{\color{mygreen}{\uline{#1}}}
-% \setdeletedmarkup{\color{alizarin}{\uwave{#1}}}
+\definecolor{alizarin}{rgb}{0.82, 0.1, 0.26}
+\definecolor{mygreen}{rgb}{0, .5, 0}
+\setaddedmarkup{\color{mygreen}{\uline{#1}}}
+\setdeletedmarkup{\color{alizarin}{\uwave{#1}}}
 
@@
 % Remove once done
+% \usepackage[colorinlistoftodos]{todonotes}
 \newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
@@
 %
-The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes associated to amplitudes having a dip towards zero.
+The misfit is generally in the order of 1\,\% or less, the biggest misfits are \added{on the one hand} close to the source and \added{on the other hand} where there are rapid phase changes associated to amplitudes having a dip towards zero.
 The increased errors towards the location of the 200\,m long source are related to the gridding, and finer discretizations (resulting in longer runtime and higher memory consumption) would reduce these errors.
@@
 \cite{GEO.19.Correa} computed CSEM data for MR3D for six frequencies from 0.125\,Hz to 1.25\,Hz, and released them under the same CC license.
-To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
+To compute the data they used a \deleted{state-of-the-art} code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
 It is therefore, on the one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
@@
   \item[(2)] The three highest frequencies of the $E_z$ fields become noisy at large offsets for all of our codes (well below any real-world noise level).
-The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
-This explains their smooth behaviour, without saying anything about their accuracy.
+\deleted{The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
+This explains their smooth behaviour, without saying anything about their accuracy.}
   \item[(3)] The responses for the $E_y$ component of the inline acquisition line do not agree at all.
@@
 This explains why the codes using the tetrahedra mesh, which use the bathymetry as well, do not show this feature.
+\added{None of your codes has currently special interpolation routines implemented to take particular care of a source injection close to a dipping interface, such as the bathymetry, with discontinuities in the normal electrical field and the normal derivatives of both electric and magnetic tangential fields.
+This effect alone can potentially contribute several percents of NRMSD, as shown by \mbox{\cite{GJI.15.Shantsev}}.}
 
@@
 %% 1. Results: good agreement %%
-Overall, we observed an excellent match between the solutions.
-The amplitudes and phases of the layered model have mostly a relative error of less than 1--2\,\%.
-The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
-For the large, complex MR3D model it is a bit different.
-First it can be noted that the misfits are higher for higher frequencies.
-For the lowest frequency, 0.125\,Hz, the normalised difference is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
-For higher frequencies these numbers increase to the order of $\pm10\,$\%.
-The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategy.
-While one might argue that 5--10\,\% NRMSD is a lot, we argue that this is probably as good as it gets, given that the code with which the responses we compare to were computed is not open-source.
-This has been shown within the process of this study.
-Our first attempts were based on the originally published, fine MR3D model.
-This model is very detailed, but its extent is too small in the x- and y-directions for CSEM computations.
-In order to represent the fine-scale model on a mesh suitable for computation, each of our codes did its own upscaling and extrapolation.
-However, we were unsuccessful in our attempt to reproduce the published results.
-The reason is that there are many ways how you can extrapolate a model, and without knowing the details of how MR3D represents the model on the computational mesh, we could not re-produce this step.
-We reached out to the authors of MR3D, and they kindly agreed to also publish the upscaled and extended computational model.
-It is only with this model that we were able to obtain comparable results.
+Overall, we observed an excellent match between the solutions. The amplitudes
+and phases of the layered model have mostly a relative error of less than
+1--2\,\%. The cross-validation of the results for the block model yields a
+similar picture, with normalised differences within a few percents. For the
+large, complex MR3D model it is a bit different. First it can be noted that the
+misfits are higher for higher frequencies. For the lowest frequency, 0.125\,Hz,
+the normalised difference is a few percent for inline and broadside $E_x$
+components, and up to 10\,\% for the broadside $E_y$ component. For higher
+frequencies these numbers increase to the order of $\pm10\,$\%. The reason for
+the higher misfit for MR3D than for the layered or block model lies mostly in
+the discretization, boundary effects, and interpolation
+\replaced{strategies}{strategy} \added{for the model, the source distribution
+on the mesh, and to obtain the response at receiver locations}. While one might
+argue that 5--10\,\% NRMSD is a lot, we argue that this is probably as good as
+it gets, given that the code with which the responses we compare to were
+computed is not open-source. This has been shown within the process of this
+study. Our first attempts were based on the originally published, fine MR3D
+model. This model is very detailed, but its extent is too small in the x- and
+y-directions for CSEM computations. In order to represent the fine-scale model
+on a mesh suitable for computation, each of our codes did its own upscaling and
+extrapolation. However, we were unsuccessful in our attempt to reproduce the
+published results.  The reason is that there are many ways how you can
+extrapolate a model, and without knowing the details of how MR3D represents the
+model on the computational mesh, we could not re-produce this step. We reached
+out to the authors of MR3D, and they kindly agreed to also publish the upscaled
+and extended computational model. It is only with this model that we were able
+to obtain comparable results.
 
@@
 The MR3D model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
-In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization and handling of the bathymetry.
+In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization and handling of the bathymetry \added{with corresponding advanced interpolations of the electromagnetic fields}.
 The required runtime and memory consumption is primarily controlled by the used solver.

### 2021-04-09 manuscript/Manuscript.tex
Start revision II (#44)

@@
   \begin{tcolorbox}[colback=yellow!40!white]#1\end{tcolorbox}}
-
-% Remove once done
-% \usepackage[colorinlistoftodos]{todonotes}
-\newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
-% \newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
-\newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
-\newcommand{\dul}[1]{\underline{\underline{#1}}}
-\newcommand{\ul}[1]{\underline{#1}}
 \newcommand{\rmk}[1]{{\color{red}{#1}}}
@@
 This explains why the codes using the tetrahedra mesh, which use the bathymetry as well, do not show this feature.
-\added{None of your codes has currently special interpolation routines implemented to take particular care of a source injection close to a dipping interface, such as the bathymetry, with discontinuities in the normal electrical field and the normal derivatives of both electric and magnetic tangential fields.
+\added{None of our codes has currently special interpolation routines implemented to take particular care of a source injection close to a dipping interface, such as the bathymetry, with discontinuities in the normal electrical field and the normal derivatives of both electric and magnetic tangential fields.
 This effect alone can potentially contribute several percents of NRMSD, as shown by \mbox{\cite{GJI.15.Shantsev}}.}
@@
 %% 1. Results: good agreement %%
-Overall, we observed an excellent match between the solutions. The amplitudes
-and phases of the layered model have mostly a relative error of less than
-1--2\,\%. The cross-validation of the results for the block model yields a
-similar picture, with normalised differences within a few percents. For the
-large, complex MR3D model it is a bit different. First it can be noted that the
-misfits are higher for higher frequencies. For the lowest frequency, 0.125\,Hz,
-the normalised difference is a few percent for inline and broadside $E_x$
-components, and up to 10\,\% for the broadside $E_y$ component. For higher
-frequencies these numbers increase to the order of $\pm10\,$\%. The reason for
-the higher misfit for MR3D than for the layered or block model lies mostly in
-the discretization, boundary effects, and interpolation
-\replaced{strategies}{strategy} \added{for the model, the source distribution
-on the mesh, and to obtain the response at receiver locations}. While one might
-argue that 5--10\,\% NRMSD is a lot, we argue that this is probably as good as
-it gets, given that the code with which the responses we compare to were
-computed is not open-source. This has been shown within the process of this
-study. Our first attempts were based on the originally published, fine MR3D
-model. This model is very detailed, but its extent is too small in the x- and
-y-directions for CSEM computations. In order to represent the fine-scale model
-on a mesh suitable for computation, each of our codes did its own upscaling and
-extrapolation. However, we were unsuccessful in our attempt to reproduce the
-published results.  The reason is that there are many ways how you can
-extrapolate a model, and without knowing the details of how MR3D represents the
-model on the computational mesh, we could not re-produce this step. We reached
-out to the authors of MR3D, and they kindly agreed to also publish the upscaled
-and extended computational model. It is only with this model that we were able
-to obtain comparable results.
+Overall, we observed an excellent match between the solutions.
+The amplitudes and phases of the layered model have mostly a relative error of less than 1--2\,\%.
+The cross-validation of the results for the block model yields a similar picture, with normalised differences within a few percents.
+For the large, complex MR3D model it is a bit different.
+First it can be noted that the misfits are higher for higher frequencies.
+For the lowest frequency, 0.125\,Hz, the normalised difference is a few percent for inline and broadside $E_x$ components, and up to 10\,\% for the broadside $E_y$ component.
+For higher frequencies these numbers increase to the order of $\pm10\,$\%.
+The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation \replaced{strategies}{strategy} \added{for the model, the source distribution on the mesh, and to obtain the response at receiver locations}.
+While one might argue that 5--10\,\% NRMSD is a lot, we argue that this is probably as good as it gets, given that the code with which the responses we compare to were computed is not open-source.
+This has been shown within the process of this study.
+Our first attempts were based on the originally published, fine MR3D model.
+This model is very detailed, but its extent is too small in the x- and y-directions for CSEM computations.
+In order to represent the fine-scale model on a mesh suitable for computation, each of our codes did its own upscaling and extrapolation.
+However, we were unsuccessful in our attempt to reproduce the published results.
+The reason is that there are many ways how you can extrapolate a model, and without knowing the details of how MR3D represents the model on the computational mesh, we could not re-produce this step.
+We reached out to the authors of MR3D, and they kindly agreed to also publish the upscaled and extended computational model.
+It is only with this model that we were able to obtain comparable results.
 

### 2021-04-15 manuscript/Manuscript.tex
Revision II

--- 2021-02-15 manuscript/Manuscript.tex
@@
   \begin{tcolorbox}[colback=yellow!40!white]#1\end{tcolorbox}}
-
-% Remove once done
-\newcommand{\itodo}[1]{\todo[color=blue!40!white, inline]{\sffamily #1}}
-% \newcommand{\mtodo}[1]{\todo[inline]{\sffamily #1}}
-\newcommand{\etodo}[1]{\todo[color=blue!40!white]{#1}}
-\newcommand{\dul}[1]{\underline{\underline{#1}}}
-\newcommand{\ul}[1]{\underline{#1}}
 \newcommand{\rmk}[1]{{\color{red}{#1}}}
@@
 %
-The misfit is generally in the order of 1\,\% or less, the biggest misfits are close to the source and where there are rapid phase changes associated to amplitudes having a dip towards zero.
+The misfit is generally in the order of 1\,\% or less, the biggest misfits are on the one hand close to the source and on the other hand where there are rapid phase changes associated to amplitudes having a dip towards zero.
 The increased errors towards the location of the 200\,m long source are related to the gridding, and finer discretizations (resulting in longer runtime and higher memory consumption) would reduce these errors.
@@
 \cite{GEO.19.Correa} computed CSEM data for MR3D for six frequencies from 0.125\,Hz to 1.25\,Hz, and released them under the same CC license.
-To compute the data they used a state-of-the-art code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
+To compute the data they used a code from the industry \citep[][ \emph{SBLwiz} software from \emph{EMGS}]{GEO.07.Maao}.
 It is therefore, on the one hand, an ideal case to validate our open-source codes against, as it is a complex, realistic model and the data were computed by an industry-proofed code.
@@
   \item[(2)] The three highest frequencies of the $E_z$ fields become noisy at large offsets for all of our codes (well below any real-world noise level).
-The reason why the published responses are not noisy is probably because they were computed in the time domain, and transformed to the frequency domain.
-This explains their smooth behaviour, without saying anything about their accuracy.
   \item[(3)] The responses for the $E_y$ component of the inline acquisition line do not agree at all.
@@
 This explains why the codes using the tetrahedra mesh, which use the bathymetry as well, do not show this feature.
+None of our codes has currently special interpolation routines implemented to take particular care of a source injection close to a dipping interface, such as the bathymetry, with discontinuities in the normal electrical field and the normal derivatives of both electric and magnetic tangential fields.
+This effect alone can potentially contribute several percents of NRMSD, as shown by \mbox{\cite{GJI.15.Shantsev}}.
 
@@
 For higher frequencies these numbers increase to the order of $\pm10\,$\%.
-The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategy.
+The reason for the higher misfit for MR3D than for the layered or block model lies mostly in the discretization, boundary effects, and interpolation strategies for the model, the source distribution on the mesh, and to obtain the response at receiver locations.
 While one might argue that 5--10\,\% NRMSD is a lot, we argue that this is probably as good as it gets, given that the code with which the responses we compare to were computed is not open-source.
@@
 The MR3D model and corresponding CSEM responses are open-source, allowing an independent validation of our results with results from another (closed-source) code.
-In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization and handling of the bathymetry.
+In this scenario the normalised difference is in the order of 5--10\,\%, where the main source of error can be attributed to differences in discretization and handling of the bathymetry with corresponding advanced interpolations of the electromagnetic fields.
 The required runtime and memory consumption is primarily controlled by the used solver.

### 2021-06-08 manuscript/Manuscript.tex
Point Zenodo to newest version

@@
 \section{Data}
-The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (\href{https://doi.org/10.5281/zenodo.4535603}{10.5281/zenodo.4535603}).
+The resulting CSEM responses of the four codes for the three models, as well as all files to rerun the different models with the four codes and reproduce the shown results are available at Zenodo (\href{https://doi.org/10.5281/zenodo.4535602}{10.5281/zenodo.4535602}).
 

### 2021-07-05 manuscript/Manuscript.tex
Final edits

@@
 
-\date{Received 2021 MMMM DD; in original form 2020 October 23}
+\date{Accepted 2021 June 17. Received 2021 June 8; in original form 2020 October 23}
 \pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\volume{VVV}
-\pubyear{202Y}
+% \volume{VVV}
+\pubyear{2021}
 
@@
   Website & \href{https://custem.rtfd.io}{custem.rtfd.io}
-          & \href{https://emsig.github.io}{emsig.github.io}
+          & \href{https://emsig.xyz}{emsig.xyz}
           & \href{http://petgem.bsc.es}{petgem.bsc.es}
@@
 The model was upscaled for the computation to $515\times563\times310$ cells, totalling to almost 90 million cells, where each cell has dimensions of $100\times100\times20$\,m.
-Both the full model and the upscaled computational model are released as open source.
+Both the full model and the upscaled computational model are released openly.
 The published data set consists of a regular grid of receivers of 20 in eastern direction by 25 in northern direction, 500 receivers in total, with 1\,km spacing located on the irregular seafloor.
